### 2021-08-06 Main_code/3_Time_series_gen.Rmd
init

---
title: "Input time series generation for the WASA model"
author: "Paolo Colombo"
date: "3/5/2021"
output: html_document
---

# Libraries

```{r libraries}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

# Precipitation

## Upload precipitation data

```{r precipitation upload}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")

#FUNCEME dataset
input<-list.files(path="./Meteorological_stations_FUNCEME/precipitation_subset",full.names = T,recursive = TRUE)

prec_input<-list()
for(i in 1:length(input)){
  tryCatch(prec_input[[i]]<-read.table(input[i],header = FALSE,
                              sep = "",col.names = c("year","month","day","data"),
                              skip=6),
           error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
}
```

## Set up the main dataframe

Creation of the position vector (positions_prec) and the main dataframe containing all the data from the meteorological stations (main_dataframe_prec).

```{r precipitation dataframe}
#Positions vector
for(i in 1:length(input)){
  lines<-readLines(input[i],n = 6)
  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
  name<-unlist(strsplit(lines[2], ":"))[2]
  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
  p<-data.frame(ID,name,long,lat)
  if(i > 1) positions_prec<-rbind(positions_prec,p,make.row.names=FALSE)
  else positions_prec<-p
}
positions_prec$ID<-paste0("St",positions_prec$ID)

#Unified dataframe

start_y <- 1980
end_y <- 2020
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")

##Create a date column inside each station dataframe
for(i in 1:length(prec_input[])){
  d<-as.Date(paste0(prec_input[[i]]$year,"-",prec_input[[i]]$month,"-",prec_input[[i]]$day))
  prec_input[[i]]$date<-d
}

tic("Unified dataframe - Optimized")
main_dataframe_prec<-data.frame(date)
index<-matrix(NA,ncol = 2,nrow = 744)
j<-1

for(i in 1:length(prec_input[])){
  check<-prec_input[[i]][which(prec_input[[i]]$date %in% main_dataframe_prec$date),]
  if(dim(check)[1]!=0){
      #main_dataframe_prec$new<-rep(NA,nrow(main_dataframe_prec))
      new_v<-sistemadati(vettore = prec_input[[i]],lung = nrow(main_dataframe_prec),g = date)
      main_dataframe_prec$new<-new_v[,2]
      names(main_dataframe_prec)[names(main_dataframe_prec) == "new"]<-positions_prec$ID[i]
  }else{
      index[j,1]<-i
      index[j,2]<-positions_prec$ID[i]
      j<-j+1
  }
}
index_clean<-subset(index, (!is.na(index[,1])) & (!is.na(index[,2])))
toc()
#519.94 sec = 8.65 min
#818.79 sec

remove(index,j,new_v)
View(index_clean) #Stations with no observations

path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
write.table(main_dataframe_prec,paste0(path,"/main_dataframe_precipitation_3005.txt"),
            quote=FALSE,sep="\t",row.names = FALSE)

```

## Interpolation

```{r precipitation interpolation}
#Upload the main dataframe of precipitation data
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
# main_dataframe_prec<-read.table(paste0(path,"/main_dataframe_precipitation_opt_v2.txt"),
#                                 header = TRUE, sep="\t")

#Import of the subbasins shapefile
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/streamgauges"
subbasins<-readOGR(paste0(path,"/Subbasins_geomfix.shp"))

#Output dataframe creation
tic("Output generation - Precipitation - With function")
output_prec<-create_time_series(main_dataframe = main_dataframe_prec,
                                positions = positions_prec,
                                layer = subbasins,
                                dates = date)
toc()

#7335.77 sec = 2 h
#6608.21 sec
#With new create_time_series function
#
```

```{r check the interpolation procedure}
#Export the generated files to visualize them on QGIS
#Only useful while set upping the interpolation algorithm

shape<-data.frame(t(second),
                      positions_prec$long[which(positions_prec$ID %in% col)],
                      positions_prec$lat[which(positions_prec$ID %in% col)],
                      positions_prec$ID[which(positions_prec$ID %in% col)])
    names(shape)<-c("data","long","lat","ID")

coordinates(shape)<-c("long","lat")
proj4string(shape)<-CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
shape <- spTransform(shape, raster::crs(subbasins))
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/prove_shape"
#raster::shapefile(shape,paste0(path,"/stazioni_temp_conID.shp"))

try<-data_sub
coordinates(try)<-c("x","y")
coordinates(try)<-c("long","lat")
proj4string(try)<-CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
try <- spTransform(try, raster::crs(subbasins))
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/prove_shape"
#raster::shapefile(try,paste0(path,"/subbasins_con_prec_prova2.shp"),overwrite=TRUE)

#raster::shapefile(thiessen,paste0(path,"/thiessen_temp_new.shp"),overwrite=TRUE)

```

### Output dataframe creation and export

```{r precipitation output}
#Insert the date
year<-lubridate::year(main_dataframe_prec$date)
month<-lubridate::month(main_dataframe_prec$date)
month[which(month < 10)]<-paste0("0",month[which(month < 10)])
day<-lubridate::day(main_dataframe_prec$date)
day[which(day < 10)]<-paste0("0",day[which(day < 10)])

output_prec$date<-paste0(day,month,year)

#Insert the number of days
output_prec$`number of days`<-lubridate::yday(main_dataframe_prec$date)

#Round the values
output_exp<-output_prec
output_exp[,3:ncol(output_exp)]<-round(output_exp[,3:ncol(output_exp)], digits = 1)

#Export as an Input file for WASA
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"

my.write(output_exp,file=paste0(path,"/rain_daily_3005.dat"),
         header = "Daily average precipitation [mmd] for each subasin, ordered according Map-IDs/nDate No. of days Subasin-ID/n0 0 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36 37 38 39 40 41 42 43 44 45 46 47 48 49 50 51 52 53 54 55 56 57 58 59 60 61 62 63 64 65 66 67 68 69 70 71 72 73 74 75 76 77 78 79 80 81 82 83 84 85 86 87 88 89 90 91 92 93 94 95 96 97 98 99 100 101 102 103 104 105 106 107 108 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215",f = write.table,sepset = FALSE)

#Save it as it is for future use
write.table(output_prec,paste0(path,"/output_prec_save_3005.txt"),quote = FALSE,sep="\t",row.names = FALSE)
```

# Temperature

## Upload temperature data

Since FUNCEME stations present numerous days without temperature data, here INMET stations are also considered. This guarantees at least one observation for each year.

```{r temperature upload}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")

#FUNCEME and INMET dataset
input<-list.files(path="./Meteorological_stations_FUNCEME/t2m",full.names = T,recursive = TRUE)

temp_input<-list()
for(i in 1:length(input)){
  tryCatch(temp_input[[i]]<-read.table(input[i],header = FALSE,
                              sep = "",col.names = c("year","month","day","data"),
                              skip=6),
           error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
}
```

## Set up the main dataframe

```{r temperature dataframe}
#Positions vector
for(i in 1:length(input)){
  lines<-readLines(input[i],n = 6)
  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
  name<-unlist(strsplit(lines[2], ":"))[2]
  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
  p<-data.frame(ID,name,long,lat)
  if(i > 1) positions_temp<-rbind(positions_temp,p,make.row.names=FALSE)
  else positions_temp<-p
}
positions_temp$ID<-paste0("St",positions_temp$ID)

#Unified dataframe

start_y <- 1980
end_y <- 2020
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")

##Create a date column inside each station dataframe
for(i in 1:length(temp_input[])){
  d<-as.Date(paste0(temp_input[[i]]$year,"-",temp_input[[i]]$month,"-",temp_input[[i]]$day))
  temp_input[[i]]$date<-d
}

tic("Unified dataframe Temperature - Optimized")

main_dataframe_temp<-data.frame(date)
index<-matrix(NA,ncol = 2,nrow = 744)
j<-1

for(i in 1:length(temp_input[])){
  check<-temp_input[[i]][which(temp_input[[i]]$date %in% main_dataframe_temp$date),]
  if(dim(check)[1]!=0){
      #main_dataframe_temp$new<-rep(NA,nrow(main_dataframe_temp))
      new_v<-sistemadati(vettore = temp_input[[i]],lung = nrow(main_dataframe_temp),g = date)
      main_dataframe_temp$new<-new_v[,2]
      names(main_dataframe_temp)[names(main_dataframe_temp) == "new"]<-positions_temp$ID[i]
  }else{
      index[j,1]<-i
      index[j,2]<-positions_temp$ID[i]
      j<-j+1
  }
}
index_clean<-subset(index, (!is.na(index[,1])) & (!is.na(index[,2])))
toc() #154.5 sec = 2.575 min

remove(index,j,new_v)
View(index_clean)

# path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
# write.table(main_dataframe_temp,paste0(path,"/main_dataframe_temperature_3005.txt"),
#            quote=FALSE,sep="\t",row.names = FALSE)

```

## Interpolation

```{r temperature interpolation}
# Upload the main dataframe of temperature data
path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
main_dataframe_temp<-read.table(paste0(path,"/main_dataframe_temperature_3005.txt"),
                               header = TRUE, sep="\t")

#Import of the subbasins shapefile
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
subbasins<-readOGR(paste0(path,"/subbasins_cut_geomfix.shp"))

tic("Output generation - Temperature - With function")
output_temp<-create_time_series_Wmean(main_dataframe = main_dataframe_temp,
                                positions = positions_temp,
                                layer = subbasins)
toc()

#Various checks
length(sum(!is.na(main_dataframe_temp[which(lubridate::year(main_dataframe_temp$date)==1986),])))
length(main_dataframe_temp[which(is.na(lubridate::year(main_dataframe_temp$date)==1986)),])

#2610.95 sec = 43 min
#3017.68 sec = 50 min
#2716.2  sec = 45 min
#3682.45 sec
```

### Output dataframe creation and export

```{r temperature output}
#Insert the date
year<-lubridate::year(main_dataframe_temp$date)
month<-lubridate::month(main_dataframe_temp$date)
month[which(month < 10)]<-paste0("0",month[which(month < 10)])
day<-lubridate::day(main_dataframe_temp$date)
day[which(day < 10)]<-paste0("0",day[which(day < 10)])

output_temp$date<-paste0(day,month,year)

#Insert the number of days
output_temp$`number of days`<-lubridate::yday(main_dataframe_temp$date)

#Round the values
output_exp<-output_temp
output_exp[,3:ncol(output_exp)]<-round(output_exp[,3:ncol(output_exp)], digits = 1)

#Export as an Input file for WASA
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"

my.write(output_exp,file=paste0(path,"/temperature_3005.dat"),
         header = "Daily average temperature (in degree Celcius) for each subasin, ordered according to Map-IDs\nDate No. of days Subasin-ID\n0 0 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36 37 38 39 40 41 42 43 44 45 46 47 48 49 50 51 52 53 54 55 56 57 58 59 60 61 62 63 64 65 66 67 68 69 70 71 72 73 74 75 76 77 78 79 80 81 82 83 84 85 86 87 88 89 90 91 92 93 94 95 96 97 98 99 100 101 102 103 104 105 106 107 108 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215",f = write.table,sepset = FALSE)

#Save it as it is for future use
write.table(output_temp,paste0(path,"/output_temp_save_3005.txt"),quote = FALSE,sep="\t",row.names = FALSE)

```

# Humidity

## Upload humidity data

Both FUNCEME and INMET dataset are uploaded. Only the stations named "air_humidity" are considered, to avoid duplicated stations.

```{r humidity upload}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")

#FUNCEME and INMET dataset
input<-list.files(path="./Meteorological_stations_FUNCEME/humidity_subset",full.names = T,recursive = TRUE)

hum_input<-list()
for(i in 1:length(input)){
  tryCatch(hum_input[[i]]<-read.table(input[i],header = FALSE,
                              sep = "",col.names = c("year","month","day","data"),
                              skip=6),
           error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
}
```

## Set up the main dataframe

```{r humidity dataframe}
#Positions vector
for(i in 1:length(input)){
  lines<-readLines(input[i],n = 6)
  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
  name<-unlist(strsplit(lines[2], ":"))[2]
  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
  p<-data.frame(ID,name,long,lat)
  if(i > 1) positions_hum<-rbind(positions_hum,p,make.row.names=FALSE)
  else positions_hum<-p
}
positions_hum$ID<-paste0("St",positions_hum$ID)

#Unified dataframe

start_y <- 1980
end_y <- 2020
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")

##Create a date column inside each station dataframe
for(i in 1:length(hum_input[])){
  d<-as.Date(paste0(hum_input[[i]]$year,"-",hum_input[[i]]$month,"-",hum_input[[i]]$day))
  hum_input[[i]]$date<-d
}

tic("Unified dataframe humidity - Optimized")

main_dataframe_hum<-data.frame(date)
index<-matrix(NA,ncol = 2,nrow = 744)
j<-1

for(i in 1:length(hum_input[])){
  check<-hum_input[[i]][which(hum_input[[i]]$date %in% main_dataframe_hum$date),]
  if(dim(check)[1]!=0){
      #main_dataframe_hum$new<-rep(NA,nrow(main_dataframe_hum))
      new_v<-sistemadati(vettore = hum_input[[i]],lung = nrow(main_dataframe_hum),g = date)
      main_dataframe_hum$new<-new_v[,2]
      names(main_dataframe_hum)[names(main_dataframe_hum) == "new"]<-positions_hum$ID[i]
  }else{
      index[j,1]<-i
      index[j,2]<-positions_hum$ID[i]
      j<-j+1
  }
}
index_clean<-subset(index, (!is.na(index[,1])) & (!is.na(index[,2])))
toc() #277.06 sec = 4.6 min

remove(index,j,new_v)
View(index_clean)

path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
write.table(main_dataframe_hum,paste0(path,"/main_dataframe_humidity_8019.txt"),
            quote=FALSE,sep="\t",row.names = FALSE)

```

## Interpolation

```{r humidity interpolation}
#Upload the main dataframe of precipitation data
#path="C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/main_datasets"
#main_dataframe_prec<-read.table(paste0(path,"/main_dataframe_precipitation_opt_v2.txt"),
#                                header = TRUE, sep="\t")

#Import of the subbasins shapefile
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/streamgauges"
subbasins<-readOGR(paste0(path,"/Subbasins_geomfix.shp"))

#Output dataframe creation
tic("Output generation - Humidity - With function")
output_hum<-create_time_series(main_dataframe = main_dataframe_hum,
                                positions = positions_hum,
                                layer = subbasins,
                                dates = date)
toc()

#1437.31 sec = 24 min
```

### Output dataframe creation and export

```{r humidity output}
#Insert the date
year<-lubridate::year(main_dataframe_hum$date)
month<-lubridate::month(main_dataframe_hum$date)
month[which(month < 10)]<-paste0("0",month[which(month < 10)])
day<-lubridate::day(main_dataframe_hum$date)
day[which(day < 10)]<-paste0("0",day[which(day < 10)])

output_hum$date<-paste0(day,month,year)

#Insert the number of days
output_hum$`number of days`<-lubridate::yday(main_dataframe_hum$date)

#Round the values
output_exp<-output_hum
output_exp[,3:ncol(output_exp)]<-round(output_exp[,3:ncol(output_exp)], digits = 1)

#Export as an Input file for WASA
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"

my.write(output_exp,file=paste0(path,"/humidity_v1.dat"),
         header = "Daily average humidity [in %] for each subasin, ordered according to Map-IDs\nDate No. of days Subasin-ID\n0 0 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36 37 38 39 40 41 42 43 44 45 46 47 48 49 50 51 52 53 54 55 56 57 58 59 60 61 62 63 64 65 66 67 68 69 70 71 72 73 74 75 76 77 78 79 80 81 82 83 84 85 86 87 88 89 90 91 92 93 94 95 96 97 98 99 100 101 102 103 104 105 106 107 108 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215",f = write.table,sepset = FALSE)

#Save it as it is for future use
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
write.table(output_hum,paste0(path,"/output_hum_save_v1.txt"),quote = FALSE,sep="\t",row.names = FALSE)

```

# Radiation

## Upload radiation data

Both FUNCEME and INMET datasets are uploaded

```{r radiation upload}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")

#FUNCEME and INMET dataset
input<-list.files(path="./Meteorological_stations_FUNCEME/radiation_KJ_subset/FUNCEME",full.names = T,recursive = TRUE)

rad_input<-list()
for(i in 1:length(input)){
  tryCatch(rad_input[[i]]<-read.table(input[i],header = FALSE,
                              sep = "",col.names = c("year","month","day","data"),
                              skip=6),
           error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
}
```

## Set up the main dataframe

```{r radiation dataframe}
#Positions vector
for(i in 1:length(input)){
  lines<-readLines(input[i],n = 6)
  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
  name<-unlist(strsplit(lines[2], ":"))[2]
  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
  p<-data.frame(ID,name,long,lat)
  if(i > 1) positions_rad<-rbind(positions_rad,p,make.row.names=FALSE)
  else positions_rad<-p
}
positions_rad$ID<-paste0("St",positions_rad$ID)

#Unified dataframe

start_y <- 1980
end_y <- 2020
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")

##Create a date column inside each station dataframe
for(i in 1:length(rad_input[])){
  d<-as.Date(paste0(rad_input[[i]]$year,"-",rad_input[[i]]$month,"-",rad_input[[i]]$day))
  rad_input[[i]]$date<-d
}

tic("Unified dataframe radiation - Optimized")

main_dataframe_rad<-data.frame(date)
index<-matrix(NA,ncol = 2,nrow = 744)
j<-1

for(i in 1:length(rad_input[])){
  check<-rad_input[[i]][which(rad_input[[i]]$date %in% main_dataframe_rad$date),]
  if(dim(check)[1]!=0){
      #main_dataframe_rad$new<-rep(NA,nrow(main_dataframe_rad))
      new_v<-sistemadati(vettore = rad_input[[i]],lung = nrow(main_dataframe_rad),g = date)
      main_dataframe_rad$new<-new_v[,2]
      names(main_dataframe_rad)[names(main_dataframe_rad) == "new"]<-positions_rad$ID[i]
  }else{
      index[j,1]<-i
      index[j,2]<-positions_rad$ID[i]
      j<-j+1
  }
}
index_clean<-subset(index, (!is.na(index[,1])) & (!is.na(index[,2])))
toc() #519.94 sec = 8.65 min

remove(index,j,new_v)
View(index_clean)

path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
write.table(main_dataframe_rad,paste0(path,"/main_dataframe_radiation_FUNCEME.txt"),
            quote=FALSE,sep="\t",row.names = FALSE)

```

## Interpolation

```{r radiation interpolation}
#Upload the main dataframe of precipitation data
#path="C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/main_datasets"
#main_dataframe_prec<-read.table(paste0(path,"/main_dataframe_radiation_FUNCEME.txt"),
#                                header = TRUE, sep="\t")

#Import of the subbasins shapefile
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
subbasins<-readOGR(paste0(path,"/subbasins_cut_geomfix.shp"))

#Output dataframe creation
#Output dataframe creation
tic("Output generation - Radiation - Wmean")
output_rad<-create_time_series_Wmean(main_dataframe = main_dataframe_rad,
                                positions = positions_rad,
                                layer = subbasins)
toc()

#1150.56 sec
#With only Bana reservoirs:
# - Old function: 364.34 sec
# - New function: 586.64 sec
```

### Output dataframe creation and export

ATTENTION
For WASA, the input radiation need to be in W/m2, we have it in KJoule
Make the transformation!
[Here][KJ] they say to multiply the KJ by 3.6. Compare the two time series and see if by multiplying by 3.6 they are in the same range.

[KJ]: https://electronics.stackexchange.com/questions/538921/how-to-convert-calculate-textkj-textm2-to-textw-textm2

```{r scale change}
#Transform from KJ to W/m2

output_rad_Wm2_v1<-output_rad
output_rad_Wm2_v1<-output_rad_Wm2_v1[,3:ncol(output_rad)]*3.6

```

```{r radiation output}
#Insert the date
year<-lubridate::year(main_dataframe_rad$date)
month<-lubridate::month(main_dataframe_rad$date)
month[which(month < 10)]<-paste0("0",month[which(month < 10)])
day<-lubridate::day(main_dataframe_rad$date)
day[which(day < 10)]<-paste0("0",day[which(day < 10)])

output_rad$date<-paste0(day,month,year)

#Insert the number of days
output_rad$`number of days`<-lubridate::yday(main_dataframe_rad$date)

#Round the values
output_exp<-output_rad
output_exp[,3:ncol(output_exp)]<-round(output_exp[,3:ncol(output_exp)], digits = 1)

#Export as an Input file for WASA
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"

my.write(output_exp,file=paste0(path,"/radiation_v1.dat"),
         header = "Daily average shortwave radiation [in Wm2] for each subasin, ordered according to MAP-IDs\nDate No. of days Subasin-ID\n0 0 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36 37 38 39 40 41 42 43 44 45 46 47 48 49 50 51 52 53 54 55 56 57 58 59 60 61 62 63 64 65 66 67 68 69 70 71 72 73 74 75 76 77 78 79 80 81 82 83 84 85 86 87 88 89 90 91 92 93 94 95 96 97 98 99 100 101 102 103 104 105 106 107 108 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215",f = write.table,sepset = FALSE)

#Save it as it is for future use
write.table(output_rad,paste0(path,"/output_rad_v1.txt"),quote = FALSE,sep="\t",row.names = FALSE)
```

# Extraterrestrial radiation

Extraterrestrial radiation has a different style compared to the other time series, and it can be obtained easily.

# Comparison between generated and Alexandre's time series

```{r}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")

#Load Banabuiu reservoirs' names and IDs
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
reservoirs<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
```

## Precipitation visual comparison

```{r}
#Precipitation
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
rain_gen<-read.table(paste0(path,"/output_prec_save_v2.txt"),skip = 1)
path<-"C:/Thesis_fortran/WASA/Input/Time_series"
rain_alex<-read.table(paste0(path,"/rain_daily.dat"),skip = 3)
rain_gen<-rain_gen[1:11323,]
rain_alex<-rain_alex[1:11323,] #end in 2010

#Plots
time_index<-seq(as.Date("1980-01-01"),as.Date("2010-12-31"),by="days")
for(i in 1:nrow(reservoirs)){
  #Creation of the dataset for the visualization
  n<-as.numeric(reservoirs$SubbasinID[i])+2
  visual1<-data.frame(rain_alex[,n],rep("Alexandre",length(rain_alex[,n])),time_index)
  names(visual1)<-c("data","id","time")
  visual2<-data.frame(rain_gen[,n],rep("Generated",length(rain_gen[,n])),time_index)
  names(visual2)<-c("data","id","time")
  visual<-cbind(rbind(visual1,visual2))
  Legend<-visual$id
  p<-ggplot(data = visual,
            aes(x = `time`,
                y = `data`))+
    geom_line(aes(colour = Legend),alpha = 0.5) +
    labs(x = "Date",
         y = "Precipitation", 
         title = paste0("Subbasin ",reservoirs$SubbasinID[i]," - ",reservoirs$Reservoir_name[i])) +
    theme_ipsum()
  print(p)
  # path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/plots"
  # ggsave(
  #   filename = paste0("0517_prec_",reservoirs$SubbasinID[i],".png"),
  #   plot = p,
  #   device = "png",
  #   path = path,
  #   scale = 1,
  #   width = NA,
  #   height = NA,
  #   units = c("in", "cm", "mm"),
  #   dpi = 300,
  #   limitsize = TRUE
  # )
}
```

## Temperature visual comparison

```{r temperature visual comparison}
#Temperature

#Upload
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
temp_gen<-read.table(paste0(path,"/output_temp_save_v3.txt"),skip = 1)
path<-"C:/Thesis_fortran/WASA/Input/Time_series"
temp_alex<-read.table(paste0(path,"/temperature.dat"),skip = 3)
temp_gen<-temp_gen[1:11323,]
temp_alex<-temp_alex[1:11323,] #end in 2010

#Plots
time_index<-seq(as.Date("1980-01-01"),as.Date("2010-12-31"),by="days")
for(i in 1:nrow(reservoirs)){
  #Creation of the dataset for the visualization
  n<-as.numeric(reservoirs$SubbasinID[i])+2
  visual1<-data.frame(temp_alex[,n],rep("Alexandre",length(temp_alex[,n])),time_index)
  names(visual1)<-c("data","id","time")
  visual2<-data.frame(temp_gen[,n],rep("Generated",length(temp_gen[,n])),time_index)
  names(visual2)<-c("data","id","time")
  visual<-cbind(rbind(visual1,visual2))
  Legend<-visual$id
  p<-ggplot(data = visual,
            aes(x = `time`,
                y = `data`))+
    geom_line(aes(colour = Legend),size=0.75,alpha = 0.5) +
    labs(x = "Date",
         y = "Temperature", 
         title = paste0("Subbasin ",reservoirs$SubbasinID[i]," - ",reservoirs$Reservoir_name[i]))+
    theme_ipsum()
  print(p)
  # path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/plots"
  # ggsave(
  #   filename = paste0("0517_temp_",reservoirs$SubbasinID[i],".png"),
  #   plot = p,
  #     device = "png",
  #     path = path,
  #     scale = 1,
  #     width = NA,
  #     height = NA,
  #     units = c("in", "cm", "mm"),
  #     dpi = 300,
  #     limitsize = TRUE
  #   )
}
```

## Humidity visual comparison

```{r humidity visual comparison}
#Humidity

#Upload
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
hum_gen<-read.table(paste0(path,"/output_hum_save_v1.txt"),skip = 1)
path<-"C:/Thesis_fortran/WASA/Input/Time_series"
hum_alex<-read.table(paste0(path,"/humidity.dat"),skip = 3)
hum_gen<-hum_gen[1:11323,]
hum_alex<-hum_alex[1:11323,] #end in 2010

#Plots
time_index<-seq(as.Date("1980-01-01"),as.Date("2010-12-31"),by="days")

for(i in 1:nrow(reservoirs)){
  #Creation of the dataset for the visualization
  n<-as.numeric(reservoirs$SubbasinID[i])+2
  visual1<-data.frame(hum_alex[,n],rep("Alexandre",length(hum_alex[,n])),time_index)
  names(visual1)<-c("data","id","time")

  visual2<-data.frame(abs(hum_gen[,n]),rep("Generated",length(hum_gen[,n])),time_index)
  names(visual2)<-c("data","id","time")
  visual<-cbind(rbind(visual1,visual2))
  Legend<-visual$id
  p<-ggplot(data = visual,
            aes(x = `time`,
                y = `data`))+
    geom_line(aes(colour = Legend),size=0.75,alpha = 0.5) +
    labs(x = "Date",
         y = "Humidity", 
         title = paste0("Subbasin ",reservoirs$SubbasinID[i]," - ",reservoirs$Reservoir_name[i]))+
    theme_ipsum()
  print(p)
  # path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/plots"
  # ggsave(
  #   filename = paste0("0517_hum_",reservoirs$SubbasinID[i],".png"),
  #   plot = p,
  #     device = "png",
  #     path = path,
  #     scale = 1,
  #     width = NA,
  #     height = NA,
  #     units = c("in", "cm", "mm"),
  #     dpi = 300,
  #     limitsize = TRUE
  #   )
}
```

## Radiation visual comparison

```{r radiation visual comparison}
#Radiation

#Upload
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
rad_gen<-read.table(paste0(path,"/output_rad_v1.txt"),skip = 1)
path<-"C:/Thesis_fortran/WASA/Input/Time_series"
rad_alex<-read.table(paste0(path,"/radiation.dat"),skip = 3)
rad_gen<-rad_gen[1:11323,]
rad_alex<-rad_alex[1:11323,] #end in 2010

#Chech the coefficient
coeff<-data.frame(reservoirs$SubbasinID)
coeff$mean_coeff<-NA
for(i in 1:nrow(reservoirs)){
  n1<-as.numeric(reservoirs$SubbasinID[i])+2
  n2<-i+2
  div<-rad_alex[,n1]/rad_gen[,n2]
  coeff$mean_coeff[i]<-round(mean(div[is.finite(div)], na.rm = TRUE))
}

#Plots
time_index<-seq(as.Date("1980-01-01"),as.Date("2010-12-31"),by="days")

for(i in 1:nrow(reservoirs)){
  #Creation of the dataset for the visualization
  #n<-as.numeric(reservoirs$SubbasinID[i])+2
  n<-as.numeric(reservoirs$SubbasinID[i])+2
  visual1<-data.frame(rad_alex[,n],rep("Alexandre",length(rad_alex[,n])),time_index)
  names(visual1)<-c("data","id","time")

  n<-i+2
  visual2<-data.frame(abs(rad_gen[,n]),rep("Generated",length(rad_gen[,n])),time_index)
  names(visual2)<-c("data","id","time")
  visual<-cbind(rbind(visual1,visual2))
  Legend<-visual$id
  p<-ggplot(data = visual,
            aes(x = `time`,
                y = `data`))+
    geom_line(aes(colour = Legend),size=0.75,alpha = 0.5) +
    labs(x = "Date",
         y = "Radiation", 
         title = paste0("Subbasin ",reservoirs$SubbasinID[i]," - ",reservoirs$Reservoir_name[i]))+
    theme_ipsum()
  print(p)
  # path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/plots"
  # ggsave(
  #   filename = paste0("0517_hum_",reservoirs$SubbasinID[i],".png"),
  #   plot = p,
  #     device = "png",
  #     path = path,
  #     scale = 1,
  #     width = NA,
  #     height = NA,
  #     units = c("in", "cm", "mm"),
  #     dpi = 300,
  #     limitsize = TRUE
  #   )
}
```

```{r}
#Try changing the measuring unit
output_rad_Wm2_v1<-rad_gen
output_rad_Wm2_v1<-output_rad_Wm2_v1[,3:ncol(output_rad)]*3.6

n<-5+2
visual1<-data.frame(rad_alex[,n],rep("Alexandre",length(rad_alex[,n])),time_index)
names(visual1)<-c("data","id","time")
visual2<-data.frame(abs(output_rad_Wm2_v2[,n]),rep("Generated",length(output_rad_Wm2_v2[,n])),time_index)
names(visual2)<-c("data","id","time")
visual<-cbind(rbind(visual1,visual2))
Legend<-visual$id
p<-ggplot(data = visual,
          aes(x = `time`,
              y = `data`))+
    geom_line(aes(colour = Legend),size=0.75,alpha = 0.5) +
    labs(x = "Date",
         y = "Radiation", 
         title = paste0("Subbasin ",reservoirs$SubbasinID[i]," - ",reservoirs$Reservoir_name[i]))+
    theme_ipsum()
print(p)

output_rad_Wm2_v2<-rad_gen
output_rad_Wm2_v2<-output_rad_Wm2_v2[,3:ncol(output_rad_Wm2_v2)]*86.4

```

## Root Mean Square Deviation

RMSE provides a single number that answers the question: "How similar, on average, are the numbers in list1 to list2?".

```{r}

RMSE = function(m, o){
  #m: model values
  #o: observed values
  sqrt(mean((m - o)^2))
}

#Precipitation RMSE
rain_gen[is.na(rain_gen),]<-0

#Define a matrix containing the range of variability for each Sub-basin and its
#RMSE
for(i in 3:ncol(rain_gen)){
  subID<-i-2
  y0<-round(RMSE(rain_gen[,i],rain_alex[,i]), digits = 3)
  y1<-paste0(min(rain_gen[,i])," - ",round(max(rain_gen[,i]),digits = 1))
  y2<-round(mean(rain_gen[,i]), digits = 2)
  y3<-paste0(min(rain_alex[,i])," - ",round(max(rain_alex[,i],digits = 1)))
  y4<-round(mean(rain_alex[,i]), digits = 2)

  if(i > 3){
      prec_comparison<-rbind(prec_comparison, data.frame(subID,y0,y1,y2,y3,y4))
  }else prec_comparison<-data.frame(subID,y0,y1,y2,y3,y4)
}
names(prec_comparison)<-c("SubbasinID","RMSE", "Range generated", "Mean generated", "Range Alexandre", "Mean Alexandre")

#Focus on Banabuiu subbasins

View(prec_comparison[which(prec_comparison$SubbasinID %in% reservoirs$SubbasinID),])
#Save this
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation"
write.table(prec_comparison[which(prec_comparison$SubbasinID %in% reservoirs$SubbasinID),],
            paste0(path,"/RMSE_prec.txt"), row.names = FALSE, sep = "\t")

Bana_prec_RMSE<-read.table(paste0(path,"/RMSE_prec.txt"), header = TRUE, sep = "\t")
View(Bana_prec_RMSE)
```

```{r}
#Temperature RMSE
#Define a matrix containing the range of variability for each Sub-basin and its
#RMSE

temp_gen[is.na(temp_gen)]<-0

for(i in 3:ncol(rain_gen)){
  subID<-i-2
  y0<-round(RMSE(temp_gen[,i],temp_alex[,i]), digits = 3)
  y1<-paste0(min(temp_gen[,i])," - ",round(max(temp_gen[,i]),digits = 1))
  y2<-round(mean(temp_gen[,i]), digits = 2)
  y3<-paste0(min(temp_alex[,i])," - ",round(max(temp_alex[,i],digits = 1)))
  y4<-round(mean(temp_alex[,i]), digits = 2)

  if(i > 3){
      temp_comparison<-rbind(temp_comparison, data.frame(subID,y0,y1,y2,y3,y4))
  }else temp_comparison<-data.frame(subID,y0,y1,y2,y3,y4)
}
names(temp_comparison)<-c("SubbasinID","RMSE", "Range generated", "Mean generated", "Range Alexandre", "Mean Alexandre")

#Focus on Banabuiu subbasins

View(temp_comparison[which(temp_comparison$SubbasinID %in% reservoirs$SubbasinID),])
#Save this
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation"
write.table(temp_comparison[which(temp_comparison$SubbasinID %in% reservoirs$SubbasinID),],
            paste0(path,"/RMSE_temp.txt"), row.names = FALSE, sep = "\t")

Bana_temp_RMSE<-read.table(paste0(path,"/RMSE_temp.txt"), header = TRUE, sep = "\t")

```

# SIGA (abandoned)

* Export the position vector as a point shapefile
* Create a unique dataframe containing all the stations' observations: rows = date, columns = stations. Export it in a .csv file

```{r}
#Export the positions vector as a point shapefile
remove(shp_stations)
shp_stations<-positions_prec[which(positions_prec$ID %in% colnames(main_dataframe_prec)),]
coordinates(shp_stations)<-c("long","lat")

#Import the subbasins shapefile
path<-"C:/Thesis_fortran/WASA/shapefile/streamgauges/Subbasins.shp"
subbasins<-readOGR(path)
summary(subbasins)

#Assign the same reference system as the subbasins shapefile
proj4string(shp_stations)<-CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
shp_stations <- spTransform(shp_stations, raster::crs(subbasins))
summary(shp_stations)
#EPSG:32724 - WGS 84 / UTM zone 24S - Proiettato

path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME"
raster::shapefile(shp_stations, paste0(path,"/prec_stations_FUNCEME.shp"),overwrite=TRUE)

#Rearrange main_dataframe so SIGA can read it
#1. Insert "-999" where NA are present
#2. Change the date column in DD/MM/AAAA

SIGA_data<-main_dataframe_prec
#insert -999
SIGA_data[is.na(SIGA_data)] <- -999
#change the date column
date_correct<-main_dataframe_prec$date
SIGA_data$date<-format(date_correct,"%d/%m/%Y")

#Save as a .srs file
write.table(SIGA_data,paste0(path,"/SIGA_precipitation.srs"),
            quote=FALSE,sep="\t",row.names = FALSE)

```

# Drafts

## Visualization

```{r}

# Usual area chart
p <- visual %>%
  ggplot( aes(x = time, y = data)) +
  geom_area(aes(colour = Legend), alpha=0.5) +
  geom_line(color="#69b3a2") +
  theme_ipsum()

# Turn it interactive with ggplotly
p <- ggplotly(p)
p

vis<-data.frame(visual1$data,visual2$data)
names(vis)<-c("vis1","vis2")
p <- ggplot(vis, aes(x = x) ) +
  # Top
  geom_density( aes(x = vis1, y = ..density..)) +
  geom_label( aes(x=4.5, y=1, label="variable1")) +
  # Bottom
  geom_density( aes(x = vis2, y = -..density..)) +
  geom_label( aes(x=4.5, y=-1, label="variable2")) +
  theme_ipsum() +
  xlab("value of x")
p

```

```{r old dataset}
#FUNCEME dataset, organized in "Dia 1, Dia 2..."
#input<-list.files(path="./Prec_stations",full.names = T,recursive = TRUE)

#prec_input<-list()
#for(i in 1:length(input)){
#  prec_input[[i]]<-read.table(input[i],header = TRUE,sep = ";")
#}
```

## Clean the data

```{r}
#Remove the stations with non allowed positions (NA or 0)
for(i in 1:length(prec_input[])){
  #If coordinates are 0, remove the station
  if(is.na(prec_input[[i]]$Latitude[1]) || prec_input[[i]]$Latitude[1] == 0){
    prec_input[[i]]<-NULL
  }
  if(i >= length(prec_input[])) break
}

#Replace 888 and 999 with NA
for(i in 1:length(prec_input[])){
    #Put NA instead of 888
    prec_input[[i]]<-na_if(prec_input[[i]],888)
    prec_input[[i]]<-na_if(prec_input[[i]],999)
    #Create a unique ID for each station
    ID<-rep(paste0("Station ",i),length(prec_input[[i]]$Municipios))
    prec_input[[i]]<-data.frame(prec_input[[i]],ID)
}

#Give the stations' ID to the list
for(i in 1:length(prec_input[])){
  names(prec_input)[i]<-prec_input[[i]]$ID[1]
}
```

## Create the matrix and the positions vector

### Positions vector

```{r poition vector}
#Position vector
for(i in 1:length(prec_input[])){
  name<-prec_input[[i]]$Postos[1]
  ID<-paste0("Station ",i)
  lat<-prec_input[[i]]$Latitude[1]
  long<-prec_input[[i]]$Longitude[1]
  if(i !=1 ){
    positions<-rbind(positions, data.frame(name,ID,long,lat))
  }else{
    positions<-data.frame(name,ID,long,lat)
  }
}
```

### Output dataframe creation

```{r}
start_y<-1980; start_m<-1
end_y<-2010;   end_m<-12
test1 <- as.Date("1980-01-01")
test2 <- as.Date("2010-12-31")
test2-test1
ndays<-11322  #result of the difference above

#Import of the subbasins shapefile
path<-"C:/Thesis_fortran/WASA/shapefile/streamgauges/Subbasins.shp"
subbasins<-readOGR(path)

#Output dataframe creation
output<-data.frame(matrix(NA,nrow=ndays,ncol=2+length(subbasins@data$SubbasinID)))
names(output)<-c("date","number of days",t(subbasins@data$SubbasinID))

tic("Output generation")
j<-1
for(year in start_y:end_y){
  for(month in start_m:end_m){
    #Creation of a matrix containing the data for all the stations for 1 month
    st<-0
    for(i in 1:length(prec_input[])){
      v<-prec_input[[i]][which(prec_input[[i]]$Anos == year & prec_input[[i]]$Meses == month),
                         9:ncol(prec_input[[i]])-1]

      if(dim(v)[1] != 0){
        if(st != 0){
          matrix<-data.frame(matrix,t(v))
          st<-append(st,prec_input[[i]]$ID[1])
        }else{
          matrix<-t(v)
          st<-prec_input[[i]]$ID[1]
        }
      }
    }
    names(matrix)<-st
    for(i in 1:nrow(matrix)){
      #First day data, with coordinates associated
      #NA are removed, and stations with NA on that day are not considered
      check<-matrix[i,][which(!is.na(matrix[i,]))]
      row.names(check)<-NULL
      if(ncol(check)>0){
        col<-colnames(check)
        shape<-data.frame(t(check),
                          positions$long[which(positions$ID %in% col)],
                          positions$lat[which(positions$ID %in% col)])
        names(shape)<-c("data","long","lat")

        #Creation of a spatial element
        coordinates(shape)<-c("long","lat")
        crs.pos<-CRS("+proj=longlat") #definition of the projection
        proj4string(shape)<-crs.pos
        shape <- spTransform(shape, crs(subbasins))
        shape@bbox <- subbasins@bbox

        #Interpolate to create a raster
        th <- as(dirichlet(as.ppp(shape)), "SpatialPolygons")
        proj4string(th) <- proj4string(shape)
        th.z <- over(th, shape)
        th.z$data[is.na(th.z$data)] <- 0
        th.spdf <- SpatialPolygonsDataFrame(th, th.z)

        #Superimpose the subbasin shapefile and obtain a mean of the values in the 
        #Thiessen polygons for each subbasin

        data_sub<-over(subbasins,th.spdf,fn=mean)
        #at the spatial locations of object x retrieves the indexes
        #or attributes from spatial object y

        #Save the values in a pre-made data.frame
        output[j,3:ncol(output)]<-t(data_sub)
        j <- j+1
        #}else if(i!=nrow(matrix)){
        #  j <- j+1
      }
    }
    remove(shape,th,th.z,th.spdf,data_sub)
  }
}
toc()
#First try: it took 3h 38m
#Over was done using the function "mean"

```

### Interpolation update

```{r}
#Interpolation update

year<-start_y
month=start_m
i<-1

## Primo tentativo

require(deldir)
require(sp)

del <- deldir(x = shape$long,y = shape$lat,z = shape$data)
del_sp <- tile.list(del)

wcols <- topo.colors(length(del_sp)) 
plot(del_sp, fillcol=wcols, close=TRUE)

#Ok, questo mi crea una tessellazione
#Problema: si può fare analisi spaziale utilizzando questo "oggetto"?

#Prova di soluzione, a questo link: https://stackoverflow.com/questions/9403660/how-to-create-thiessen-polygons-from-points-using-r-packages
polys<-vector(mode='list',length=length(del_sp))
 for (i in seq(along=polys)) {
    pcrds <- cbind(del_sp[[i]]$x, del_sp[[i]]$y)
    pcrds <- rbind(pcrds, pcrds[1,])
    polys[[i]] <- Polygons(list(Polygon(pcrds)), ID=as.character(i))
 }
SP <- SpatialPolygons(polys)
voronoi <- SpatialPolygonsDataFrame(SP,
    data=data.frame(x = shape$long,
    y = shape$lat,z=shape$data))

## Secondo tentativo

voronoipolygons <- function(x) {
  require(deldir)
  require(sp)
  if (.hasSlot(x, 'coords')) {
    crds <- x@coords  
  } else crds <- x
  op <- deldir(x=crds[,2],y= crds[,3],z=crds[,1])
  w <- tile.list(op)
  polys <- vector(mode='list', length=length(w))
  for (i in seq(along=polys)) {
    pcrds <- cbind(w[[i]]$x, w[[i]]$y)
    pcrds <- rbind(pcrds, pcrds[1,])
    polys[[i]] <- Polygons(list(Polygon(pcrds)), ID=as.character(i))
  }
  SP <- SpatialPolygons(polys)
  voronoi <- SpatialPolygonsDataFrame(SP, data=data.frame(x=crds[,2],
    y=crds[,3],z=crds[,1], row.names=sapply(slot(SP, 'polygons'), 
    function(x) slot(x, 'ID'))))
}

tic()
prova<-voronoipolygons(shape)
toc()
#così creo direttamente uno SpatialPolygon
#posso poi applicare il sistema di riferimento ecc, e tagliare
#andare avanti su questa strada!

```

## SIGA first try (not completed)

```{r}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara"

#Export the positions vector as a point shapefile
shp_stations<-positions
coordinates(shp_stations)<-c("long","lat")
proj4string(shp_stations)<-CRS("+proj=longlat")
raster::shapefile(shp_stations, paste0(path,"/stations.shp"),overwrite=TRUE)
#summary(shp_stations)

#Create a unique dataframe containing all the stations' observations
#Row: date
#Columns: stations

start_y <- 1980
end_y <- 2010
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")

main_dataframe<-data.frame(date)
i<-1
for(i in 1:length(prec_input[])){
  for(j in 1:nrow(main_dataframe)){
    y<-lubridate::year(main_dataframe$date[j])
    m<-lubridate::month(main_dataframe$date[j])

    check1<-prec_input[[i]]$Anos[1]
    check2<-prec_input[[i]]$Meses[1]

    if(check1 == y & check2 == m){
      for(a in 1:length(prec_input[[i]])){
        prec_input[[i]][a,8:ncol(prec_input[[i]])]
      }
      break
    }
  }
}

for(month in start_m:end_m){
    #Creation of a matrix containing the data for all the stations for 1 month
    st<-0
    for(i in 1:length(prec_input[])){
      v<-prec_input[[i]][which(prec_input[[i]]$Anos == year & prec_input[[i]]$Meses == month),
                         9:ncol(prec_input[[i]])-1]

      if(dim(v)[1] != 0){
        if(st != 0){
          matrix<-data.frame(matrix,t(v))
          st<-append(st,prec_input[[i]]$ID[1])
        }else{
          matrix<-t(v)
          st<-prec_input[[i]]$ID[1]
        }
      }
    }
    names(matrix)<-st
}
```

### 2021-08-06 Main_code/downstreamness_analysis.Rmd
init

---
title: "Downstreamness Analysis"
author: "Paolo Colombo"
date: "4/6/2021"
output: html_document
---

# What is the downstreamness analysis

The downstreamness of a location is the ratio of its upstream catchment area to the entire river basin area. The downstreamness of a function on the basin, such as water availability or water demand, is defined as the downstreamness-weighted integral of that function divided by its regular integral.
The downstreamness concept will be used in the analysis performed here by considering it applied to Banabuiu's reservoirs' storage capacities and stored volumes.

# How to perform it

The first step requires to compute the downstreamness of the reservoirs (D~x~), by dividing the upstream catchment area by the whole catchment area.

For analyzing the downstreamness of a basin’s storage capacity, the capacity of reservoirs and the locations of dams are relevant. The downstreamness of the total storage capacity in a basin, D~SC~, can change over time attributable to newly built reservoirs or capacity loss by sedimentation. **Need to address this!**
The storage capacities of the reservoirs are then used as weights to determine D~SC~, which is a measure of how far downstream storage capacity in the basin is located on average.

D~SC~ computation equation: ![1](C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/downstreamness/Dsc.png)

For analyzing the downstreamness of stored volumes in reservoirs, D~SV~, in a basin, reservoir volumes and the locations of the dams are relevant. D~SV~ changes because volumes at different locations can change over time at different rates. The stored volumes at different time steps of the reservoirs are then used as weights to determine D~SV~, which is a measure of how far downstream stored water in the basin is located on average.

D~SV~ computation equation: ![2](C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/downstreamness/Dsv.png)

# Downstreamness

## Pre-processing

* Merge the DEM
* Cut it around the Banabuiu basin area

## D~x~ computation

* Extract the outlet points from the main reservoir shapefile and create a point shapefile
* Be sure to associate the capacities of each reservoir to the points shapefile
* Join the outlet points of the main reservoirs with the HDRN shapefile (v2)
  + This point shapefile should contain, for each point: coordinates, capacity, SubbasinID, a Boolean value indicating if it is a monitored reservoir
* Download a DEM of the Banabuiu region [Here how to download it from NASA][youtube tutorial]

[youtube tutorial]: https://www.youtube.com/watch?v=0nmYzQo0OSY

### Considering the whole Banabuiu catchment

* Superimpose the joined shapefile to a DEM of the Banabuiu
* From the DEM, compute the area of the upstream catchment relative to each reservoir
* Compute D~x~ for each reservoir by dividing their upstream area by the total area
* Insert the D~x~ as a new column in the attributes of the point shapefile

### Considering each sub-catchment separately

* Subdivide the whole Banabuiu DEM into the sub-catchments
* From the DEM, compute the area of the upsream sub-catchment relative to each reservoir in that sub-catchment
* Compute D~x~ for each reservoir by dividing their upstream area by the total area
* Insert the sub-catchment D~x~ as a new column in the attributes of the point shapefile

# Downstreamness in the HDRN scenario

## D~SC~ computation, monitored reservoirs and HDRN

For the last year, consider both the monitored reservoirs and the HDRN. The storage capacities of the monitored reservoirs are found in *reservoir.dat*, while the storage capacities of the HDRN is found in the attribute table of *HDRN_afterR_v2.shp*.

* Extract the monitored reservoirs capacities
* Extract the HDRN capacities
* Whole Banabuiu D~SC~: Compute D~SC~ referred to the whole Banabuiu following the first equation
* Sub-catchments D~SC~: Compute D~SC~ referred to each sub-catchment by:
  + Selecting the reservoirs inside the sub-catchments present in that year
  + Compute the D~SC~ for each sub-catchment by considering the selected reservoirs

## D~SV~ computation

In *lake_storage.out*, the water volume is found for each one of the 5 reservoir classes for each subbasin. Since the real positions of the small reservoirs are not considered in the WASA model, we cannot rely on the volume allocation throughout the five classes operated by the model. So, for each subcatchment we can consider all the reservoirs in the 5 classes, and assign them the same volume, obtained by summing the volumes of the classes and dividing by the number of reservoirs.
The number of reservoirs to calculate the mean volume can be obtained by reclassifying the HDRN reservoirs considering the increase coefficient in the WASA model backwards, so by computing  the number of reservoirs in the previous years by applying the increase coefficient backwards. In this way, the position information of the small reservoirs gets lost. So, it would be probably better to just consider the final number of small reservoirs to compute the volumes. Anyway, the growing number of small reservoirs has to be taken into account while calibrating the model.

The volume of the monitored reservoirs is provided in different *res_watbal.out* files, one for each reservoirs, so the operation above won't be needed for them.

For the whole Banabuiu:

* Extract the stored volume of the monitored reservoirs:
  + Obtain monthly values
  + Assign the mean volume to each reservoir
* Extract the stored volume in the 5 small reservoirs classes:
  + Obtain monthly values
  + Sum the monthly values of each class together
  + Obtain a mean volume by dividing the sum by the number of small reservoirs
  + Assign the mean volume to each reservoir
* Compute D~SV~ for each month by using the formula

For each sub-catchment:

* Extract the stored volume of the monitored reservoirs in that subcatchment:
  + Obtain monthly values
  + Assign the mean volume to each reservoir
* Extract the stored volume in the 5 small reservoirs classes in that subcatchment:
  + Obtain monthly values
  + Sum the monthly values of each class together
  + Obtain a mean volume by dividing the sum by the number of small reservoirs
  + Assign the mean volume to each reservoir
* Compute D~SV~ for each month by using the formula

# Downstreamness in the only monitored reservoirs scenario

## D~SC~ computation, only monitored reservoirs

Compute an yearly D~SC~, by selecting the reservoirs present each year. The results will show the evolution of the downstreamness of the monitored reservoirs throughout the years.

For each year:
* Compute D~SC~ referred to the whole Banabuiu following the first equation, selecting the reservoirs present is that year.
* Compute D~SC~ referred to each sub-catchment by:
  + Selecting the reservoirs inside the sub-catchments present in that year
  + Compute the D~SC~ for each sub-catchment by considering the selected reservoirs

##

## Libraries and functions

```{r libraries and functions}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

### 2021-08-06 Main_code/drought_cycle_analysis.Rmd
init

---
title: "Drought Cycle Analysis"
author: "Paolo Colombo"
date: "17/5/2021"
output: html_document
---

# Why the Drought Cycle Analysis

By looking at the precipitation index and at the volume of the monitored reservoirs, we can determine if the area we are considering is in a drought condition, and in which phase it is in. By considering two different scenarios (one including the HDRN and one excluding it), we can evaluate the differences in the drought cycles generated by the presence of the HDRN.

Drought Cycle Analysis can then express the impacts of the HDRN on the centralized reservoirs system, by checking how the volume deficit of the monitored reservoirs changes during time.

# Steps for the Drought Cycle Analysis

The Drought Cycle Analysis is carried forward through the classification of drought events into four possible stages regarding the simultaneous occurrence of precipitation deficit and water storage deficit. It uses the Precipitation Index (PI) and the Water Storage Index (WSI).
-	Wet quadrant (non-occurrence of drought):   PI > 0		WSI > 0
-	Meteorological drought:                     PI < 0		WSI > 0
-	Hydro-meteorological drought:               PI < 0		WSI < 0
-	Hydrological drought:                       PI > 0		WSI < 0

* **PI**: SPI12 within CHIRPS data
* **WSI**: obtained by considering the variation of the largest and most important reservoir in the area as a proxy. The variation (called Volume Deficit, VD) was standardized considering a deviation from halved maximum capacity. It thus varies from -1 to 1.

## Libraries and functions

```{r libraries and functions}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

## Pre-steps

```{r}
#Load the IDs of subbasins in the Banabuiu region 
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
reservoirs<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")

#Create the date vector
start_y <- 1980
end_y <- 2020   #change to 2020 when actually using the updated time series
start_m <- 01
end_m <- 12

start<-paste0("01/0",start_m,"/",start_y)
end<-paste0("31/",end_m,"/",end_y)
date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")
```

## SPI12

Monthly sum of the precipitation for each subbasins and for the whole basin, considering a one year window.
Implement it by using the library James sent me.

Do this for each subbasin and for the whole Banabuiu (by summing the precipitation in each subbasin)

```{r precipitation dataframe}
#Create the dataset
#Three columns: Year, Month, Precipitation

#Upload the precipitation dataframe generated by Thiessen polygons
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
prec_Banabuiu<-read.table(paste0(path,"/output_prec_save_v2.txt"), header = TRUE, sep = "\t")

#Change the date format of the precipitation dataframe
prec_Banabuiu$date<-date

#Separate months and years in the precipitation dataframe
prec_Banabuiu$year<-lubridate::year(prec_Banabuiu$date)
prec_Banabuiu$month<-lubridate::month(prec_Banabuiu$date)

#Create a new dataframe with monthly sums of daily precipitation
for(i in 0:(end_y-start_y)){
  year<-rep(start_y+i,12)
  month<-seq(1,12,1)
  if(i != 0){
    month_prec_Banabuiu<-rbind(month_prec_Banabuiu,data.frame(year,month))
  }else  month_prec_Banabuiu<-data.frame(year, month)
}

#Add the monthly sums for each reservoir
for(i in 1:nrow(reservoirs)){
  n<-as.numeric(reservoirs$SubbasinID[i])+2
  month_prec_Banabuiu$new<-rep(0,nrow(month_prec_Banabuiu))
  for(j in 1:nrow(month_prec_Banabuiu)){
  month_prec_Banabuiu$new[j]<-
    sum(prec_Banabuiu[,n][which(prec_Banabuiu$year == month_prec_Banabuiu$year[j] &
                          prec_Banabuiu$month == month_prec_Banabuiu$month[j])],
        na.rm = TRUE)
  }
  names(month_prec_Banabuiu)[names(month_prec_Banabuiu) == "new"]<-
    paste0("SubID_",as.numeric(reservoirs$SubbasinID[i]))
}
month_prec_Banabuiu$Banabuiu<-0
for(i in 1:nrow(month_prec_Banabuiu)){
  month_prec_Banabuiu$Banabuiu[i]<-sum(month_prec_Banabuiu[i,3:ncol(month_prec_Banabuiu)]) 
}

month_prec_Banabuiu[,3:ncol(month_prec_Banabuiu)]<-
  round(month_prec_Banabuiu[,3:ncol(month_prec_Banabuiu)],3)
```

```{r SPI computation}
library(SPEI)

list_spi<-list()
j<-1
for(i in 3:ncol(month_prec_Banabuiu)){
  list_spi[[j]]<-spi(month_prec_Banabuiu[,i], 12)
  j<-j+1
}
names(list_spi)<-paste0("SPI12_",names(month_prec_Banabuiu)[3:ncol(month_prec_Banabuiu)])

for(i in 1:length(list_spi)){
  plot.spei(list_spi[[i]], main = paste0("SPI12 of ",names(month_prec_Banabuiu)[i+2]))
}
#plot(list_spi$SPI12_SubID_123$fitted)
#plot.spei(list_spi$SPI12_SubID_123)

#Find a better way to visualize it, for now this is enough
#The SPI result is stored in $fitted
```

## Volume deficit

Consider the median of the time series of reservoirs' volumes
Then, calculate VD as the difference between the median and the volume at each time, and standardize it

Germano in his study used only the variation of the biggest monitored reservoir as an index, so:

* Implement the VD by considering only the biggest reservoir in the Banabuiu region
* Implement the VD by considering the variation of each monitored reservoirs from its own median. Standardize each VD, then take the mean of all of them

### Data input

```{r reservoirs model dataframe}
#Create a column containing the WASA output files paths
path<-"C:/Thesis_fortran/WASA"
reservoirs$file_WASA<-paste0(path,"/Output/res_",reservoirs$SubbasinID,"_watbal.out")

#Create an index for WASA output files
output<-list.files(path = paste0(path,"/Output"),full.names = T,recursive = TRUE)
#View(output)

#Check if some reservoir is missing from WASA output files
check<-length(reservoirs$file_WASA)-length(output[which(output %in% reservoirs$file_WASA)])
if(check > 0){
  print(reservoirs$Reservoir_name[which(!(reservoirs$file_WASA %in% output))])
  print("The reservoirs above are missing from WASA's output files")
  not_present<-which(!(reservoirs$file_WASA %in% output))
}
#Morada Nova and Umari reservoirs are missing from WASA's output files

#Order the file list and names by the SubbasinID
reservoirs<-reservoirs[order(reservoirs$SubbasinID),]
row.names(reservoirs)<-NULL

#Create a list containing the WASA output files
tic("Import WASA reservoir output files")
position<-c(0,7,13,19,25,35,45,55,68,81,91,101,111,121,131,141,155,169)
widths<-diff(position)
columns<-c("Subasin-ID", "year", "day", "hour", "qlateral(m**3/s)", "transposition(m**3/s)", "inflow(m**3/s)", "evap(m**3)", "prec(m**3)", "intake(m**3/s)", "overflow(m**3/s)", "qbottom(m**3/s)", "qout(m**3/s)", "withdrawal(m**3/s)", "elevation(m)", "area(m**2)", "volume(m**3)")

#Create a dataframe with dates in the rows and volumes in the columns
tic("Import WASA reservoir output volumes")
WASA_volumes<-data.frame(date)
for(i in 1:nrow(reservoirs)){
  if(!(i %in% not_present)){
    name<-paste0("res_",reservoirs$SubbasinID[i])
    res<-read.fwf(reservoirs$file_WASA[i], widths = widths, skip = 3)
    names(res)<-columns
    res$time<-time_index(res)

    WASA_volumes$new<-NA
    WASA_volumes$new[which(WASA_volumes$date %in% res$time)]<-
      res$`volume(m**3)`[which(res$time %in% WASA_volumes$date)]
    # WASA_volumes$new<-sistemadati_DCA(vettore = res, lung = length(date),
    #                    g = date, coldata = 17, coltime = 18)[,2]
    names(WASA_volumes)[names(WASA_volumes) == "new"]<-name
  }
}
toc() #105 sec

```

```{r reservoirs observation dataframe}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/volume_series_banabuiu_reservoirs_ID"

obs<-data.frame(list.files(path = path, full.names = T, recursive = TRUE))
names(obs)<-"path"
obs$SubbasinID<-gsub("\\..*","",basename(obs$path))

reservoirs$file_OBS<-NA
reservoirs$file_OBS[which(reservoirs$SubbasinID %in% obs$SubbasinID)] <- obs$path

#Create a dataframe with dates in the rows and volumes in the columns
tic("Import volumes from reservoir observations")
OBS_volumes<-data.frame(date)
for(i in 1:nrow(reservoirs)){
  if(!is.na(reservoirs$file_OBS[i])){
  #if(!(i %in% not_present)){
    name<-paste0("res_",reservoirs$SubbasinID[i])
    res<-read.csv(reservoirs$file_OBS[i], header = TRUE, sep = ",")
    res$date<-as.Date(res$date, format = "%Y-%m-%d")

    OBS_volumes$new<-NA
    OBS_volumes$new[which(OBS_volumes$date %in% res$date)]<-
      res$volume[which(res$date %in% OBS_volumes$date)]
    # 0.31 sec
    # modificare sistemadati in modo che sia ancora più efficiente

    # OBS_volumes$new<-sistemadati_DCA(vettore = res, lung = length(date),
    #                    g = date, coldata = 2, coltime = 1)[,2]
    # 28.15 sec
    names(OBS_volumes)[names(OBS_volumes) == "new"]<-name
  }
}
toc()

#Export as a .txt

```

```{r monthly volumes}
#Sum the volumes to obtain monthly volumes
month_OBS_volumes<-obt_monthly_values(OBS_volumes)
names(month_OBS_volumes)[names(month_OBS_volumes) == "total"]<-"Banabuiu"

month_WASA_volumes<-obt_monthly_values(WASA_volumes)
names(month_OBS_volumes)[names(month_OBS_volumes) == "total"]<-"Banabuiu"
```

### Test

For each reservoir, check if the volume has been higher than half of the total capacity for at least 50% of the time.
Considering the series until 2020, the test is not passed by the majority of the reservoirs, meaning that for more than 50% of the time its volumes have been under the half of the storage capacity. Since from 2010 an exceptional drought started, these years have been excluded from the second test. In this case, the majority of reservoirs passes the test, meaning that in the period outside the exceptional drought the reservoirs reached the half of their total capacity for at least the 50% of the time. The reservoirs which don't pass this second test didn't reach this threshold, which could mean that their storage capacity is oversized with respect of the actual volume available, or that for management reasons the water have been dispatched in other reservoirs during the years. In any case, for these reservoirs, the deviation from the median is a more feasible indicator to determine the condition of the reservoir, as it represents the value dividing the sample in two halves with 50% probability of occurrence.

Median: computed until 2010, used for the whole series!

The median could not be the best indicator for the VD, because it implies that half of the time the reservoir is in a dry condition and half of the time it is in a wet condition. The mean could be a better indicator then, considering not the 50% probability value, but a

```{r test_VD}
test_VD = function (volumes, IDs, years, thresholds, lubryear){
  test = data.frame(matrix (NA, ncol(volumes)-1, 5))
  names (test) = c("SubbasinID", "perc_2020", "test_passed_2020", "perc_2010", "test_passed_2010")

  for(i in 1:(ncol(volumes)-1)){
  volume = volumes[which(lubryear >= years[i]+3), i+1]

  test$SubbasinID[i] = IDs[i]
  test$perc_2020[i] = sum(volume > thresholds[i]/2, na.rm = TRUE)/sum(!is.na(volume))
  test$test_passed_2020[i] = ifelse(test$perc_2020[i]>=0.5, "YES", "NO")

  volume = volumes[which(lubryear >= years[i]+3 & lubryear <= 2010), i+1]

  test$perc_2010[i] = sum(volume > thresholds[i]/2, na.rm = TRUE)/sum(!is.na(volume))
  test$test_passed_2010[i] = ifelse(test$perc_2010[i]>=0.5, "YES", "NO")
  }
  test
}

#Max capacities
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/new_reservoirs"
max_cap<-read.table(paste0(path,"/reservoir_toupdate.dat"), skip = 2, sep = "\t")
max_cap<-data.frame(max_cap[,1],max_cap[,9],max_cap[,5]*1000)
names(max_cap)<-c("SubbasinID","year","capacity")

year<-lubridate::year(OBS_volumes[,1])

test = test_VD(OBS_volumes, max_cap$SubbasinID, max_cap$year, max_cap$capacity, year)
View(test)

path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/drought_cycle_analysis"
write.table(test, paste0(path, "/test_VD.txt"),sep = "\t", quote = FALSE, row.names = FALSE)
```

### VD computation

```{r VD computation method 1}
#Considering the biggest reservoir in the region
max(apply(month_OBS_volumes[,3:(ncol(month_OBS_volumes)-1)],2,max,na.rm = TRUE))
# Maximum daily volume registered: 1531156000, by Acude Arrojado Lisboa, SubbasinID 156
# Maximum monthly volume registered: 46728798000, by Acude Arrojado Lisboa, SubbasinID 156

#Take the median of the observed volumes of this reservoir
VD_median <- median(month_OBS_volumes$res_156, na.rm = TRUE)

#By considering only this reservoir's variation
VD_v1<-data.frame(month_OBS_volumes$year, month_OBS_volumes$month)
names(VD_v1)<-c("year","month")
VD_v1$VD <-  month_OBS_volumes$res_156 - VD_median

#Standardize
# VD_v1$VD <- (VD_v1$VD - mean(VD_v1$VD, na.rm = TRUE))/sd(VD_v1$VD, na.rm = TRUE)

#Normalize between -1 and 1
VD_v1$VD <- 2*(VD_v1$VD - min(VD_v1$VD, na.rm = TRUE))/
            (max(VD_v1$VD, na.rm = TRUE)-min(VD_v1$VD, na.rm = TRUE)) - 1

# min(VD_v1,na.rm = TRUE)
# View(VD_v1)
```

```{r VD computation method 2}
#Each reservoir is associated with a VD considering its own median
VD_median2 <- apply(month_OBS_volumes[,3:(ncol(month_OBS_volumes)-1)],2,median,na.rm = TRUE)
VD_v2 <- month_OBS_volumes[,3:(ncol(month_OBS_volumes)-1)]
#Normalize between -1 and 1
for(i in 1:ncol(VD_v2)){
  VD_v2[,i]<-VD_v2[,i] - median(VD_v2[,i],na.rm = TRUE)
  VD_v2[,i]<-2*(VD_v2[,i] - min(VD_v2[,i], na.rm = TRUE))/
            (max(VD_v2[,i], na.rm = TRUE) - min(VD_v2[,i], na.rm = TRUE)) - 1
}
#Take the mean for each month to obtain a single index
VD_v2$VD <- apply(VD_v2,1,mean,na.rm = TRUE)

#Add years and months
VD_v2$year<-month_OBS_volumes$year
VD_v2$month<-month_OBS_volumes$month
```

```{r VD Germano formula}

VD_v3<-data.frame(month_OBS_volumes$year, month_OBS_volumes$month)
names(VD_v3)<-c("year","month")
VD_v3$VD <- (month_OBS_volumes$res_156 - VD_median)/VD_median

#VD_v3$VD <- 2*(month_OBS_volumes$res_156 - min(month_OBS_volumes$res_156, na.rm = TRUE))/
#            (max(month_OBS_volumes$res_156, na.rm = TRUE)-min(month_OBS_volumes$res_156, na.rm = TRUE)) - 1

```

```{r plot the VDs}
VD_v1$ID<-"Normalized median - Arrojado Lisboa"
VD_v3$ID<-"Standardized median - Arrojado Lisboa (Germano formula)"
VD_v2$ID<-"Normalized median - Mean of all the reservoirs"

visual <- rbind(VD_v1,VD_v3)
vv<-data.frame(VD_v2$year,VD_v2$month,VD_v2$VD,VD_v2$ID)
names(vv)<-c("year","month","VD","ID")
visual <- rbind(visual,vv)
visual$date<-zoo::as.yearmon(paste(visual$year, visual$month), "%Y %m")
visual %>%
  ggplot( aes(x=date, y=VD, group=ID, color=ID)) +
    geom_line()
```

## Quadrant attribution

1 -	Wet quadrant (non-occurrence of drought):   PI > 0		WSI > 0
2 -	Meteorological drought:                     PI < 0		WSI > 0
3 -	Hydro-meteorological drought:               PI < 0		WSI < 0
4 -	Hydrological drought:                       PI > 0		WSI < 0

```{r quadrant attribution VD1}
#SPI Banabuiu
# list_spi[["SPI12_Banabuiu"]][["fitted"]]

#VD Banabuiu (only res_156 considered)
# VD_v1$VD

DCA<-data.frame(VD_v1, list_spi[["SPI12_Banabuiu"]][["fitted"]])
names(DCA)<-c("year","month","VD","SPI")

DCA$quadrant<-0
for(i in 1:nrow(DCA)){
  if(!is.na(DCA$SPI[i]) & !is.na(DCA$VD[i])){
  if(DCA$SPI[i] > 0 & DCA$VD[i] > 0) DCA$quadrant[i]<-1
  else if(DCA$SPI[i] < 0 & DCA$VD[i] > 0) DCA$quadrant[i]<-2
  else if(DCA$SPI[i] < 0 & DCA$VD[i] < 0) DCA$quadrant[i]<-3
  else if(DCA$SPI[i] > 0 & DCA$VD[i] < 0) DCA$quadrant[i]<-4
}}

plot(DCA$quadrant, type = 'p', main = "DCA with VD method 1")
```

```{r quadrant attribution VD2}
DCA<-data.frame(VD_v2$year, VD_v2$month, VD_v2$VD, list_spi[["SPI12_Banabuiu"]][["fitted"]])
names(DCA)<-c("year","month","VD","SPI")

DCA$quadrant<-0
for(i in 1:nrow(DCA)){
  if(!is.na(DCA$SPI[i]) & !is.na(DCA$VD[i])){
  if(DCA$SPI[i] > 0 & DCA$VD[i] > 0) DCA$quadrant[i]<-1
  else if(DCA$SPI[i] < 0 & DCA$VD[i] > 0) DCA$quadrant[i]<-2
  else if(DCA$SPI[i] < 0 & DCA$VD[i] < 0) DCA$quadrant[i]<-3
  else if(DCA$SPI[i] > 0 & DCA$VD[i] < 0) DCA$quadrant[i]<-4
}}

plot(DCA$quadrant, type = 'p', main = "DCA with VD method 2")
```

### 2021-08-06 Libraries/Functions.R

@@ -1,0 +1,340 @@
+#Functions
+
+create_time_series_Wmean = function(main_dataframe, positions, layer){
+  #main_dataframe: the main dataframe with all stations observations
+  #positions: the dataframe containing the positions of the stations
+  #layer: the layer to superimpose to the Voronoi diagram
+
+  require(deldir)
+  require(sp)
+  output<-data.frame(matrix(NA, nrow = nrow(main_dataframe),
+                            ncol=2+length(layer@data$SubbasinID)))
+  names(output)<-c("date","number of days",t(layer@data$SubbasinID))
+  j<-1
+  
+  #Boundaries of the Voronoi diagram
+  #They are fixed over the whole Cearà state, in order to take into
+  #account every station available
+  corners<-c(-41.64, -37.26, -7.85, -2.78) #(xmin, xmax, ymin, ymax)
+  
+  for(i in 1:nrow(main_dataframe)){
+    #Extract the data for the ith day
+    first<-main_dataframe[i,which(!is.na(main_dataframe[i,]))]
+    if(!is.null(dim(first)[1]) && dim(first)[2] > 2){
+      #Extract the positions of the stations and associate them to the data
+      col<-colnames(first); col<-col[2:length(col)]
+      second<-first[,2:ncol(first)]
+      shape<-data.frame(t(second),
+                        positions$long[which(positions$ID %in% col)],
+                        positions$lat[which(positions$ID %in% col)])
+      names(shape)<-c("data","long","lat")
+      
+      #Create the Voronoi diagram
+      thiessen<-voronoipolygons(shape, corners=corners)
+      proj4string(thiessen)<-CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+      thiessen <- spTransform(thiessen, raster::crs(layer))
+      #summary(thiessen)
+      
+      data_sub<-raster::intersect(layer, thiessen)
+      areas<-0
+      for(k in 1:length(data_sub)){
+        areas[k]<-data_sub@polygons[[k]]@area
+      }
+      weighted_value<-tapply(data_sub@data$z*areas, data_sub@data$SubbasinID, sum)
+      sum_area<-tapply(areas, data_sub@data$SubbasinID, sum)
+      data_sub_Wmean<-weighted_value/sum_area
+      remove(areas)
+      
+      #Save the values in a pre-made data.frame
[…]

### 2021-08-06 Libraries/Functions_CO.R

@@ -1,0 +1,131 @@
+# Functions for the comparison of the time series
+
+change_date_WASA_input = function(date_col){
+  #From the format ot the date in the WASA input, return a date column
+  #in the Date format (YYYY-MM-DD)
+  
+  n_digits <- floor(log10(date_col)) + 1
+  date_col[which(n_digits == 7)] <- paste0("0", date_col[which(n_digits == 7)])
+  date_col <- as.Date(date_col, format = "%d%m%Y")
+  return(date_col)
+}
+
+plot_subbasins_df = function(df, y = "Value", label = "Title", interactive = FALSE, file = "plot",
+                             save = FALSE, path = "nopath", doy = TRUE, line = FALSE){
+  require(reshape2)
+  if(doy) df[,2] <- NULL
+  df<-melt(df, id.vars = 'date', variable.name = 'Subbasins')
+  if(line){
+    p <- ggplot(df, aes(date, value)) + geom_line(aes(colour = Subbasins), alpha = 0.5, size = 1.5) +
+      xlab("Date") + ylab(y) + ggtitle(label)
+  }else{
+    p <- ggplot(df, aes(date, value)) + geom_point(aes(colour = Subbasins), alpha = 0.5) +
+      xlab("Date") + ylab(y) + ggtitle(label)
+  }
+  if(interactive){
+    #ggplotly(p)
+    #Saves an interactive version
+    if(path == "nopath") htmlwidgets::saveWidget(plotly::ggplotly(p), paste0(file,".html"))
+    else htmlwidgets::saveWidget(plotly::ggplotly(p), paste0(path, "/",file,".html"))
+  }else if(save){
+    #Saves a static version
+    ggsave(
+      filename = paste0(file,".png"),
+      plot = p,
+      device = "png",
+      path = path,
+      scale = 1,
+      width = 40,
+      height = 30,
+      units = "cm",
+      dpi = 300,
+      limitsize = TRUE
+    )
+  }else{
+    print(p)
+  }
+}
+
+RMSE = function(m, o){
+  #m: model values
+  #o: observed values
+  sqrt(mean((m - o)^2, na.rm = TRUE))
+}
+
+compare_TS_stat = function(gen_TS, alex_TS, start = "2005-01-01", end = "2010-12-31", skip = 2){
[…]

### 2021-08-06 Libraries/Functions_DP.R

@@ -1,0 +1,301 @@
+#Functions for data processing
+#Outlier removal and NA filling
+
+check_outlier_IQR = function(dataframe, skip = 1, maxcol = 0){
+  #skip: number of columns to skip
+  skip <- skip+1
+  maxcol<-ifelse(maxcol!=0, maxcol, ncol(dataframe))
+  for(i in skip:maxcol){
+    Q1<-quantile(dataframe[,i],0.25, na.rm = TRUE)
+    Q3<-quantile(dataframe[,i],0.75, na.rm = TRUE)
+    IQR<-abs(Q3-Q1)
+    upper_limit<-Q3 + 1.5*IQR
+    lower_limit<-Q1 - 1.5*IQR
+    print(paste0("Column: ", colnames(dataframe)[i], " \ Number of upper outliers: ",
+                 sum(dataframe[,i] > upper_limit, na.rm = TRUE), " \ Number of lower outliers: ",
+                 sum(dataframe[,i] < lower_limit, na.rm = TRUE)))
+    print(paste0("Outlier percentage: ", 
+                 round((sum(dataframe[,i] > upper_limit, na.rm = TRUE)+sum(dataframe[,i] < lower_limit, na.rm = TRUE))/
+                   sum(!is.na(dataframe[,i])), 2)*100, " %"))
+  }
+}
+
+check_outlier_3sd = function(dataframe, skip = 1, maxcol = 0){
+  #skip: number of columns to skip
+  skip <- skip+1
+  maxcol<-ifelse(maxcol!=0, maxcol, ncol(dataframe))
+  for(i in skip:maxcol){
+    mean<-mean(dataframe[,i], na.rm = TRUE)
+    sd<-sd(dataframe[,i], na.rm = TRUE)
+    upper_limit <- 3*sd+mean
+    lower_limit <- -3*sd+mean
+    print(paste0("Column: ", colnames(dataframe)[i], " \ Number of upper outliers: ",
+                 sum(dataframe[,i] > upper_limit, na.rm = TRUE), " \ Number of lower outliers: ",
+                 sum(dataframe[,i] < lower_limit, na.rm = TRUE)))
+    print(paste0("Outlier percentage: ", 
+                 round((sum(dataframe[,i] > upper_limit, na.rm = TRUE)+sum(dataframe[,i] < lower_limit, na.rm = TRUE))/
+                         sum(!is.na(dataframe[,i])), 2)*100, " %"))  }
+}
+
[…]

### 2021-08-06 Libraries/Functions_MC.R

@@ -1,0 +1,363 @@
+#Functions for Model calibration
+
+#Other functions needed
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+source("Functions_TG.R")
+
+#Library needed
+library(hydroGOF)
+
+# Dataframe operations -----------------------------------------------------
+
+remove_high_values = function(df, maxval, skip = 1){
+  skip = skip + 1
+  for(i in skip:ncol(df)){
+    df[,i][df[,i] > maxval[i-skip+1]] <- maxval[i-skip+1]
+  }
+  return(df)
+}
+
+date_col_WASA_out = function(df){
+  start <- as.Date(df$day[1]-1, origin = paste0(df$year[1], "-01-01"))
+  end <- as.Date(df$day[nrow(df)]-1, origin = paste0(df$year[nrow(df)], "-01-01"))
+  dates <- create_date_vector(lubridate::year(start), lubridate::year(end),
+                              lubridate::month(start), lubridate::month(end),
+                              lubridate::day(start), lubridate::day(end))
+  df$date <- dates
+  return(df)
+}
+
+load_WASA_results = function(path, IDs, dates){
+  #position<-c(0,7,13,19,25,35,45,55,68,81,91,101,111,121,131,141,155,169)
+  #widths<-diff(position)
+  columns<-c("Subasin-ID", "year", "day", "hour", "qlateral",
+             "transposition", "inflow", "evap",
+             "prec", "intake", "overflow",
+             "qbottom", "qout", "withdrawal", "elevation", "area", "volume")
+  files <- paste0(path, "/res_", IDs$ID,"_watbal.out")
+  data_list<-list()
+  for(i in 1:length(files)){
+    data_list[[i]]<-read.table(files[i], skip = 3, header = FALSE)
+    names(data_list[[i]]) <- columns
+  }
+  #Add the date column to the vector
+  for(i in 1:length(data_list[])){
+    data_list[[i]] <- date_col_WASA_out(data_list[[i]])
+  }
+  df <- create_main_dataframe(dates, data_list, IDs, timecol = 18, datacol = 17)
+  return(df)
+}
+
+sumx = function(x){ return(sum(x, na.rm = TRUE)) }
+
+monthly_scale = function(df, skip = 1, f = sum){
+  skip = skip + 1
[…]

### 2021-08-06 Libraries/Functions_TG.R

@@ -1,0 +1,94 @@
+#Functions to execute the time series generation
+
+create_date_vector = function(start_y, end_y, start_m = 01, end_m = 12, start_d = 01,
+                              end_d = 31){
+  start<-paste0(start_d, "/0",start_m,"/",start_y)
+  end<-paste0(end_d,"/",end_m,"/",end_y)
+  date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")
+  return(date)
+}
+
+create_data_list = function(path, names, skip = 6, f = read.table, s = ""){
+  #skip = 6 for the FUNCEME files in .txt
+  #skip = 1 for the volume observation values in .csv
+  #skip = 3 for WASA input files
+  
+  files<-list.files(path=path,full.names = T,recursive = TRUE)
+  data_list<-list()
+  for(i in 1:length(files)){
+    tryCatch(data_list[[i]]<-f(files[i],header = FALSE,
+                                 sep = s,col.names = names, skip = skip),
+             error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
+  }
+  return(list(files, data_list))
+}
+
+create_position_vector = function(files){
+  #Positions vector
+  for(i in 1:length(files)){
+    lines<-readLines(files[i],n = 6)
+    ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
+    name<-unlist(strsplit(lines[2], ":"))[2]
+    long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
+    lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
+    p<-data.frame(ID,name,long,lat)
+    if(i > 1) positions<-rbind(positions,p,make.row.names=FALSE)
+    else positions<-p
+  }
+  positions$ID<-paste0("St",positions$ID)
+  return(positions)
+}
+
+add_date_column = function(data_list){
+  #Creates a date column inside each station dataframe
+  for(i in 1:length(data_list[])){
+    d<-as.Date(paste0(data_list[[i]]$year,"-",data_list[[i]]$month,"-",
+                      data_list[[i]]$day))
+    data_list[[i]]$date<-d
+  }
+  return(data_list)
+}
+
+create_main_dataframe = function(date, data_list, positions, timecol = 5, datacol = 4){
+  main_dataframe<-data.frame(date)
+  index<-matrix(NA,ncol = 2,nrow = length(data_list[]))
+  j<-1
+  
[…]

### 2021-08-06 Libraries/Libraries.R

@@ -1,0 +1,23 @@
+#Libraries
+
+#General
+library(tictoc)
+library(rlist)
+library(tidyverse)
+
+#Pre-Processing for WASA
+#library(lumpR)
+
+#Visualization
+library(ggplot2)
+require(scales)
+library(gridExtra)
+library(plotly)
+library(hrbrthemes)
+
+#Georeferenced data
+library(deldir)
+library(sf)
+library(rgeos)
+library(rgdal)
+

### 2021-08-06 Main_code/Automatic_calibration.R

@@ -1,0 +1,183 @@
+#Automatic calibration
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_obs <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/Observed_volumes/volume_series_banabuiu_reservoirs_ID"
+path_baseline <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Output_Second_Run"
+path_save <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/Model_calibration/Iterations"
+path_performance <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/Model_calibration/Automatic_calibration/Performances"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+source("Functions_CO.R")
+source("Functions_MC.R")
+
+#Load the maximum capacities of the reservoirs
+path_maxcap <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Input/Reservoir/reservoir.dat"
+reservoirs <- read.table(path_maxcap, skip = 2, sep = "\t")
+maxcap <- reservoirs[,c(1,5)]
+names(maxcap) <- c('ID','max')
+maxcap[,2] <- maxcap[,2]*1000 #m3
+
+# Load the observations ---------------------------------------------------
+
+obs_input <- create_data_list(path_obs, c('date', 'volume'), skip = 1, f = read.csv, s = ",")
+date <- create_date_vector(1980, 2018)
+IDs <- data.frame(ID = gsub("\\..*","",basename(obs_input[[1]])))
+for(i in 1:length(obs_input[[2]])){
+  obs_input[[2]][[i]]$date <- change_date_format(obs_input[[2]][[i]]$date)
+}
+obs_df <- create_main_dataframe(date, obs_input[[2]], IDs, timecol = 1, datacol = 2)
+obs_df <- remove_high_values(obs_df, maxcap$max)
+obs_df <- monthly_scale(obs_df, f = sumx)
+
+# Load the baseline -------------------------------------------------------
+
+date <- create_date_vector(1980, 2018)
+base_df <- load_WASA_results(path_baseline, IDs, dates = date)
[…]

### 2021-08-06 Main_code/DRAFTS_IMPORTANT.R

@@ -1,0 +1,58 @@
+#New functions to create
+
+#Check stations who present negative values, print their names
+
+#Remove the stations which present negative values
+
+#Maxima analysis for precipitation data
+
+
+
+#Radiation: they could have values lower than 1000
+#place NA when it happens
+
+find_anomalous_stations(rad_input, 1000)
+
+replace_value = function(input_list, value){
+  j <- find_anomalous_stations(input_list, value)
+  if(j > 0){
+    for(i in 1:length(input_list[[2]])){
+      input_list[[2]][[i]]$data[input_list[[2]][[i]]$data < value] <- NA
+    }
+  }else{
+    print("There are no anomalous stations")
+  }
+  return(input_list)
+}
+
+rad_input_fix <- replace_value(rad_input_fix, 1000)
+
+
+for(i in 1:length(rad_input_fix[[2]])){
+  check_outlier_IQR(rad_input_fix[[2]][[i]], skip = 3)
+}
+
+
+rad_input_fix[[2]] <- add_date_column(rad_input_fix[[2]])
+
+
+
+plot_stations(rad_input_fix, 4, 5, label = "Radiation")
+
+rad_input[[2]] <- add_date_column(rad_input[[2]])
+plot_stations(rad_input, 4, 5, label = "Radiation")
+
+for(i in 1:length(rad_input[[2]])){
+  print(paste0("Station ", i))
+  check_outlier_3sd(rad_input[[2]][[i]], skip = 3)
+}
+
+
+for(i in 1:length(rad_input[[2]])){
+  print(paste0("Station ", i))
+  check_outlier_IQR(rad_input[[2]][[i]], skip = 3, 4)
+}
+
+for(i in 1:length(rad_input_fix[[2]])){
+  rad_input[[2]][[i]] <- remove_outlier_IQR(rad_input_fix[[2]][[i]], skip = 3)
+}

### 2021-08-06 Main_code/MODEL_CALIBRATION.R

@@ -1,0 +1,165 @@
+#Model calibration script
+# In this script, the evaluation of the model results will be performed
+
+# Definition of the evaluation indicators of the model's performance --------
+#The evaluation will be done on a monthly time scale
+
+## R2 (Coefficient of determination)
+
+## NSE (Nash-Sutcliffe efficiency)
+#N.B.: Calculated on the discharge. Ask for this data
+#In the meantime use it on the volume data as well
+#NSE_index wil be a vector containing the NSE for each column
+
+## PBIAS (% of bias)
+#PBIAS wil be a vector containing the NSE for each column
+
+## KGE (Kling-Gupta Efficiency)
+#N.B.: same as NSE
+#KGE_index wil be a vector containing the NSE for each column
+
+## RMSE and NRMSE
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_obs <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/Observed_volumes/volume_series_banabuiu_reservoirs_ID"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+source("Functions_CO.R")
+source("Functions_MC.R")
+
+#Load the maximum capacities of the reservoirs
+path_maxcap <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Input/Reservoir/reservoir.dat"
+reservoirs <- read.table(path_maxcap, skip = 2, sep = "\t")
+maxcap <- reservoirs[,c(1,5)]
+names(maxcap) <- c('ID','max')
+maxcap[,2] <- maxcap[,2]*1000 #m3
+
+# Load the observations and place them in a dataframe ---------------------
+
+obs_input <- create_data_list(path_obs, c('date', 'volume'), skip = 1, f = read.csv, s = ",")
+date <- create_date_vector(1980, 2018)
+IDs <- data.frame(ID = gsub("\\..*","",basename(obs_input[[1]])))
+for(i in 1:length(obs_input[[2]])){
+  obs_input[[2]][[i]]$date <- change_date_format(obs_input[[2]][[i]]$date)
+}
[…]

### 2021-08-06 Main_code/comparison.R

@@ -1,0 +1,72 @@
+#Comparison
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+
+#Load Banabuiu reservoirs' names and IDs
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
+reservoirs<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
+
+
+# Visual comparison -------------------------------------------------------
+
+#Load what you want to compare
+
+path_import1 <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
+path_import2 <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Input/Time_series"
+columns <- c("date", "doy", 123, 125, 126, 127, 134, 137, 138, 139, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152, 153, 154, 155, 156, 157, 158, 159, 160)
+
+rad_gen_F<-read.table(paste0(path_import1, "/radiation_FUNCEME_1706.dat"), skip = 3)
+rad_gen_I<-read.table(paste0(path_import1, "/radiation_INMET_1706.dat"), skip = 3)
+rad_alex<-read.table(paste0(path_import2,"/radiation.dat"),skip = 3)
+
+names(rad_alex) <- names(rad_gen_F) <- names(rad_gen_I) <- columns
+
+rad_gen_F <- rad_gen_F[1:9711,]
+rad_gen_I <- rad_gen_I[1:9711,]
+rad_alex <- rad_alex[3805:nrow(rad_alex),]
+
+#Since Alexandre's time series end in 2016, we need to cut the generated time series
+
+#Plots
+
+time_index<-seq(as.Date("1990-01-01"),as.Date("2016-08-02"),by="days")
+for(i in 1:nrow(reservoirs)){
+  #Creation of the dataset for the visualization
+  n<-i+2
+  visual1<-data.frame(rad_alex[,n],rep("Alexandre",length(rad_alex[,n])),time_index)
+  names(visual1)<-c("data","id","time")
[…]

### 2021-08-06 Main_code/comparison_new.R

@@ -1,0 +1,225 @@
+#Script to visualize the generated time series and then compare them with
+#Alexandre's ones
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_input_gen <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/gen_2006"
+path_input_alex <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/Alex_Time_series"
+columns <- c("date", "doy", "ID123", "ID125", "ID126", "ID127", "ID134", "ID137", "ID138", "ID139", "ID142", "ID143", "ID144", "ID145", "ID146", "ID147", "ID148", "ID149", "ID150", "ID151", "ID152", "ID153", "ID154", "ID155", "ID156", "ID157", "ID158", "ID159", "ID160")
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+source("Functions_CO.R")
+
+# Load the generated time series ------------------------------------------
+
+prec_gen_F <- read.table(paste0(path_input_gen, "/precipitation_FUNCEME_2006.dat"), skip = 3); names(prec_gen_F) <- columns
+temp_gen_F <- read.table(paste0(path_input_gen, "/temperature_FUNCEME_2006.dat"), skip = 3); names(temp_gen_F) <- columns
+temp_gen_I <- read.table(paste0(path_input_gen, "/temperature_INMET_2006.dat"), skip = 3); names(temp_gen_I) <- columns
+hum_gen_F <- read.table(paste0(path_input_gen, "/hum_FUNCEME_2006.dat"), skip = 3); names(hum_gen_F) <- columns
+hum_gen_I <- read.table(paste0(path_input_gen, "/hum_INMET_2006.dat"), skip = 3); names(hum_gen_I) <- columns
+rad_gen_I <- read.table(paste0(path_input_gen, "/radiation_INMET_2006.dat"), skip = 3); names(rad_gen_I) <- columns
+
+prec_gen_F$date <- change_date_WASA_input(prec_gen_F$date)
[…]

### 2021-08-06 Main_code/create_time_series.R

@@ -1,0 +1,48 @@
+create_time_series = function(main_dataframe, positions, layer, dates){
+  #main_dataframe: the main dataframe with all stations observations
+  #positions: the dataframe containing the positions of the stations
+  #layer: the layer to superimpose to the Voronoi diagram
+  #dates: vector containing the dates to consider when creating the output
+  
+  output<-data.frame(matrix(NA, nrow = length(dates),
+                            ncol=2+length(layer@data$SubbasinID)))
+  names(output)<-c("date","number of days",t(layer@data$SubbasinID))
+  j<-1
+  
+  #Boundaries of the Voronoi diagram
+  corners<-c(-41.64, -37.26, -7.85, -2.78) #(xmin, xmax, ymin, ymax)
+  
+  for(i in 1:nrow(main_dataframe)){
+    #Extract the data for the ith day
+    first<-main_dataframe[i,which(!is.na(main_dataframe[i,]))]
+    if(!is.null(dim(first)[1]) && dim(first)[2] > 2){
+      #Extract the positions of the stations and associate them to the data
+      col<-colnames(first); col<-col[2:length(col)]
+      second<-first[,2:ncol(first)]
+      shape<-data.frame(t(second),
+                        positions$long[which(positions$ID %in% col)],
+                        positions$lat[which(positions$ID %in% col)])
+      names(shape)<-c("data","long","lat")
+      
+      #Create the Voronoi diagram
+      thiessen<-voronoipolygons(shape, corners=corners)
+      proj4string(thiessen)<-CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+      thiessen <- spTransform(thiessen, raster::crs(layer))
+      #summary(thiessen)
+      
+      #Overlay the layer layer to extract the mean precipitation
+      #over function: at the spatial locations of object x retrieves the indexes
+      #or attributes from spatial object y
+      data_sub<-over(layer, thiessen, fn=mean)
+      
+      #Save the values in a pre-made data.frame
+      output[j,3:ncol(output)]<-t(data_sub[,3])
+    }else if(!is.null(dim(first)[1]) && dim(first)[2] == 2){
+      output[j,3:ncol(output)]<-rep(first[,2],length(output[j,3:ncol(output)]))
+    }
+    j <- j+1
+  }
+  output
+}
+
+

### 2021-08-06 Main_code/download_DEM.R

@@ -1,0 +1,8 @@
+#Script to download the DEM of the Banabuiu basin
+
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/NASA_DEM/1112536144-download.txt"
+links<-read.table(path)
+for(i in 1:nrow(links)){
+  browseURL(links[i,1])
+}
+

### 2021-08-06 Main_code/intake_generation.R

@@ -1,0 +1,87 @@
+#intake.dat generation
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+
+# Load files --------------------------------------------------------------
+
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/waterdrawal_banabuiu_basin/renamed"
+index_files <- data.frame(list.files(path = path, full.names = T, recursive = TRUE))
+names(index_files) <- "path"
+index_files$SubbasinID <- gsub("\\..*","",basename(index_files$path))
+
+withdrawal_list<-list()
+for(i in 1:nrow(index_files)){
+  name<-paste0("res_",index_files$SubbasinID[i])
+  withdrawal_list[[name]]<-read.csv(index_files$path[i], header = TRUE, sep = ",")
+}
+
+#Change the format of the date column to date
+for(i in 1:length(withdrawal_list[])){
+  withdrawal_list[[i]][["date"]] <- as.Date(withdrawal_list[[i]][["date"]])
+}
+
+#Check the percentage of NAs in the observations
+for(i in 1:length(withdrawal_list[])){
+  print(sum(is.na(withdrawal_list[[i]]$flow))/length(withdrawal_list[[i]]$flow))
+}
+
+# Create the dataframe ----------------------------------------------------
+
+#Specify the date range
+#Create the date vector
+start_y <- 1980
+end_y <- 2018
+start_m <- 01
+end_m <- 12
+start<-paste0("01/0",start_m,"/",start_y)
+end<-paste0("31/",end_m,"/",end_y)
+date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")
+
+#Create the dataframe
+withdrawal_df<-data.frame(date)
+withdrawal_df$doy<-NA
+
+for(i in 1:length(withdrawal_list[])){
+  new_v<-sistemadati_DCA(vettore = withdrawal_list[[i]], lung = nrow(withdrawal_df), g = date,
+                         coltime = 1, coldata = 2)
+  withdrawal_df$new<-new_v[,2]
+  names(withdrawal_df)[names(withdrawal_df) == "new"]<-index_files$SubbasinID[i]
+}
+
[…]

### 2021-08-06 Main_code/mod_cal.R

@@ -1,0 +1,188 @@
+#Model calibration
+# "Active" script, to operate a semi-automatic model calibration
+# The scaling factors of the subbasins can be changed through modify_scaling_factor,
+# which will create a new file with the selected parameters
+# 
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_obs <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/Observed_volumes/volume_series_banabuiu_reservoirs_ID"
+path_baseline <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Output_baseline_left_end"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+source("Functions_CO.R")
+source("Functions_MC.R")
+
+#Load the maximum capacities of the reservoirs
+path_maxcap <- "C:/Thesis_fortran/Directory_WASA_Banabuiu/Input/Reservoir/reservoir.dat"
+reservoirs <- read.table(path_maxcap, skip = 2, sep = "\t")
+maxcap <- reservoirs[,c(1,5)]
+names(maxcap) <- c('ID','max')
+maxcap[,2] <- maxcap[,2]*1000 #m3
+
+# Load the observations ---------------------------------------------------
+
+obs_input <- create_data_list(path_obs, c('date', 'volume'), skip = 1, f = read.csv, s = ",")
+date <- create_date_vector(1980, 2018)
+IDs <- data.frame(ID = gsub("\\..*","",basename(obs_input[[1]])))
+for(i in 1:length(obs_input[[2]])){
+  obs_input[[2]][[i]]$date <- change_date_format(obs_input[[2]][[i]]$date)
+}
+obs_df <- create_main_dataframe(date, obs_input[[2]], IDs, timecol = 1, datacol = 2)
+obs_df <- remove_high_values(obs_df, maxcap$max)
+obs_df <- monthly_scale(obs_df, f = sumx)
+
+# Load the baseline and its performance ---------------------------------------
+
+date <- create_date_vector(1980, 2018)
+base_df <- load_WASA_results(path_baseline, IDs, dates = date)
+base_df <- remove_high_values(base_df, maxcap$max)
[…]

### 2021-08-06 Main_code/output_na_removal.R

@@ -1,0 +1,100 @@
+#Outlier removal and NA filling for the generated time series
+
+# Setup ---------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/processed"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_DP.R")
+
+starting_date<-"1990-01-01"
+ending_date<-"2018-12-31"
+time_index<-seq(as.Date(starting_date),as.Date(ending_date),by="days")
+
+# Load the generated time series ------------------------------------------
+#Load, assign the column names and change the date format
+
+path_import <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
+columns <- c("date", "doy", 123, 125, 126, 127, 134, 137, 138, 139, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152, 153, 154, 155, 156, 157, 158, 159, 160)
+
+prec <- read.table(paste0(path_import, "/precipitation_FUNCEME_1706.dat"), skip = 3)
+names(prec) <- columns
+prec$date<-time_index
+temp_I <- read.table(paste0(path_import, "/temperature_INMET_1706.dat"), skip = 3)
+names(temp_I) <- columns
+temp_I$date<-time_index
+temp_F <- read.table(paste0(path_import, "/temperature_FUNCEME_1706.dat"), skip = 3)
+names(temp_F) <- columns
+temp_F$date<-time_index
+temp_B <- read.table(paste0(path_import, "/temperature_BOTH_1706.dat"), skip = 3)
+names(temp_B) <- columns
+temp_B$date<-time_index
+hum <- read.table(paste0(path_import, "/humidity_1706.dat"), skip = 3)
+names(hum) <- columns
+hum$date<-time_index
+rad_F <- read.table(paste0(path_import, "/radiation_FUNCEME_1706.dat"), skip = 3)
+names(rad_F) <- columns
+rad_F$date<-time_index
[…]

### 2021-08-06 Main_code/prec_out_rem.R

@@ -1,0 +1,159 @@
+# Precipitation outlier analyisis ------------------------------------------
+#Since precipitation data has a skewed distribution, expecially in semi-arid
+#areas as North-East Brazil, a normal outlier rejection wouldn't work properly.
+#Here an analysis on the maxima is performed in order to define a threshold
+#above which an observation can be considered as an outlier.
+
+# Results:
+#The threshold for the outlier detection has been put equal 250 mm,
+#an approximated estimation of the 100 years return period in
+#Rodrigues, D. T. et al. Spatial distribution of the level of return of extreme precipitation events in Northeast Brazil. (2020)
+#doi:10.1002/joc.6507.
+#So:
+#   - Stations with exceptionally high outliers have been completely removed from
+#     the dataframe, considering them not reliable
+#   - Singular observations above this threshold have been removed from the dataframe
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+
+
+# Precipitation FUNCEME ---------------------------------------------------
+
+#Load the stations
+path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
+prec_input = create_data_list(path, c("year","month","day","data"))
+
+#Check and remove the stations which present negative values
+n <- find_anomalous_stations(prec_input)
+if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
+
+#Create a dataframe to plot the stations data and check anomalous behaviour
+date <- create_date_vector(1980, 2018)
+prec_pos <- create_position_vector(prec_input[[1]])
+prec_input[[2]] <- add_date_column(prec_input[[2]])
+prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
+f<-2
+l<-21
+for(i in 1:round(ncol(prec_df)/20)){
+  vis_prec <- data.frame(prec_df$date, prec_df[,f:l])
[…]

### 2021-08-06 Main_code/radiation_cleaning.R

@@ -1,0 +1,31 @@
+#Radiation dataset cleaning
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_DP.R")
+source("Functions_TG.R")
+source("Functions_CO.R")
+
+# Load the precipitation time series --------------------------------------
+
+path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/WASA_Time_Series"
+rad <- read.table(paste0(path, "/radiation.dat"), skip = 3)
+columns <- c("date", "n_days", "ID123", "ID125", "ID126", "ID127", "ID134", "ID137", "ID138", "ID139", "ID142", "ID143", "ID144", "ID145", "ID146", "ID147", "ID148", "ID149", "ID150", "ID151", "ID152", "ID153", "ID154", "ID155", "ID156", "ID157", "ID158", "ID159", "ID160")
+names(rad) <- columns
+rad$date <- change_date_WASA_input(rad$date)
+
+
+# Visualize the data and find the anomalous subbasins ---------------------
+
+plot_subbasins_df(rad, y = "W/m2", label = "Radiation INMET - All subbasins",
+                  interactive = TRUE, file = "radiation_anomalies")
+#All subbasins present anomalies
+
+# Remove the anomalies ----------------------------------------------------
+
+
+

### 2021-08-06 Main_code/rainy_season_update.R

@@ -1,0 +1,91 @@
+#rainy_season.dat update
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_CO.R")
+
+# Load the precipitation time series --------------------------------------
+
+path <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/WASA_Time_Series"
+prec <- read.table(paste0(path, "/rain_daily.dat"), skip = 3)
+columns <- c("date", "n_days", "ID123", "ID125", "ID126", "ID127", "ID134", "ID137", "ID138", "ID139", "ID142", "ID143", "ID144", "ID145", "ID146", "ID147", "ID148", "ID149", "ID150", "ID151", "ID152", "ID153", "ID154", "ID155", "ID156", "ID157", "ID158", "ID159", "ID160")
+names(prec) <- columns
+prec$date <- change_date_WASA_input(prec$date)
+
+
+# Compute the rainy season file -------------------------------------------
+#For each subbasin, extract the first day of the year with precipitation > 0
+#and the last day of the year with precipitation > 0, for each year
+
+df <- prec
+i<-skip
+j<-1
+
+get_rainy_season = function(df, years, date_col = 1, skip = 2){
+  #The rainy season in North-East Brazil goes from January to June.
+  #This function will extract the first occurrence of rain in January and the last
+  #occurrence of rain in June for the precipitation data in input (df).
+  #If no rain is found in January, the first day is searched in the following
+  #months. If no rain is found in June, the last day is searched in the previous
+  #months.
+  
+  start_m <- 1 #January
+  end_m <- 6 #June
+  skip <- skip + 1
+  rainy_season <- data.frame(rep(colnames(df)[skip:ncol(df)], length(years)),
+                             year = 0, start_30 = 0, start = 0, end = 0, end_30 = 0)
+  names(rainy_season) <- c('ID', 'year', 'start_30', 'start', 'end', 'end_30')
+  k <- 1
+  for(j in 1:length(years)){
+    for(i in skip:ncol(df)){
+      v <- df[which(lubridate::year(df[,date_col]) == years[j] &
[…]

### 2021-08-06 Main_code/stations_outlier_removal.R

@@ -1,0 +1,331 @@
+#Stations outliers rejection experiments and analysis
+#In this script the qualitative and quantitative analysis on the outlier rejection
+#are made in order to obtain:
+# - Which one of the methods to use to remove the outliers (IQR or 3sd)
+# - How many iterations to make in order to obtain a satisfactory clean dataset (n)
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+
+
+# Temperature INMET -------------------------------------------------------
+
+path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/t2m_INMET"
+temp_input = create_data_list(path, c("year","month","day","data"))
+
+#Check and remove the stations which present negative values
+n <- find_anomalous_stations(temp_input)
+if(n > 0) temp_input <- remove_anomalous_stations(temp_input)
+
+#Create a dataframe to plot the stations data to check anomalous behavior
+date <- create_date_vector(2005, 2018)
+temp_pos <- create_position_vector(temp_input[[1]])
+temp_input[[2]] <- add_date_column(temp_input[[2]])
+temp_df <- create_main_dataframe(date, temp_input[[2]], temp_pos)
+plot_stations_df(temp_df, y = "°C", label = "INMET Temperature Stations")
+#St168 and St590 have values ranging around 20°C for all the time series
+#This seem an anomalous behaviour, let's check where these stations are in the region
+
+#Export a shapefile of the stations positions to visualize the stations in QGIS
+shape_temp <- temp_pos
+coordinates(shape_temp)=~long+lat
+proj4string(shape_temp)<- CRS("+proj=longlat +datum=WGS84")
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/prove_shape"
[…]

### 2021-08-06 Main_code/temp_func_inmet.R

@@ -1,0 +1,123 @@
+#Temperature with only FUNCEME stations
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")
+
+for(kk in 1:2){
+if(kk == 1){
+  #FUNCEME dataset
+  input<-list.files(path="./Meteorological_stations_FUNCEME/t2m_FUNCEME",full.names = T,recursive = TRUE)
+  
+  temp_input<-list()
+  for(i in 1:length(input)){
+    tryCatch(temp_input[[i]]<-read.table(input[i],header = FALSE,
+                                         sep = "",col.names = c("year","month","day","data"),
+                                         skip=6),
+             error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
+  }
+}else{
+  #INMET dataset
+  input<-list.files(path="./Meteorological_stations_FUNCEME/t2m_INMET",full.names = T,recursive = TRUE)
+  
+  temp_input<-list()
+  for(i in 1:length(input)){
+    tryCatch(temp_input[[i]]<-read.table(input[i],header = FALSE,
+                                         sep = "",col.names = c("year","month","day","data"),
+                                         skip=6),
+             error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
+  }
+}
+
+#Positions vector
+for(i in 1:length(input)){
+  lines<-readLines(input[i],n = 6)
+  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
+  name<-unlist(strsplit(lines[2], ":"))[2]
+  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
+  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
+  p<-data.frame(ID,name,long,lat)
+  if(i > 1) positions_temp<-rbind(positions_temp,p,make.row.names=FALSE)
+  else positions_temp<-p
+}
+positions_temp$ID<-paste0("St",positions_temp$ID)
+
+#Unified dataframe
+
+start_y <- 1980
+end_y <- 2020
+start_m <- 01
+end_m <- 12
+
+start<-paste0("01/0",start_m,"/",start_y)
+end<-paste0("31/",end_m,"/",end_y)
+date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")
+
[…]

### 2021-08-06 Main_code/temperature_visual.R

@@ -1,0 +1,62 @@
+#Temperature comparison between FUNCEME, INMET, both and Alexandre
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+
+source("Libraries.R")
+source("Functions.R")
+
+#Load Banabuiu reservoirs' names and IDs
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
+reservoirs<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
+
+#Upload
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/output_time_series_gen"
+temp_gen_both<-read.table(paste0(path,"/output_temp_save_v2.txt"), header = TRUE, sep = "\t")
+temp_gen_FUNCEME<-read.table(paste0(path,"/output_temp_FUNCEME.txt"), header = TRUE, sep = "\t")
+temp_gen_INMET<-read.table(paste0(path,"/output_temp_INMET.txt"), header = TRUE, sep = "\t")
+
+path<-"C:/Thesis_fortran/WASA/Input/Time_series"
+temp_alex<-read.table(paste0(path,"/temperature.dat"),skip = 3)
+temp_gen_both<-temp_gen_both[1:11323,]
+temp_gen_FUNCEME<-temp_gen_FUNCEME[1:11323,]
+temp_gen_INMET<-temp_gen_INMET[1:11323,]
+temp_alex<-temp_alex[1:11323,] #end in 2010
+
+#Plots
+time_index<-seq(as.Date("1980-01-01"),as.Date("2010-12-31"),by="days")
+for(i in 1:nrow(reservoirs)){
+  #Creation of the dataset for the visualization
+  n<-as.numeric(reservoirs$SubbasinID[i])+2
+  visual1<-data.frame(temp_alex[,n],rep("Alexandre",length(temp_alex[,n])),time_index)
+  names(visual1)<-c("data","id","time")
+  visual2<-data.frame(temp_gen_both[,n],rep("Both stations",length(temp_gen_both[,n])),time_index)
+  names(visual2)<-c("data","id","time")
+  visual3<-data.frame(temp_gen_FUNCEME[,n],rep("FUNCEME",length(temp_gen_FUNCEME[,n])),time_index)
+  names(visual3)<-c("data","id","time")
[…]

### 2021-08-06 Main_code/test_over_function.R

@@ -1,0 +1,115 @@
+#Test on the over function to create the time series
+
+#Create the file list
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara")
+
+#FUNCEME dataset
+input<-list.files(path="./Meteorological_stations_FUNCEME/precipitation_subset",full.names = T,recursive = TRUE)
+
+prec_input<-list()
+for(i in 1:length(input)){
+  tryCatch(prec_input[[i]]<-read.table(input[i],header = FALSE,
+                                       sep = "",col.names = c("year","month","day","data"),
+                                       skip=6),
+           error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
+}
+
+#Create the position vector
+#Positions vector
+for(i in 1:length(input)){
+  lines<-readLines(input[i],n = 6)
+  ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
+  name<-unlist(strsplit(lines[2], ":"))[2]
+  long<-as.numeric(unlist(strsplit(lines[5], ":"))[2])
+  lat<-as.numeric(unlist(strsplit(lines[6], ":"))[2])
+  p<-data.frame(ID,name,long,lat)
+  if(i > 1) positions_prec<-rbind(positions_prec,p,make.row.names=FALSE)
+  else positions_prec<-p
+}
+positions_prec$ID<-paste0("St",positions_prec$ID)
+remove(lines, ID, name, long, lat, p, input)
+
+#Upload the main dataframe of precipitation data
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/main_datasets"
+main_dataframe_prec<-read.table(paste0(path,"/main_dataframe_precipitation_opt_v2.txt"),
+                                header = TRUE, sep="\t")
+
+#Import of the subbasins shapefile
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/streamgauges/Subbasins_geomfix.shp"
+subbasins<-readOGR(path)
+
+main_dataframe = main_dataframe_prec
+positions = positions_prec
+layer = subbasins
+dates = date
+
+  #main_dataframe: the main dataframe with all stations observations
+  #positions: the dataframe containing the positions of the stations
[…]

### 2021-08-06 Main_code/time_series_generation_script.R

@@ -1,0 +1,178 @@
+#Time series generation script
+
+# Setup ---------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/gen_2006"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+
+#Load the subbasins' shapefile
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
+subbasins<-readOGR(paste0(path,"/subbasins_cut_geomfix.shp"))
+
+# Precipitation FUNCEME ----------------------------------------------------
+
+#Load the stations
+path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
+prec_input = create_data_list(path, c("year","month","day","data"))
+
+#Remove anomalous stations (more information: "prec_out_rem.R")
+n <- find_anomalous_stations(prec_input)
+if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
+date <- create_date_vector(1980, 2018)
+prec_pos <- create_position_vector(prec_input[[1]])
+prec_input[[2]] <- add_date_column(prec_input[[2]])
+prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
+#Other anomalous stations removal (more information: "prec_out_rem.R")
+remove_st <- anomalous_prec_st(prec_df, 250)
+prec_df <- prec_df[-remove_st]
+#Outlier removal (more information: "prec_out_rem.R")
+prec_df <- rejection_threshold(prec_df, method = "value", 250)
+
+tic("Precipitation FUNCEME - Creation of the WASA input file")
+output_prec <- create_time_series_Wmean(main_dataframe = prec_df,
+                                        positions = prec_pos,
+                                        layer = subbasins)
[…]

### 2022-03-02 Data/Germanos/AL_scenarios_DCA.m
general update

@@ -1,0 +1,276 @@
+%% Plotagem
+clc
+clear all
+close all
+%% Files
+% drought_event - a struct variable with the basic information of the analyzed drought events 
+% %% Input 
+%load('Ciclo_Seca')
+% % vd_r017_nt - Volume Defict of the scenario without small reservoirs of the analyzed reservoir for the whole study period
+% % vd_r017_ob - Volume Defict of the scenario with small reservoirs of the analyzed reservoir for the whole study period
+% % CS - Structured variable that shows, for each drought event, in which quadrant of the DCA the pair of variables (SPI and VD) was in each month.
+% % data_reserv_completa - date variable (in the format Y, M ,D)
+
+load('AL_Scenarios.mat')
+
+%% Scale the VD
+%The VD is automatically scaled
+
+%a = -2.7;
+%b = 2.7;
+%spi = (b-a)*(spi - min(spi))/(max(spi) - min(spi)) + a;
+%vd_r017_nt = (b-a)*(vd_r017_nt - min(vd_r017_nt))/(max(vd_r017_nt) - min(vd_r017_nt)) + a;
+%vd_r017_ob = (b-a)*(vd_r017_ob - min(vd_r017_ob))/(max(vd_r017_ob) - min(vd_r0 17_ob)) + a;
+
+%% Drought Event 
+drought_event{1,1}=[datenum([1992 01 1]) datenum([1994 08 01])];  % First and last date of each drought event
+drought_event{2,1}=[datenum([1997 01 1]) datenum([2002 06 01])];  % First and last date of each drought event
+drought_event{3,1}=[datenum([2010 01 1]) datenum([2018 12 01])];  % First and last date of each drought event
+%% Selected dates of each drouhgt event to be ploted in the DCA with the marks (circles and stars that appear in the chart)
+% First drought event
+drought_event{1,2}(1,:)=[1992 04 01]; 
+drought_event{1,2}(2,:)=[1993 05 01];
+drought_event{1,2}(3,:)=[1994 08 01];
+% Second drought event
[…]

### 2022-03-02 Data/Germanos/DCA_plot_thesis.m

@@ -10,7 +10,7 @@ clear all
 % % CS - Structured variable that shows, for each drought event, in which quadrant of the DCA the pair of variables (SPI and VD) was in each month.
 % % data_reserv_completa - date variable (in the format Y, M ,D)
  
-load('new_data.mat')
+load('AL_data.mat')
 
 %% Scale the VD
 %The VD is automatically scaled
@@ -22,32 +22,32 @@ load('new_data.mat')
 %vd_r017_ob = (b-a)*(vd_r017_ob - min(vd_r017_ob))/(max(vd_r017_ob) - min(vd_r017_ob)) + a;
 
 %% Drought Event 
-drought_event{1,1}=[datenum([1992 5 1]) datenum([1994 08 01])];  % First and last date of each drought event
-drought_event{2,1}=[datenum([1997 10 1]) datenum([2002 6 01])];  % First and last date of each drought event
-drought_event{3,1}=[datenum([2010 01 1]) datenum([2018 12 01])]; % First and last date of each drought event
+drought_event{1,1}=[datenum([1992 01 1]) datenum([1994 08 01])];  % First and last date of each drought event
+drought_event{2,1}=[datenum([1997 01 1]) datenum([2002 06 01])];  % First and last date of each drought event
+drought_event{3,1}=[datenum([2010 01 1]) datenum([2018 12 01])];  % First and last date of each drought event
 %% Selected dates of each drouhgt event to be ploted in the DCA with the marks (circles and stars that appear in the chart)
 % First drought event
-drought_event{1,2}(1,:)=[1992 06 01]; 
-drought_event{1,2}(2,:)=[1993 06 01];
+drought_event{1,2}(1,:)=[1992 04 01]; 
+drought_event{1,2}(2,:)=[1993 05 01];
 drought_event{1,2}(3,:)=[1994 08 01];
 % Second drought event
-drought_event{2,2}(1,:)=[2001 12 01];
-drought_event{2,2}(2,:)=[1998 05 01];
+drought_event{2,2}(1,:)=[1997 05 01];
+drought_event{2,2}(2,:)=[1998 03 01];
 drought_event{2,2}(3,:)=[1999 05 01];
[…]

### 2022-03-02 Drafts/check_156_vd.R

@@ -1,0 +1,34 @@
+table1 <- data.frame(matrix(NA, 5, 3))
+names(table1) <- c("real", "noH", "obs")
+for(i in 1:4){
+  table1$real[i] <- sum(DCA_real[["156"]]$quadrant == i, na.rm = TRUE)
+  table1$noH[i] <- sum(DCA_noH[["156"]]$quadrant == i, na.rm = TRUE)
+  table1$obs[i] <- sum(DCA_obs[["156"]]$quadrant == i, na.rm = TRUE)
+}
+table1[5, ] <- apply(table1, 2, function(x) sum(x, na.rm = TRUE))
+View(table1)
+
+table2 <- table1/table1[5,1]
+table2$obs <- table1$obs/table1[5,3]
+View(table2)
+#The observations have less actual months in drought phases both totally and relatively
+#but the behavior is the same
+
+table2$obs <- NULL
+table2 <- round(table2, 2)
+table2$real_tot <- table1$real
+table2$noH_tot <- table1$noH
+#Re-order the columns
+table2 <- table2[, c(3,4,1,2)]
+names(table2) <- c("real_tot", "noH_tot", "real_perc", "noH_perc")
+
+write.table(table2, file = "./Data/Plot_table/cumulative_phases_156.txt", sep = "\t", quote = FALSE, 
+            row.names = TRUE)
+
+
+df <- data.frame(date = DCA_real[["156"]]$date, real = DCA_real[["156"]]$WSI, noH = DCA_noH[["156"]]$WSI)
+plot_df_interactive(df)
+
+df <- data.frame(date = DCA_real[["Banabuiu"]]$date, real = DCA_real[["Banabuiu"]]$WSI, noH = DCA_noH[["Banabuiu"]]$WSI)
+plot_df_interactive(df)
+

### 2022-03-02 Drafts/spaghetti_plot.R

@@ -1,0 +1,32 @@
+# Libraries
+library(tidyverse)
+library(hrbrthemes)
+library(kableExtra)
+options(knitr.table.format = "html")
+library(babynames)
+library(streamgraph)
+library(viridis)
+library(DT)
+library(plotly)
+
+# Load dataset from github
+data <- babynames %>% 
+  filter(name %in% c("Mary","Emma", "Ida", "Ashley", "Amanda", "Jessica",    "Patricia", "Linda", "Deborah",   "Dorothy", "Betty", "Helen")) %>%
+  filter(sex=="F")
+
+tmp <- data %>%
+  mutate(name2=name)
+
+tmp %>%
+  ggplot( aes(x=year, y=n)) +
+  geom_line( data=tmp %>% dplyr::select(-name), aes(group=name2), color="grey", size=0.5, alpha=0.5) +
+  geom_line( aes(color=name), color="#69b3a2", size=1.2 )+
+  scale_color_viridis(discrete = TRUE) +
+  theme_ipsum() +
+  theme(
+    legend.position="none",
+    plot.title = element_text(size=14),
+    panel.grid = element_blank()
+  ) +
+  ggtitle("A spaghetti chart of baby names popularity") +
+  facet_wrap(~name)

### 2022-03-02 Drafts/spatial_DCA_draft.R

@@ -1,0 +1,75 @@
+#Spatial DCA
+#Drafts and trials to obtain the network chart
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+
+#igraph
+library("igraph")
+
+#ggnet
+library(GGally)
+library(network)
+library(sna)
+library(ggplot2)
+
+
+# Network chart -----------------------------------------------------------
+
+links <- data.frame(
+  source = c(154, 153, 150, 145, 149, 155, 146, 144,
+             142, 157, 158, 151, 152, 159, 148, 147, 143, 160),
+  target = c(150, 149, 155, 155, 144, 144, 156, 156,
+             157, 160, 160, 160, 159, 160, 143, 143, 156, 143)
+)
+
+#igraph
+network <- graph_from_data_frame(d = links, directed = F)
+plot(layout_nicely(network))
+plot(network)
+
+#ggnet
+net <- network(links, directed = TRUE)
+ggnet2(net)
+
+ggnet2(net, mode = "kamadakawai")
+
+left_branch <- c(154, 150, 145, 155,
+                 153, 149, 144,
+                 127, 123,
+                 146, 156,
+                 126,
+                 125,
+                 138)
+right_branch <- c(142, 157,
+                  158,
+                  151,
+                  152, 159, 160,
+                  148,
+                  147,
+                  143, 156) #re-calibration of 156 after the results of the right branch
+subbasins <- c(left_branch, right_branch)
+no_res_sub <- c(134, 137, 139, 144, 155, 157, 158, 159)
+
+links_res <- data.frame(
+  source = c(154, 153, 145, 149, 146, 150,
+             142, 151, 152, 148, 147, 160, 143),
+  target = c(150, 149, 156, 156, 156, 156,
+             160, 160, 160, 143, 143, 143, 156)
+)
+net <- network(links_res, directed = TRUE)
+ggnet2(net)
+
+# Map ---------------------------------------------------------------------
+
+install.packages("cartography")
+library(cartography)
+library(rgdal)
+
+subbasins<-readOGR("./Data/Shapefile/subbasins_cut_geomfix.shp")
+
+
+
+

### 2022-03-02 Drafts/stored_volume.R

@@ -1,0 +1,89 @@
+
+load("./Data/Downstreamness/Dsv_r.Rdata")
+load("./Data/Downstreamness/HDNR_vol_mean.Rdata")
+load("./Data/Scenarios/Real/real_daily.RData")
+load("./Data/Scenarios/No_HDNR/noH_daily.RData")
+
+real_df <- monthly_scale(df = real_df, f = mean)
+noH_df <- monthly_scale(df = noH_df, f = mean)
+
+HDNR_vol <- apply(HDNR_vol_mean[, 2:ncol(HDNR_vol_mean)], 1, sumx)
+res_r_vol <- apply(real_df[, 2:ncol(real_df)], 1, sumx)
+res_nH_vol <- apply(noH_df[, 2:ncol(noH_df)], 1, sumx)
+
+#Stored volume
+SV_R <- HDNR_vol + res_r_vol
+SV_nH <- res_nH_vol
+df <- data.frame(date = Dsv_r$date, Real = SV_R, noHDNR = SV_nH) #, hdnr = HDNR_vol*500)
+#plot_df_interactive(df, t = 'Stored volumes')
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+
+date_ranges <- date_ranges_SPI
+ylabel <- (expression(paste("Stored Volume (monthly mean) [ ",m^3," ]", sep="")))
+p <- ggplot() +
+  #Add the drought rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
+  #Add the Stored volume lines
+  geom_line(data = df, aes(x = date, y = value, linetype = Scenario), alpha = 0.5, size = 1.25) +
+  scale_y_continuous(name = ylabel) + #, limits = c(-1, 1)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  theme(axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12))
+
+print(p)
+
+#add 
+
+
+
+df <- data.frame(date = Dsv_r$date, centr = res_r_vol,
+                 hdnrX100 = HDNR_vol*100, centr_noH = res_nH_vol,
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/allocate_h.f90

@@ -1,0 +1,845 @@
+!allocate dynamic arrays
+module allocate_h
+
+    contains
+
+subroutine allocate_general()
+
+    use params_h
+    use climo_h
+    use common_h
+
+    implicit none
+
+    INTEGER :: istate
+   	allocate( &
+     temp(366,subasin), &
+	 precip(366,subasin), &
+	 preciph(366*24,subasin), &
+	 pet(366,subasin), &
+	 rad(366,subasin), &
+	 rhum(366,subasin), &
+	 wind(366,subasin), &
+	 do_pre_outflow(subasin), &
+      STAT = istate)
+
+	if (istate/=0) then
+		write(*,'(A,i0,a)')'ERROR: Memory allocation error (',istate,') in general-module: '
+		stop
+	end if
+    do_pre_outflow=.true.
+
+end subroutine allocate_general
+
+
+subroutine allocate_hymo()
+
+use hymo_h
+use params_h
+
+implicit none
+
+INTEGER :: istate
+
+	 allocate( &
+     area(subasin), &
+	 id_subbas_extern(subasin), &
+	 id_subbas_intern(subasin), &
+	 nbr_lu(subasin), &
+	 id_lu_intern(maxsoter,subasin), &
+	 tcallid(subasin, maxsoter, maxterrain), &
+	 frac_lu(maxsoter,subasin), &
+	 kfkorrc(subasin), &
+	 intcfc(subasin), &
+	 !period(4,subasin,tstop-tstart+1), &
+	 laimun(366,subasin), &
+	 soilm(366,subasin), &
+	 soilmroot(366,subasin), &
+	 aet(366,subasin), &
+	 soilet(366,subasin), &
+	 intc(366,subasin), &
+	 ovflow(366,subasin), &
+	 hortflow(366,subasin), &
+	 subflow(366,subasin), &
+	 gw_recharge(366,subasin), &
+	 deepgw(subasin,maxsoter), &
+	 !deepgw_r(366,subasin), &
+	 qgen(366,subasin), &
+	 water_subbasin_t(366,nt,subasin), &
+	 water_subbasin(366,subasin), &
+	 qloss(366,subasin), &
+	 sofarea(366,subasin), &
+	 avail_all(366,subasin), &
+	 avail_ac(366,subasin), &
+
+	 nbr_svc(ntcinst), &
+
+	 rocky(ntcinst), &
+	 laitc(ntcinst), &
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/calcyear.f90

@@ -1,0 +1,107 @@
+SUBROUTINE calcyear
+
+! Code converted using TO_F90 by Alan Miller
+! Date: 2005-06-30  Time: 13:50:58
+use time_h
+
+INTEGER :: i
+
+
+daymon( 1) = 31
+daymon( 3) = 31
+daymon( 4) = 30
+daymon( 5) = 31
+daymon( 6) = 30
+daymon( 7) = 31
+daymon( 8) = 31
+daymon( 9) = 30
+daymon(10) = 31
+daymon(11) = 30
+daymon(12) = 31
+
+dayoutsim = 0
+
+IF (is_leapyear(t)) THEN !check for leap year
+	daymon(2) =  29
+ELSE
+	daymon(2) =  28
+END IF
+
+mon_day(1)= 1 !compute julian day of start of each month
+DO i=2,12
+  mon_day(i)=mon_day(i-1)+daymon(i-1)
+END DO
+
+
+! first simulation year
+IF (t == tstart) THEN
+  dstart=min(dstart, daymon(mstart)) !correct start/stop days, when larger than days in month
+  dstop =min(dstop,  daymon(mstop))
+
+  dprev     = sum(daymon(mstart:12)) !ii: is this correct? leap year and  dstart are apparently not considered
+
+  dayyear   = sum(daymon(mstart:12)) !number of days to treat in current year
+  dayyear	  =	dayyear   - (dstart-1) !reduce by start_day_of month
+
+!  dtot=dayyear !Calculation of total days since simulation started (for first year)
+
+	!Ge check total number of days before the start month in the start year
+	IF (mstart /= 1) THEN
+	  dayoutsim = sum(daymon(1:mstart-1))
+	ENDIF
+
+	dayoutsim = dayoutsim + (dstart-1)
+
+END IF
+
+! Calculates no. of days of simulated days in previous year (as a function of leap years)
+daylastyear = -1 !debug option, can be removed
+IF (t == tstart + 1) THEN
+  daylastyear = dtot-1
+else
+    IF ( is_leapyear(t-1) ) THEN
+        daylastyear = 366
+    ELSE
+        daylastyear = 365
+    END IF
+END IF
+
+
+
+
+
+
+! intermediate simulation years
+IF (t /= tstart .AND. t /= tstop) THEN
+  dayyear   = sum(daymon(1:12))
+!  dtot=dtot+dayyear !count simulation days
+END IF
+
+
+! last simulation year
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/climo_h.f90

@@ -1,0 +1,66 @@
+! Till: separated modules to allow easier use by eclipse
+! 2013-10-02 
+
+! Till: computationally irrelevant: relocated vars
+! 2012-09-21 
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+! Till: computationally irrelevant: added program version information to parameter.out
+! 2009-06-17
+
+! Till: added output for River_Sediment_Storage.out
+! 2008-11-13
+
+! 2008-07-11
+! Till: implemented optional pre-specified sediment outflow of selected subbasins
+
+! 2008-07-03
+! Till: implemented optional pre-specified outflow of selected subbasins
+
+! 2008-01-31 
+! Till: included variables for loading and saving of initial conditions
+! included variables for controling evaporation calculation
+
+! 2007-10-18
+! Till: increased length of pathp variable to 160
+
+! 2007-06-04
+! Till: added flag f_tc_theta
+
+! 2007-04-28
+! Till: added flag f_tc_theta
+
+! 2007-01-10
+! Till: renamed f_deep_gw to f_deep_gw_recharge, added f_deep_gw_discharge
+
+!Till: added variable f_deep_gw as flag for fileoutput
+
+!
+
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+module climo_h
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+save
+! daily average temperatures (oC)
+real, allocatable :: temp(:,:)
+! daily precipitation (mm/day)
+real, allocatable :: precip(:,:)
+! daily potential evapotranspiration (mm/day)
+real, allocatable :: pet(:,:)
+! daily mean shortwave radiation (W/m^2)
+real, allocatable :: rad(:,:)
+! incoming radiation above atmosphere (W/m²)
+REAL :: radex(366)
+! relative humidity (%)
+real, allocatable :: rhum(:,:)
+! wind velocity (m/s)
+real, allocatable :: wind(:,:)
+! climate variables for hourly model version
+real, allocatable :: preciph(:,:)
+
+INTEGER :: store_day, store_timestep	!Till: day and timestep for which ETP-values were stored
+
+end module climo_h
+

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/common_h.f90

@@ -1,0 +1,85 @@
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+module common_h
+    !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+    save
+    ! logicals for inclusion of modules in calculation
+    CHARACTER (LEN=80) ::rev_string1,rev_string2   !Till: revision information string
+    LOGICAL :: doacud
+    LOGICAL :: doreservoir
+    LOGICAL :: dolattc
+    LOGICAL :: doalllattc
+    LOGICAL :: dolatsc
+    LOGICAL :: dolatscsub
+    LOGICAL :: dotrans
+    LOGICAL :: docellprec
+    LOGICAL :: dohour
+    LOGICAL :: doscale
+    LOGICAL :: domuncell
+    LOGICAL :: doreserv
+    LOGICAL, allocatable :: do_pre_outflow(:)   !Till: consider pre-specified outflow time series from subbasins
+    LOGICAL :: do_pre_outsed=.TRUE.   !Till: consider pre-specified sediment outflow time series from subbasins
+
+    INTEGER :: ezgt
+    INTEGER :: zahlt
+    INTEGER :: nameti
+    INTEGER :: nmunt
+    INTEGER :: nroutt
+    INTEGER :: batch
+    INTEGER :: scenario
+    INTEGER :: krig
+    REAL :: sensfactor
+    CHARACTER (LEN=10) :: namet
+    CHARACTER (LEN=10) :: caset
+    CHARACTER (LEN=160) :: pfadn
+    CHARACTER (LEN=160) :: pfadp
+    INTEGER :: pfadi
+    INTEGER :: pfadj
+    INTEGER :: ncaset
+    INTEGER :: nezgt
+    INTEGER :: pyear
+    INTEGER :: dt               !time step in [hours]
+    LOGICAL :: dosediment         !do sediment calculation for hillslope, river and reservoir
+    INTEGER :: n_sed_class         !number of particles classes
+    INTEGER :: river_transport      !type of river sediment transport
+    INTEGER :: reservoir_transport   !type of reservoir sediment transport
+    INTEGER :: nt               !number of timesteps per day (computed as 24/dt)
+    INTEGER :: dosnow               !snow module to be used: 0 => NO; 1 => YES
+    INTEGER :: julian_day ! julian day
+
+    real, allocatable :: upper_limit(:)         !upper limits of particle size class intervalls (mm)
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/params_h.f90

@@ -1,0 +1,70 @@
+! Till: separated modules to allow easier use by eclipse
+! 2013-10-02 
+
+! Till: computationally irrelevant: relocated vars
+! 2012-09-21 
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+! Till: computationally irrelevant: added program version information to parameter.out
+! 2009-06-17
+
+! Till: added output for River_Sediment_Storage.out
+! 2008-11-13
+
+! 2008-07-11
+! Till: implemented optional pre-specified sediment outflow of selected subbasins
+
+! 2008-07-03
+! Till: implemented optional pre-specified outflow of selected subbasins
+
+! 2008-01-31 
+! Till: included variables for loading and saving of initial conditions
+! included variables for controling evaporation calculation
+
+! 2007-10-18
+! Till: increased length of pathp variable to 160
+
+! 2007-06-04
+! Till: added flag f_tc_theta
+
+! 2007-04-28
+! Till: added flag f_tc_theta
+
+! 2007-01-10
+! Till: renamed f_deep_gw to f_deep_gw_recharge, added f_deep_gw_discharge
+
+!Till: added variable f_deep_gw as flag for fileoutput
+
+!
+
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+module params_h
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+save
+! TOTAL NUMBER OF SUB-BASINS IN STUDY AREA (e.g. 10 sub-basins)
+INTEGER :: subasin
+! TOTAL NUMBER OF SOTER UNITS IN STUDY AREA (e.g. 321 units)
+INTEGER :: nsoter
+! TOTAL NUMBER OF TERRAIN COMPONENTS IN STUDY AREA (e.g. 515 components)
+INTEGER :: nterrain
+! TOTAL NUMBER OF SOIL COMPONENTS IN STUDY AREA (e.g. 72 components)
+INTEGER :: nsoil
+! TOTAL NUMBER OF VEGETATION UNITS IN STUDY AREA (e.g. 34 units)
+INTEGER :: nveg
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/General/wasa.f90

@@ -1,0 +1,79 @@
+PROGRAM wasa_sed
+
+use common_h
+use hymo_h
+use params_h
+use time_h
+use routing_h
+use model_state_io
+
+IMPLICIT NONE
+
+!CCCCCCCCCCCCCCCCCCCCC MAIN PROGRAM CCCCCCCCCCCCCCCCCCCCCCCCCCCC
+
+CALL GETARG(1, pfadn)		!Till: try to read path to central control file (do.dat)
+
+!include 'svn_rev.f90' !Till: import revision information string
+
+WRITE(*,'(A,A,/,A)') 'WASA model, ',trim(rev_string1),' '//trim(rev_string2)
+
+WRITE(*,*) ':Initialization'
+CALL readgen(pfadn)
+t = tstart
+CALL calcyear
+dtot = 1 ! count days of simulation
+
+! READ INPUT DATA (STATUS 0) AND INITIALISE ARRAYS (STATUS 0)
+CALL hymo_all(0)
+CALL climo(0)
+
+
+!initialization of routing routines
+if (river_transport.eq.1) CALL routing(0)
+if (river_transport.ne.1) CALL routing_new(0)
+call init_river_state
+
+CALL save_model_state(doloadstate, .TRUE.) !Till: do backups of state files if loaded from them, and save only summary on initial storage
+
+!!! MAIN LOOP FOR EACH YEAR
+DO t=tstart, tstop
+  WRITE(*,*) tstart,tstop
+  IF (t /= tstart) CALL calcyear
+  WRITE(*,*) 'calculations for year ',t
+
+! Call routines for climate time series for current year
+  CALL climo(1)
+
+! Update annual values for hydrology and agriculture at start of each simulation year
+     call hymo_all(1)
+	 if (river_transport.eq.1) call routing(1)
+	 if (river_transport.ne.1) call routing_new(1)
+
+!!! MAIN LOOP FOR DAILY TIME STEPS
+  DO d=1,dayyear
+  write(*,*) d
+    CALL hymo_all(2)
+ !Call routing routine
+	if (river_transport.eq.1) CALL routing(2)
+    if (river_transport.ne.1) CALL routing_new(2)
+    dprev = d
+    dtot = dtot + 1 ! count days of simulation
+  END DO
+!!! END LOOP FOR DAILY TIME STEPS
+
+! Generate output for hillslope
+   CALL hymo_all(3)
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Hillslope/erosion_h.f90

@@ -1,0 +1,143 @@
+! Till: added specifiyable SDR for TCs
+! 2013-10-02
+
+! Pedro: added variables for TC_wise output
+! 2009-06-03
+
+! Till: include optional specification for LU-based correction of beta/m (exponent for L-factor calculation)
+! 2008-10-22
+
+! Till: added specifyable SDR for LUs
+! 2008-09-09
+
+! Till: implemented variables for optional pre-specified sediment outflow of selected subbasins
+! 2008-07-11
+
+! Till: included coefficients for estimation of maximum half-hour rainfall intensity 
+! 2008-07-10
+
+! Pedro
+! added variables
+! 2008-02-07
+
+! Till: changed addressing scheme of sediment_subbasin_t from (366*nt,subasin,n_sed_class) to (366,nt,subasin,n_sed_class)
+! 2005-12-20
+
+
+module erosion_h
+
+
+
+    INTEGER  :: erosion_equation            !erosion equation to be used:1: USLE, 2: Onstad-Foster, 3:    MUSLE, 4: MUST
+    LOGICAL :: do_musle_subbasin        !1: compute erosion on subbasin scale; 0: compute erosion on TC-scale
+
+    !coefficients for estimation of maximum half-hour rainfall intensity (ri_05) from timestep rainfall data (R_dt) 
+    REAL    :: a_i30, b_i30  ! ri_05=a*R_dt^b
+
+
+    INTEGER :: transport_limit_mode=2    !different modes how/if transport capacity of runoff is limited (default, taken from erosion.ctl, if present)
+        !(1)                        !no transport capacity limit
+        !(2)                        !transport capacity according to Everaert (1991)
+        !(3)                        !transport capacity computed from MUSLE with maximum erodibility
+
+                                
+
+    TYPE t_svc2
+        INTEGER :: svc_id
+        REAL    :: fraction
+    END TYPE t_svc2
+
+    TYPE t_svc_pointer_array
+        type (t_svc2), pointer :: p(:)
+    END TYPE t_svc_pointer_array
+
+       
+
+
+    !Till: Hillslope erosion
+    !real, allocatable :: musle_fac(:,:)    !contains MUSLE-factors (K C P CFRG ManningsN) for each SVC (LS comes from the TC itself)
+    real, pointer :: svc_k_fac(:,:)    !contains MUSLE-factor K for each SVC and seasonal node(LS comes from the TC itself)
+    real, pointer :: svc_c_fac(:,:)    !contains MUSLE-factor C for each SVC and seasonal node
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Hillslope/etp_soil_hour.f90

@@ -1,0 +1,547 @@
+SUBROUTINE etp_soil_hour(hh,i_subbas3,vegi,defi,facwi,act,actveg,acts,  &
+        height_act,lai_act,alb_act,rsfinal)
+
+!Jose: an upper theshold for soil surface resistance "rss" was introduced. For very high values of "rss" a divi! jose miguel: for very low soil water content, the rss tends to infinity. This is not accepted by the computations, so the maximum of surface resistance of bare soil is limited to 1.0e6 (arbitrary huge number beyond maximum value obtained by Domingo et al. 1999) in order to prevent errors. See Domingo et al./Agricultural and Forest Meteorology 95 (1999) 76-77
+!2012-12-05
+!Till: computationally irrelevant: minor changes to improve compiler compatibility
+!2011-04-29
+
+!Till: excluded domean, donight as logicals to module common_h
+! excluded daily_delta_temp (daily temperature variation),hours_of_daylight
+! 2008-02-05
+
+!Till: added safety checks to prevent NaN values when LAI or plant height=0
+! renamed muni to i_subbas3
+!2006-08-16
+!
+! Code converted using TO_F90 by Alan Miller
+! Date: 2005-06-30  Time: 13:46:04
+
+use climo_h
+use common_h
+use hymo_h
+use params_h
+use time_h
+
+!** EVAPOTRANSPIRATION
+
+!   Update 05/2001 , Stundenversion
+!   Two-layer and two-source model gemaess Brenner & Incoln (1997).
+!   modification: soil heat flux is taken to be different for
+!   soil below shrubs and for bare soil (see also Domingo et al. (1999)).
+
+
+! Ausgehend davon, das Temperatur, Globalstrahlung und Luftfeuchte als taegl.,
+! Sub-basin abhaengige  Werte gegeben sind, also temp(id,imun), rad(id,imun),
+! rhum(id,imun), wind(d,imun)
+
+IMPLICIT NONE
+
+INTEGER, INTENT(IN)                      :: hh
+INTEGER, INTENT(IN)                  :: i_subbas3
+INTEGER, INTENT(IN)                  :: vegi
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Hillslope/hymo_h.f90

@@ -1,0 +1,751 @@
+module hymo_h
+    use common_h
+    save
+
+    !Till: computationally irrelevant: added options for LU-wise sediment output
+    !2014-05-15
+
+    ! Till: optional subdaily output of actetranspiration.out,qhorton.out,subsurface_runoff.out,total_overlandflow.out,gw_discharge.out,potetranspiration.out,gw_loss.out,gw_recharge.out
+    ! 2009-04-16
+
+    ! Till: outcommented unnecessary variable
+    ! 2008-06-24
+
+    ! 2007-10-29 Till:
+    ! added variables for time-variant kfkorr and debug-output
+
+    ! 2007-08-20 Till:
+    ! added variable frac_direct_gw
+
+    ! 2005-07-11 Till:
+    ! replaced misleading variable names
+
+    ! Code converted using TO_F90 by Alan Miller
+    ! Date: 2005-06-30  Time: 13:59:19
+
+    ! WATERSHED / Sub-basin PARAMETERS
+
+    ! IDs of cells in watershed (changed to model internal number)
+    !Allocatable      integer id_subbas_intern(subasin)
+    ! area of sub-basin (square kilometer)
+    !      real area(subasin)
+
+    real, allocatable :: area(:)
+
+    ! SUBBASIN / GRID CELL PARAMETERS
+    ! IDs of subbasins (external and internal IDs)
+    !Allocatable integer id_subbas_extern(subasin)
+    integer, allocatable ::  id_subbas_extern(:),id_subbas_intern(:)
+    ! number of landscape units within each subbasin
+    !Allocatable     integer nbr_lu(subasin)
+    integer, allocatable ::  nbr_lu(:)
+    ! IDs of landscape units in cell
+    !Allocatable       integer id_lu_intern(maxsoter,subasin)
+    integer, allocatable ::  id_lu_intern(:,:)
+    ! fraction of LU in subbasin
+    !Allocatable       real frac_lu(maxsoter,subasin)
+    real, allocatable :: frac_lu(:,:)
+    ! scaling factor for hydraulic conductivity in infiltration routine
+    !Allocatable       real kfkorrc(subasin)
+    real, allocatable :: kfkorrc(:)
+    ! scaled interception capacity (at the scale of cells for interpolated daily rainfall)
+    !Allocatable       real intcfc(subasin)
+    real, allocatable :: intcfc(:)
+
+
+    ! Landscape UNIT PARAMETERS
+    ! IDs of LUs
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Hillslope/model_state_io.f90

@@ -1,0 +1,1447 @@
+module model_state_io
+    !contains subroutines for saving and loading model state (soil water, ground water, interception)
+
+
+    use common_h
+contains
+    subroutine init_hillslope_state        !load initial conditions for hillslopes and reservoirs
+            !if (.not. doloadstate) return   !do not load files, if disabled
+            call init_soil_conds      (trim(pfadn)//'soil_moisture.stat')    !Till: load initial status of soil moisture
+            call init_intercept_conds (trim(pfadn)//'intercept_storage.stat')    !Till: load initial status of gw storage
+            call init_gw_conds        (trim(pfadn)//'gw_storage.stat')    !Till: load initial status of gw storage
+            call init_interflow_conds (trim(pfadn)//'interflow_storage.stat')    !Till: load initial status of interflow storage
+            call init_snow_conds      (trim(pfadn)//'snow_storage.stat')    !Till: load initial status of snow storage
+            call init_lake_conds      (trim(pfadn)//'lake_volume.stat')    !Jose Miguel: load initial status of lake storage
+    end subroutine init_hillslope_state
+
+   subroutine init_river_state        !load initial conditions for riverscape
+            if (.not. doloadstate) return   !do not load files, if disabled
+            call init_river_conds(trim(pfadn)//'river_storage.stat')    !Jose Miguel: load initial status of river storage
+            if (dosediment) then
+               call init_sediment_conds(trim(pfadn)//'sediment_storage.stat')    !Jose Miguel: load initial status of deposited sediment storage
+               call init_susp_sediment_conds(trim(pfadn)//'susp_sediment_storage.stat')    !Jose Miguel: load initial status of suspended sediment storage
+            endif
+    end subroutine init_river_state
+
+    subroutine save_model_state(backup_files, start)        !save all model state variables, optionally backup older files
+    implicit none
+    logical, intent(in) :: backup_files
+    logical, intent(in) :: start
+
+        if (.not. dosavestate) return
+            !keep files with initial conditions (if existing), save new summary on initial storages
+        CALL save_all_conds(&
+        rename_or_return('soil_moisture.stat'        , backup_files),&
+        rename_or_return('gw_storage.stat'           , backup_files),&
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Hillslope/sedi_yield.f90

@@ -1,0 +1,372 @@
+SUBROUTINE sedi_yield(precip_dt, subbas_id, lu_id, tc_type_id, tcid_instance2, q_in, q_out, q_peak_in, v_ov_in, sed_in, timestep, tc_area, sed_yield)
+
+    ! hillslope erosion module for WASA
+    ! to be called by soilwat.f90, Till Francke (till@comets.de)
+
+    ! Till: runoff during no-rain days caused math error (log(0)) - fixed
+    ! 2012-05-30
+
+    ! Till: computationally irrelevant: removed unused parameter h
+    ! 2011-05-05
+
+    ! Till: computationally relevant: fixed overestimation of transport capacity according to Everaert due to integer division
+    ! minor changes to improve compiler compatibility
+    ! 2011-04-29
+
+    ! Pedro: added variables for TC_wise output
+    ! 2009-06-03
+
+    ! Pedro: fixed stream power calculation - computationally relevant for sediment estimations
+    ! 2009-06-03
+
+    ! Till: include optional specification for LU-based correction of beta/m (exponent for L-factor calculation)
+    ! 2008-10-22
+
+    ! Till: switched back from cumulative to ordinary L-factor
+    ! 2008-10-15
+
+    ! Till: cleanup of storage structure for SVCs
+    ! 2008-09-11
+
+    ! 2008-07-15
+    ! Till: clarified code
+
+    ! 2008-07-10
+    ! Till: outsourced coefficients for estimation of maximum half-hour rainfall intensity
+    ! minor correction for transport capacity limit=off
+
+    ! 2008-01-23
+    ! Version with the modifications proposed by Pedro
+
+    ! 2007-11-07
+    ! Till: corrected MUSLE (SWAT-version had wrong units) to version by Krysanova et al. in Summer&Walling (2002) which is equivalent to Williams, 1995
+
+    ! 2005-10-10
+    ! Till: d50 no more calculated internally but used from global array
+
+    ! 2005-09-29
+    ! Till: structure changed from FUNCTION to SUBROUTINE: variables are passed by reference anyway and SUBROUTINE allows easier handling of array return values
+    ! sediment yield is returned in fractions (MUSLE-result distributed according to mean particle size fractions in TC)
+
+    ! 2005-08-10
+    ! Till: fixed minor bugs with unit conversions
+
+    ! 2005-07-08
+    ! Till: adapt to new WASA-structure and headers
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Reservoir/lake_h.f90

@@ -1,0 +1,145 @@
+! Till: computationally irrelevant: outcommented unused variables
+! 2012-09-14
+!
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+!
+!The module file contains two modules: reservoir_h and lake_h
+!
+
+module lake_h
+save
+
+! Logical for reading or calculation ofthe number of reservoir per size class per year
+LOGICAL :: doacudyear
+! number of small reservoirs per volume class (5 volume classes)
+! rounded to nearest integer
+!Allocatable      real acud(nmun,5)
+real, allocatable :: acud(:,:)
+! number of acudes per volume class (5 volume classes)
+! not rounded, for calculation of growth per year
+!Allocatable       real acudfloat(nmun,5)
+real, allocatable :: acudfloat(:,:)
+! Andreas
+! number of acudes per volume class (5 volume classes) and year
+! specific values for each year, read from small_rservoirs_year.dat
+! calculation of growth per year is not used if data are in the file
+!Allocatable       real acudfloatyear(nmun,5,200)
+real, allocatable :: acudfloatyear(:,:,:)
+! initial maximum storage capacity in one acude of each volume classes (m3)
+real :: maxlake0(5)
+! initial maximum storage capacity in one acude of each volume classes (m3)
+real, allocatable :: maxlakesub0(:,:)
+! trend in number of acudes for each volume class (+-nbr/year)
+!Allocatable       real laketrend(nmun,5)
+real, allocatable :: laketrend(:,:)
+! maximum capacity of water storage (m3)
+!Allocatable       real maxlakewater(nmun,5)
+real, allocatable ::  maxlakewater(:,:)
+! fraction of generated river runoff being routed through small acudes
+real :: intercepted
+! water stored in small reservoirs (m3)
+!Allocatable      real lakewater(366*nt,nmun,5)
+real, allocatable :: lakewater(:,:,:)
+! water released from small reservoirs (m3)
+!Allocatable      real laketot(366*nt,nmun)
+real, allocatable :: lakerelease(:,:)
+! water stored in small reservoirs (m3)
+!Allocatable      real laketot(366*nt,nmun)
+real, allocatable :: laketot(:,:)! relative water storage (-)
+!Allocatable      real laketotfrac(366*nt,nmun)
+real, allocatable :: laketotfrac(:,:)
+! evaporation from lakes, all classes (m3)
+!Allocatable      real lakeevap(366*nt,nmun,5)
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Reservoir/lake_routing.f90

@@ -1,0 +1,160 @@
+SUBROUTINE lake_routing(muni,k,help,help2,help3)
+!Till: computationally irrelevant: outcommented unused vars
+!2012-09-14
+
+! Code converted using TO_F90 by Alan Miller
+! Date: 2005-08-23  Time: 12:57:31
+
+
+use lake_h
+use common_h
+use time_h
+use reservoir_h
+use params_h
+
+IMPLICIT NONE
+
+INTEGER, INTENT(IN)               :: muni
+INTEGER, INTENT(IN)               :: k
+REAL, INTENT(IN)                  :: help
+REAL, INTENT(IN)                  :: help2
+REAL, INTENT(OUT)                  :: help3
+
+INTEGER :: i,n !,j,npts
+INTEGER :: ninterac !,nbrbat1
+
+REAL :: par_c,par_d !,par_a,par_b
+REAL :: y1,y2,vol1,vol2,dvol !,elev,out1,out2
+REAL :: frtime,inflow_t,inflow_mean,outflow_mean
+REAL :: inflow,outflow
+REAL :: dummy1,dummy2,error !,dummy3,dummy4,dummy5
+REAL :: volmax,volstep,time !,areamax
+REAL :: hmax0,vmax0,par_k,par_alpha
+REAL :: dummy
+! -----------------------------------------------------------------------
+
+! Initialization
+! Initialization
+if (acud(muni,k)>0.) then
+ inflow=help/(86400./nt)
+ volstep=help2
+
+ inflow=inflow/acud(muni,k)
+ volstep=volstep/acud(muni,k)
+
+ outflow=outflow_last_hrr(muni,k)
+ volmax=maxlake(muni,k)
+ par_c=damc_hrr(k)
+ par_d=damd_hrr(k)
+ par_k=damk_Molle(k)
+ par_alpha=alpha_Molle(k)
+ vmax0=maxlakesub0(muni,k)
+ hmax0=hmax_hrr(muni,k)
+
+!write(*,'(2I6,2F7.3,F13.1,2F8.3,F13.1)')muni,k,par_c,par_d,par_k,par_alpha,hmax0,vmax0
+
+!stop
+
+
+ IF (outflow==0.) THEN
+  vol2=max(0.,volstep-volmax)
+ ELSE
+  vol2=volume_last_hrr(muni,k)
+ ENDIF
+
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Reservoir/reservoir - com transposicao.f90

@@ -1,0 +1,1897 @@
+SUBROUTINE reservoir (STATUS,upstream,res_h)
+
+! Till: made reading of reservoir.dat, cav.dat independent of order of IDs
+! memory allocation according to content of these files
+! various minor code beautifications
+! 2012-09-17
+
+! Till: computationally irrelevant: outcommented unused vars
+! 2012-09-14
+
+! Till: computationally irrelevant: streamlined code and improved error message with routing.dat
+! 2011-07-05
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+! Code converted using TO_F90 by Alan Miller
+! Date: 2005-08-23  Time: 12:56:42
+
+use common_h
+use params_h
+use routing_h
+use climo_h
+use hymo_h
+use time_h
+use reservoir_h
+use utils_h
+
+! water balance for a reservoir of a large river dam
+
+IMPLICIT NONE
+
+
+INTEGER, INTENT(IN)                  :: STATUS
+INTEGER, INTENT(IN OUT)                  :: upstream
+INTEGER, INTENT(IN)                  :: res_h
+
+! STATUS of CALL (0=initialization run, 1=initialization year,
+!                 2=calculation day,    3=finalization year)
+
+INTEGER :: i,id,dummy1,dummy2,s,p,q,h,istate,ka,ih !,irout,imun,dummy1a,dummy2a,f
+character(100) :: dummy_char
+!Ge include j,nbrbat1,cont,upstream,downstream
+INTEGER :: j,nbrbat1,flag_cav,dummy3,dayyear_t(10000)
+REAL :: elevhelp,evaphelp2,volhelp !,elevhelp2,elevhelp3
+REAL :: help,help1,help2,help3,evaphelp,areahelp,helpout,prechelp !,helpin,infhelp
+!Ge actual storage capacity of large river reservoir in a certain year[10**6 m**3]
+!REAL :: storcapact
+
+CHARACTER(12) :: subarea
+
+!REAL :: r_level0,r_level1,r_overflow,r_qbottom
+!REAL :: r_precip,r_etp,r_qinflow
+
+INTEGER :: idummy,n !,npt, nbrsec1
+!INTEGER :: dummy3
+REAL :: dummy4,dummy5,dummy6
+character(len=1000) :: fmtstr	!string for formatting file output
+
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Reservoir/reservoir.f90

@@ -1,0 +1,1896 @@
+SUBROUTINE reservoir (STATUS,upstream,res_h)
+
+! Till: made reading of reservoir.dat, cav.dat independent of order of IDs
+! memory allocation according to content of these files
+! various minor code beautifications
+! 2012-09-17
+
+! Till: computationally irrelevant: outcommented unused vars
+! 2012-09-14
+
+! Till: computationally irrelevant: streamlined code and improved error message with routing.dat
+! 2011-07-05
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+! Code converted using TO_F90 by Alan Miller
+! Date: 2005-08-23  Time: 12:56:42
+
+use common_h
+use params_h
+use routing_h
+use climo_h
+use hymo_h
+use time_h
+use reservoir_h
+use utils_h
+
+! water balance for a reservoir of a large river dam
+
+IMPLICIT NONE
+
+
+INTEGER, INTENT(IN)                  :: STATUS
+INTEGER, INTENT(IN OUT)                  :: upstream
+INTEGER, INTENT(IN)                  :: res_h
+
+! STATUS of CALL (0=initialization run, 1=initialization year,
+!                 2=calculation day,    3=finalization year)
+
+INTEGER :: i,id,dummy1,dummy2,s,p,q,h,istate,ka,ih !,irout,imun,dummy1a,dummy2a,f
+character(100) :: dummy_char
+!Ge include j,nbrbat1,cont,upstream,downstream
+INTEGER :: j,nbrbat1,flag_cav,dummy3,transpo_flag(10000)
+REAL :: elevhelp,evaphelp2,volhelp !,elevhelp2,elevhelp3
+REAL :: help,help1,help2,help3,evaphelp,areahelp,helpout,prechelp !,helpin,infhelp
+!Ge actual storage capacity of large river reservoir in a certain year[10**6 m**3]
+!REAL :: storcapact
+
+CHARACTER(12) :: subarea
+
+!REAL :: r_level0,r_level1,r_overflow,r_qbottom
+!REAL :: r_precip,r_etp,r_qinflow
+
+INTEGER :: idummy,n !,npt, nbrsec1
+!INTEGER :: dummy3
+REAL :: dummy4,dummy5,dummy6
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/Reservoir/reservoir_h.f90

@@ -1,0 +1,504 @@
+! Till: computationally irrelevant: outcommented unused variables
+! 2012-09-14
+!
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+!
+!The module file contains two modules: reservoir_h and lake_h
+!
+
+module reservoir_h
+save
+
+INTEGER :: nxsection_res=200 !number of cross sections at the strategic reservoirs
+INTEGER :: npointsxsect=200  !number of points (x,y) along the cross sections
+
+
+
+! Options to run the WASA Model without river and hillslope modules
+INTEGER :: reservoir_balance	!option to read (0) or calculate (1) outflow discharges and reservoir levels
+INTEGER :: reservoir_check		!option to run the WASA Model with river and hillslope modules (0) or without them (1)
+INTEGER :: reservoir_print		!option to print the output files within the timestep (0) or once a year (1)
+!
+!!Reservoir water balance arrays
+!!simulation timestep
+integer :: step
+!hour (on day)
+integer :: hour
+! temporary array for reading of data from intake.dat
+real, allocatable :: r_qintake(:)
+! number of columns in intake.dat
+integer :: no_col_intake
+! for each subasin position in intake.dat
+integer, allocatable :: corr_column_intakes(:)
+! does intake.dat exist for specific subasin (and contain information)?
+logical, allocatable :: f_intake_obs(:)
+! flag indicating if a specific subbasin contains a strategic reservoir; FALSE: no reservoir; TRUE: contains a reservoir
+logical, allocatable :: res_flag(:)
+!flag to calculate the ratio between the reservoir volumes given in the file cav.dat and that derived from the cross sections  [0 = initial value; 1 = after first calculation]
+integer, allocatable :: fcav(:)
+!flag to simulate reservoir routing during spillway overflow of the sub-basin's reservoir [0 = without time delay; 1 = with time delay]
+integer, allocatable :: fvol_over(:)
+!flag to identify the ocurrence of lateral inflow into the dowstream reservoir (0 = no and 1 = yes)
+integer, allocatable :: latflow_res(:)
+!arrays used for the routing of lateral inflow into the dowstream reservoir
+integer, allocatable :: reservoir_down(:)
+!year of construction of the dam in the sub-basin
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/River/muskingum.f90

@@ -1,0 +1,238 @@
+SUBROUTINE muskingum (i, h)
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+!Till: re-modified transmission losses, various optimizations 
+!2009-12-17
+ 
+!Till: modified transmission losses (affect rout instead of storage in reach); infiltration is restricted to bottom width, not full wetted perimeter
+!2008-10-30
+
+!! subroutine routes a daily or hourly water flow through a reach using the Muskingum method
+
+!!    ~ ~ ~ INCOMING VARIABLES ~ ~ ~
+!! r_sideratio(:)   |none        |change in horizontal distance per unit change in vertical distance on channel side slopes
+
+!!    ~ ~ ~ OUTGOING VARIABLES ~ ~ ~
+!! flow             |m^3/s       |average flow on day in reach
+!! r_Vin(1,i)		|m3			 |volume of water into reach on current day at beginning of time step
+!! r_Vin(2,i)		|m3			 |volume of water entering reach on day at end of the time step
+!! r_Vout(1,i)		|m3			 |volume of flow out of reach on current day at beginning of time step
+!! r_Vout(2,i)		|m3			 |water leaving reach on day at end of time step
+!! r_ksat(i)        |mm/hr       |effective hydraulic conductivity of main channel alluvium
+!! r_infil          |m^3 H2O     |transmission losses from reach in time step
+
+!! LOCAL DEFINTIONS
+!! vol              |m^3 H2O     |volume of water in reach at beginning of day
+!! r_area           |m^2         |cross-sectional area of flow
+!! c                |none        |change in horizontal distance per unit change in vertical distance on channel side slopes; always set to 2 (slope=1/2)
+!! r_depth_cur(i)   |m           |depth of flow on day
+!! tbase            |none        |flow duration (fraction of 24 hr)
+!! topw             |m           |top width of main channel
+!! r_evp            |m^3 H2O     |evaporation from reach per timestep
+
+
+use routing_h
+use time_h
+use hymo_h
+use common_h
+use climo_h
+
+IMPLICIT NONE
+INTEGER, INTENT(IN) :: i !internal subbasin-ID
+INTEGER, INTENT(IN) :: h !subdaily timestep
+real ::  r_area !cross section area
+real ::  flow !discharge
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/River/route_sediments.f90

@@ -1,0 +1,195 @@
+SUBROUTINE route_sediments(i)
+
+! Till: computationally irrelevant: removed unused parameters flow, rarea
+! 2011-05-05
+
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+!!    ~ ~ ~ PURPOSE ~ ~ ~
+!!    this subroutine routes sediment through the river system;
+!!    deposition is based on method velocity and degradation on stream
+
+!!    ~ ~ ~ INCOMING VARIABLES ~ ~ ~
+!!    name        |units         |definition
+!!    ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~
+!!    r_cover(:)   |none          |channel cover factor (0.0-1.0)
+!!                               |0 channel is completely protected from
+!!                               |  erosion by cover
+!!                               |1 no vegetative cover on channel
+!!    r_depth(:)     |m             |average depth of main channel
+!!    r_efactor(:)  |none          |channel erodibility factor (0.0-1.0)
+!!                               |0 non-erosive channel
+!!                               |1 no resistance to erosion
+!!    r_length(:)    |km            |initial length of main channel
+!!    r_width(:)   |m             |average width of main channel
+!!    ideg        |none          |channel degredation code
+!!                               |0: do not compute channel degradation
+!!                               |1: compute channel degredation (downcutting
+!!                               |   and widening)
+!!    phi(5,:)    |m^3/s         |flow rate when reach is at bankfull depth
+!!    prf         |none          |Peak rate adjustment factor for sediment
+!!                               |routing in the channel. Allows impact of
+!!                               |peak flow rate on sediment routing and
+!!                               |channel reshaping to be taken into account
+!!    r_depth_cur(i)      |m             |depth of flow on day
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/River/routing_coefficients.f90

@@ -1,0 +1,335 @@
+SUBROUTINE routing_coefficients(i, STATUS, flow, r_area, p)
+! Till: computationally irrelevant: minor changes to improve compiler compatibility
+! 2011-04-29
+
+!Till: computationally relevant for very initial phase of simulation: fixed bug in iterative estimation of depth from discharge
+!2009-12-18
+
+!Till: computationally relevant: major changes, bugfixes and optimization
+!2009-12-17
+
+!Till: computationally irrelevant: increased iteration counter for determination of river cross section
+!2009-12-11
+
+
+!!    this subroutine computes travel time coefficients for the Muskingum Routing
+!!    along the main channel
+
+!!    ~ ~ ~ INCOMING VARIABLES ~ ~ ~
+!!    name        |units         |definition
+!!    ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~
+!!    r_depth(:)     |m             |average depth of main channel
+!!    r_length(:)    |km            |length of main channel
+!!    manning(:)     |none          |Manning's "n" value for the main channel
+!!    r_slope(:)     |m/m           |average slope of main channel
+!!    r_width(:)     |m             |average width of main channel
+!!    ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~
+
+!!    ~ ~ ~ OUTGOING VARIABLES ~ ~ ~
+!!    name        |units         |definition
+!!    ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~
+!!    r_sideratio(:)   |none          |change in horizontal distance per unit
+!!                               |change in vertical distance on channel side slopes
+!!    area_bankful(:)          |m^2           |cross-sectional area of flow at bankfull
+!!    bottom_width(:)    |m             |bottom width of main channel depth
+!!    phi5(i)    |m^3/s         |flow rate when reach is at bankfull depth
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/River/routing_h.f90

@@ -1,0 +1,147 @@
+module routing_h
+save
+
+!ROUTING ARRAYS
+! Arrays used for the routing of q
+integer, allocatable :: upbasin(:), downbasin(:)
+! qin: river inflow into the Sub-basins [m**3/s]
+real, allocatable :: qin(:)
+! qin: river inflow into the Sub-basins [m**3/s]
+real, allocatable :: qin_sed(:)
+! qout: runoff out of the Sub-basin [m**3/s]
+!Allocatable      real qout (372,nmun)
+real, pointer :: qout(:,:)
+! qout: sediment output of the Sub-basin [t/timestep]
+!real, pointer :: qout_sed(:,:)
+!river inflow (m3/s) at time t and t+1 (2,subasin)
+real, allocatable :: r_qin(:,:)
+!river outflow (m3/s) at time t and t+1 (2,subasin)
+real, allocatable :: r_qout(:,:)
+!storage volume (m3) in river reach
+real, pointer :: r_storage (:)
+!array stores runoff from hillslopes (m3/s) and erosion (tons), if it is generated outside WASA
+!real, allocatable :: runoff(:,:)
+!real, allocatable :: sediment(:,:,:)
+
+! ORIGINAL WASA ROUTING SCHEME	
+! routing parameter (lag time and retention time) (days)
+!Allocatable      real prout(nmun,2)
+real, allocatable :: prout (:,:)
+real, allocatable :: hrout(:,:) !memory for triangular unit hydrograph (allochtonous runoff)
+real, allocatable :: hrout_intern(:,:) !memory for triangular unit hydrograph (autochtonous runoff)
+
+! RIVER CHARACTERISTICS
+! river channel width (bankful width) (m)
+real, allocatable ::	r_width(:)
+! river channel depth (m)
+real, allocatable :: r_depth(:)
+! current river depth at calculation step (m)
+real, allocatable :: r_depth_cur(:)
+! river slope(m/m)
+real, allocatable :: r_slope(:)
+!river side ratio: change in horizontal distance per unit change in vertical distance on channel side slopes (m/m)
+real, allocatable :: r_sideratio(:)
+! river bottom width of floodplain (m)
+real, allocatable :: r_width_fp(:)
+! river side ratio for the floodplain (m/m)
+real, allocatable :: r_sideratio_fp(:)
+! river length (km)
+real, allocatable :: r_length(:)
+! manning's n(-)
+real, allocatable :: manning(:)
[…]

### 2022-03-02 Inputs/Model_input/Directory_WASA_Banabuiu/Code/update_revision_no.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#update file General/svn_rev.f90 with current revision numbering to be included in the binary
+#to be executed within the directory where you downloaded WASA-SED files into (manually or by Makefile)
+
+# set output of git to variable
+gitstr=`git describe --tags --long`
+
+# check for local modifications
+mod_files=`git status --porcelain`
+
+if [ -z "$mod_files" ]
+then
+cmmt=""
+else
+cmmt="(local modifications)"
+fi
+
+# Absolute path to this script
+# SCRIPT=$(readlink -f $0)
+# SCRIPTPATH=`dirname $SCRIPT`
+
+REP_DATE=`git show -s --format=%ci`
+DATE=` date +%Y-%m-%d" "%H:%M`
+echo "!this file is updated by update_revision_no.sh/.bat" > $1/General/svn_rev.f90
+echo "rev_string1='$gitstr $cmmt'" >> $1/General/svn_rev.f90
+echo "rev_string2='repository date $REP_DATE, built $DATE'" >> $1/General/svn_rev.f90

### 2022-03-02 Main_code/DCA.R

@@ -4,7 +4,7 @@
 # Script setup ------------------------------------------------------------
 
 #Directory and paths
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 path_maxcap <- "./Inputs/Model_input/Base/Reservoir/reservoir.dat"
 
 source("./Libraries/Libraries.R")

### 2022-03-02 Main_code/DCA_plot.R

@@ -1,23 +1,46 @@
 #Plots and tables for the DCA analysis
 
-
 # Setup -------------------------------------------------------------------
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 source("./Libraries/Libraries.R")
+source("./Libraries/Functions.R")
 
 DCA_real <- list.load("./Data/DCA/DCA_real.RData")
 DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
 DCA_obs <- list.load("./Data/DCA/DCA_obs.RData")
+DCA_SR <- list.load("./Data/DCA/DCA_SR.RData")
+DCA_N <- list.load("./Data/DCA/DCA_N.RData")
+
+rename_scenarios = function(df){
+  #df BEFORE reshape::melt!
+  names(df)[names(df) == "Real"] <- "AR"
+  names(df)[names(df) == "noHDNR"] <- "LR"
+  return(df)
+}
+
+#Meteorological drought periods
+#Based on Marengo et al., 2016
+date_ranges_Marengo <- data.frame(
+  from = as.Date(c("1981-01-01", "1982-01-01", "1992-01-01", "1997-01-01", "2001-01-01", "2005-01-01", "2007-01-01", "2010-01-01")),
+  to = as.Date(c("1981-12-01", "1983-12-01", "1993-12-01", "1998-12-01", "2002-12-01", "2005-12-01", "2007-12-01", "2018-12-01"))
+)
+#Based on SPI
+# negSPI <- DCA_real$Banabuiu$date[DCA_real$Banabuiu$PI < 0]
+# negSPI
+date_ranges_SPI <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
 
 # Table: Cumulative months of drought phases ------------------------------
 
 table1 <- data.frame(matrix(NA, 5, 3))
 names(table1) <- c("real", "noH", "obs")
[…]

### 2022-03-02 Main_code/downstreamness_analysis.R

@@ -2,7 +2,7 @@
 
 # Setup -------------------------------------------------------------------
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 
 source("./Libraries/Libraries.R")
 source("./Libraries/Functions.R")
@@ -108,6 +108,8 @@ save(HDNR_vol, file = "./Data/Downstreamness/HDNR_vol.Rdata")
 dx_hdnr <- HDNR_df$dx
 dx_res <- res_df$dx[order(res_df$subID)]
 
+mean(HDNR_df$dx)
+
 tic("Dsv real computation")
 Dsv_r <- data.frame(date = real_df$date)
 Dsv_r$Dsv <- 0
@@ -116,8 +118,15 @@ for(i in 1:nrow(Dsv_r)){
   den <- sum(HDNR_vol[i, 2:ncol(HDNR_vol)]) + sum(real_df[i, 2:ncol(real_df)])
   Dsv_r$Dsv[i] <- num/den
 }
+
+Dsv_r$noH <- 0
+for(i in 1:nrow(Dsv_r)){
+  num <- sum(real_df[i, 2:ncol(real_df)]*dx_res)
+  den <- sum(real_df[i, 2:ncol(real_df)])
+  Dsv_r$noH[i] <- num/den
+}
 toc()
-plot(Dsv_r)
+plot_df_interactive(Dsv_r)
 
 #NoH scenario
 tic("Dsv noH computation")
@@ -129,13 +138,13 @@ for(i in 1:nrow(Dsv_nH)){
   Dsv_nH$Dsv[i] <- num/den
 }
 toc()
-plot(Dsv_nH)
+plot_df_interactive(Dsv_nH)
 
 mean(Dsv_r$Dsv)
 mean(Dsv_nH$Dsv)
 
 #Save
-save(Dsv_r, file = "./Data/Downstreamness/Dsv_r.Rdata")
+save(Dsv_r, file = "./Data/Downstreamness/Dsv_r_v2.Rdata")
 save(Dsv_nH, file = "./Data/Downstreamness/Dsv_nH.Rdata")
 
 # Notes -------------------------------------------------------------------

### 2022-03-02 Main_code/downstreamness_plot.R

@@ -2,8 +2,23 @@
 
 # Setup -------------------------------------------------------------------
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 source("./Libraries/Libraries.R")
+source("./Libraries/Functions.R")
+source("./Libraries/Functions_MC.R")
+
+#Meteorological drought period
+date_ranges_SPI <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+
+rename_scenarios = function(df){
+  #df BEFORE reshape::melt!
+  names(df)[names(df) == "Real"] <- "AR"
+  names(df)[names(df) == "noHDNR"] <- "LR"
+  return(df)
+}
 
 # Dsc results -------------------------------------------------------------
 
@@ -14,29 +29,38 @@ load("./Data/Downstreamness/Dsc_r.Rdata")
 load("./Data/Downstreamness/Dsc_nH.Rdata")
 
 df <- data.frame(date = Dsc_r$date, Real = Dsc_r$Dsc, noHDNR = Dsc_nH$Dsc)
+df <- rename_scenarios(df)
 df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
 
 p <- df %>%
   ggplot(aes(date, value)) + 
   geom_line(aes(linetype = Scenario), size = 1.5, alpha = 0.5) +
   #Add lines at the reservoirs construction
-  geom_vline(xintercept = 1992, size = 1.25, alpha = 0.5, color = 'cornflowerblue') +
-  geom_text(aes(1992, 55, label = "Cipoada", hjust = -0.25)) +
-  geom_vline(xintercept = 1996, size = 1.25, alpha = 0.5, color = 'cornflowerblue') +
[…]

### 2022-03-02 Main_code/other_plots.R

@@ -1,0 +1,232 @@
+#Other plots
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+source("./Libraries/Libraries.R")
+source("./Libraries/Functions.R")
+
+date_ranges_SPI <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+
+rename_scenarios = function(df){
+  #df BEFORE reshape::melt!
+  names(df)[names(df) == "Real"] <- "AR"
+  names(df)[names(df) == "noHDNR"] <- "LR"
+  return(df)
+}
+
+# VD comparison: Real, noHDNR, observations ----------------------------------
+
+DCA_real <- list.load("./Data/DCA/DCA_real.RData")
+DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
+DCA_obs <- list.load("./Data/DCA/DCA_obs.RData")
+
+#Arrojado Lisboa
+df <- data.frame(date = DCA_real[['156']]$date, Real = DCA_real[['156']]$WSI,
+                 noHDNR = DCA_noH[['156']]$WSI, Observations = DCA_obs[['156']]$WSI)
+plot_df_interactive(df)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+
+date_ranges <- date_ranges_SPI
+
+p <- ggplot() +
+  #Add the drought rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
+  #Add the VD lines
+  geom_line(data = df, aes(x = date, y = value, linetype = Scenario, color = Scenario), alpha = 0.8, size = 1.25) +
+  #VD = 0 line
+  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
+  #geom_text(aes(as.Date("1985-01-01"), 0, label = "VD = 0", vjust = -1, hjust = 0)) +
[…]

### 2022-03-02 Supporting_scripts/Plot&tables/table_hdnr.R

@@ -1,6 +1,6 @@
 #Table construction
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 
 
 HDNR <- readOGR("./Data/HDNR/HDNR.shp")
@@ -34,3 +34,5 @@ View(table)
 
 options(scipen = 0)
 write.table(table, file = "./Data/Plot_table/small_res_rip.txt", sep = "\t", quote = FALSE)
+
+

### 2022-03-02 Supporting_scripts/check_new_scenarios.R

@@ -1,0 +1,128 @@
+
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+
+source("./Libraries/Libraries.R")
+source("./Libraries/Functions.R")
+source("./Libraries/Functions_TG.R")
+source("./Libraries/Functions_DP.R")
+source("./Libraries/Functions_CO.R")
+source("./Libraries/Functions_MC.R")
+
+#Load the maximum capacities of the reservoirs
+path_maxcap <- "./Inputs/Model_input/Directory_WASA_Banabuiu/Input/Reservoir/reservoir.dat"
+reservoirs <- read.table(path_maxcap, skip = 2, sep = "\t")
+maxcap <- reservoirs[,c(1,5)]
+names(maxcap) <- c('ID','max')
+maxcap[,2] <- maxcap[,2]*1000 #m3
+
+#Load the reservoirs' IDs
+load("./Inputs/General/IDs.RData")
+
+#Load the observations and the scenarios
+load("./Inputs/Calibration/df_observations.RData") #name: obs_df
+load("./Data/Scenarios/No_HDNR/nohdnr_volumes.RData") #name: noH_df
+load("./Data/Scenarios/Real/real_volumes.RData") #name: real_df
+
+#Names of the WASA outputs columns
+columns<-c("Subasin-ID", "year", "day", "hour", "qlateral",
+           "transposition", "inflow", "evap",
+           "prec", "intake", "overflow",
+           "qbottom", "qout", "withdrawal", "elevation", "area", "volume")
+
+
+
+# Compare noHDNR ----------------------------------------------------------
+#Compare the run with the intake time series with the run without
+#the intake time series
+
+path <- "./Data/Scenarios/No_HDNR/Model_output_nointake"
+date <- create_date_vector(1980, 2018)
+
+filepath <- paste0(path, "/res_156_watbal.out")
+ALvol <- read.table(filepath, skip = 3, header = FALSE)
+names(ALvol) <- columns
+ALvol <- date_col_WASA_out(ALvol)
+listt <- list(ALvol)
+ALvol <- create_main_dataframe(date, listt, IDs, timecol = 18, datacol = 17)
+ALvol <- monthly_scale(df, f = sumx)
+
[…]

### 2022-03-02 Supporting_scripts/diff_influence_updown.R

@@ -1,0 +1,91 @@
+#Different influence of the HDNR between downstream and upstream reservoirs
+
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+source("./Libraries/Libraries.R")
+source("./Libraries/Functions.R")
+
+DCA_real <- list.load("./Data/DCA/DCA_real.RData")
+DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
+
+res <- readOGR("./Data/Reservoirs/centralized_res.shp")
+res <- res@data
+
+# Compute the % of drought phases for each reservoir ----------------------------
+
+#Problem: each reservoir has a different SPI associated
+#> different meteorological conditions can influence more the number of months
+#> show also the cumulative number of months in a meteorological drought condition
+# ordered by downstreamness
+
+realDP <- nohDP <- data.frame(matrix(0, 4, length(res$subID)))
+names(realDP) <- names(nohDP) <- res$subID
+for(i in names(realDP)){
+  for(q in 1:4){
+    realDP[[i]][q] <- sum(DCA_real[[i]]$quadrant == q, na.rm = TRUE)
+    nohDP[[i]][q] <- sum(DCA_noH[[i]]$quadrant == q, na.rm = TRUE)
+  }
+}
+names(realDP) <- names(nohDP) <- paste0("x", res$subID)
+realDP$x138 <- nohDP$x138 <- NULL
+dum <- unname(apply(realDP, 2, function(x) sum(x)))
+for(i in 1:ncol(realDP)){
+  realDP[,i] <- realDP[,i]/dum[i]
+  nohDP[,i] <- nohDP[,i]/dum[i]
+}
+
+# Compute the % of increase in each reservoir -----------------------------
+#% of increase: in the hydrological drought phases (3 and 4)
+#Here the different SPI doesn't bother the results, since they are increases between
+#two scenarios, thus independent from each other
+#Cosa fa geom_abline e cosa fa
+#geom_smooth
+
+increase <- realDP - nohDP
+increase <- data.frame(ID = res$subID[res$subID != 138],
+                       Dx = res$dx[res$subID != 138],
+                       phase3 = t(increase[3,]*100),
+                       phase4 = t(increase[4,]*100))
+rownames(increase) <- NULL
[…]

### 2022-03-02 Supporting_scripts/lake_volume_handling.R

@@ -2,7 +2,7 @@
 
 # Setup -------------------------------------------------------------------
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
+setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
 
 source("./Libraries/Libraries.R")
 source("./Libraries/Functions.R")
@@ -16,7 +16,8 @@ extract_class = function(df, class_n, n_col = 4){
 }
 
 # Load the results of the model ------------------------------------------
-path <- "./Data/Scenarios/Real/Model_output"
+#path <- "./Data/Scenarios/Real/Model_output"
+path <- "./Data/Scenarios/SR/Model_output"
 WASA_hdnr <- read.table(paste0(path, "/lake_volume.out"), skip = 2)
 col <- unlist(strsplit(readLines(paste0(path, "/lake_volume.out"),n = 3)[2], "            "))
 col <- c("year", "month", "day", "class", col[4:length(col)])
@@ -28,6 +29,10 @@ class2 <- extract_class(WASA_hdnr, 2)
 class3 <- extract_class(WASA_hdnr, 3)
 class4 <- extract_class(WASA_hdnr, 4)
 class5 <- extract_class(WASA_hdnr, 5)
+
+c <- rep(4, 12)
+sum(c[1:6])
+sum(c[7:12])
 
 #Obtain monthly values (sum)
 date <- create_date_vector(1980, 2018)
@@ -58,9 +63,71 @@ class5 <- class5[, col_order]
 
 # Save the results --------------------------------------------------------
 
-save(class1, file = "./Data/Scenarios/Real/class1.RData")
-save(class2, file = "./Data/Scenarios/Real/class2.RData")
-save(class3, file = "./Data/Scenarios/Real/class3.RData")
-save(class4, file = "./Data/Scenarios/Real/class4.RData")
-save(class5, file = "./Data/Scenarios/Real/class5.RData")
+#path_save <- "./Data/Scenarios/Real"
+path_save <- "./Data/Scenarios/SR"
+save(class1, file = paste0(path_save, "/class1.RData"))
+save(class2, file = paste0(path_save, "/class2.RData"))
[…]

### 2022-03-02 Supporting_scripts/plot_without_baseline.R

@@ -1,0 +1,29 @@
+
+source("./Libraries/Functions_MC.R")
+load("./Data/volume_obs.RData")
+load("./Data/Scenarios/Real/real_daily.RData")
+
+obs <- monthly_scale(obs_df, f = mean)
+it <- monthly_scale(real_df, f = mean)
+ID <- 156
+code <- "Arrojado Lisboa"
+
+
+ID <- ID[which(ID %in% colnames(it))]
+vis_df <- data.frame(it$date, it[, which(colnames(it) %in% ID)],
+                     obs[, which(colnames(obs) %in% ID)])
+names(vis_df) <- c('date', "Calibrated", "Observations")
+df <- reshape2::melt(vis_df, id.vars = 'date', variable.name = 'Legend')
+p <- ggplot(df, aes(date, value/1e+9)) +
+  geom_line(aes(linetype = Legend, color = Legend), alpha = 0.8, size = 1.25) +
+  xlab('Date') + ylab(expression('Monthly volume (mean) [ km'^3*' ]')) +
+  theme(axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y') +
+  scale_color_manual(values = c("salmon1", "royalblue")) +
+  theme(axis.text.x = element_text(size = 16),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 16),
+        legend.position = "bottom")
+plot(p)

### 2022-03-03 Scripts/Drafts/Time_series_processing.Rmd
folders reorganization

---
title: "Time series processing"
author: "Paolo Colombo"
date: "14/6/2021"
output: html_document
---

# Purpose

Processing of the generated time series. At first, remove the outliers, then remove the NAs.

## Functions

```{r functions definition}
check_outlier = function(dataframe, datecol = 1){
  for(i in 1:ncol(dataframe)){
    if(i != datecol){
      Q1<-quantile(dataframe[,i],0.25, na.rm = TRUE)
      Q3<-quantile(dataframe[,i],0.75, na.rm = TRUE)
      IQR<-Q3-Q1
      upper_limit<-Q3 + 1.5*IQR
      lower_limit<-Q1 - 1.5*IQR
      print(i)
      print(sum(dataframe[,i] > upper_limit, na.rm = TRUE)+sum(dataframe[,i] < lower_limit, na.rm = TRUE))
    }
  }
}

remove_outlier = function(dataframe, datecol = 1, fill_val = NA){
  for(i in 1:ncol(dataframe)){
    if(i != datecol){
      Q1<-quantile(dataframe[,i],0.25, na.rm = TRUE)
      Q3<-quantile(dataframe[,i],0.75, na.rm = TRUE)
      IQR<-Q3-Q1
      upper_limit<-Q3 + 1.5*IQR
      lower_limit<-Q1 - 1.5*IQR
      dataframe[,i][dataframe[,i] > upper_limit]<-fill_val
      dataframe[,i][dataframe[,i] < lower_limit]<-fill_val
    }
  }
  dataframe
}

remove_na = function(dataframe, skipcol = 1, k = 7, maxgap = 31){
  #skipcol: number of columns to skip
  firstcol<-1+skipcol
  for(i in firstcol:ncol(dataframe)){
    dataframe[,i]<-imputeTS::na_ma(dataframe[,i], k = k, maxgap = maxgap)
  }
  dataframe
}

```

# Remove outliers

```{r}
#Load the generated time series file

```

### 2022-03-03 Scripts/Main_code/downstreamness_analysis.Rmd
folders reorganization

--- 2021-08-06 Main_code/downstreamness_analysis.Rmd
@@
 
+* Download a DEM of the Banabuiu region [Here how to download it from NASA][youtube tutorial]
 * Merge the DEM
 * Cut it around the Banabuiu basin area
+* Obtain flow accumulation
+
+[youtube tutorial]: https://www.youtube.com/watch?v=0nmYzQo0OSY
 
@@
   + This point shapefile should contain, for each point: coordinates, capacity, SubbasinID, a Boolean value indicating if it is a monitored reservoir
-* Download a DEM of the Banabuiu region [Here how to download it from NASA][youtube tutorial]
-
-[youtube tutorial]: https://www.youtube.com/watch?v=0nmYzQo0OSY
 
@@
 * Subdivide the whole Banabuiu DEM into the sub-catchments
-* From the DEM, compute the area of the upsream sub-catchment relative to each reservoir in that sub-catchment
+* From the DEM, compute the area of the upstream sub-catchment relative to each reservoir in that sub-catchment
 * Compute D~x~ for each reservoir by dividing their upstream area by the total area
@@
 Since the real positions of the small reservoirs are not considered in the WASA model, we cannot rely on the volume allocation throughout the five classes operated by the model.
-So, for each subcatchment we can consider all the reservoirs in the 5 classes, and assign them the same volume, obtained by summing the volumes of the classes and dividing by the number of reservoirs.
+So, for each subcatchment we can consider all the reservoirs in the 5 classes, and assign them the same volume, obtained by summing the volumes of the classes and dividing by the number of reservoirs in that catchment.
 The number of reservoirs to calculate the mean volume can be obtained by reclassifying the HDRN reservoirs considering the increase coefficient in the WASA model backwards, so by computing  the number of reservoirs in the previous years by applying the increase coefficient backwards.

### 2022-03-03 Scripts/Core_code/2_DRN_operations/2_New_hdrn.Rmd
folders reorganization

---
title: "Creation of the new HDRN shapefile with capacities associated"
author: "Paolo Colombo"
date: "26/4/2021"
output: html_document
---

# Libraries and functions

```{r libraries}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

# Cleaning of the Global Water shapefile

The Global Water was vectorialized from a raster using QGIS. Since it was distributed over two rasters, they were merged and then cut over the Banabuiu area.

## Load of the shapefile

```{r}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data")

global_water<-readOGR(dsn = "./Global_surface_water/shape/cut_merged.shp")
```

## Remove the big reservoirs from Global Water

```{r}
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
main_resI<-st_read(paste0(path,"/mainreservoirsI_cut_ref.shp"))
main_resII<-st_read(paste0(path,"/mainreservoirsII_cut_ref.shp"))

threshold<-min(main_resI$AREA)
glob_wat_cut<-global_water[which(global_water$area_geom < threshold),]

```

## Remove DN = 0 from Global Water

DN = 1 means that in that element water is present. Removing the shapes which present DN = 0 is then useful for the next step in QGIS (the NNJoin), so that the HDRN points will not be matched with the areas which don't present water in them.

```{r}
glob_wat_cut<-glob_wat_cut[which(glob_wat_cut$DN == 1),]
```

## Export the "clean" shapefile

```{r}
writeOGR(glob_wat_cut,dsn = "./Global_surface_water/shape", layer = "global_wat_cut",
         driver = "ESRI Shapefile" )
```

# HDRN update

The Global Water shapefile has been joined to the FUNCEME reservoirs shapefile. In the joined output, each reservoir has an associated area. There are reservoirs that are associated to the same water body in the Global Water shapefile, meaning that there wasn't the same number of water bodies in the Global Water shapefile as the number of small reservoirs present in the FUNCEME shapefile. The duplicate with the highest distance from the water body will be assigned to the lowest class of reservoirs, following the hypothesis that if it is not present in the Global Water map, it was too small to be detected.

## Load of the new shapefile

```{r load HDRN to update}
HDRN_update<-readOGR(dsn = "./HDRN/HDRN_update_area_ID.shp")
```

## Calculate capacities and define the reservoir classes

```{r Molle relationship}
# Molle area-volume relationship
#Volume = k*(Area/(a*k))^(a/(a-1))
#Area = a*k*(Volume/k)^((a-1)/a)

k <- damk_Molle <- 1500
a <- alpha_Molle <- 2.7

HDRN_update$capacity<-k*(HDRN_update$join_area_/(a*k))^(a/(a-1)) #m3

#Area = a*k*(100000/k)^((a-1)/a)

#Reservoirs classes definition
# res_class<-c(
#               102179,
#               151360,
#               265735,
#               758010,
#               875797530
#             )
#this classification doesn't make any sense with the values we have
#quantile(HDRN_update$capacity, probs = seq(0, 1, 0.2))

#cap_glob<-k*(glob_wat_cut$area_geom/(a*k))^(a/(a-1))
#quantile(cap_glob, probs = seq(0, 1, 0.2))

#Reservoirs classes definition
#From Mamede et al. 2018
res_class<-c(
              5000, #m3
              25000,
              50000,
              100000,
              max(HDRN_update$capacity)+1
            )

```

## Filtering of the duplicates

Find the HDRN's reservoirs (id) that present the same Global Water reservoir (join_fid). To the one with the highest distance, associate the capacity of the smallest reservoir class

```{r associate lowest res class (m1)}
#First method: associate the lowest class to the points with no associate global water
#1. Find the duplicates
#2. Select the point with the lowest distance
#3. To the points with a distance higher than the minimum, associate the lowest reservoir class

tic("Lowest reservoir class to points with no associate global water")
subset<-HDRN_update[duplicated(HDRN_update$join_fid),]
for(i in 1:length(subset$join_fid)){
  #Take the first duplicate ID
  check1<-subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]

  #Associate the lowest reservoir class to the points with distance higher
  #than check2
  HDRN_update$capacity[which(HDRN_update$join_fid %in% check1
                             & HDRN_update$distance > check2
                             & HDRN_update$id != check3)]<-res_class[1]-0.1
}
remove(subset, check1, check2, check3)
toc()

summary(HDRN_update@data)

#Export the updated HDRN
# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v1",
#          driver = "ESRI Shapefile")
```

```{r remove (m2)}
#Second method: remove the points with no associate global water
#1. Find the duplicates
#2. Select the point with the lowest distance
#3. Remove the points with a distance higher than the minimum

tic("Removal of points with no associated global water")
subset<-HDRN_update[duplicated(HDRN_update$join_fid),] #Finds the duplicates
for(i in 1:length(subset$join_fid)){
  #Take the first duplicate ID
  check1<-subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]

  #Remove the duplicate points with a distance higher than check2
  HDRN_update<-HDRN_update[which(!(HDRN_update$join_fid %in% check1
                                      & HDRN_update$distance > check2
                                      & HDRN_update$id != check3)),]
}
remove(subset, check1, check2, check3)
toc()

summary(HDRN_update@data)

#Export the updated HDRN
# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v2",
#          driver = "ESRI Shapefile" )
```

## Classification

On QGIS, visualized that none of the reservoirs in the highest class are the same as the main reservoirs.

```{r classification}
#Do the classification in the same way as the other script

#Load the updated HDRN
#Method 1 (Unidentified reservoirs associated to the lowest class)
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v1.shp"
#Method 2 (Unidentified reservoirs removed)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v2.shp"

HDRN_update<-readOGR(path)

#Dataframe creation: first column SubbasinID, others number of reservoirs in the classes
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
subbasins<-st_read(paste0(path,"/subbasins_cut.shp"))
count_class <- subbasins %>%
                filter(!is.na(SubbasinID)) %>%
                group_by(SubbasinID) %>%
                summarize()
count_class <- data.frame(count_class$SubbasinID)
names(count_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(count=n())
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(count_class$SubbasinID)){
        if(c$SubbasinID[a]==count_class$SubbasinID[b]) count_class[b,i+1]<-c$count[a]
    }
  }
}
names(count_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
count_class[is.na(count_class)]<-0

#Class ripartition
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
count_class<-read.table(paste0(path, "/lake_number_newHDRN_met2.dat"), skip = 2)

for(i in 2:6){
  print(paste0("Percentage of resevoirs in Class ",i-1))
  print(paste0(round(sum(count_class[,i])/sum(count_class[,2:6]),digits = 3)*100," %"))
}
```

### Creation of lake.dat

```{r lake.dat}
#Create the dataframe
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: this parameter can be changed in the calibration phase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
View(par_class)

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

### Creation of lake_number.dat

```{r lake_number}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(count_class,file=paste0(path,"/lake_number_newHDRN_met2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
```

### Creation of lake_maxvol.dat

For each subbasin, a representative reservoir in each class can be identified, and its starting volume can be provided to WASA in the lake_maxvol.dat file. To identify the representative reservoir for each class, take the median capacity in each reservoir class, for each subbasin.
In the gen_files folder a lake_maxvol computed with the mean can also be found.

```{r representative reservoirs}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
res<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")

median_class<- data.frame(res$SubbasinID)
names(median_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(median(capacity))
  }else{
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(median(capacity))
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(median_class$SubbasinID)){
        if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
    }
  }
}
names(median_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
median_class[is.na(median_class)]<-0
```

```{r export lake_maxvol}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newHDRN_m2_median.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
```

# Scenario without the HDRN

Create lake_number.dat in order to be able to evaluate the scenario without small reservoirs in the WASA model.
Since lake_maxvol.dat is an optional file, it will not be provided to the model when evaluating this scenario.

```{r no HDRN lake}
#Dataframe construction
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake_noHDRN.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

```{r no HDRN lake_number}
#Sub-basins without networks of small reservoirs must not be entered in the file.
#Create a blank file and try if it works
#Otherwise, create a file with only 1 reservoir for each subbasin, in the lowest class

#No reservoirs
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noHDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)

#Only one resevoir in the smallest reservoir class
count_class[,2]<-1
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

#Only zeros
#it works!!!!
count_class[,2]<-0
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v3.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

```

### 2022-03-03 Scripts/Core_code/main.R

@@ -1,0 +1,35 @@
+#Main to launch the core operations
+#
+#The launched operations are all stored in the "Core_code" folder.
+#Each code has the name of the operation it performs.
+#
+#Author: Paolo Colombo
+
+# Data processing ------------------------------------------------
+
+#download_DEM
+#stations_outlier_removal
+#time_series_generation_script
+#prec_out_removal
+#output_na_removal
+
+# DRN operations -------------------------------------------------
+
+#2_new_hdrn
+
+# WASA-SED model pre-procedures ----------------------------------
+
+#intake_generation
+#rainy_season_update
+
+# WASA-SED model calibration and validation ----------------------
+
+#mod_cal
+#Validation
+
+# Analysis -------------------------------------------------------
+
+#downstreamness_analysis
+#drought_cycle_analysis
+#drought_evo
+#NSR_scenarios

### 2022-03-03 Scripts/Figures_code/downstreamness_plot.R

@@ -178,7 +178,7 @@ dt <- Dsv_r$date
 rdsc <- data.frame(date = dt, dsc = 0)
 nhdsc <- data.frame(date = dt, dsc = 0)
 
-for(i in 1:length(Dsc_r$date)){
+for(i in seq_len(length(Dsc_r$date))){
   rdsc$dsc[lubridate::year(rdsc$date) == Dsc_r$date[i]] <- Dsc_r$Dsc[i]
   nhdsc$dsc[lubridate::year(nhdsc$date) == Dsc_nH$date[i]] <- Dsc_nH$Dsc[i]
 }

### 2022-03-17 R/Core_code/1_Data_processing/time_series_generation_script.R
update repository

@@ -1,0 +1,178 @@
+#Time series generation script
+
+# Setup ---------------------------------------------------------------
+
+setwd("C:/Directory_thesis_codes")
+path_export <- "C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/gen_2006"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+
+#Load the subbasins' shapefile
+path <- "C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
+subbasins <- readOGR(paste0(path, "/subbasins_cut_geomfix.shp"))
+
+# Precipitation FUNCEME ----------------------------------------------------
+
+#Load the stations
+path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
+prec_input = create_data_list(path, c("year","month","day","data"))
+
+#Remove anomalous stations (more information: "prec_out_rem.R")
+n <- find_anomalous_stations(prec_input)
+if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
+date <- create_date_vector(1980, 2018)
+prec_pos <- create_position_vector(prec_input[[1]])
+prec_input[[2]] <- add_date_column(prec_input[[2]])
+prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
+#Other anomalous stations removal (more information: "prec_out_rem.R")
+remove_st <- anomalous_prec_st(prec_df, 250)
+prec_df <- prec_df[-remove_st]
+#Outlier removal (more information: "prec_out_rem.R")
+prec_df <- rejection_threshold(prec_df, method = "value", 250)
+
+tic("Precipitation FUNCEME - Creation of the WASA input file")
+output_prec <- create_time_series_Wmean(main_dataframe = prec_df,
+                                        positions = prec_pos,
+                                        layer = subbasins)
+h = "Daily average precipitation [mmd] for each subasin, ordered according Map-IDs\nDate No. of days Subasin-ID\n0 0 123 125 126 127 134 137 138 139 142 143 144 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160"
[…]

### 2022-03-17 R/drafts/1_WASA_inout_comp.Rmd
update repo

---
title: "WASA input and output files import and Comparison with reservoirs observations"
author: "Paolo Colombo"
date: "2/4/2021"
output: html_document
---

# Libraries and functions

Load the libraries and functions needed and set the correct directory.

```{r libraries and functions}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")

setwd("C:/Thesis_fortran/WASA")
```

# WASA input files

## Creation of an index for the WASA input files and import them

```{r Creation of an index for the input files}
input<-list.files(path="./Input",full.names = T,recursive = TRUE)
input_index<-as.data.frame(matrix(nrow = length(input),ncol = 2))
names(input_index)<-c("path","description")
input_index$path<-input; remove(input)
for(i in 1:length(input_index$path)){
  input_index$description[i]<-readLines(input_index$path[i], n=5)[1]
}
View(input_index)

#Import the values to correctly read each file
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
read_value<-read.table(paste0(path,"/sk_vn_sep.txt"),header = TRUE,sep = "\t")

#Creation of a list containing all the input files
#Work in progress, it needs in input all the sk, vn and sep for each file

input_files<-list()
for(i in 1:nrow(input_index)){
  name<-basename(input_index$path[i])
  if(read_value$sk[i] == "-"){
    input_files[[name]]<-c("This file is not a standard dataset")
  }else if(read_value$problem[i] == 1){
    input_files[[name]]<-c("This file has problems in the number of columns")
  }else{
    x<-read.table(input_index$path[i], skip = read_value$sk[i], sep = "\t")
    input_files[[name]]<-x
    vn<-as.numeric(read_value$vn[i])
    if(read_value$sep[i] == 1){
      col<-unlist(strsplit(readLines(input_index$path[i], n = 5)[vn], "[,]"))
    }else col<-unlist(strsplit(readLines(input_index$path[i],n = 5)[vn], " "))
    names(input_files[[name]])<-col; remove(col)
  }
}
remove(x)
```

## WASA input files visualization

```{r Input files visualization}
#Write the number of the file you would like to visualize
nfile<-16

#Look at the first 5 lines of the file
print(basename(input_index$path[nfile]))
readLines(input_index$path[nfile], n = 5)

#View the file as it has been imported in R
View(input_files[[nfile]])
```

# WASA output data

In the Output folder are stored all the output files generated by WASA.
Each file refers to a reservoir in the Cearà state, and each reservoir has an assigned code which is the code assigned to its sub-basin.
The three biggest sub-basins/reservoirs included in the Banabuiu basin are:
  - Acude Arrojado Lisboa (Banabuiu): Sub-basin ID 156
  - Acude Pedras Brancas: Sub-basin ID 123
  - Acude Fogareiro: Sub-basin ID 160
Alongside them, in the Banabuiu basin are also present:
  - Acude Pirabibu: Sub-Basin ID 147
  -	Acude Cedro: Sub-Basin ID:127
  -	Acude Patu: Sub-Basin ID: 149
  -	Acude Serafim Dias: Sub-basin ID 150
  -	Acude Cipoada: Sub-Basin ID 126
  -	Acude Poco do Barro: Sub-Basin ID 125
  -	Acude Vieirao: Sub-Basin ID 151
  -	Acude Sao Jose II: Sub-Basin ID 145
  -	Acude Quixeramobim: Sub-Basin ID 143
  -	Acude Trapia II: Sub-Basin ID 153
  -	Acude Sao José I: Sub-Basin ID 148
  -	Acude Capitao Mor: Sub-Basin ID 154
  -	Acude Monsenhor Tabosa: Sub-Basin ID 152
  -	Acude Jatoba: Sub-Basin ID 146
  -	Acude Curral Velho (Morada Nova): Sub-Basin ID 138
  -	Acude Umari: Sub-Basin ID 142

## Load Banabuiu reservoirs' names and IDs

```{r}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
reservoirs<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
```

## Set up the procedure to import WASA output files

Since WASA's output files are in the _.out_ format, the function needed to import them is _read.fwf_, which needs in input the positions of each column to be selected. Below this need is set up.

```{r set up for the import of WASA output files}
position<-c(0,7,13,19,25,35,45,55,68,81,91,101,111,121,131,141,155,169)
widths<-diff(position)
columns<-c("Subasin-ID", "year", "day", "hour", "qlateral(m**3/s)", "transposition(m**3/s)", "inflow(m**3/s)", "evap(m**3)", "prec(m**3)", "intake(m**3/s)", "overflow(m**3/s)", "qbottom(m**3/s)", "qout(m**3/s)", "withdrawal(m**3/s)", "elevation(m)", "area(m**2)", "volume(m**3)")

#Create a column
reservoirs$file<-paste0("./Output/res_",reservoirs$SubbasinID,"_watbal.out")
```

## Load of WASA's reservoirs' water balance output files

```{r load WASA output files}
#Create an index for WASA output files
output<-list.files(path="./Output",full.names = T,recursive = TRUE)
#View(output)

#Check if some reservoir is missing from WASA output files
check<-length(reservoirs$file)-length(output[which(output %in% reservoirs$file)])
if(check > 0){
  reservoirs$Reservoir_name[which(!(reservoirs$file %in% output))]
  print("The reservoirs above are missing from WASA's output files")
  not_present<-which(!(reservoirs$file %in% output))
}
#Morada Nova and Umari reservoirs are missing from WASA's output files

#Order the file list and names by the SubbasinID
reservoirs<-reservoirs[order(reservoirs$SubbasinID),]
row.names(reservoirs)<-NULL

#Create a list containing the WASA output files
tic("Import WASA reservoir output files")
WASA_reservoirs<-list()
for(i in 1:nrow(reservoirs)){
  name<-paste0("modres_",reservoirs$SubbasinID[i])
  if(i %in% not_present){
    WASA_reservoirs[[name]]<-"The WASA output file for this reservoir is not present"
  }else{
    WASA_reservoirs[[name]]<-read.fwf(reservoirs$file[i], widths = widths, skip = 3)
    names(WASA_reservoirs[[name]])<-columns
    #Add a column with the full date
    WASA_reservoirs[[name]]$time<-time_index(WASA_reservoirs[[name]])
  }
}
toc() # 1 min
```

## Modelled reservoirs time boundaries

Since not all reservoirs exist from the same year, and since the model is run only until a prefixed date, below the starting and ending date for each time series of the modelled reservoirs are stored in the *starts_ends_mod* dataframe.

```{r mod time boundaries}
#Creation of a dataframe containing the starting and ending date of each reservoir

starts<-data.frame(WASA_reservoirs[[1]]$time[1])
ends<-data.frame(WASA_reservoirs[[1]]$time[length(WASA_reservoirs[[1]]$time)])

for(i in 2:(length(WASA_reservoirs))){
  if(is.data.frame(WASA_reservoirs[[i]])){
    starts[i]<-as.Date(WASA_reservoirs[[i]]$time[1], format = "%Y-%m-%d")
    ends[i]<-as.Date(WASA_reservoirs[[i]]$time[length(WASA_reservoirs[[i]]$time)],
                      format = "%Y-%m-%d")    
  }else{
    starts[i]<-NA
    ends[i]<-NA
  }
}
colnames(starts)<-NULL; colnames(ends)<-NULL

starts_ends_mod<-data.frame(t(starts),t(ends));  remove(starts,ends)
names(starts_ends_mod)<-c("starts","ends")
```

# Observations
## Observations upload

Creare indice per i file nella cartella
Associargli il SubbasinsID corretto

```{r obs upload}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/volume_series_banabuiu_reservoirs_ID"

obs<-data.frame(list.files(path = path, full.names = T, recursive = TRUE))
names(obs)<-"path"
obs$SubbasinID<-gsub("\\..*","",basename(obs$path))

tic("Import files of reservoir observations")
Obs_reservoirs<-list()
for(i in 1:nrow(obs)){
  name<-paste0("obsres_",obs$SubbasinID[i])
  Obs_reservoirs[[name]]<-read.csv(obs$path[i], header = TRUE, sep = ",")
}
toc() # 1 sec
```

## Observations time boundaries

```{r mod time boundaries}
#Creation of a dataframe containing the starting and ending date of each reservoir

starts<-data.frame(Obs_reservoirs[[1]]$date[1])
ends<-data.frame(Obs_reservoirs[[1]]$date[length(Obs_reservoirs[[1]]$date)])
for(i in 2:(length(Obs_reservoirs))){
  starts[i]<-as.Date(Obs_reservoirs[[i]]$date[1], format = "%Y-%m-%d")
  ends[i]<-as.Date(Obs_reservoirs[[i]]$date[length(Obs_reservoirs[[i]]$date)],
                   format = "%Y-%m-%d")
}
colnames(starts)<-NULL; colnames(ends)<-NULL

starts_ends_obs<-data.frame(t(starts),t(ends));  remove(starts,ends)
names(starts_ends_obs)<-c("starts","ends")
```

# Visual comparison between obseved and modelled reservoirs
## Creation of the dataset for visualization

```{r combining modelled and observed datasets}
#Combining modelled and observed datasets

list_mod<-WASA_reservoirs
list_obs<-Obs_reservoirs

list_comb<-list()
list_comb_vis<-list()
for(i in 1:length(list_mod)){
  if(!is.na(starts_ends_mod$starts[i])){
  index1<-which(list_mod[[i]][["time"]] == starts_ends_obs$starts[i])
  mod<-data.frame(list_mod[[i]][["volume(m**3)"]][index1:length(list_mod[[i]][["volume(m**3)"]])])
  names(mod)<-c("volume")
  index2<-which(list_obs[[i]][["date"]] == starts_ends_mod$ends[i])
  obs<-data.frame(list_obs[[i]][["volume"]][1:index2])
  names(obs)<-c("volume")
  date<-list_mod[[i]][["time"]][index1:length(list_mod[[i]][["time"]])]
  mod$id<-"Model"; mod$date<-date
  obs$id<-"Observation"; obs$date<-date

  #Analysis dataframe creation
  comb<-data.frame(mod,obs)
  list_comb[[i]]<-comb
  #Visualization dataframe creation
  vis_comb<- rbind.data.frame(mod,obs)
  list_comb_vis[[i]]<-vis_comb
  }else{
    list_comb[[i]]<-"Remove"
    list_comb_vis[[i]]<-"Remove"
  }
}
list_comb<-remove_list_elements(list_comb)
list_comb_vis<-remove_list_elements(list_comb_vis)

reservoir_names<-paste0("res_",reservoirs$SubbasinID[which(!is.na(starts_ends_mod$starts))])
names(list_comb)<-reservoir_names
names(list_comb_vis)<-reservoir_names
```

## Visualization of modelled and observed time series

```{r visualization of modelled and observed time series}
scaling_factor<-1000
graph_titles<-paste0(reservoirs$Reservoir_name[which(!is.na(starts_ends_mod$starts))],
                     " (",reservoir_names,")")
for(i in 1:length(list_comb_vis)){
  Legend<-list_comb_vis[[i]][["id"]]
  print(ggplot(data = list_comb_vis[[i]],
         aes(x = list_comb_vis[[i]][["date"]],
             y = list_comb_vis[[i]][["volume"]]/scaling_factor))+
        geom_line(aes(colour = Legend),size = 1)+
        labs(x = "Date", y = paste0("Volume [", scaling_factor," ",
                                parse(text='m^3'),"]"), 
              title = graph_titles[i])+
        scale_x_date(breaks = scales::breaks_width("5 years"),
               labels = scales::label_date_short())+
        scale_y_continuous(labels = scales::label_comma()))
}
```

### 2022-03-17 R/drafts/Input_file_gen.Rmd
update repo

---
title: "Input file generation"
author: "Paolo Colombo"
date: "20/4/2021"
output: html_document
---

# Notes

* (in Big Reservoirs load and visualization) Pirabibu, Sità Cedro and Banabuiu reservoirs don't have a capacity associated to them in the shapefile. Which is the unit measure of the capacity in both shapefiles? Look online to find the capacities.
* (in Computation of the storage capacities) The area-volume relationship used seems to provide small volumes, check if it is correct.
* (in Reservoir classification by size) Are there standard classes to use to distinguish the different small reservoirs? **in Krol 2011** I found a reference to the classes but not to their boundaries
* (in Computation of the storage capacities) The file from Germano doesn't have the area information since the shapefile is a point shapefile. _We have to obtain this data in order to use the shapefile!_
* (in Time series update) Where should I download the data? I need georeferenced data to be able to create that kind of file (rows: days, columns: rain intensity for each SubbasinID)
* Subbasin 134 ends up in Subbasin 121 which is not defined! How to solve this?
* The number of the reservoirs in the different classes are not the same as the file provided by George and Alexandre. It may be that the coefficients change depending on the reservoir area (1), or it may depend on the classes they defined to divide the reservoirs (2). 1 > Check if this is true and then find the coefficients 2 > Ask them what did the do

# Files that have to be updated

**Just cut them around the Banabuiu basin**

* Hillslope/hymo.dat
* Hillslope/rainy_season.dat
* Hillslope/soil.dat
* Hillslope/soil_vegetation.dat
* Hillslope/soter.dat
* Hillslope/terrain.dat
* Hillslope/vegetation.dat

_all these can be generated through lumpR_

**Update them**

Parameters

* (lumpR) River/routing.dat         _done_ by "cutting"
* (lumpR) River/response.dat        _done_ by "cutting"
* Reservoir/lake.dat                _done_
* Reservoir/lake_maxvol.dat         _done_ by "cutting"
* Reservoir/lake_number.dat         _done_ **NEEDS TO BE CHECKED**
* (lumpR) Reservoir/reservoir.dat   _done_ by "cutting"
* Reservoir/cav.dat                 _done_ by "cutting"
* Reservoir/exttranspo_168_res.dat  _done_ by "cutting"

Time series

* Time_series/extraterrestrail_radiation.dat
* Time_series/humidity.dat
* Time_series/radiation.dat
* Time_series/rain_daily.dat
* Time_series/temperature.dat

**New optional files**

* Others/**calibration.dat**
* Reservoir/lake_frarea.dat
* Reservoir/**lake_year.dat**   (specification of changes in the number of reservoirs in the size classes)

**Decide what to do with these**

* Input/maxdim.dat
* Others/scaling_factor.dat
* Input/outfiles.dat

# Things to do on QGIS

- Associate to each reservoir the sub-basin ID (create a new column) _done_
-

# Libraries and functions

```{r libraries}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

# Load and visualization

Before importing the data here, to each shapefile a new column containing the SubbasinID corresponding to the objects (the reservoirs) has been added via QGIS

## Subbasins load and visualization

```{r subbasins.shp}
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
subbasins<-st_read(paste0(path,"/subbasins_cut.shp"))
subbasins_plot<-ggplot()+
            geom_sf(data = subbasins)+
            ggtitle("Subbasins in Banabuiu basin - Mamede file")+
            coord_sf()
subbasins_plot

#subbasins$SubbasinID contains all the Subbasin IDs in the Banabuiu basin

```

## HDRN load and visualization

```{r HDRN1 load}
#Shapefile provided by Mamede
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
HDRN1<-st_read(paste0(path,"/smalldams_cut_ref.shp"))
HDRN1_plot<-ggplot()+
            geom_sf(data = HDRN1)+
            ggtitle("Small reservoirs in Banabuiu basin - Mamede file")+
            coord_sf()

nHDRN1<-length(HDRN1$Area__m2_) #1381 small reservoirs

HDRN1[which(is.na(HDRN1$SubbasinID)),]
#check in QGIS if there are geometries that need to be fixed
#and redo the SubbasinID association

```

```{r HDRN2 load}
#Shapefile provided by Germano
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu_shapefile/reserv_banabuiu.shp"
HDRN2<-st_read(path)
HDRN2_plot<-ggplot()+
            geom_sf(data = HDRN2)+
            ggtitle("Small reservoirs in Banabuiu basin - Germano file")+
            coord_sf()

nHDRN2<-length(HDRN2$geometry) #17322 reservoirs
```

```{r HDRN visual comparison}
#Visual comparison between the two shapefiles
#install.packages("gridExtra")

grid.arrange(HDRN1_plot,HDRN2_plot,ncol=2)
```

## Big reservoirs load and visualization

```{r mainI, mainII}
setwd("C:/Thesis_fortran/WASA/shapefile/Banabuiu")

main_resI<-st_read("mainreservoirsI_cut_ref.shp")
main_resI_plot<-ggplot()+
                geom_sf(data = main_resI)+
                ggtitle("Main reservoirs in Banabuiu basin - I")+
                coord_sf()
main_resI_plot

#summary(main_resI)
main_resI[which(is.na(main_resI$SubbasinID)),]
sum(is.na(main_resI$SubbasinID))
#no NA generated in the SubbasinID association

main_resII<-st_read("mainreservoirsII_cut_ref.shp")
main_resII_plot<-ggplot()+
                geom_sf(data = main_resII)+
                ggtitle("Main reservoirs in Banabuiu basin - II")+
                coord_sf()
main_resII_plot

#summary(main_resII)
main_resI[which(is.na(main_resI$SubbasinID)),]
sum(is.na(main_resI$SubbasinID))
```

```{r adjust (to do!)}
#Adjust the two dataframes to have only name, Subbasin ID and capacity
#Then put them togheter

```

# lake_number.dat

## Computation of the storage capacities

From the area of the geometrical elements, obtain the storage capacity of the reservoirs. The storage capacity can be obtained from the reservoir area through Molle area-volume relationship.

The Molle area-volume relationship here used and its parameters are explained in [Mamede et al., 2018, Eq. 9][1]

```{r Molle relationship}
# Molle area-volume relationship
#Volume = k*(Area/(a*k))^(a/(a-1))
#Area = a*k*(Volume/k)^((a-1)/a)

k <- damk_Molle <- 1500
a <- alpha_Molle <- 2.7

HDRN1$capacity<-k*(HDRN1$Area__m2_/(a*k))^(a/(a-1)) #m3

```

## Reservoir classification by size

Classification of the reservoirs depending of the volume classes.
In lake_number.dat are not included the big reservoirs.

The classes boundaries are defined based on the storage capacities of the reservoirs. The classification present in [Mamede et al., 2018, Table 2][1] can't be represented here, as capacities of the reservoirs in HDRN1 exceeds the maximum class present in the article. So, another classification is used.

```{r class definition}
#Class boundaries definition

res_class<-c(
              102179,
              151360,
              265735,
              758010,
              875797530
            )

res_class <- c(69977.1,	124097.8,	201545.9,	403173.9,	883301)

#Classes defined based on the quantiles
#res_class<-quantile(HDRN1$capacity, probs = seq(0, 1, 0.2))
#res_class
```

## Count of the reservoirs

Count the number of reservoirs in the different volume classes

Comparing these results with the lake_number.dat file we already have it is clear that the big reservoirs aren't included in lake_number.dat
Also, the reservoirs used for this classification are the ones from the smalldams.shp, so approximately 1/10 of the reservoirs in the other shapefile.

```{r reservoir count}
#Dataframe creation: first column SubbasinID, others number of reservoirs in the classes
count_class <- subbasins %>%
                filter(!is.na(SubbasinID)) %>%
                group_by(SubbasinID) %>%
                summarize()
count_class <- data.frame(count_class$SubbasinID)
names(count_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- HDRN1 %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification
          filter(capacity <= res_class[i] & capacity > res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- HDRN1 %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification
          filter(capacity <= res_class[i]) %>%
          summarize(count=n())
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(count_class$SubbasinID)){
        if(c$SubbasinID[a]==count_class$SubbasinID[b]) count_class[b,i+1]<-c$count[a]
    }
  }
}
names(count_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
count_class[is.na(count_class)]<-0

115+	19	+17+	16	+3
```

## File generation

```{r lake_number.dat}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"

my.write(count_class,file=paste0(path,"/lake_number.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
```

# lake.dat

* *Reservoir_class-ID* : ID of reservoir size class
* *maxlake0*: Upper limit of reservoir size class in terms of volume [m³]
* *lake_vol0_factor*: Fraction of storage capacity that indicates the initial water volume in the reservoir size classes [-]
* *lake_change*: Factor that indicates yearly variation in the number of reservoirs of the size classes [-]
* *alpha_Molle*, *damk_Molle*: Parameters of the area-volume relationship in the reservoir size classes (Area=alpha.k.(Vol/k)alpha/(alpha-1)) [-]. Values of reservoir area and volume are expressed in m² and m³, respectively
* *damc_hrr*, *damd_hrr*: Parameters of the spillway rating curve in the reservoir size classes (Qout=damc_hrr.Hvdamd_hrr) [-]. Values of water height over the spillway and overflow discharges are expressed in m and m³/s, respectively

```{r par_class creation}

par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      res_class,      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

View(par_class)
```

## File generation

```{r lake.dat}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"

my.write(par_class,file=paste0(path,"/lake.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
```

# lake_maxvol.dat

This method could be used also for the Hillslope module in case we don't understand the lumpR package/the data needed is difficult to find.

```{r lake_maxvol.dat}
#Upload of the complete file from the input files provided by Mamede

path<-"C:/Thesis_fortran/WASA/Input/Reservoir"
lake_maxvol<-read.table(paste0(path,"/lake_maxvol.dat"),skip=2,sep="\t")
names(lake_maxvol)<-c(unlist(strsplit(readLines(paste0(path,"/lake_maxvol.dat"),n=5)[2], "[,]")),"class2","class3","class4","class5")

#Select only the Banabuiu subbasins
lake_maxvol<-lake_maxvol[lake_maxvol[,1] %in% subbasins$SubbasinID,]

path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(lake_maxvol,file=paste0(path,"/lake_maxvol.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
```

# routing.dat

```{r routing.dat}
path<-"C:/Thesis_fortran/WASA/Input/River"

#Load
routing<-read.table(paste0(path,"/routing.dat"),skip=2,sep="\t")
names(routing)<-c(unlist(strsplit(readLines(paste0(path,"/routing.dat"),n=5)[2], "[,]")))

#Cut + Order update
routing<-routing[routing$` Subasin-ID(upstream)` %in% subbasins$SubbasinID,]
routing$No.<-seq(1,length(routing$No.),1)

#Subbasin 134 ends up in Subbasin 121 which is not defined!
#How to solve this?

#File generation
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(routing,file=paste0(path,"/routing.dat"),
         header = "Specification of routing order (flow directions)\nNo., Subasin-ID(upstream), Subasin-ID(downstream)", f = write.table)

```

# File gereration by cutting the original files for the whole Cearà state

All the files below will be obtained starting from the files provided by Mamede, by selecting the subbasins included in the Banabuiu river basin.

* Hillslope/hymo.dat
* Hillslope/rainy_season.dat
* Hillslope/soil_vegetation.dat
* River/routing.dat   _possible problem: subbasin 121 is not defined_
* River/response.dat
* Reservoir/reservoir.dat
* Reservoir/cav.dat

```{r file cutting}
path<-"C:/Thesis_fortran/WASA/Input/Hillslope"
#hymo.dat
hymo<-read.table(paste0(path,"/hymo.dat"),skip=2,sep="\t")
names(hymo)<-c(unlist(strsplit(readLines(paste0(path,"/hymo.dat"),n=5)[2], "[,]")))
hymo<-hymo[hymo[,1] %in% subbasins$SubbasinID,]

#rainy_season.dat
rainy_season<-read.table(paste0(path,"/rainy_season.dat"),skip=3,sep="\t")
names(rainy_season)<-c(unlist(strsplit(readLines(paste0(path,"/rainy_season.dat"),n=5)[3], " ")))
rainy_season<-rainy_season[rainy_season$Subasin %in% subbasins$SubbasinID,]

#soil_vegetation.dat
soil_vegetation<-read.table(paste0(path,"/soil_vegetation.dat"),skip=3,sep="\t")
names(soil_vegetation)<-c(unlist(strsplit(readLines(paste0(path,"/soil_vegetation.dat"),n=5)[3], "[,]")))
soil_vegetation<-soil_vegetation[soil_vegetation[,1] %in% subbasins$SubbasinID,]

path<-"C:/Thesis_fortran/WASA/Input/River"
#response.dat
response<-read.table(paste0(path,"/response.dat"),skip=2,sep="\t")
names(response)<-c(unlist(strsplit(readLines(paste0(path,"/response.dat"),n=5)[2], "[,]")))
response<-response[response$`Subasin-ID` %in% subbasins$SubbasinID,]

path<-"C:/Thesis_fortran/WASA/Input/Reservoir"
#reservoir.dat
reservoir<-read.table(paste0(path,"/reservoir.dat"),skip=2,sep="\t")
names(reservoir)<-c(unlist(strsplit(readLines(paste0(path,"/reservoir.dat"),n=5)[2], "[,]")))
reservoir<-reservoir[reservoir$`Subasin-ID` %in% subbasins$SubbasinID,]

#cav.dat
cav<-read.table(paste0(path,"/cav.dat"),skip=2,sep="\t",fill=TRUE)
names(cav)<-c(unlist(strsplit(readLines(paste0(path,"/cav.dat"),n=5)[2], "[,]")))
cav<-cav[cav$`Subasin-ID` %in% subbasins$SubbasinID,]

```

## File generation

```{r gen file cut}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"

#hymo.dat
my.write(hymo,file=paste0(path,"/hymo.dat"),
         header = "Specification of the sub-basins and their total number, type and areal fraction of SOTER units\nSubasin-ID [-], Area[km**2],  nbr[-],  LU-IDs[-], areal fraction of Soter[-]\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t",
         f = write.table, nafill=TRUE)

#rainy_season.dat
my.write(rainy_season,file=paste0(path,"/rainy_season.dat"),
         header = "Specification of the rainy season (per year)\nfor the interpolation o temporal distribution of  vegetation characteristics (Rootdepth, height, lai, albedo)\nSubasin Year (Start-30) Startday Endday (End+30)",
         f = write.table)

#soil_vegetation.dat
my.write(soil_vegetation,file=paste0(path,"/soil_vegetation.dat"),
         header = "Specification of soil-vegetation components (links soter, terrain component, soil and vegetation properties)\nFor each block: first line Soil IDs, Second line Land use, third line fraction of SVCs in each terrain component\nSubasin-ID[-],LU-ID[-],TC-ID[-],fraction_rocky[-],nbrSVC[-],Soil-ID(30 values)[-],Vegetation-ID (30 values)[-],fraction (30 values)[-]\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t\t",
         f = write.table, nafill=TRUE)

#response.dat
my.write(response,file=paste0(path,"/response.dat"),
         header = "Specification of routing parameter\nSubasin-ID,lag time [d],retention [d]",
         f = write.table)

#reservoir.dat
my.write(reservoir,file=paste0(path,"/reservoir.dat"),
         header = "Specification of reservoir	parameters\nSubasin-ID, minlevel[m], maxlevel[m], vol0([1000m**3]; unknown=-999), storcap[1000m**3], damflow[m**3/s], damq_frac[-], withdrawal[m**3/s], damyear[YYYY], maxdamarea[ha], damdead[1000m**3], damalert[1000m**3], dama[-], damb[-], qoutlet[m**3/s], fvol_bottom[-], fvol_over[-], damc[-], damd[-], elevbottom[m]",
         f = write.table)

#cav.dat
my.write(cav,file=paste0(path,"/cav.dat"),
         header = "Specification of stage-area and stage-volume curves of the sub-basin’s reservoir\nSubasin-ID, nbr. points, 1st row: elevation [m], 2nd row: reservoir area [1000m**2], 3rd row: reservoir volume [1000m**3]",f = write.table,
         nafill=TRUE)

```

# Time series update

```{r}

```

# Time series cut

```{r}
path<-"C:/Thesis_fortran/WASA/Input/Time_series"

rain<-read.table(paste0(path,"/rain_daily.dat"),skip=2,sep=" ")
rain<-data.frame(rain[,1],rain[,2],rain[,rain[1,] %in% subbasins$SubbasinID])

humidity<-read.table(paste0(path,"/humidity.dat"),skip=2,sep=" ")
humidity<-data.frame(humidity[,1],humidity[,2],humidity[,humidity[1,] %in% subbasins$SubbasinID])

radiation<-read.table(paste0(path,"/radiation.dat"),skip=2,sep=" ")
radiation<-data.frame(radiation[,1],radiation[,2],radiation[,radiation[1,] %in% subbasins$SubbasinID])

temperature<-read.table(paste0(path,"/temperature.dat"),skip=2,sep=" ")
temperature<-data.frame(temperature[,1],temperature[,2],temperature[,temperature[1,] %in% subbasins$SubbasinID])

path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"

my.write(rain,file=paste0(path,"/rain_daily.dat"),
         header = "Daily average precipitation [mmd] for each subasin, ordered according Map-IDs\nDate No. of days Subasin-ID",
         f = write.table, sepset = FALSE)
my.write(humidity,file=paste0(path,"/humidity.dat"),
         header = "Daily average humidity [in %] for each subasin, ordered according to Map-IDs\nDate No. of days Subasin-ID",
         f = write.table, sepset = FALSE)
my.write(radiation,file=paste0(path,"/radiation.dat"),
         header = "Daily average shortwave radiation [in Wm2] for each subasin, ordered according to MAP-IDs\nDate No. of days Subasin-ID",
         f = write.table, sepset = FALSE)
my.write(temperature,file=paste0(path,"/temperature.dat"),
         header = "Daily average temperature (in degree Celcius) for each subasin, ordered according to Map-IDs\nDate No. of days Subasin-ID",
         f = write.table, sepset = FALSE)
```

# References

[1]: https://doi.org/10.1061/(ASCE)HE.1943-5584.0001701

### 2022-03-17 R/Core_code/1_Data_processing/download_DEM.R

@@ -1,0 +1,8 @@
+#Script to download the DEM of the Banabuiu basin
+
+path <- "C:/Directory_thesis_codes/Data/1112536144-download.txt"
+links <- read.table(path)
+for(i in 1:nrow(links)){
+  browseURL(links[i,1])
+}
+

### 2022-03-17 R/Core_code/1_Data_processing/output_na_removal.R

@@ -2,16 +2,16 @@
 
 # Setup ---------------------------------------------------------------
 
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+setwd("C:/Directory_thesis_codes")
 path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/processed"
 
-source("Libraries.R")
-source("Functions.R")
-source("Functions_DP.R")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_DP.R")
 
-starting_date<-"1990-01-01"
-ending_date<-"2018-12-31"
-time_index<-seq(as.Date(starting_date),as.Date(ending_date),by="days")
+starting_date <- "1990-01-01"
+ending_date <- "2018-12-31"
+time_index <- seq(as.Date(starting_date), as.Date(ending_date),by="days")
 
 # Load the generated time series ------------------------------------------
 #Load, assign the column names and change the date format

### 2022-03-17 Scripts/Core_code/1_Data_processing/download_DEM.R

@@ -1,8 +1,0 @@
-#Script to download the DEM of the Banabuiu basin
-
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/NASA_DEM/1112536144-download.txt"
-links<-read.table(path)
-for(i in 1:nrow(links)){
-  browseURL(links[i,1])
-}
-

### 2022-03-17 Scripts/Core_code/1_Data_processing/time_series_generation_script.R

@@ -1,178 +1,0 @@
-#Time series generation script
-
-# Setup ---------------------------------------------------------------
-
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
-path_export <- "C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/gen_2006"
-
-source("Libraries.R")
-source("Functions.R")
-source("Functions_TG.R")
-source("Functions_DP.R")
-
-#Load the subbasins' shapefile
-path<-"C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
-subbasins<-readOGR(paste0(path,"/subbasins_cut_geomfix.shp"))
-
-# Precipitation FUNCEME ----------------------------------------------------
-
-#Load the stations
-path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
-prec_input = create_data_list(path, c("year","month","day","data"))
-
-#Remove anomalous stations (more information: "prec_out_rem.R")
-n <- find_anomalous_stations(prec_input)
-if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
-date <- create_date_vector(1980, 2018)
-prec_pos <- create_position_vector(prec_input[[1]])
-prec_input[[2]] <- add_date_column(prec_input[[2]])
-prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
-#Other anomalous stations removal (more information: "prec_out_rem.R")
-remove_st <- anomalous_prec_st(prec_df, 250)
-prec_df <- prec_df[-remove_st]
-#Outlier removal (more information: "prec_out_rem.R")
-prec_df <- rejection_threshold(prec_df, method = "value", 250)
-
-tic("Precipitation FUNCEME - Creation of the WASA input file")
-output_prec <- create_time_series_Wmean(main_dataframe = prec_df,
-                                        positions = prec_pos,
-                                        layer = subbasins)
[…]

### 2022-03-17 R/Core_code/1_Data_processing/download_DEM.R
repo update

@@ -1,8 +1,0 @@
-#Script to download the DEM of the Banabuiu basin
-
-path <- "C:/Directory_thesis_codes/Data/1112536144-download.txt"
-links <- read.table(path)
-for(i in 1:nrow(links)){
-  browseURL(links[i,1])
-}
-

### 2022-03-17 R/Core_code/1_Data_processing/prec_out_rem.R

@@ -1,159 +1,0 @@
-# Precipitation outlier analyisis ------------------------------------------
-#Since precipitation data has a skewed distribution, expecially in semi-arid
-#areas as North-East Brazil, a normal outlier rejection wouldn't work properly.
-#Here an analysis on the maxima is performed in order to define a threshold
-#above which an observation can be considered as an outlier.
-
-# Results:
-#The threshold for the outlier detection has been put equal 250 mm,
-#an approximated estimation of the 100 years return period in
-#Rodrigues, D. T. et al. Spatial distribution of the level of return of extreme precipitation events in Northeast Brazil. (2020)
-#doi:10.1002/joc.6507.
-#So:
-#   - Stations with exceptionally high outliers have been completely removed from
-#     the dataframe, considering them not reliable
-#   - Singular observations above this threshold have been removed from the dataframe
-
-
-# Setup -------------------------------------------------------------------
-
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
-path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
-
-source("Libraries.R")
-source("Functions.R")
-source("Functions_TG.R")
-source("Functions_DP.R")
-
-
-# Precipitation FUNCEME ---------------------------------------------------
-
-#Load the stations
-path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
-prec_input = create_data_list(path, c("year","month","day","data"))
-
-#Check and remove the stations which present negative values
-n <- find_anomalous_stations(prec_input)
-if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
-
-#Create a dataframe to plot the stations data and check anomalous behaviour
-date <- create_date_vector(1980, 2018)
-prec_pos <- create_position_vector(prec_input[[1]])
-prec_input[[2]] <- add_date_column(prec_input[[2]])
-prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
-f<-2
-l<-21
-for(i in 1:round(ncol(prec_df)/20)){
-  vis_prec <- data.frame(prec_df$date, prec_df[,f:l])
[…]

### 2022-03-17 R/Core_code/1_Data_processing/time_series_generation_script.R

@@ -3,22 +3,22 @@
 # Setup ---------------------------------------------------------------
 
 setwd("C:/Directory_thesis_codes")
-path_export <- "C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/gen_2006"
+path_export <- "./Data/Generated/WASA_time_series"
 
-source("Libraries.R")
-source("Functions.R")
-source("Functions_TG.R")
-source("Functions_DP.R")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_TG.R")
+source("./R/Libraries/Functions_DP.R")
 
 #Load the subbasins' shapefile
-path <- "C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/shapefile/Banabuiu"
+path <- "./Data/Shapefile"
 subbasins <- readOGR(paste0(path, "/subbasins_cut_geomfix.shp"))
 
 # Precipitation FUNCEME ----------------------------------------------------
 
 #Load the stations
-path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
-prec_input = create_data_list(path, c("year","month","day","data"))
+path <- "./Data/Meteorological_data/precipitation_subset_FUNCEME"
+prec_input <- create_data_list(path, c("year", "month", "day", "data"))
 
 #Remove anomalous stations (more information: "prec_out_rem.R")
 n <- find_anomalous_stations(prec_input)
@@ -42,11 +42,10 @@ output_prec <- WASA_input_format(prec_df, output_prec, header = h, path = path_e
 write.table(output_prec,paste0(path_export,"/output_prec_FUNCEME_save_2006.txt"),quote = FALSE,sep="\t",row.names = FALSE)
 toc() #2h 55 minutes
 
-
 # Temperature INMET -------------------------------------------------------
 
-path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/t2m_INMET"
-temp_input = create_data_list(path, c("year","month","day","data"))
+path <- "./Data/Meteorological_data/t2m_INMET"
+temp_input <- create_data_list(path, c("year", "month", "day", "data"))
 
[…]

### 2022-03-17 R/Libraries/Functions_AN.R

@@ -3,9 +3,9 @@
 
 # Drought Cycle Analysis --------------------------------------------------
 
-meanx = function(x) mean(x, na.rm = TRUE)
+meanx <- function(x) mean(x, na.rm = TRUE)
 
-VD = function(df, maxcap, skip = 1){
+VD <- function(df, maxcap, skip = 1){
   skip <- skip + 1
   
   VD <- data.frame(date = df$date)
@@ -23,7 +23,7 @@ quadrant_attribution = function(PI, WSI, dates){
   DCA <- data.frame(dates, PI, WSI)
   names(DCA) <- c("date","PI", "WSI")
   DCA$quadrant <- NA
-  for(i in 1:nrow(DCA)){
+  for(i in seq_len(nrow(DCA))){
     if(!is.na(DCA$PI[i]) & !is.na(DCA$WSI[i])){
       if(DCA$PI[i] > 0 & DCA$WSI[i] > 0)      DCA$quadrant[i] <- 1
       else if(DCA$PI[i] < 0 & DCA$WSI[i] > 0) DCA$quadrant[i] <- 2
@@ -33,4 +33,3 @@ quadrant_attribution = function(PI, WSI, dates){
   }
   return(DCA)
 }
-

### 2022-03-17 R/Libraries/Functions_TG.R

@@ -1,31 +1,31 @@
 #Functions to execute the time series generation
 
-create_date_vector = function(start_y, end_y, start_m = 01, end_m = 12, start_d = 01,
-                              end_d = 31){
-  start<-paste0(start_d, "/0",start_m,"/",start_y)
-  end<-paste0(end_d,"/",end_m,"/",end_y)
-  date<-seq(as.Date(start,"%d/%m/%Y"), as.Date(end,"%d/%m/%Y"), by="days")
+create_date_vector <- function(start_y, end_y, start_m = 01, end_m = 12,
+                              start_d = 01, end_d = 31) {
+  start <- paste0(start_d, "/0", start_m, "/", start_y)
+  end <- paste0(end_d, "/", end_m, "/", end_y)
+  date <- seq(as.Date(start, "%d/%m/%Y"), as.Date(end, "%d/%m/%Y"), by = "days")
   return(date)
 }
 
-create_data_list = function(path, names, skip = 6, f = read.table, s = ""){
+create_data_list <- function(path, names, skip = 6, f = read.table, s = "") {
   #skip = 6 for the FUNCEME files in .txt
   #skip = 1 for the volume observation values in .csv
   #skip = 3 for WASA input files
-  
-  files<-list.files(path=path,full.names = T,recursive = TRUE)
-  data_list<-list()
-  for(i in 1:length(files)){
-    tryCatch(data_list[[i]]<-f(files[i],header = FALSE,
+
+  files <- list.files(path = path, full.names = T, recursive = TRUE)
+  data_list <- list()
+  for (i in seq_len(length(files))) {
+    tryCatch(data_list[[i]] <- f(files[i], header = FALSE,
                                  sep = s,col.names = names, skip = skip),
-             error=function(e){cat("ERROR :",conditionMessage(e),i, "\n")})
+             error = function(e) {cat("ERROR :", conditionMessage(e), i, "\n")})
   }
   return(list(files, data_list))
 }
 
-create_position_vector = function(files){
+create_position_vector <- function(files){
   #Positions vector
-  for(i in 1:length(files)){
+  for(i in seq_len(length(files))){
     lines<-readLines(files[i],n = 6)
     ID<-as.numeric(unlist(strsplit(lines[1], ":"))[2])
     name<-unlist(strsplit(lines[2], ":"))[2]
@@ -39,33 +39,35 @@ create_position_vector = function(files){
   return(positions)
 }
 
-add_date_column = function(data_list, complete = FALSE){
[…]

### 2022-03-17 R/Supporting_code/1_Data_processing/download_DEM.R

@@ -1,0 +1,7 @@
+#Script to download the DEM of the Banabuiu basin
+
+path <- "C:/Directory_thesis_codes/Data/1112536144-download.txt"
+links <- read.table(path)
+for(i in seq_len(nrow(links))){
+  browseURL(links[i,1])
+}

### 2022-03-17 R/Supporting_code/1_Data_processing/prec_out_rem.R

@@ -1,0 +1,160 @@
+# Precipitation outlier analyisis ------------------------------------------
+#Since precipitation data has a skewed distribution, expecially in semi-arid
+#areas as North-East Brazil, a normal outlier rejection wouldn't work properly.
+#Here an analysis on the maxima is performed in order to define a threshold
+#above which an observation can be considered as an outlier.
+
+# Results:
+#The threshold for the outlier detection has been put equal 250 mm,
+#an approximated estimation of the 100 years return period in
+#Rodrigues, D. T. et al.
+# Spatial distribution of the level of return of extreme precipitation events
+# in Northeast Brazil. (2020), doi:10.1002/joc.6507.
+#So:
+# - Stations with exceptionally high outliers have been completely removed from
+#     the dataframe, considering them not reliable
+# - Singular observations above this threshold have been removed
+#     from the dataframe
+
+# Setup -------------------------------------------------------------------
+
+setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
+
+source("Libraries.R")
+source("Functions.R")
+source("Functions_TG.R")
+source("Functions_DP.R")
+
+
+# Precipitation FUNCEME ---------------------------------------------------
+
+#Load the stations
+path = "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/meteorological_stations_ceara/Meteorological_stations_FUNCEME/precipitation_subset"
+prec_input = create_data_list(path, c("year","month","day","data"))
+
+#Check and remove the stations which present negative values
+n <- find_anomalous_stations(prec_input)
+if(n > 0) prec_input <- remove_anomalous_stations(prec_input)
+
+#Create a dataframe to plot the stations data and check anomalous behaviour
+date <- create_date_vector(1980, 2018)
+prec_pos <- create_position_vector(prec_input[[1]])
+prec_input[[2]] <- add_date_column(prec_input[[2]])
+prec_df <- create_main_dataframe(date, prec_input[[2]], prec_pos)
+f<-2
+l<-21
+for(i in 1:round(ncol(prec_df)/20)){
+  vis_prec <- data.frame(prec_df$date, prec_df[,f:l])
[…]

### 2022-03-17 R/Core_code/1_Data_processing/time_series_na_removal.R
update

@@ -3,7 +3,7 @@
 # Setup ---------------------------------------------------------------
 
 setwd("C:/Directory_thesis_codes")
-path_export <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen/processed"
+path_export <- "./Data/Generated/WASA_time_series_input"
 
 source("./R/Libraries/Libraries.R")
 source("./R/Libraries/Functions.R")
@@ -11,12 +11,12 @@ source("./R/Libraries/Functions_DP.R")
 
 starting_date <- "1990-01-01"
 ending_date <- "2018-12-31"
-time_index <- seq(as.Date(starting_date), as.Date(ending_date),by="days")
+time_index <- seq(as.Date(starting_date), as.Date(ending_date), by = "days")
 
 # Load the generated time series ------------------------------------------
 #Load, assign the column names and change the date format
 
-path_import <- "C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/time_series_generation/input_WASA_gen"
+path_import <- "./Data/Generated/WASA_time_series_input/unprocessed"
 columns <- c("date", "doy", 123, 125, 126, 127, 134, 137, 138, 139, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152, 153, 154, 155, 156, 157, 158, 159, 160)
 
 prec <- read.table(paste0(path_import, "/precipitation_FUNCEME_1706.dat"), skip = 3)
@@ -40,7 +40,6 @@ rad_F$date<-time_index
 rad_I <- read.table(paste0(path_import, "/radiation_INMET_1706.dat"), skip = 3)
 names(rad_I) <- columns
 rad_I$date<-time_index
-
 
 # Outliers removal -------------------------------------
 

### 2022-03-17 R/Core_code/DRN_operations/2_New_hdrn.Rmd
repo update

--- 2022-03-03 Scripts/Core_code/2_DRN_operations/2_New_hdrn.Rmd
@@
 ---
-title: "Creation of the new HDRN shapefile with capacities associated"
+title: "Creation of a DRN shapefile with associated capacities"
 author: "Paolo Colombo"
@@
 ```{r libraries}
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")
+setwd("C:/Directory_thesis_codes")
 
-source("Libraries.R")
-source("Functions.R")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
 ```
@@
 ```{r}
-setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data")
-
-global_water<-readOGR(dsn = "./Global_surface_water/shape/cut_merged.shp")
+global_water <- readOGR(dsn = "./Data/DRN/Global_surface_water/cut_merged.shp")
 ```
@@
 ```{r}
-path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
-main_resI<-st_read(paste0(path,"/mainreservoirsI_cut_ref.shp"))
-main_resII<-st_read(paste0(path,"/mainreservoirsII_cut_ref.shp"))
+path <- "C:/Thesis_fortran/WASA/shapefile/Banabuiu"
+main_resI <- st_read(paste0(path, "/mainreservoirsI_cut_ref.shp"))
+main_resII <- st_read(paste0(path, "/mainreservoirsII_cut_ref.shp"))
 
-threshold<-min(main_resI$AREA)
-glob_wat_cut<-global_water[which(global_water$area_geom < threshold),]
+threshold <- min(main_resI$AREA)
+glob_wat_cut <- global_water[which(global_water$area_geom < threshold),]
 

### 2022-03-22 R/Core_code/DRN_operations/2_New_hdrn.Rmd
DRN processing uèdate

@@
 ```{r}
-path <- "C:/Thesis_fortran/WASA/shapefile/Banabuiu"
-main_resI <- st_read(paste0(path, "/mainreservoirsI_cut_ref.shp"))
-main_resII <- st_read(paste0(path, "/mainreservoirsII_cut_ref.shp"))
+main_resI <- st_read("./Data/Shapefile/Reservoirs/mainreservoirsI_cut_ref.shp")
+main_resII <- st_read("./Data/Shapefile/Reservoirs/mainreservoirsII_cut_ref.shp")
 
@@
 glob_wat_cut <- global_water[which(global_water$area_geom < threshold),]
-
 ```
@@
 DN = 1 means that in that element water is present.
-Removing the shapes which present DN = 0 is then useful for the next step in QGIS (the NNJoin), so that the HDRN points will not be matched with the areas which don't present water in them.
+Removing the shapes which present DN = 0 is then useful for the next step in QGIS (the NNJoin), so that the DRN points will not be matched with the areas which don't present water in them.
 
 ```{r}
-glob_wat_cut<-glob_wat_cut[which(glob_wat_cut$DN == 1),]
+glob_wat_cut <- glob_wat_cut[which(glob_wat_cut$DN == 1),]
 ```
@@
 ```{r}
-writeOGR(glob_wat_cut,dsn = "./Global_surface_water/shape", layer = "global_wat_cut",
+writeOGR(glob_wat_cut, dsn = "./Global_surface_water", layer = "global_wat_cut",
          driver = "ESRI Shapefile" )
@@
 
-# HDRN update
+# DRN update
 
@@
 
-```{r load HDRN to update}
-HDRN_update<-readOGR(dsn = "./HDRN/HDRN_update_area_ID.shp")
+```{r load DRN to update}
+DRN_update <- readOGR(dsn = "./DRN/DRN_update_area_ID.shp")
 ```
@@
 a <- alpha_Molle <- 2.7
-
-HDRN_update$capacity<-k*(HDRN_update$join_area_/(a*k))^(a/(a-1)) #m3
-
-#Area = a*k*(100000/k)^((a-1)/a)
-
-#Reservoirs classes definition
-# res_class<-c(
-#               102179,
-#               151360,
-#               265735,
-#               758010,
-#               875797530
-#             )
-#this classification doesn't make any sense with the values we have
-#quantile(HDRN_update$capacity, probs = seq(0, 1, 0.2))
-
-#cap_glob<-k*(glob_wat_cut$area_geom/(a*k))^(a/(a-1))
-#quantile(cap_glob, probs = seq(0, 1, 0.2))
+DRN_update$capacity <- k*(DRN_update$join_area_/(a*k))^(a/(a-1)) #m3
 
@@
               100000,
-              max(HDRN_update$capacity)+1
+              max(DRN_update$capacity)+1
             )
-
 ```
@@
 
-Find the HDRN's reservoirs (id) that present the same Global Water reservoir (join_fid). To the one with the highest distance, associate the capacity of the smallest reservoir class
+Find the DRN's reservoirs (id) that present the same Global Water reservoir (join_fid). To the one with the highest distance, associate the capacity of the smallest reservoir class
 
@@
 tic("Lowest reservoir class to points with no associate global water")
-subset<-HDRN_update[duplicated(HDRN_update$join_fid),]
-for(i in 1:length(subset$join_fid)){
+subset <- DRN_update[duplicated(DRN_update$join_fid),]
+for(i in seq_len(length(subset$join_fid))){
   #Take the first duplicate ID
-  check1<-subset$join_fid[i] 
+  check1 <- subset$join_fid[i] 
   #Take the minimum distance from the points with the same associated ID
-  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
+  check2 <- min(DRN_update$distance[DRN_update$join_fid %in% check1])
   #Take the point associated to the minimum distance
-  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]
+  check3 <- DRN_update$id[which(DRN_update$join_fid %in% check1 & DRN_update$distance == check2)]
 
@@
   #than check2
-  HDRN_update$capacity[which(HDRN_update$join_fid %in% check1
-                             & HDRN_update$distance > check2
-                             & HDRN_update$id != check3)]<-res_class[1]-0.1
+  DRN_update$capacity[which(DRN_update$join_fid %in% check1
+                             & DRN_update$distance > check2
+                             & DRN_update$id != check3)] <- res_class[1] - 0.1
 }
@@
 
-summary(HDRN_update@data)
+summary(DRN_update@data)
 
-#Export the updated HDRN
-# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v1",
+#Export the updated DRN
+# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v1",
 #          driver = "ESRI Shapefile")
@@
 tic("Removal of points with no associated global water")
-subset<-HDRN_update[duplicated(HDRN_update$join_fid),] #Finds the duplicates
-for(i in 1:length(subset$join_fid)){
+subset <- DRN_update[duplicated(DRN_update$join_fid),] #Finds the duplicates
+for(i in seq_len(length(subset$join_fid))){
   #Take the first duplicate ID
-  check1<-subset$join_fid[i] 
+  check1 <- subset$join_fid[i] 
   #Take the minimum distance from the points with the same associated ID
-  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
+  check2 <- min(DRN_update$distance[DRN_update$join_fid %in% check1])
   #Take the point associated to the minimum distance
-  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]
+  check3 <- DRN_update$id[which(DRN_update$join_fid %in% check1 & DRN_update$distance == check2)]
 
   #Remove the duplicate points with a distance higher than check2
-  HDRN_update<-HDRN_update[which(!(HDRN_update$join_fid %in% check1
-                                      & HDRN_update$distance > check2
-                                      & HDRN_update$id != check3)),]
+  DRN_update <- DRN_update[which(!(DRN_update$join_fid %in% check1
+                                      & DRN_update$distance > check2
+                                      & DRN_update$id != check3)),]
 }
@@
 
-summary(HDRN_update@data)
+summary(DRN_update@data)
 
-#Export the updated HDRN
-# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v2",
+#Export the updated DRN
+# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v2",
 #          driver = "ESRI Shapefile" )
@@
 
-#Load the updated HDRN
+#Load the updated DRN
 #Method 1 (Unidentified reservoirs associated to the lowest class)
-# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v1.shp"
+# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v1.shp"
 #Method 2 (Unidentified reservoirs removed)
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v2.shp"
+path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v2.shp"
 
-HDRN_update<-readOGR(path)
+DRN_update<-readOGR(path)
 
@@
   if(i != 1){
-    c <- HDRN_update@data %>%
+    c <- DRN_update@data %>%
           filter(!is.na(SubbasinID)) %>%
@@
   }else{
-    c <- HDRN_update@data %>%
+    c <- DRN_update@data %>%
           filter(!is.na(SubbasinID)) %>%
@@
   }
-  for(a in 1:length(c$SubbasinID)){
-    for(b in 1:length(count_class$SubbasinID)){
-        if(c$SubbasinID[a]==count_class$SubbasinID[b]) count_class[b,i+1]<-c$count[a]
+  for(a in seq_len(length(c$SubbasinID))){
+    for(b in seq_len(length(count_class$SubbasinID))){
+        if(c$SubbasinID[a] == count_class$SubbasinID[b]) count_class[b,i+1] <- c$count[a]
     }
@@
 }
-names(count_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
-count_class[is.na(count_class)]<-0
+names(count_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
+count_class[is.na(count_class)] <- 0
 
@@
 path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-count_class<-read.table(paste0(path, "/lake_number_newHDRN_met2.dat"), skip = 2)
+count_class<-read.table(paste0(path, "/lake_number_newDRN_met2.dat"), skip = 2)
 
@@
 path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(count_class,file=paste0(path,"/lake_number_newHDRN_met2.dat"),
+my.write(count_class,file=paste0(path,"/lake_number_newDRN_met2.dat"),
          header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
@@
 path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newHDRN_m2_median.dat"),
+my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newDRN_m2_median.dat"),
          header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
@@
 
-# Scenario without the HDRN
+# Scenario without the DRN
 
@@
 
-```{r no HDRN lake}
+```{r no DRN lake}
 #Dataframe construction
@@
 path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(par_class,file=paste0(path,"/lake_noHDRN.dat"),
+my.write(par_class,file=paste0(path,"/lake_noDRN.dat"),
          header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
@@
 
-```{r no HDRN lake_number}
+```{r no DRN lake_number}
 #Sub-basins without networks of small reservoirs must not be entered in the file.
@@
 path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noHDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)
+write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)
 
@@
 count_class[,3:6]<-0
-my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v2.dat"),
+my.write(count_class,file=paste0(path,"/lake_number_noDRN_v2.dat"),
          header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
@@
 count_class[,3:6]<-0
-my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v3.dat"),
+my.write(count_class,file=paste0(path,"/lake_number_noDRN_v3.dat"),
          header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

### 2022-03-22 R/Core_code/DRN_operations/DRN_processing.Rmd
update repo and drn_processing

--- 2022-03-22 R/Core_code/DRN_operations/2_New_hdrn.Rmd
@@
 ```{r}
-writeOGR(glob_wat_cut, dsn = "./Global_surface_water", layer = "global_wat_cut",
-         driver = "ESRI Shapefile" )
+writeOGR(glob_wat_cut, dsn = "./Data/DRN/Global_surface_water", layer = "global_wat_cut",
+         driver = "ESRI Shapefile")
 ```
@@
 ```{r load DRN to update}
-DRN_update <- readOGR(dsn = "./DRN/DRN_update_area_ID.shp")
+DRN_update <- readOGR(dsn = "./Data/DRN/DRN_update_area_ID.shp")
 ```
@@
 #Export the updated DRN
-# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v1",
-#          driver = "ESRI Shapefile")
+writeOGR(DRN_update, dsn = "./DRN", layer = "DRN_afterR_v1",
+          driver = "ESRI Shapefile")
 ```
@@
 #Export the updated DRN
-# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v2",
-#          driver = "ESRI Shapefile" )
+writeOGR(DRN_update, dsn = "./DRN", layer = "DRN_afterR_v2",
+          driver = "ESRI Shapefile")
 ```
@@
 #Method 2 (Unidentified reservoirs removed)
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v2.shp"
+path <- "./Data/DRN/DRN_afterR_v2.shp"
 
@@
 #Dataframe creation: first column SubbasinID, others number of reservoirs in the classes
-path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
-subbasins<-st_read(paste0(path,"/subbasins_cut.shp"))
+subbasins <- st_read("./Data/Shapefile/subbasins_cut_geomfix.shp")
 count_class <- subbasins %>%
@@
           group_by(SubbasinID) %>%
-      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
-      #for Mamede classification: below
           filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
@@
           group_by(SubbasinID) %>%
-          #filter(capacity <= res_class[i+1]) %>%
-      #for Mamede classification: below
           filter(capacity < res_class[i]) %>%
-          summarize(count=n())
+          summarize(count = n())
   }
@@
 }
-names(count_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
+names(count_class) <- c("SubbasinID", "class1", "class2", "class3", "class4", "class5")
 count_class[is.na(count_class)] <- 0
@@
 #Class ripartition
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-count_class<-read.table(paste0(path, "/lake_number_newDRN_met2.dat"), skip = 2)
-
 for(i in 2:6){
-  print(paste0("Percentage of resevoirs in Class ",i-1))
+  print(paste0("Percentage of resevoirs in Class ", i-1))
   print(paste0(round(sum(count_class[,i])/sum(count_class[,2:6]),digits = 3)*100," %"))
@@
 #Create the dataframe
-par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
+par_class <- data.frame(seq(1,5,1),     #Reservoir_class-ID
                         round(res_class,2),      #maxlake0
@@
                        )
-names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
+names(par_class) <- c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
 View(par_class)
@@
 options(scipen = 999)
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(par_class,file=paste0(path,"/lake.dat"),
-         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
+path <- "./Data/Scenarios/AR"
+my.write(par_class, file = paste0(path, "/lake.dat"),
+         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",
+         f = write)
 options(scipen = 0)
@@
 ```{r lake_number}
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(count_class,file=paste0(path,"/lake_number_newDRN_met2.dat"),
-         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
+path <- "./Data/Scenarios/AR"
+my.write(count_class, file = paste0(path,"/lake_number.dat"),
+         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",
+         f = write)
+
+#Check class ripartition
+path <- "./Data/Scenarios/AR"
+count_class <- read.table(paste0(path, "/lake_number.dat"), skip = 2)
 ```
@@
 
-```{r representative reservoirs}
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
-res<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
+```{r lake_maxvol}
+path <- "./Data/General"
+res <- read.table(paste0(path, "/reservoir_name_ID.txt"), header = TRUE, sep = "\t")
 
-median_class<- data.frame(res$SubbasinID)
+median_class <- data.frame(res$SubbasinID)
 names(median_class) <- "SubbasinID"
@@
   }
-  for(a in 1:length(c$SubbasinID)){
-    for(b in 1:length(median_class$SubbasinID)){
+  for(a in seq_len(length(c$SubbasinID))){
+    for(b in seq_len(length(median_class$SubbasinID))){
         if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
@@
 }
-names(median_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
-median_class[is.na(median_class)]<-0
+names(median_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
+median_class[is.na(median_class)] <- 0
 ```
@@
 ```{r export lake_maxvol}
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newDRN_m2_median.dat"),
-         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
+path <- "./Data/Scenarios/AR"
+my.write(round(median_class,2), file=paste0(path, "/lake_maxvol.dat"),
+         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",
+         f = write)
 ```
@@
 #Dataframe construction
-par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
-                      round(res_class,2),      #maxlake0
+par_class <- data.frame(seq(1,5,1),     #Reservoir_class-ID
+                       round(res_class, 2),      #maxlake0
                         rep(1,5),       #lake_vol0_factor
                         rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
-                      rep(alpha_Molle,5),   
-                      rep(damk_Molle,5),
+                        rep(alpha_Molle, 5),   
+                        rep(damk_Molle, 5),
                         c(12.5,18.75,25,37.5,50),       #damc_hrr
-                      rep(1.5,5)      #damd_hrr
+                        rep(1.5, 5)      #damd_hrr
                         )
-names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
+names(par_class) <- c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
 
@@
 options(scipen = 999)
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-my.write(par_class,file=paste0(path,"/lake_noDRN.dat"),
-         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
+path <- "./Data/Scenarios/LR"
+my.write(par_class, file=paste0(path, "/lake.dat"),
+         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",
+         f = write)
 options(scipen = 0)
@@
 #No reservoirs
-path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
-write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)
-
-#Only one resevoir in the smallest reservoir class
-count_class[,2]<-1
-count_class[,3:6]<-0
-my.write(count_class,file=paste0(path,"/lake_number_noDRN_v2.dat"),
-         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
-
+path <- "./Data/Scenarios/LR"
 #Only zeros
-#it works!!!!
-count_class[,2]<-0
-count_class[,3:6]<-0
-my.write(count_class,file=paste0(path,"/lake_number_noDRN_v3.dat"),
-         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
-
+count_class[, 2] <- 0
+count_class[, 3:6] <- 0
+my.write(count_class,file = paste0(path, "/lake_number.dat"),
+         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",
+         f = write.table)
 ```

### 2022-05-08 R/Figures_code/paper_figures.Rmd
first draft of the figures code

---
title: "Code to generate the figures needed in 'The influence of small reservoirs on hydrological drought propagation in space and time'"
author: "Paolo Colombo"
date: "08/05/2022"
output: html_document
---

# Load general libraries and functions
```{r}
setwd('C:/Directory_thesis_codes')
```

# Figure generation
## Figure 1
Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right.
Made in QGIS for now. A code can be written by loading the shapefiles used there.

## Figure 2
Comparison between the modelled and observed volumes of the reservoirs.
### Version 1
*Line graph of Arrojado Lisboa modelled vs observed volumes*

### Version 2 
*Scatterplot of modelled vs observed volumes. Arrojado Lisboa, Pedras Brancas, Fogareiro*

## Figure 3
Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al., 2022.
![Drought Cycle Analysis quadrant representation]('Figures and tables/DCA_wheel_update.jpg')

## Figure 4

### 2022-07-02 R/Figures_code/paper_figures.Rmd
Figure 1

@@
 ---
-title: "Code to generate the figures needed in 'The influence of small reservoirs on hydrological drought propagation in space and time'"
+title: Code to generate the figures needed in 'The influence of small reservoirs on
+  hydrological drought propagation in space and time'
 author: "Paolo Colombo"
 date: "08/05/2022"
-output: html_document
+output:
+  html_document: default
+  pdf_document: default
 ---
 
-# Load general libraries and functions
-```{r}
-setwd('C:/Directory_thesis_codes')
+# Setup
+
+Set the working directory and load general libraries and custom functions.
+```{r, setwd, include = FALSE}
+knitr::opts_knit$set(root.dir = "C:/Directory_thesis_codes")
+```
+
+```{r, setup, include = FALSE}
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_MC.R")
 ```
@@
 ## Figure 2
-Comparison between the modelled and observed volumes of the reservoirs.
-### Version 1
-*Line graph of Arrojado Lisboa modelled vs observed volumes*
+Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al., 2022.
+![Drought Cycle Analysis quadrant representation](C:/Directory_thesis_codes/Figures and tables/DCA_wheel_update.jpg)
 
-### Version 2 
-*Scatterplot of modelled vs observed volumes. Arrojado Lisboa, Pedras Brancas, Fogareiro*
+## Figure 6
 
-## Figure 3
-Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al., 2022.
-![Drought Cycle Analysis quadrant representation]('Figures and tables/DCA_wheel_update.jpg')
+```{r figure 6}
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
 
-## Figure 4
+DCA_real <- list.load("./Data/DCA/DCA_real.RData")
+DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
+DCA_obs <- list.load("./Data/DCA/DCA_obs.RData")
+DCA_SR <- list.load("./Data/DCA/DCA_SR.RData")
+DCA_N <- list.load("./Data/DCA/DCA_N.RData")
+
+rename_scenarios = function(df){
+  #df BEFORE reshape::melt!
+  names(df)[names(df) == "Real"] <- "AR"
+  names(df)[names(df) == "noHDNR"] <- "LR"
+  return(df)
+}
+
+#Meteorological drought periods
+#Based on Marengo et al., 2016
+date_ranges_Marengo <- data.frame(
+  from = as.Date(c("1981-01-01", "1982-01-01", "1992-01-01", "1997-01-01", "2001-01-01", "2005-01-01", "2007-01-01", "2010-01-01")),
+  to = as.Date(c("1981-12-01", "1983-12-01", "1993-12-01", "1998-12-01", "2002-12-01", "2005-12-01", "2007-12-01", "2018-12-01"))
+)
+#Based on SPI
+# negSPI <- DCA_real$Banabuiu$date[DCA_real$Banabuiu$PI < 0]
+# negSPI
+date_ranges_SPI <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+
+#Arrojado Lisboa
+df <- data.frame(date = DCA_real[['156']]$date, Real = DCA_real[['156']]$WSI, noHDNR = DCA_noH[['156']]$WSI)
+plot_df_interactive(df)
+
+df <- rename_scenarios(df)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+
+date_ranges <- date_ranges_SPI
+
+p <- ggplot() +
+  #Add the drought rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
+  #Add the VD lines
+  geom_line(data = df, aes(x = date, y = value, linetype = Scenario), alpha = 0.5, size = 1.25) +
+  #VD = 0 line
+  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
+  #geom_text(aes(as.Date("1985-01-01"), 0, label = "VD = 0", vjust = -1, hjust = 0)) +
+  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  theme(axis.text.x = element_text(size = 16),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 18),
+        legend.position = "bottom")
+  #scale_color_manual(values = c("royalblue3", "steelblue"))
+  #scale_color_manual(values = c("salmon1", "royalblue"))
+
+print(p)
+plot.save(p, width = 1280, height = 657, filename = "./Plots/vd_ARLR_present.png")
+
+```
+
+## Figure 8
+
+```{r figure 8a}
+setwd("C:/Directory_thesis_codes")
+load("./Data/Analysis/Downstreamness/Dsv_AR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_LR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_N.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_SR.Rdata")
+df <- data.frame(date = Dsv_AR$date,
+                 AR = Dsv_AR$Dsv, LR = Dsv_LR$Dsv, 
+                 N = Dsv_N$Dsv, SR = Dsv_SR$Dsv)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+df$Scenario <- as.character(df$Scenario)
+
+date_ranges <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+#Colours
+#         AR        LR          N         SR
+col <- c("#a651a3", "#429649", "#e2703a", "#046582")
+p <- ggplot() +
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.2) +
+  geom_line(data = df, aes(x = date, y = value, colour = Scenario, linetype = Scenario), size = 1.25, alpha = 0.9) +
+  scale_y_continuous(name = expression(paste('D'['SV'], " [%]")), limits = c(25, 75)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  scale_color_manual(values = col) +
+  theme(
+        axis.text.x = element_text(size = 18),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 18),
+        legend.position = "bottom"
+        )
+
+print(p)
+
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
+```
+
+```{r figure 8b}
+setwd("C:/Directory_thesis_codes")
+load("./Data/Analysis/Downstreamness/Dsv_AR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_LR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_N.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_SR_new.Rdata")
+
+df <- data.frame(date = Dsv_AR$date,
+                 `AR modified` = Dsv_AR$Dsv_modified, LR = Dsv_LR$Dsv,
+                 N = Dsv_N$Dsv, `SR modified` = Dsv_SR$Dsv_modified)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+df$Scenario <- as.character(df$Scenario)
+df$Scenario[df$Scenario == "AR.modified"] <- "AR modified"
+df$Scenario[df$Scenario == "SR.modified"] <- "SR modified"
+
+date_ranges <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+#Colours
+#         AR        LR              N           SR
+col <- c("#a651a3", "#429649", "#e2703a", "#046582")
+p <- ggplot() +
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.2) +
+  geom_line(data = df, aes(x = date, y = value, colour = Scenario, linetype = Scenario), size = 1.25, alpha = 0.9) +
+  scale_y_continuous(name = expression(paste('D'['SV'], " [%]")), limits = c(25, 75)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years",
+               date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  scale_color_manual(values = col) +
+  theme(
+        axis.text.x = element_text(size = 18),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 18),
+        legend.position = "bottom"
+        )
+
+print(p)
+
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8b.png")
+```

### 2022-07-02 R/Figures_code/downstreamness_plot.R

@@ -2,10 +2,10 @@
 
 # Setup -------------------------------------------------------------------
 
-setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
-source("./Libraries/Libraries.R")
-source("./Libraries/Functions.R")
-source("./Libraries/Functions_MC.R")
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_MC.R")
 
 #Meteorological drought period
 date_ranges_SPI <- data.frame(

### 2022-07-02 R/Libraries/Libraries.R

@@ -6,14 +6,14 @@ library(rlist)
 library(tidyverse)
 
 #Pre-Processing for WASA
-#library(lumpR)
+# library(lumpR)
 
 #Visualization
 library(ggplot2)
 require(scales)
 library(gridExtra)
 library(plotly)
-library(hrbrthemes)
+# library(hrbrthemes)
 
 #Georeferenced data
 library(deldir)

### 2022-07-02 R/Supporting_code/downstreamness_SV_clean.R

@@ -30,18 +30,27 @@ for (class in 1:5){
 }
 
 load("./Data/Analysis/Downstreamness/DRN_AR_vol_mean.Rdata")
+load("./Data/Analysis/Downstreamness/DRN_SR_vol_mean.Rdata")
 DRN_AR_vol <- apply(DRN_AR_vol_mean[, 2:ncol(DRN_AR_vol_mean)], 1, sumx)
-SVperc <- mean(perc_increment(totcap, DRN_AR_vol))
+SVperc_AR <- mean(perc_increment(totcap, DRN_AR_vol))
+DRN_SR_vol <- apply(DRN_SR_vol_mean[, 2:ncol(DRN_SR_vol_mean)], 1, sumx)
+SVperc_SR <- mean(perc_increment(totcap, DRN_SR_vol))
 
 #Dataframes
 load("./Data/Scenarios/AR/AR_daily.RData") #AR
 load("./Data/Scenarios/LR/LR_daily.RData") #LR
+load("./Data/Scenarios/SR/SR_daily.RData") #SR
+load("./Data/Scenarios/N/N_daily.RData") #N
 AR <- monthly_scale(df = AR_daily)
 LR <- monthly_scale(df = LR_daily)
+SR <- monthly_scale(df = SR_daily)
+N <- monthly_scale(df = N_daily)
 
 #DRN AR scenario
 load("./Data/Analysis/Downstreamness/DRN_AR_vol_sum.Rdata")
 DRN_AR <- HDNR_vol
+load("./Data/Analysis/Downstreamness/DRN_SR_vol_sum.Rdata")
+DRN_SR <- HDNR_vol
 
 #Dx
 library(rgdal)
@@ -56,22 +65,36 @@ dx_res <- res_df$dx[order(res_df$subID)]
 
 # Obtain Dsv --------------------------------------------------------------
 
-tic("Obtain Dsv AR and LR")
+tic("Obtain Dsv AR, LR, SR and N")
 Dsv_AR <- Dsv_LR <- data.frame(date = AR$date)
+Dsv_SR <- Dsv_N <- data.frame(date = AR$date)
 Dsv_AR$Dsv <- Dsv_AR$Dsv_modified <- Dsv_AR$noDRN <- Dsv_LR$Dsv <- 0
-coeff <- 100/(100 + SVperc)
+Dsv_SR$Dsv <- Dsv_SR$Dsv_modified <- Dsv_N$Dsv <- 0
[…]

### 2022-07-02 R/Supporting_code/obtain_numbers_paper.R

@@ -14,6 +14,8 @@ perc_increment = function(xi, xf){
   return((xf-xi)/xi * 100)
 }
 
+perc_increment(10, 19)
+
 #Table of number of months in the phases
 table <- data.frame(matrix(NA, 4, 4))
 names(table) <- c("AR", "LR", "SR", "N")
@@ -42,8 +44,8 @@ for (i in c(1, 3)){
 # Percentage increment in the Dsc and Dsv ---------------------------------
 
 #Dsc
-load("./Data/Analysis/Downstreamness/Dsc_r.Rdata")
-load("./Data/Analysis/Downstreamness/Dsc_nH.Rdata")
+load("./Data/Analysis/Downstreamness/Dsc_AR.Rdata")
+load("./Data/Analysis/Downstreamness/Dsc_LR.Rdata")
 
 Dsc_AR <- Dsc_r
 Dsc_LR <- Dsc_nH
@@ -55,8 +57,8 @@ max(pi)
 min(pi)
 
 #Dsv
-load("./Data/Analysis/Downstreamness/Dsv_r.Rdata")
-load("./Data/Analysis/Downstreamness/Dsv_nH.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_AR.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_LR.Rdata")
 load("./Data/Analysis/Downstreamness/Dsv_SR.Rdata")
 load("./Data/Analysis/Downstreamness/Dsv_N.Rdata")
 
@@ -177,3 +179,41 @@ for (year in Dsc_AR$date){
 }
 
 sum(Dsc_long$value > Dsv_AR$Dsv)/length(Dsv_AR$Dsv)*100
+
+
+# Dsv modified ------------------------------------------------------------
+
+load("./Data/Analysis/Downstreamness/Dsv_AR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_LR_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_N_new.Rdata")
+load("./Data/Analysis/Downstreamness/Dsv_SR_new.Rdata")
+
+idx <- which(Dsv_AR$date > "2000-01-01")
[…]

### 2022-07-02 R/Figures_code/paper_figures.Rmd
name change folder DNR

@@
 output:
-  html_document: default
+  html_document: 
+    fig_width: 10
+    fig_height: 7
   pdf_document: default
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 Set the working directory and load general libraries and custom functions.
+
 ```{r, setwd, include = FALSE}
@@
 # Figure generation
+
 ## Figure 1
-Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right.
-Made in QGIS for now. A code can be written by loading the shapefiles used there.
+
+Map of the study area localization on the left.
+Centralized reservoirs visualization and density representation of the DRN on the right.
+Made in QGIS utilizing the shapefiles and rasters found in ./Data/DNR and ./Data/Shapefile.
+![Study area framing.
+North-East Brazil, Ceará and Banabuiú catchment on the left.
+On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure_1.png)
 
 ## Figure 2
-Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al., 2022.
-![Drought Cycle Analysis quadrant representation](C:/Directory_thesis_codes/Figures and tables/DCA_wheel_update.jpg)
+
+Graphical representation of the Drought Cycle Analysis, taken from Ribeiro Neto et al., 2022.
+![Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al.
+(2022).
+WSI: Water Scarcity Index, PI: Precipitation Index.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure%202.jpg){width="682"}
 
@@
 ```{r figure 6}
-setwd("C:/Directory_thesis_codes")
-source("./R/Libraries/Libraries.R")
-source("./R/Libraries/Functions.R")
-
-DCA_real <- list.load("./Data/DCA/DCA_real.RData")
-DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
-DCA_obs <- list.load("./Data/DCA/DCA_obs.RData")
-DCA_SR <- list.load("./Data/DCA/DCA_SR.RData")
-DCA_N <- list.load("./Data/DCA/DCA_N.RData")
-
-rename_scenarios = function(df){
-  #df BEFORE reshape::melt!
-  names(df)[names(df) == "Real"] <- "AR"
-  names(df)[names(df) == "noHDNR"] <- "LR"
-  return(df)
-}
-
-#Meteorological drought periods
-#Based on Marengo et al., 2016
-date_ranges_Marengo <- data.frame(
-  from = as.Date(c("1981-01-01", "1982-01-01", "1992-01-01", "1997-01-01", "2001-01-01", "2005-01-01", "2007-01-01", "2010-01-01")),
-  to = as.Date(c("1981-12-01", "1983-12-01", "1993-12-01", "1998-12-01", "2002-12-01", "2005-12-01", "2007-12-01", "2018-12-01"))
-)
-#Based on SPI
-# negSPI <- DCA_real$Banabuiu$date[DCA_real$Banabuiu$PI < 0]
-# negSPI
-date_ranges_SPI <- data.frame(
-  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
-  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
-)
-
-#Arrojado Lisboa
-df <- data.frame(date = DCA_real[['156']]$date, Real = DCA_real[['156']]$WSI, noHDNR = DCA_noH[['156']]$WSI)
-plot_df_interactive(df)
-
-df <- rename_scenarios(df)
-df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
-
-date_ranges <- date_ranges_SPI
-
-p <- ggplot() +
-  #Add the drought rectangles
-  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
-  #Add the VD lines
-  geom_line(data = df, aes(x = date, y = value, linetype = Scenario), alpha = 0.5, size = 1.25) +
-  #VD = 0 line
-  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
-  #geom_text(aes(as.Date("1985-01-01"), 0, label = "VD = 0", vjust = -1, hjust = 0)) +
-  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
-  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
-  theme(axis.text.x = element_text(size = 16),
-        axis.text.y = element_text(size = 20),
-        axis.title = element_text(size = 22),
-        legend.title = element_text(size = 20),
-        legend.text = element_text(size = 18),
-        legend.position = "bottom")
-  #scale_color_manual(values = c("royalblue3", "steelblue"))
-  #scale_color_manual(values = c("salmon1", "royalblue"))
-
-print(p)
-plot.save(p, width = 1280, height = 657, filename = "./Plots/vd_ARLR_present.png")
 
@@
 
-plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
+# plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
 ```

### 2022-07-02 R/Figures_code/figure6_tool.R

@@ -1,0 +1,38 @@
+setwd("C:/Directory_thesis_codes")
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+DCA_LR <- list.load("./Data/Analysis/DCA/DCA_LR.RData")
+DCA_SR <- list.load("./Data/Analysis/DCA/DCA_SR.RData")
+DCA_N <- list.load("./Data/Analysis/DCA/DCA_N.RData")
+
+library(paletteer)
+
+#Drought date ranges (retrieved from SPI results)
+date_ranges <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+
+df <- data.frame(date = DCA_AR[['156']]$date,
+                 AR = DCA_AR[['156']]$WSI, LR = DCA_LR[['156']]$WSI,
+                 SR = DCA_SR$WSI, N = DCA_N$WSI)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+
+p <- ggplot() +
+  #Add the drought rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.2) +
+  #Add the VD lines
+  geom_line(data = df, aes(x = date, y = value, linetype = Scenario, col = Scenario), alpha = 0.9, size = 1.25) +
+  #VD = 0 line
+  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
+  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  scale_color_paletteer_d("colorBlindness::paletteMartin") +
+  theme(axis.text.x = element_text(size = 16),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
[…]

### 2022-07-02 R/Libraries/Libraries.R

@@ -9,10 +9,10 @@ library(tidyverse)
 # library(lumpR)
 
 #Visualization
-library(ggplot2)
-require(scales)
-library(gridExtra)
-library(plotly)
+# library(ggplot2)
+# require(scales)
+# library(gridExtra)
+# library(plotly)
 # library(hrbrthemes)
 
 #Georeferenced data

### 2022-07-02 R/Libraries/Libraries_plot.R

@@ -1,0 +1,7 @@
+#Libraries for Visualization
+
+library(ggplot2)
+require(scales)
+library(gridExtra)
+library(plotly)
+library(paletteer)

### 2022-07-02 R/Figures_code/paper_figures.Rmd
figure 6 done, figure 5 started

@@
 
-Graphical representation of the Drought Cycle Analysis, taken from Ribeiro Neto et al., 2022.
 ![Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al.
@@
 
+## Figure 5
+
+```{r figure 5}
+
+```
+
 ## Figure 6
 
+Volume Deviation visualization for all modeled scenarios. Different relationships between storage conditions and the DNR effect are indicated.
+
 ```{r figure 6}
+setwd("C:/Directory_thesis_codes")
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+DCA_LR <- list.load("./Data/Analysis/DCA/DCA_LR.RData")
+DCA_SR <- list.load("./Data/Analysis/DCA/DCA_SR.RData")
+DCA_N <- list.load("./Data/Analysis/DCA/DCA_N.RData")
 
+#Drought date ranges (retrieved from SPI results)
+date_ranges <- data.frame(
+  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
+  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
+)
+#Create the VD dataframe
+df <- data.frame(date = DCA_AR[['156']]$date,
+                 AR = DCA_AR[['156']]$WSI, LR = DCA_LR[['156']]$WSI,
+                 SR = DCA_SR$WSI, N = DCA_N$WSI)
+df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
+
+p <- ggplot() +
+  #Add the drought rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.2) +
+  #Add the VD lines
+  geom_line(data = df, aes(x = date, y = value, linetype = Scenario, col = Scenario), alpha = 0.9, size = 1.25) +
+  #VD = 0 line
+  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
+  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  scale_color_paletteer_d("colorBlindness::paletteMartin") +
+  theme(axis.text.x = element_text(size = 16),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 18),
+        legend.position = "bottom")
+print(p)
+
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_6.png")
 ```

### 2022-07-02 R/Figures_code/figure6_tool.R

@@ -1,38 +1,0 @@
-setwd("C:/Directory_thesis_codes")
-DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
-DCA_LR <- list.load("./Data/Analysis/DCA/DCA_LR.RData")
-DCA_SR <- list.load("./Data/Analysis/DCA/DCA_SR.RData")
-DCA_N <- list.load("./Data/Analysis/DCA/DCA_N.RData")
-
-library(paletteer)
-
-#Drought date ranges (retrieved from SPI results)
-date_ranges <- data.frame(
-  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
-  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
-)
-
-df <- data.frame(date = DCA_AR[['156']]$date,
-                 AR = DCA_AR[['156']]$WSI, LR = DCA_LR[['156']]$WSI,
-                 SR = DCA_SR$WSI, N = DCA_N$WSI)
-df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')
-
-p <- ggplot() +
-  #Add the drought rectangles
-  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.2) +
-  #Add the VD lines
-  geom_line(data = df, aes(x = date, y = value, linetype = Scenario, col = Scenario), alpha = 0.9, size = 1.25) +
-  #VD = 0 line
-  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
-  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
-  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
-  scale_color_paletteer_d("colorBlindness::paletteMartin") +
-  theme(axis.text.x = element_text(size = 16),
-        axis.text.y = element_text(size = 20),
-        axis.title = element_text(size = 22),
-        legend.title = element_text(size = 20),
[…]

### 2022-07-02 R/Figures_code/figure_5_tool.R

@@ -1,0 +1,57 @@
+#Figure 5 tool
+
+find_bounds = function(df, x = 1, skip = 0){
+  minx <- function(x) min(x, na.rm = TRUE)
+  maxx <- function(x) max(x, na.rm = TRUE)
+  skip <- skip + 1
+  lowbound <- apply(df[, skip:ncol(df)], x, minx)
+  highbound <- apply(df[, skip:ncol(df)], x, maxx)
+  bounds <- data.frame(date = df$date, low = lowbound, high = highbound)
+  return(bounds)
+}
+
+SPI_df <- data.frame(date = DCA_real$Banabuiu$date)
+for(i in 1:length(DCA_real)){
+  SPI_df$new <- DCA_real[[i]]$PI
+  names(SPI_df)[names(SPI_df) == "new"] <- names(DCA_real)[i]
+}
+
+newdf <- SPI_df[,1:ncol(SPI_df)-1]
+bounds <- find_bounds(newdf, 1, 1)
+bounds[bounds == Inf | bounds == -Inf] <- 0
+
+date_ranges <- date_ranges_Marengo
+
+df <- SPI_df[, c(1,ncol(SPI_df))]
+col <- c("Mean SPI-12"="royalblue2", "Sub-basins variation"="sandybrown")
+p <- ggplot() +
+  #Add the droughts rectangles
+  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
+  #Add the sub-basins variation
+  geom_ribbon(data = bounds, aes(x = date, ymin = low, ymax = high, fill = "Sub-basins variation"), alpha = 0.5) +
+  #Add the mean line
+  geom_line(data = df, aes(x = date, y = Banabuiu, colour = "Mean SPI-12"), size = 1) +
+  #Add the drought indicator lines
+  geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 5) +
+  geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 5) +
[…]

### 2022-07-19 R/Figures_code/paper_figures.Rmd
moved data

@@
 source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Libraries_plot.R")
 source("./R/Libraries/Functions.R")
@@
 ```{r figure 5}
+setwd("C:/Directory_thesis_codes")
 
+#Custom functions
+#Moving average
+ma <- function(x, n = 5){stats::filter(x, rep(1 / n, n), sides = 2)}
+#Find the lower and upper bounds
+find_bounds = function(df, x = 1, skip = 0, ma = FALSE, n = 5){
+  minx <- function(x) min(x, na.rm = TRUE)
+  maxx <- function(x) max(x, na.rm = TRUE)
+  skip <- skip + 1
+  lowbound <- apply(df[, skip:ncol(df)], x, minx)
+  highbound <- apply(df[, skip:ncol(df)], x, maxx)
+  if(ma){
+    lowbound <- ma(lowbound, n)
+    highbound <- ma(highbound, n)
+  }
+  bounds <- data.frame(date = df$date, low = lowbound, high = highbound)
+  return(bounds)
+}
+
+#Cunstruct the dataframe
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+
+df <- data.frame(date = DCA_AR$Banabuiu$date)
+for(i in seq_len(length(DCA_AR))){
+  df$new <- DCA_AR[[i]]$PI
+  names(df)[names(df) == "new"] <- names(DCA_AR)[i]
+}
+
+newdf <- df[, 1:ncol(df)-1]
+bounds <- find_bounds(newdf, 1, 1, ma = TRUE, 6)
+bounds[bounds == Inf | bounds == -Inf] <- 0
+df <- df[, c(1, ncol(df))]
+df$lowbound <- bounds$low
+df$highbound <- bounds$high
+df$ma <- ma(df$Banabuiu, 6)
+df <- df[14:nrow(df), ]
+
+#Plot
+col <- c("Mean precipitation" = "#293462",
+         "Sub-basin variation" = "#F24C4C")
+p <- ggplot() +
+  #Add the droughts rectangles
+  # geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
+  #Add the sub-basins variation
+  geom_ribbon(data = df, aes(x = date, ymin = lowbound, ymax = highbound, fill = "Sub-basin variation"), alpha = 0.5) +
+  #Add the mean line
+  geom_line(data = df, aes(x = date, y = ma, colour = "Mean precipitation"), size = 1.25) +
+  #Add the drought indicator lines
+  geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 6) +
+  geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 6) +
+  geom_hline(yintercept = -1.5, color = 'orange', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), -1.5, label = "Severely dry", vjust = -0.5, hjust = 0), size = 6) +
+  geom_hline(yintercept = -2, color = 'red', linetype = "dashed", size = 1.25, alpha = 0.8) +
+  geom_text(aes(as.Date("1985-01-01"), -2, label = "Extremely dry", vjust = -0.5, hjust = 0), size = 6) +
+  #Modify the axis
+  scale_y_continuous(name = 'SPI-12', limits = c(-4, 4), breaks = seq(-4, 4, 1)) +
+  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
+  #Add the legend
+  scale_color_manual(name = "", values = col) +
+  scale_fill_manual(name = "", values = col) +
+  theme(
+        axis.text.x = element_text(size = 16),
+        axis.text.y = element_text(size = 20),
+        axis.title = element_text(size = 22),
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 18),
+        legend.position = "bottom",
+        panel.background = element_rect(fill = "white", colour = "grey50")
+        )
+
+print(p)
+
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5.png")
 ```

### 2022-07-20 R/Figures_code/figure_5_tool.R
moved data

@@ -1,36 +1,83 @@
 #Figure 5 tool
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_MC.R")
+source("./R/Libraries/Libraries_plot.R")
 
-find_bounds = function(df, x = 1, skip = 0){
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+
+# df$Banabuiu <- NULL
+
+
+#Based on Marengo et al., 2016
+date_ranges <- data.frame(
+  from = as.Date(c("1981-01-01", "1982-01-01", "1992-01-01", "1997-01-01", "2001-01-01", "2005-01-01", "2007-01-01", "2010-01-01")),
+  to = as.Date(c("1981-12-01", "1983-12-01", "1993-12-01", "1998-12-01", "2002-12-01", "2005-12-01", "2007-12-01", "2018-12-01"))
+)
+
+# library(SPEI)
+# load("./Data/Observations/precipitation.Rdata")
+# 
+# avgprec <- apply(prec[, 2:ncol(prec)], 1, mean)
+# avgSPI <- spi(avgprec, 12)
+# 
+# df <- data.frame(date = DCA_AR$Banabuiu$date, avgSPI =avgSPI$fitted, old = DCA_AR$Banabuiu$PI)
+# plot_df_interactive(df)
+# 
+
+
+#per fare il boxplot, rimuovere Banabuiu dal df
+
+ma <- function(x, n = 5){stats::filter(x, rep(1 / n, n), sides = 2)}
+
+find_bounds = function(df, x = 1, skip = 0, ma = FALSE, n = 5){
   minx <- function(x) min(x, na.rm = TRUE)
   maxx <- function(x) max(x, na.rm = TRUE)
   skip <- skip + 1
   lowbound <- apply(df[, skip:ncol(df)], x, minx)
   highbound <- apply(df[, skip:ncol(df)], x, maxx)
+  if(ma){
+    lowbound <- ma(lowbound, n)
+    highbound <- ma(highbound, n)
+  }
   bounds <- data.frame(date = df$date, low = lowbound, high = highbound)
   return(bounds)
 }
 
-SPI_df <- data.frame(date = DCA_real$Banabuiu$date)
-for(i in 1:length(DCA_real)){
[…]

### 2022-07-20 R/Figures_code/paper_figures.Rmd
figure 5 done

@@
 
-```{r figure 5}
+```{r figure 5a}
 setwd("C:/Directory_thesis_codes")
@@
 
-newdf <- df[, 1:ncol(df)-1]
+newdf <- df[, seq_len(ncol(df)-1)]
 bounds <- find_bounds(newdf, 1, 1, ma = TRUE, 6)
@@
 plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5.png")
+```
+
+```{r figure 5b}
+setwd("C:/Directory_thesis_codes")
+
+sub <- readOGR("./Data/Shapefile/subbasins_cut_geomfix.shp")
+SPI_list <- list.load("./Data/Analysis/DCA/SPI_list.RData")
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+
+df <- as.data.frame(array(dim = c(length(SPI_list), 3)))
+names(df) <- c("SubbasinID", "SPI-1992", "SPI-2012")
+df$SubbasinID <- names(SPI_list)
+
+idx1992 <- DCA_AR[["123"]]$date %in% create_date_vector(1992, 1993)
+idx2012 <- DCA_AR[["123"]]$date %in% create_date_vector(2012, 2018)
+for(name in names(SPI_list)){
+  df$`SPI-1992`[df$SubbasinID %in% name] <- mean(SPI_list[[name]][["fitted"]][idx1992], na.rm = T)
+  df$`SPI-2012`[df$SubbasinID %in% name] <- mean(SPI_list[[name]][["fitted"]][idx2012], na.rm = T)
+}
+
+sub_merge <- merge(sub, df, by = "SubbasinID")
+
+writeOGR(sub_merge, dsn = "./Data/Shapefile/analysis", layer = "subbasin_SPI_all", driver = "ESRI Shapefile")
 ```

### 2022-07-20 R/Core_code/Analysis/DCA.R

@@ -4,25 +4,25 @@
 # Script setup ------------------------------------------------------------
 
 #Directory and paths
-setwd("C:/Users/paolo/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Directory_thesis_codes")
-path_maxcap <- "./Inputs/Model_input/Base/Reservoir/reservoir.dat"
+setwd("C:/Directory_thesis_codes")
+path_maxcap <- "./Input/Model_input/Base/Reservoir/reservoir.dat"
 
-source("./Libraries/Libraries.R")
-source("./Libraries/Functions.R")
-# source("./Libraries/Functions_TG.R")
-# source("./Libraries/Functions_DP.R")
-source("./Libraries/Functions_CO.R")
-source("./Libraries/Functions_MC.R")
-source("./Libraries/Functions_AN.R")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Functions.R")
+# source("./R/Libraries/Functions_TG.R")
+# source("./R/Libraries/Functions_DP.R")
+source("./R/Libraries/Functions_CO.R")
+source("./R/Libraries/Functions_MC.R")
+source("./R/Libraries/Functions_AN.R")
 
 #Load the IDs of the subbasins in the Banabuiu region
-load("./Inputs/General/IDs.RData")
-subID <- read.table("./Inputs/General/reservoir_name_ID.txt", header = TRUE, sep = "\t")
+load("./Data/Generated/General/IDs.RData")
+subID <- read.table("./Data/Generated/General/reservoir_name_ID.txt", header = TRUE, sep = "\t")
 
 # Analysis setup ----------------------------------------------------------
 
 #Load precipitation data
-prec <- read.table("./Inputs/Model_input/Base/Time_series/rain_daily.dat", skip = 3)
+prec <- read.table("./Input/Model_input/Base/Time_series/rain_daily.dat", skip = 3)
 columns <- c("date", "doy", subID$SubbasinID)
 names(prec) <- columns
 prec$date <- change_date_WASA_input(prec$date)

### 2022-07-20 R/Figures_code/DCA_allsub.R

@@ -1,0 +1,18 @@
+# SPI calculation for each subbasin
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Functions_CO.R")
+library(rlist)
+
+prec <- read.table("./Input/Model_input/Base/Time_series/rain_daily.dat", skip = 3)
+columns <- c("date", "doy", subID$SubbasinID)
+names(prec) <- columns
+prec$date <- change_date_WASA_input(prec$date)
+prec$doy <- NULL
+prec <- monthly_scale(prec, f = sumx)
+
+library(SPEI)
+
+list_SPI <- list()
+list_SPI <- apply(prec[, 2:ncol(prec)], 2, function(x) spi(x, 12))
+
+list.save(list_SPI, "./Data/Analysis/DCA/SPI_list.RData")

### 2022-07-20 R/Libraries/Functions_TG.R

@@ -1,10 +1,10 @@
 #Functions to execute the time series generation
 
 create_date_vector <- function(start_y, end_y, start_m = 01, end_m = 12,
-                              start_d = 01, end_d = 31) {
+                              start_d = 01, end_d = 31, by = "days") {
   start <- paste0(start_d, "/0", start_m, "/", start_y)
   end <- paste0(end_d, "/", end_m, "/", end_y)
-  date <- seq(as.Date(start, "%d/%m/%Y"), as.Date(end, "%d/%m/%Y"), by = "days")
+  date <- seq(as.Date(start, "%d/%m/%Y"), as.Date(end, "%d/%m/%Y"), by = by)
   return(date)
 }
 

### 2022-08-05 R/Figures_code/paper_figures.Rmd
images ended

@@
 ---
-title: Code to generate the figures needed in 'The influence of small reservoirs on
-  hydrological drought propagation in space and time'
+title: "Code and information needed to generate the figures needed in 'The influence of small reservoirs on hydrological drought propagation in space and time'"
 author: "Paolo Colombo"
@@
 Made in QGIS utilizing the shapefiles and rasters found in ./Data/DNR and ./Data/Shapefile.
-![Study area framing.
+The density visualization was made with the QGIS “Density Analysis” plugin.
+The field NUMPOINTs was then divided by the area of each cell ($25 \hspace{0.1cm} km^2$) to obtain the density ($n°small\hspace{0.1cm}reservoirs/km^2$).
+The equation used in the new field was: "NUMPOINTS"/($area/1000000) ![Study area framing.
 North-East Brazil, Ceará and Banabuiú catchment on the left.
@@
 
+## Figure 4
+
 ## Figure 5
+
+SPI-12 visualization.
+a.) 6-months moving average of the SPI-12 computed on the basin’s average precipitation and variability spectrum across the sub-basins.
+Spatial distribution of  SPI-12 in Banabuiu watershed sub-basins averaged for b.) 1992-1993 drought and c.) 2012-2018 drought.
 
@@
 
-newdf <- df[, seq_len(ncol(df)-1)]
+newdf <- df[, 1:ncol(df)-1]
 bounds <- find_bounds(newdf, 1, 1, ma = TRUE, 6)
@@
 
+## Figure 7
+
 ## Figure 8
 
-```{r figure 8a}
+Barplot of the drought phases percentages in the four scenarios. Percentage of months in the four drought phases in AR, LR, SR and N scenarios computed for for Arrojado Lisboa.
+
+```{r figure 8}
+setwd("C:/Directory_thesis_codes")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Libraries_plot.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_MC.R")
+
+library(scales)
+
+DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")
+DCA_LR <- list.load("./Data/Analysis/DCA/DCA_LR.RData")
+DCA_SR <- list.load("./Data/Analysis/DCA/DCA_SR.RData")
+DCA_N <- list.load("./Data/Analysis/DCA/DCA_N.RData")
+
+table <- data.frame(matrix(NA, 5, 4))
+names(table) <- c("AR", "LR", "SR", "N")
+for(i in seq_len(4)){
+  table$AR[i] <- sum(DCA_AR[['156']]$quadrant == i, na.rm = TRUE)
+  table$LR[i] <- sum(DCA_LR[['156']]$quadrant == i, na.rm = TRUE)
+  table$SR[i] <- sum(DCA_SR$quadrant == i, na.rm = TRUE)
+  table$N[i] <- sum(DCA_N$quadrant == i, na.rm = TRUE)
+}
+table[5, ] <- apply(table, 2, function(x) sum(x, na.rm = TRUE))
+table <- apply(table, 2, function(x) x/457*100)
+table <- as.data.frame(table)
+table <- table[-5,]
+table$`Drought phase` <- c(
+                  "1. Non-occurrence of drought",
+                  "2. Meteorological",
+                  "3. Hydro-meteorological",
+                  "4. Hydrological")
+
+table <- pivot_longer(table, cols = 1:4, names_to = "Scenario", values_to = "Percentage")
+
+p <- ggplot(table, aes(fill = `Drought phase`, y = Percentage, x = Scenario)) + 
+      geom_bar(position = "stack", stat = "identity", 
+               alpha = 0.5, colour = "black") +
+      scale_fill_manual(values = c("#377EB8", "#FFD92F", "#E41A1C", "#B15928")) +
+      scale_y_continuous(breaks = round(seq(0, 100, by = 10))) +
+      theme(
+          axis.title = element_text(size = 26),
+          axis.text.x = element_text(size = 24),
+          axis.text.y = element_text(size = 24),
+          legend.title = element_text(size = 24, face = "bold"),
+          legend.text = element_text(size = 20),
+          # legend.position = "bottom",
+          panel.background = element_rect(fill = "white"),
+          panel.grid.major.x = element_blank(),
+          panel.grid.major.y = element_line(colour = alpha("grey50", 0.7))
+          )
+print(p)
+
+plot.save(p, width = 1920, height = 1440, filename = "./Figures and tables/paper/Figure_8.png")
+```
+
+## Figure 9
+
+```{r figure 9a}
 setwd("C:/Directory_thesis_codes")
@@
   theme(
-        axis.text.x = element_text(size = 18),
-        axis.text.y = element_text(size = 20),
-        axis.title = element_text(size = 22),
-        legend.title = element_text(size = 20),
-        legend.text = element_text(size = 18),
+        axis.text.x = element_text(size = 24),
+        axis.text.y = element_text(size = 24),
+        axis.title = element_text(size = 24),
+        legend.title = element_text(size = 26),
+        legend.text = element_text(size = 24),
         legend.position = "bottom"
@@
 
-# plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
 ```
 
-```{r figure 8b}
+```{r figure 9b}
 setwd("C:/Directory_thesis_codes")

### 2022-08-05 Data/Plot_table/Germanos/DCA_plot_paper.m

@@ -1,0 +1,276 @@
+%% Plotagem
+clc
+clear all
+%% Files
+% drought_event - a struct variable with the basic information of the analyzed drought events 
+% %% Input 
+% load('Ciclo_Seca')
+% % vd_r017_nt - Volume Defict of the scenario without small reservoirs of the analyzed reservoir for the whole study period
+% % vd_r017_ob - Volume Defict of the scenario with small reservoirs of the analyzed reservoir for the whole study period
+% % CS - Structured variable that shows, for each drought event, in which quadrant of the DCA the pair of variables (SPI and VD) was in each month.
+% % data_reserv_completa - date variable (in the format Y, M ,D)
+ 
+load('ARvsLR_data.mat')
+
+%% Scale the VD
+%The VD is automatically scaled
+
+%a = -2.7;
+%b = 2.7;
+%spi = (b-a)*(spi - min(spi))/(max(spi) - min(spi)) + a;
+%vd_r017_nt = (b-a)*(vd_r017_nt - min(vd_r017_nt))/(max(vd_r017_nt) - min(vd_r017_nt)) + a;
+%vd_r017_ob = (b-a)*(vd_r017_ob - min(vd_r017_ob))/(max(vd_r017_ob) - min(vd_r017_ob)) + a;
+
+%% Drought Event 
+
+drought_event{1,1}=[datenum([1992 01 1]) datenum([1994 08 01])];  % First and last date of each drought event
+drought_event{2,1}=[datenum([1997 01 1]) datenum([2002 06 01])];  % First and last date of each drought event
+drought_event{3,1}=[datenum([2010 01 1]) datenum([2018 12 01])];  % First and last date of each drought event
+%% Selected dates of each drouhgt event to be ploted in the DCA with the marks (circles and stars that appear in the chart)
+
+% First drought event
+drought_event{1,2}(1,:)=[1992 04 01]; 
+drought_event{1,2}(2,:)=[1993 05 01];
+drought_event{1,2}(3,:)=[1994 08 01];
+% Second drought event
[…]

### 2022-08-05 R/Figures_code/DCA_wheels/DCA_plot_paper.m

@@ -1,0 +1,266 @@
+%% Plotagem
+
+clc
+clear all
+%% Files
+% %% Input
+% drought_event - a struct variable with the basic information of the analyzed drought events 
+% vd_r017_nt - Volume Defict of the scenario without small reservoirs of the analyzed reservoir for the whole study period
+% vd_r017_ob - Volume Defict of the scenario with small reservoirs of the analyzed reservoir for the whole study period
+% CS - Structured variable that shows, for each drought event, in which quadrant of the DCA the pair of variables (SPI and VD) was in each month.
+% data_reserv_completa - date variable (in the format Y, M ,D)
+ 
+load('ARvsLR_data.mat')
+%% Drought Event 
+
+drought_event{1,1}=[datenum([1992 01 1]) datenum([1994 08 01])];  % First and last date of each drought event
+drought_event{2,1}=[datenum([1997 01 1]) datenum([2002 06 01])];  % First and last date of each drought event
+drought_event{3,1}=[datenum([2010 01 1]) datenum([2018 12 01])];  % First and last date of each drought event
+%% Selected dates of each drouhgt event to be ploted in the DCA with the marks (circles and stars that appear in the chart)
+
+% First drought event
+drought_event{1,2}(1,:)=[1992 04 01]; 
+drought_event{1,2}(2,:)=[1993 05 01];
+drought_event{1,2}(3,:)=[1994 08 01];
+% Second drought event
+drought_event{2,2}(1,:)=[1997 05 01];
+drought_event{2,2}(2,:)=[1998 03 01];
+drought_event{2,2}(3,:)=[1999 05 01];
+drought_event{2,2}(4,:)=[2002 05 01];
+% Third drought event 
+drought_event{3,2}(1,:)=[2010 12 01];
+drought_event{3,2}(2,:)=[2011 11 01];
+drought_event{3,2}(3,:)=[2014 07 01];
+drought_event{3,2}(4,:)=[2015 09 01];
+drought_event{3,2}(5,:)=[2018 05 01];
[…]

### 2022-08-05 R/Figures_code/DCA_wheels/cor_ivd2.m

@@ -1,0 +1,146 @@
+function [cc] = cor_ivd(vd,spi,rr,cq1,cq2,cq3,cq4,nt,nc)
+%% Cores Quadrandes
+% cq1=[0 1 1];
+% cq2=[1 1 0.0]; 
+% cq3=[1 0 0.0];
+% cq4=[0.5 0.0 0.5];
+%% Tons e Cores
+% nc=5; % Numero de cores
+%% Grade
+a=0:0.5:360;
+st=1.0;
+% rr=sqrt((lim_vd(2)-lim_vd(1))^2+(lim_spi(2)-lim_spi(1))^2);
+dr=0:rr/(nt-1):rr;   % Todas as posicoes R do circulo de cores
+rp=sqrt(vd^2+spi^2); % Distancia do ponto a origem
+alf=acosd(spi/rp);   % Angulo do ponto analisado
+if vd<0
+   alf=360-alf;
+end
+    
+
+c=0;
+for iii=1:length(a)
+    for ii=1:length(dr)
+        c=c+1;
+        A(c,1)=a(iii);
+    end
+end
+%% Def Quadrandes
+dq1=cq2-cq1;
+dq2=cq3-cq2;
+dq3=cq4-cq3;
+dq4=cq1-cq4;
+%% Primeiro Quadrante
+a_q1=45:90/nc:135;  % Angulo Primeiro Quadrante
+r_q1=cq1(1):dq1(1)/(length(a_q1)-1):cq2(1);r_q1=r_q1';
+g_q1=cq1(2):dq1(2)/(length(a_q1)-1):cq2(2);g_q1=g_q1';
+b_q1=cq1(3):dq1(3)/(length(a_q1)-1):cq2(3);b_q1=b_q1';
+dq1(dq1==0)=cq2(dq1==0);
+if isempty(r_q1)==1
+   r_q1=ones(length(a_q1),1)*dq1(1); 
+end
+if isempty(g_q1)==1
+   g_q1=ones(length(a_q1),1)*dq1(2); 
+end
+if isempty(b_q1)==1
+   b_q1=ones(length(a_q1),1)*dq1(3); 
+end
+cb_q1=[r_q1 g_q1 b_q1];  % Cor base Quadrante 1
+%% Segundo Quadrante
+a_q2=135:90/nc:225; % Angulo segundo Quadrante
[…]

### 2022-08-05 R/Figures_code/DCA_wheels/plot_droughwheel.m

@@ -1,0 +1,166 @@
+function [X,Y,COR] = plot_droughwheel(rr,cq1,cq2,cq3,cq4,nt,nc)
+% %% Circulo de cores
+
+
+%% Grade
+a=0:0.25:360; %% Resolucao da drought wheel
+st=1.0;
+res=100; % Resolucao do ciclo de seca;
+
+% rr=sqrt((lim_vd(2)-lim_vd(1))^2+(lim_spi(2)-lim_spi(1))^2);
+rr=0:rr/(res-1):rr;   % Todas as posicoes R do circulo de cores
+c=0;
+
+for iii=1:length(a)
+    for ii=1:length(rr)
+        c=c+1;
+        X(c,1)=sind(a(iii))*rr(ii);
+        Y(c,1)=cosd(a(iii))*rr(ii);
+        A(c,1)=a(iii);
+    end
+end
+%% Def Quadrandes
+cmx=1;
+% cq1=[0 0 1];%dq1(dq1==0)=cq2(dq1==0);
+% cq2=[0 1 1];%dq2(dq2==0)=cq3(dq2==0);
+% cq3=[1 1 0];%dq2(dq2==0)=cq3(dq2==0);
+% cq4=[1 0 0];%dq4(dq4==0)=cq5(dq4==0);
+
+
+dq1=cq2-cq1;
+dq2=cq3-cq2;
+dq3=cq4-cq3;
+dq4=cq1-cq4;
+%% Primeiro Quadrante
+a_q1=45:90/nc:135;  % Angulo Primeiro Quadrante
+r_q1=cq1(1):dq1(1)/(length(a_q1)-1):cq2(1);r_q1=r_q1';
+g_q1=cq1(2):dq1(2)/(length(a_q1)-1):cq2(2);g_q1=g_q1';
+b_q1=cq1(3):dq1(3)/(length(a_q1)-1):cq2(3);b_q1=b_q1';
+dq1(dq1==0)=cq2(dq1==0);
+if isempty(r_q1)==1
+   r_q1=ones(length(a_q1),1)*dq1(1); 
+end
+if isempty(g_q1)==1
+   g_q1=ones(length(a_q1),1)*dq1(2); 
+end
+if isempty(b_q1)==1
+   b_q1=ones(length(a_q1),1)*dq1(3); 
+end
+cb_q1=[r_q1 g_q1 b_q1];  % Cor base Quadrante 1
+%% Segundo Quadrante
+a_q2=135:90/nc:225; % Angulo segundo Quadrante
[…]

### 2022-08-05 R/Figures_code/DCA_wheels/plotagem_cliclo_seca.m

@@ -1,0 +1,271 @@
+%% Plotagem
+clc
+clear all
+%% Files
+% drought_event - a struct variable with the basic information of the analyzed drought events 
+%% Input 
+load('Ciclo_Seca')
+% vd_r017_nt - Volume Defict of the scenario without small reservoirs of the analyzed reservoir for the whole study period
+% vd_r017_ob - Volume Defict of the scenario with small reservoirs of the analyzed reservoir for the whole study period
+% CS - Structured variable that shows, for each drought event, in which quadrant of the DCA the pair of variables (SPI and VD) was in each month.
+% data_reserv_completa - date variable (in the format Y, M ,D)
+
+%load('AL_data.mat')
+%% Drought Event 
+drought_event{1,1}=[datenum([1992 5 1]) datenum([1994 08 01])];  % First and last date of each drought event
+drought_event{2,1}=[datenum([1997 10 1]) datenum([2002 6 01])];  % First and last date of each drought event
+drought_event{3,1}=[datenum([2011 12 1]) datenum([2020 07 01])]; % First and last date of each drought event
+%% Selected dates of each drouhgt event to be ploted in the DCA with the marks (circles and stars that appear in the chart)
+% First drought event
+drought_event{1,2}(1,:)=[1992 05 01]; 
+drought_event{1,2}(2,:)=[1993 06 01];
+drought_event{1,2}(3,:)=[1993 12 01];
+drought_event{1,2}(4,:)=[1994 08 01];
+drought_event{1,2}(5,:)=[1992 12 01];
+% Second drought event
+drought_event{2,2}(1,:)=[1997 10 01];
+drought_event{2,2}(2,:)=[1998 07 01];
+drought_event{2,2}(3,:)=[1999 02 01];
+drought_event{2,2}(4,:)=[2000 09 01];
+drought_event{2,2}(5,:)=[2001 02 01];
+drought_event{2,2}(6,:)=[2002 06 01];
+% Third drought event 
+drought_event{3,2}(1,:)=[2011 12 01];
[…]

### 2022-08-05 R/Figures_code/DCA_wheels/posicao3.m

@@ -1,0 +1,27 @@
+function [PLOT]=posicao(espvbi,espvbs,espvf,esphbe,esphbd,esphf,nplotx,nploty)
+%P1 - Esquerda ; P2 - Inferior ; P3 - Largura ; P4 - Altura ;
+%nplotx Número de linhas no plot
+%nploty Número de colunas no plot
+p1_1=esphbe;
+p4=(1-espvbi -espvbs - ((nplotx-1)*espvf))/nplotx;
+p3=(1-esphbe-esphbd-(((nploty*0.5)-1)*esphf))/nploty;
+p2=1-espvbs-p4;
+for j=1:nploty
+    for i=1:nplotx
+            PLOT{i,j}=[p1_1 p2 p3 p4];
+            p2=p2-espvf-p4;
+    end
+    
+    
+    p1_1=p1_1+p3+esphf;
+%     if j==1 || j==2 
+%        p1_1=p1_1+p3+esphc;
+%     elseif j==3
+%        p1_1=p1_1+esphf+p3; 
+%     elseif j==4|| j==5 || j==6
+%       p1_1=p1_1+p3+esphc;
+%     end
+    p2=1-espvbs-p4;
+end
+end
+

### 2022-08-05 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
moved folder

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements, including customized APA reference formatting.
%
% You may copy this file and give it your
% article name, and enter your text.
%
%
% Step 1: Set the \documentclass
%
%

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

\draftfalse

%% Enter journal name below.
%% Choose from this list of Journals:
%
% JGR: Atmospheres
% JGR: Biogeosciences
% JGR: Earth Surface
% JGR: Oceans
% JGR: Planets
% JGR: Solid Earth
% JGR: Space Physics
% Global Biogeochemical Cycles
% Geophysical Research Letters
% Paleoceanography and Paleoclimatology
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resources Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
% Geohealth
%
% ie, \journalname{Water Resources Research}

\journalname{Enter journal name here}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
%
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{=enter title here=}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{=list all authors here=}

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{=number=}{=Affiliation Address=}
%(repeat as many times as is necessary)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

\correspondingauthor{=name=}{=email address=}

%% Keypoints, final entry on title page.

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences

% Example:
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
% \end{keypoints}

\begin{keypoints}
\item enter point 1 here
\item enter point 2 here
\item enter point 3 here
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT and PLAIN LANGUAGE SUMMARY
%
% A good Abstract will begin with a short description of the problem
% being addressed, briefly describe the new data or analyses, then
% briefly states the main conclusion(s) and how they are supported and
% uncertainties.

% The Plain Language Summary should be written for a broad audience,
% including journalists and the science-interested public, that will not have 
% a background in your field.
%
% A Plain Language Summary is required in GRL, JGR: Planets, JGR: Biogeosciences,
% JGR: Oceans, G-Cubed, Reviews of Geophysics, and JAMES.
% see http://sharingscience.agu.org/creating-plain-language-summary/)
%
%% ------------------------------------------------------------------------ %%

%% \begin{abstract} starts the second page

\begin{abstract}
[ enter your Abstract here ]
\end{abstract}

\section*{Plain Language Summary}
[ enter your Plain Language Summary here or delete this section]

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

%%% Suggested section heads:
% \section{Introduction}
%
% The main text should start with an introduction. Except for short
% manuscripts (such as comments and replies), the text should be divided
% into sections, each with its own heading.

% Headings should be sentence fragments and do not begin with a
% lowercase letter or number. Examples of good headings are:

% \section{Materials and Methods}
% Here is text on Materials and Methods.
%
% \subsection{A descriptive heading about methods}
% More about Methods.
%
% \section{Data} (Or section title might be a descriptive heading about data)
%
% \section{Results} (Or section title might be a descriptive heading about the
% results)
%
% \section{Conclusions}

\section{= enter section title =}
%Text here ===>>>

%%

%  Numbered lines in equations:
%  To add line numbers to lines in equations,
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%% Enter Figures and Tables near as possible to where they are first mentioned:
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables;  other caption information
%  should be placed in last line of the table, using
% \multicolumn2l{$^a$ This is a table note.}
%
%----------------
% EXAMPLE FIGURES
%
% \begin{figure}
% \includegraphics{example.png}
% \caption{caption}
% \end{figure}
%
% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
% \begin{figure}
% \noindent\includegraphics[width=\textwidth]{anothersample.png}
%\caption{caption}
%\label{pngfiguresample}
%\end{figure}
%
%
% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options. This is common when trying to add a PDF figure without pdflatex.
% \begin{figure}
% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.pdf}
%\caption{caption}
%\label{pdffiguresample}
%\end{figure}
%
%
% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
%

%
% ---------------
% EXAMPLE TABLE
% Please do NOT include vertical lines in tables
% if the paper is accepted, Wiley will replace vertical lines with white space
% the CLS file modifies table padding and vertical lines may not display well
%
 \begin{table}
 \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
 \centering
 \begin{tabular}{l c}
 \hline
  Run  & Time (min)  \\
 \hline
   $l1$  & 260   \\
   $l2$  & 300   \\
   $l3$  & 340   \\
   $h1$  & 270   \\
   $h2$  & 250   \\
   $h3$  & 380   \\
   $r1$  & 370   \\
   $r2$  & 390   \\
 \hline
 \multicolumn{2}{l}{$^{a}$Footnote text here.}
 \end{tabular}
 \end{table}

%% SIDEWAYS FIGURE and TABLE
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{figsamp}
% \caption{caption here}
% \label{newfig}
% \end{sidewaysfigure}
%
%  \begin{sidewaystable}
%  \caption{Caption here}
% \label{tab:signif_gap_clos}
%  \begin{tabular}{ccc}
% one&two&three\\
% four&five&six
%  \end{tabular}
%  \end{sidewaystable}

%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
%\begin{linenomath*}
%\begin{equation}
%y|{f} \sim g(m, \sigma),
%\end{equation}
%\end{linenomath*}

%%% End of body of article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% The \appendix command resets counters and redefines section heads
%
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
%\appendix
%\section{Here is a sample appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary, Notation or Acronym section goes here:
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
%  \begin{glossary}
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \end{glossary}

%
%%%%%%%%%%%%%%
% Acronyms
%   \begin{acronyms}
%   \acro{Acronym}
%   Definition here
%   \acro{EMOS}
%   Ensemble model output statistics
%   \acro{ECMWF}
%   Centre for Medium-Range Weather Forecasts
%   \end{acronyms}

%
%%%%%%%%%%%%%%
% Notation
%   \begin{notation}
%   \notation{$a+b$} Notation Definition here
%   \notation{$e=mc^2$}
%   Equation in German-born physicist Albert Einstein's theory of special
%  relativity that showed that the increased relativistic mass ($m$) of a
%  body comes from the energy of motion of the body—that is, its kinetic
%  energy ($E$)—divided by the speed of light squared ($c^2$).
%   \end{notation}

\section{Open Research}
AGU requires an Availability Statement for the underlying data needed to understand, evaluate, and build upon the reported research at the time of peer review and publication.

Authors should include an Availability Statement for the software that has a significant impact on the research. Details and templates are in the Availability Statement section of the Data and Software for Authors Guidance: \url{https://www.agu.org/Publish-with-AGU/Publish/Author-Resources/Data-and-Software-for-Authors#availability}

It is important to cite individual datasets in this section and, and they must be included in your bibliography. Please use the type field in your bibtex file to specify the type of data cited. Options include [Dataset], [Software], [ComputationalNotebook], [Collection].
%Example:
%
%@misc{https://doi.org/10.7283/633e-1497,
%  doi = {10.7283/633E-1497},
%  url = {https://www.unavco.org/data/doi/10.7283/633E-1497},
%  author = {de Zeeuw-van Dalfsen, Elske and Sleeman, Reinoud},
%  title = {KNMI Dutch Antilles GPS Network - SAB1-St_Johns_Saba_NA P.S.},
%  publisher = {UNAVCO, Inc.},
%  year = {2019},
%  type = {dataset}
%}

For physical samples, use the IGSN persistent identifier, see the International Geo Sample Numbers section:
\url{https://www.agu.org/Publish-with-AGU/Publish/Author-Resources/Data-and-Software-for-Authors#IGSN}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments
This section is optional. Include any Acknowledgments here.
The acknowledgments should list:\\
All funding sources related to this work from all authors\\
Any real or perceived financial conflicts of interests for any author\\
Other affiliations for any author \newline that may be perceived as having a conflict of interest with respect to the results of this paper.\\
\clearpage
It is also the appropriate place to thank colleagues and other contributors. AGU does not normally allow dedications.\\
%\input{methods}
Hello here is some text in Nick's file
%\input{data}

%% ------------------------------------------------------------------------ %%
%% References and Citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \bibliography{<name of your .bib file>} don't specify the file extension
%
% don't specify bibliographystyle

% In the References section, cite the data/software described in the Availability Statement (this includes primary and processed data used for your research). For details on data/software citation as well as examples, see the Data & Software Citation section of the Data & Software for Authors guidance
% https://www.agu.org/Publish-with-AGU/Publish/Author-Resources/Data-and-Software-for-Authors#citation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliography{}

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al. (2019) have shown...
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown by \cite <e.g.,>[and others]{lewin76}.
%
% apacite uses < > for prenotes and [ ] for postnotes
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \citealp, etc.).
% \nocite is okay to use to add references from your Supporting Information
%

\end{document}

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2022-08-05 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
first draft

@@
 %
+
 %
@@
 \usepackage{soul}
+\usepackage{bm}
 \linenumbers
@@
 
-\journalname{Enter journal name here}
+\journalname{Water Resources Research}
 
@@
 
-\title{=enter title here=}
+\title{The influence of small reservoirs on hydrological drought propagation in space and time}
 
@@
 
-\authors{=list all authors here=}
+\authors{P. Colombo\affil{1,3}, G. G. Ribeiro Neto\affil{2}, P. R. Van Oel\affil{3}, A. C. Costa\affil{4}}
+%, G. Mamede\affil{5}
 
-% \affiliation{1}{First Affiliation}
-% \affiliation{2}{Second Affiliation}
-% \affiliation{3}{Third Affiliation}
-% \affiliation{4}{Fourth Affiliation}
-
-\affiliation{=number=}{=Affiliation Address=}
-%(repeat as many times as is necessary)
+\affiliation{1}{Department of Civil and Environmental Engineering, Politecnico di Milano, Milan, Italy}
+\affiliation{2}{Hydrology and Quantitative Water Management, Wageningen University, Wageningen, The Netherlands}
+\affiliation{3}{Water Resources Management Group, Wageningen University, Wageningen, The Netherlands}
+\affiliation{4}{Institute of Engineering and Sustainable Development, Universidade da Integração Internacional da Lusofonia Afro-Brasileira (Unilab), Redenção, Brazil}
+%\affiliation{5}{Institute for Engineering and Sustainable Development, Univ. of International Afro-Brazilian Integration}
 
@@
 
-\correspondingauthor{=name=}{=email address=}
+\correspondingauthor{Paolo Colombo}{paolo1.colombo@mail.polimi.it}
 
@@
 \begin{keypoints}
-\item enter point 1 here
-\item enter point 2 here
-\item enter point 3 here
+\item We evaluated how a dense network of small and unmonitored reservoirs (DRN) impacts drought events in time and space
+\item Drought cycle analyses and the downstreamness concept were coupled with hydrological modeling-based DNR scenarios to assess the impacts in time and space, respectively
+\item The presence of small reservoirs accelerated the transition towards hydrological droughts by 20\% on average and slowed down drought recovery by 25\%, while shifting upstream water storage capacity distribution in space by 8\%
 \end{keypoints}
@@
 
-%% \begin{abstract} starts the second page
-
 \begin{abstract}
-[ enter your Abstract here ]
+To increase drought preparedness in semi-arid regions many small and medium reservoirs have been built in recent decades.
+Together these reservoirs form a Dense Reservoir Network (DRN) and its presence generates numerous challenges for water management.
+Most of the reservoirs that constitute the network are unmonitored and unregistered, posing questions on their cumulative effects on centralized reservoirs and water distribution at watershed scale.
+Their influence on hydrological drought propagation is thus largely unexplored.
+The objective of this study is then to assess the DRN effects on droughts both in time and space.
+This study utilized a mesoscale semi-distributed hydrological model to reproduce the DRN in a large-scale tropical semiarid watershed (19,530 $km^2$), which presents both a network of large centralized reservoirs and a DRN.
+To investigate the effects in time and space generated by the network’s presence, the differences between multiple network scenarios were analyzed.
+Results show that the presence of the DRN accelerates the transition from meteorological to hydrological drought phases by 20\% on average and slows down the recharge in centralized reservoirs by 25\%, leading to a 12\% increase of periods in hydrological drought conditions in a highly centralized basin and 26\% without centralized reservoirs.
+In space, the DRN shifts upstream the basin’s water storage capacity by 8\%, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward.
+The findings confirm the need to consider small reservoirs when addressing drought management policies at regional scale.
 \end{abstract}
@@
 \section*{Plain Language Summary}
-[ enter your Plain Language Summary here or delete this section]
+Human impacts have been found in a broad spectrum of environmental processes and phenomena.
+Droughts make no exception.
+Droughts, as periods of exceptional lack of water, are one of the disasters that produce the most intense environmental and socio-economic impacts.
+One of the most common strategies for reducing drought-related impacts is the construction of small reservoirs to store water.
+This practice can generate a false sense of water security and increase water demand, which in turn results in more reservoirs being constructed.
+When the presence of these reservoirs becomes diffused and in high numbers, it may enhance the persistence of droughts, making them longer and more intense.
+Since these effects are still unclear, we modeled multiple scenarios representing a North-East Brazilian river basin with and without small reservoirs.
+Through two methods (the Drought Cycle Analysis and the Downstreamness analysis), these scenarios were analyzed to assess the reservoirs’ effects in time and space.
+We found that in the region drought events last on average 12\% longer due to the small reservoirs’ presence.
+This is linked to the accelerated transition from meteorological to hydrological drought (+20\%) and the slowdown of the large reservoirs’ recovery from a drought condition (-25\%).
+We found that the overall storage distribution is shifted upstream by 8\% on average, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward.
+The findings confirm the need to consider small reservoirs when addressing drought management policies.
 
@@
 
-\section{= enter section title =}
-%Text here ===>>>
+\section{Introduction}
+Droughts are defined as periods of exceptional lack of water that negatively impact human activities or environmental demands.
+(Van Loon et al., 2016).
+When drought hits, the most common effect is water shortages, which can lead to food shortages if agriculture is affected.
+Additional drought impacts include drying rivers and lakes, water use restrictions, dying forests, and wildfires.
+Combined these can cause famine, diseases, and migration.
+Human activities can both aggravate and alleviate hydrological droughts, but the former case has been found more dominant (Van Loon et al., 2022).
+Identifying droughts’ drivers, both natural and human, is a major scientific challenge (Walker et al., 2022; Zaniolo et al., 2018).
+Thus, dealing with droughts also requires identifying how humans induce and modify exposure and vulnerability to drought.\\
+Articulating the role of drought preparedness in the context of watershed management areas with long term view can be an important practice to mitigate drought events (Gutiérrez et al., 2014).
+Reservoirs are built in dryland regions both as a drought preparedness measure and as response to the growing water demand (Rabelo et al., 2021).
+However, reservoir construction without a holistic watershed management approach can in turn generate higher water demand, and at the same time reduces the incentive for adaptive actions on other levels.
+Therefore, reservoirs can intensify or even induce drought events, since storing water upstream worsened hydrological drought downstream (van Langen et al., 2021).
+This, in turn, can result in pressure to build more reservoirs, which may further aggravate the problem (Di Baldassarre et al., 2018).
+Both large publicly managed reservoirs and smaller privately owned reservoirs can play a role in this process.\\
+Many places across the world show forms of dense networks of small reservoirs: Australia (Fowler et al., 2015), France (Habets et al., 2014), Ghana (Annor et al., 2009), North-East Brazil (Mamede et al., 2012), South India (Mialhe, 2008), and Syria (Avisse et al., 2017), for example.
+The influence of small reservoirs on water distribution and droughts is still not fully understood.
+They are commonly built without regulation nor monitoring in regions where there is a general lack of observational data.
+This generates uncertainty on their number and capacity, increasing the difficulty of their analysis (Habets et al., 2018).
+Small reservoirs, when analyzed individually, are not expected to cause major impacts to a hydrological system, since their maximum storage capacity is some orders of magnitude lower than large centralized reservoirs.
+However, the accumulated effect of a network of small reservoirs can lead to a 30\% increase in the duration of hydrological droughts (Ribeiro Neto et al., 2022).
+The investigation of the hydrological impact in time and space of a Dense Reservoir Network (DRN) is then highly relevant, both from a community perspective and from a drought and water management one.
+Moreover, diagnosing droughts also needs the evaluation of the drought management measures in place (Walker et al., 2022).\\
+The aim of this research is to evaluate the spatio-temporal influence of a dense network of (small) reservoirs on drought evolution and its impacts on water availability at catchment scale.
+At the same time, assess the network modeling in a complex basin.
+We applied a methodology based on the combination of semi-distributed hydrological modeling with a framework for monitoring the evolution of drought events.
+This methodology was tested for the Banabuiú watershed in the state of Ceara in Brazil.\\
+The impact of reservoirs on drought development has been already researched.
+However, most of these studies focused on large and medium-sized reservoirs (e.g.
+van Langen et al., 2021).
+Although some studies have analyzed the effect of small reservoirs on sediment/water dynamics (e.g.
+Mamede et al, 2018), the hydrological availability (e.g.
+Krol et al.
+2011), evaporation losses, and streamflow impact (e.g.
+Wisser et al., 2010, Malveira et al.2012), there is a scientific gap related to the cumulative effect of a DRN on drought in a complex hydrological system (Walker et al., 2022).
+However, direct consideration of the DRN effects on droughts have started to be considered, such as in Ribeiro Neto et al.
+(2022), where a novel analysis on this topic is proposed and tested in the Riacho do Sangue watershed in North-East Brazil.\\
+Integrating DRN's role in a broader water management perspective which does not only consider large and centralized reservoirs may help answer one of the “unsolved problems in hydrology”, the number 22: “What are the synergies and trade-offs between societal goals related to water management?” (Blöschl et al., 2019).
 
-%%
+\section{Materials and Methods}
+To assess the impacts on drought evolution and magnitude generated by the DRN presence, differences between case study watershed scenarios, including and excluding the DRN, have been analyzed (2.3).
+Modeling the Banabuiu basin has been selected as the way to represent these scenarios (2.2).
+The small reservoirs capacities have been estimated to be able to model the network (2.1).
+\subsection{Study area}
+%Figure 1: Study area framing.
+North-East Brazil, Ceará and Banabuiú catchment on the left.
+On the right, centralized reservoirs location and storage capacity, overlayed to DRN’s density in the Banabuiú basin.
+
+%Table 1:  List of centralized reservoirs, with storage capacity and upstream catchment. The table is ordered by decreasing storage capacity.
+The semi-arid region of Brazil (North-East Brazil) occupies about 11\% of the Brazilian territory (1,542,000 $km^2$) and contains 30\% of its population (Marengo et al., 2020).
+It is a representative example of a region with a high concentration of reservoirs with great variation in size and storage capacity.
+North-East Brazil (NEB) has a highly irregular spatio-temporal precipitation regime, which means the region is frequently affected by intense drought events.
+Sixteen out of the last 25 years registered rainfall below normal in the region.
+In 2010 the most severe drought ever recorded started, which ended in 2018 (Marengo et al.
+2016, 2018).
+The combination of the predominance of soils and geology with low water storage capacity produces a dependency on the superficial storage of water (Marengo, Alves, et al., 2017; Marengo, Torres, \& Alves, 2017).
+Water supply then relies on the reservoirs that regularize discharges.
+Their storage capacity varies from small reservoirs used on private properties to large reservoirs used for urban supply, industrial demands, and large irrigation areas (also called hydrosystems).
+A total of 17,083 reservoirs with surface area greater than 5 ha are located in the NEB.
+This system has a cumulative capacity of 707.36 billion $m^3$, according to the database from Reservoir Monitoring System of the Brazilian National Water Agency (Agência Nacional de Águas e Saneamento Básico) in 2016 (Nascimento and Ribeiro Neto, 2017).
+A representative example of this situation is Ceará, a state in semi-arid Brazil, where it is estimated the presence of 105, reservoirs with more than 20 meters in length in 148,886 $km^2$ (FUNCEME, 2021).
+Ceará presents areas with reservoir concentration higher than 7 reservoirs per $km^2$ (Ribeiro Neto et al., 2022), which greatly exceed other high concentration areas such as India (4.2 reservoirs/$km^2$) and Australia (6.1 reservoirs/$km^2$) (Rabelo et.
+al, 2021).\\
+The study area is a watershed located in the state of Ceará.
+The basin takes the name from its main river, Rio Banabuiú, and covers an area of approximately 19,000 km2.
+The river network, starting from the main tributary Rio Quixeramobim, delineates the division of the basin into sub-basins and determines the distribution of the big centralized reservoirs, placed along the network branches.
+The Banabuiú basin counts 19 monitored reservoirs with storage capacity above $1\cdot10^8 m^3$, with the biggest being Arrojado Lisboa at $1.6\cdot10^9 m^3$.
+These reservoirs, listed in Table 1, are centrally managed and account for $2.79\cdot10^9 m^3$, 93\% of the overall water storage capacity in the basin.
+At the same time, a cumulative $2.1\cdot10^8 m^3$ storage capacity is retained in approximately 10,000 small reservoirs, which constitute the DRN and are visualized together with centralized reservoirs present in the basin in Figure 1.
+Despite their small proportion in relation to total capacity (7.1\%), small reservoirs have an important role in the water supply of small rural communities, whose needs are not met by the large hydrosystems, as the water stored in small reservoirs enables local distribution.
+In the region, most of the small reservoirs aim to meet the water necessities of subsistence farmers only in the short term (6-8 months in the dry season).
+However, their presence can reduce the potential yield of large, centralized reservoirs, which may determine a lower possibility to store and distribute water during droughts (Krol et al., 2011).
+
+\subsection{DRN capacity estimation}
+The capacity of the DRN-component reservoirs is needed to represent the network in the hydrological model.
+Neither capacity nor surface area were available.
+Therefore, a capacity estimation has been obtained starting from the Joint Research Center’s (JRC) Global Surface Water Explorer, which provides a worldwide database of surface water imagery (Pekel et al., 2016).
+The maximum water extent raster, which maps the maximum extent of water bodies in an area, was connected with the locations of the DRN s(surveyed in FUNCEME et al.
+2021), associating each reservoir location to the nearest water body through a nearest neighbor algorithm.
+In this way, 10,355 small reservoirs had their maximum area associated.
+Reservoirs without a corresponding water body in JRC’s representation (approximately 7,000) were left out of the final configuration, shown in Figure 1.
+The causes of them not being represented may lay in their small size, which is difficult to be detected and validated through JRC’s satellite images, or in inaccuracies in the survey operated by FUNCEME et al.
+(2021), where small topographic depressions could have been erroneously interpreted as reservoirs, such as natural depressions in lowlands and depressions close to roads.
+The capacity of each reservoir (V) was then obtained from the area (A) through Molle’s equation (Equation 1), where $\alpha$ and K parameters are equal to average values of 2.7 and 1,500 respectively, as used in literature in North-East Brazil (Mamede et al., 2018, 2012; Molle 1994).
+In this study, a reservoir is considered small when its capacity is lower or equal to 500,000 m3, since this was the highest storage capacity of the unmonitored reservoirs in the basin.
+%\begin{linenomath*}
+%\begin{equation}
+%	V = K \cdot (\frac{A}{ \alfa \cdot K})^\frac{ \alfa }{ \alfa - 1 }
+%\end{equation}
+%\end{linenomath*}
+
+\subsection{Modeling approach}
+\subsubsection{WASA-SED model}
+The model selected to model the Banabuiú river basin is WASA-SED (Water Availability in Semi-Arid environments-SEDiments), which has been developed within the joint Spanish-Brazilian-German research project SESAM (Sediment Export from Semi-Arid Catchments: Measurement and Modelling) and utilized to simulate North-East Brazil’s conditions (Güntner, 2002; Güntner et al., 2004; Mueller et al., 2010).
+The model simulates the runoff and erosion processes at meso-scale, for domains ranging from several hundreds to thousands of square kilometers.
+It uses a hierarchical top-down disaggregation scheme, dividing each sub-basin of the model into landscape units (based on the Soil and Terrain Digital Database (SOTER) concept (Oldeman and van Engelen, 1993)), represented by multiple terrain components (defined by slope-gradient, length, soil and soil-vegetation components).
+The hydrological module is fully described in Güntner (2002) and Güntner et al.
+(2004), implementing for example equations to account for interception losses, evaporation and transpiration (modified Penman-Monteith approach (Shuttleworth and Wallace, 1985)) and for infiltration (Green-Ampt approach (Green and Ampt, 1911)) and other soil and vegetation related processes.
+The model can simulate both large centralized reservoirs and small diffuse networks of reservoirs (Güntner et al., 2004).
+The user manual, the link to the source code and other useful sources can be found at \url{https://github.com/TillF/WASA-SED}.
+Detailed WASA-SED model parameterization for Banabuiú river basin was carried out by Costa et al.
+(2013), and adopted in this work.
+
+\subsubsection{Small reservoirs representation}
+The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size (Güntner et al., 2004).
+The centralized reservoirs listed in Table 1 are set as strategic and individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
+Their water balance is calculated explicitly and individually for each reservoir.
+Due to the uncontrolled and unmonitored nature of small reservoirs composing the DRN, not enough information is available concerning dam building, location, size and water use.
+They are grouped in 5 storage capacity classes and the water balance is computed for a hypothetical reservoir with mean characteristics, representative of each class and sub-basin.
+The water storage volume is then given by the product of the water storage of the representative reservoir by the total number of reservoirs from that class within a sub-basin.
+The generated runoff of the sub-basin is distributed among the reservoir classes through a cascade routing scheme starting from the lowest class to the highest, using a weighting factor computed as a ratio between the runoff contributing area of that reservoir class and the sub-basin area (Mamede et al., 2018).
+A detailed description of the calculation of water fluxes through the classes of reservoirs can be found in Mamede (2008), while equations and other information about the hydrological and reservoir module can be found in Güntner (2002).
+
+\subsubsection{Calibration and validation}
+Calibration was focused on the “scaling factor” parameter, which modifies the soil saturated hydraulic conductivity, which is the most sensitive parameter  (Güntner et al., 2002; Güntner et al., 2021).
+The calibration was carried out automatically following the sub-basins routing path of the model from upstream to downstream, testing a set of 35 values on each sub-basin (ranging from 0.2 to 7).
+For each run, five model performance indexes were computed (R2, NSE, KGE, PBIAS and NRMSE) comparing the modeled volume time series for the sub-basin’s centralized reservoir (or the direct downstream one in case the sub-basin did not present one itself) with the observed one.
+The performance indexes were selected based on recent usage in hydrological modeling (Marahatta et al., 2021; Knoben et al., 2019; Uniyal et al., 2019).
+The parameter that would produce the best performance was selected.
+The model was calibrated with 70\% of the series, running it from 1980 to 2006, it was then validated on the remaining 30\% of the series, from 2007 to 2018.
+Wet, normal and dry years were well represented in both the selected periods (calibration and validation) of the gauges.
+Therefore, the high inter-annual streamflow variability (CV greater than 1) was taken into account for both calibration and validation periods.
+
+\subsubsection{Scenarios generated and used in the analyses}
+%Figure 2: Visualization of the modeled scenarios design: Large Reservoirs (LR), centralized reservoirs only; All Reservoirs (AR), centralized reservoirs and DRN; Naturalized (N), Arrojado Lisboa only; and Small Reservoirs (SR), DRN and Arrojado Lisboa only.
+%Substitute all Figure 4 references to references to this figure (adding tag{fig:scenario} or something similar)
+Four different configurations were modeled, as visualized in Figure 4.
+The All Reservoirs (AR) configuration represents the real condition, with the co-existence of the small and large reservoirs.
+The dense reservoir network was removed to keep only large reservoirs in the Large Reservoirs (LR) scenario.
+These were also removed to obtain two scenarios not influenced by them: Small Reservoirs (SR), representing only small reservoirs and Arrojado Lisboa, and Naturalized (N), representing only Arrojado Lisboa.
+The only reservoir present in all the scenarios is Arrojado Lisboa, the most downstream, used as a reference for the comparisons in all the analyses.
+The differences between AR and LR scenarios have been explored in order to assess the effects of the DRN on droughts’ evolution in time and space.
+N and SR scenarios have been useful to explore the DRN effects without the influence of large reservoirs.
+
+\subsection{Drought analyses}
+To effectively consider the effects that the existence of a DRN produces on drought evolution, two domains have been considered: time, to address impacts on frequency and duration of drought, and space, to include the effects on water distribution.
+This dual aspect has been analyzed through the Drought Cycle Analysis (2.4.1) (Ribeiro Neto et al., 2022) and the Downstreamness Analysis (2.4.2) (van Oel et al., 2018).
+The different scenarios created through the WASA-SED model will be compared with these methods in order to estimate the influence of the DRN on hydrological drought evolution and propagation.
+
+\subsubsection{Drought Cycle Analysis}
+%Figure 3: Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al. (2022). WSI: Water Scarcity Index, PI: Precipitation Index.
+%Sostituire Figure 2 nel testo
+The Drought Cycle Analysis (DCA) is a recent method proposed by Ribeiro Neto et al., 2022, based on a combination of precipitation and hydrological indexes.
+It classifies drought events into four possible stages.
+The indexes values are positioned in quadrants in the coordinate system shown in Figure 3, with a hue and tone variation scheme to represent the intensity of drought event as well as its classification, respectively.\\
+The first quadrant is the non-occurrence of drought: positive values of both Precipitation Index (PI, vertical axis) and Water Storage Index (WSI, horizontal axis).
+The next quadrant indicates meteorological drought, when there is a precipitation deficit (PI < 0) but it has not yet affected water storage (WSI > 0).
+In the third quadrant, hydro-meteorological drought takes place, which is the coexistence of meteorological and hydrological drought.
+Water storage is affected by the persistence of meteorological drought and reservoirs deplete consistently.
+Therefore, both indexes reach negative values.
+The final quadrant is the "Hydrological drought quadrant", which is characterized by the persistence of hydrological drought (WSI < 0) after the end of meteorological drought (PI > 0).\\
+Standardized indexes are used as they allow a better division in the quadrants proposed: negative values of the index mean a scarcity condition, while positive values mean the opposite.
+In order to compute the analysis, the Precipitation Index and the Water Scarcity Index can be chosen from the many available.
+The same procedure as Ribeiro Neto et al.
+(2022) has been followed.
+The Standardized Precipitation Index (SPI) over 12 months (SPI-12) has been utilized as PI (WMO, 2012).
+The Volume Deviation (VD) of Arrojado Lisboa reservoir (the largest and most downstream one) is utilized as a proxy for the water storage of the study area (WSI).
+VD is an index considering the deviation of a reservoir’s volume from the half of its total capacity.
+It can thus vary from -1 to 1, with positive values meaning a volume higher than half of the total capacity and negative values meaning the opposite.
+The indexes are computed at monthly resolution, the results of the Drought Cycle Analysis will then have a monthly resolution themselves.
+Different studies and tools are available to select drought indicators (Zaniolo et al., 2018), more information on the selection operated here is found in Ribeiro Neto et al.
+(2022).
+This method considers a meteorological index for monitoring droughts (the vertical axis of the drought wheel) and information directly related to the impact that this can cause (the horizontal axis of the drought wheel).
+This allows us to identify drought events defined as disasters related to the exceptional lack of water that is prejudicial for human activities or environmental demands.
+Further details and discussion on this method can be found in Ribeiro Neto et al., 2022.
+
+\subsubsection{Downstreamness analysis}
+The downstreamness concept aims to analyze the availability and distribution of water resources in a river basin, first introduced in van Oel (2009) and successively developed and used to analyze basin closure and to diagnose hydrological droughts (van Oel et al., 2011, 2018; van Langen et al., 2021).
+The downstreamness of a location ($D_{x}$), for example a reservoir’s dam outlet, is the ratio of its upstream catchment area ($A_{up}$) to the entire river basin area ($A_{tot}$) (Equation 2.a).
+Higher the index, the more downstream the location x will be.\\
+%Equation 2
+The downstreamness of a basin’s function (like water availability or water demand) is defined as the downstreamness-weighted integral of that function divided by its regular integral (van Oel et al., 2011).
+Higher the index, more downstream the distribution of the variable will be.
+In this study, the functions considered are the basin’s storage capacity (Eq.
+2.b) and the basin’s stored volume (Eq 2.c).
+Each reservoir’ storage capacity ($SC_{x}$) and stored volume ($SV_{x}$) are utilized to find two monthly scaled indicators of the distribution of these variables in the basin ($D_{SC}$ and $D_{SV}$ respectively).
+To extract reservoirs’ $A_{up}$ their positions were overlaid to the flow accumulation raster obtained from the area’s Digital Elevation Model (DEM).
+$A_{tot}$ is taken at the basin outlet.
+An assumption was made in order to be able to handle the DRN keeping the spatial information on its reservoirs: the number of reservoirs was kept the same across all the years considered.
+This approximation means that considerations about the effects of the evolution of the DRN in time can not be made, but at the same time it makes the analysis on the effects more sound because it reduces the growing uncertainty about the number and location of small reservoirs in the past, since a mapping of the small reservoirs across the years is not available.\\
+The information needed to compute $D_{SC}$ was available or made available for both centralized (from FUNCEME database: \url{http://www.funceme.br/hidro-ce-zend/}) and small reservoirs (from the operations explained in 2.2).
+$D_{SV}$ was computed using the modeled reservoirs volume time series.
+For the centralized reservoirs, the model output could be used untouched.
+For the DRN, the WASA-SED model computes the small reservoirs volumes for the whole catchment after grouping them by reservoir size classes (one value for the whole catchment and each reservoir size class).
+These values were returned to an average value dividing by the number of small reservoirs in the respective sub-basin and class.
+The result was assigned to each reservoir of that sub-basin and class, as their $SV_{x}$.
+
+\section{Results}
+\subsection{Model calibration and validation results}
+%Table 2: Mean performance of WASA-SED model after calibration, validation and on the whole time series
+From approximately 945 runs that were performed and evaluated an optimal configuration of parameters was selected.
+Table 2 shows the calibration, validation and whole time series performances averaged over the sub-basins.
+
+\subsection{Drought Cycle Analysis}
+\textbf{Meteorological Drought}
+%Figure 4: SPI-12 visualization.
+a.) 6-months moving average of the SPI-12 computed on the basin’s average precipitation and variability spectrum across the sub-basins.
+Spatial distribution of  SPI-12 in Banabuiu watershed sub-basins averaged for b.) 1992-1993 drought and c.) 2012-2018 drought.
+%Sostituire Figure 5 nel testo
+
+The monthly SPI-12 computed for each sub-basin helped identify the periods of meteorological droughts (Figure 5).
+Results for the Banabuiú basin show the SPI-12 index consistently below 0 after 2012.
+Therefore, the region can be considered in a meteorological drought condition from 2012 until 2018, when the available precipitation time series ends.
+The most dry periods are 1992-1993 and 2012-2018, with mean SPI-12 surpassing -2.
+The gained knowledge on the basin’s meteorological drought period has been used to better interpret hydrological drought.
+
+\textbf{Hydrological Drought}
+%Figure 5: Volume Deviation visualization for all modeled scenarios. Different relationships between storage conditions and the DNR effect are indicated.
+%Sostituire Figure 6 nel testo
+
+In Figure 6 the Volume Deviation (VD) of Arrojado Lisboa in the four scenarios is shown.
+The shaded areas are periods of meteorological drought in the basin.
+It can be observed how the volume decreases in these periods, after which the index tends to increase.
+Comparing AR and LR scenarios, it is clear that the presence of the DRN has multiple influences on Arrojado Lisboa’s volume.
+Before the meteorological drought periods the water stored is higher without the network.
+This reflects afterwards, in a slower transition towards reservoirs’ depletion condition (e.g.
+1992, 1997).
+Thus, the presence of the DRN accelerated the transition towards hydrological droughts.
+During and between drought events (e.g.
+1994-1997, 1999-2001 and 2014), the reservoir recharge is slower by an average of 25\% in the presence of the DRN.
+This DRN-driven lower drought recovery leads the reservoir to be more vulnerable to multiple subsequent meteorological drought events.
+Removing the other large reservoirs (SR and N scenarios), the network’s effects are enhanced, with a higher difference between the two scenarios and an evident improved ability to reservoir recharge in the Naturalized scenario, as between 1996 and 2002.\\
+Depending on the storage condition in which the large reservoirs are at the beginning of the meteorological droughts, the DRN effects are found at different magnitudes (Figure 6).
+When the large reservoir is full or near the maximum capacity (VD $\geq$ 0.75) the difference between AR and LR scenarios is negligible, while with VD lower than 0.75 the difference becomes more visible.
+This suggests that when a meteorological drought happens, the existence of a DRN will enhance the drought effects on the reservoir more if the large reservoir is in depleted condition than it would do if the reservoir would have been full.
+In other words, DRN may enhance hydrological droughts' impacts when the basin is in a dry condition.
+A greater impact from DRN in dry conditions was found also in Rabelo et al.
+(2021).
+Having a better knowledge of this phenomenon may help the implementation of short term drought preparedness measures when the reservoirs are below a threshold (e.g.
+75\% of the maximum capacity).
+
+\textbf{Drought phases}
+%Figure 6: Drought Cycle Analysis results for AR and LR, for three distinct drought events.
+The colors of the monthly-spaced horizontal bars align with the colors in the Drought Wheel.
+The black circle and star in between the horizontal bars indicate time periods that are indicated inside the Drought wheel.
+The distance between the circle and the star is the difference between scenarios, showing the impact of the small reservoirs in the DNR on volume deviation.
+%Sostituire Figure 7 nel testo
+
+%Figure 7: Barplot of the drought phases percentages in the four scenarios. Percentage of months in the four drought phases in AR, LR, SR and N scenarios computed for Arrojado Lisboa.
+%Sostituire Figure 8 nel testo
+
+The percentages of months in the 4 drought phases are shown in Figure 8.
+The scenarios follow the same pattern across the 4 phases.
+Without the small reservoirs the percentage of months without droughts increases.
+The LR scenario presents a lower percentage of months in drought conditions compared to AR: 71\% against 75\%, respectively, which translates to 25 more months in hydrological-related droughts in AR.
+The scenarios with small reservoirs (AR and SR) have a lower percentage in Phases 1 and 2 (non-occurrence and meteorological drought), and a higher percentage in Phases 3 and 4 compared with N and SR scenarios.
+Focusing on AR and LR, the months missing from the meteorological drought state moved towards hydro-meteorological droughts (6.8\% increase of Phase 3 in AR), while hydrological droughts extended over periods with non-occurrence of drought (17\% increase of Phase 4 in AR).
+The result is an overall 12\% increase in hydrological related phases when small reservoirs were present.
+The increase of hydrological droughts due to the presence of the DRN is enhanced by the absence of large reservoirs: an overall 26\% increase, with 19\% and 38\% in Phase 3 and 4 respectively in SR compared with N.
+The existence of the DRN thus extends the hydrological related droughts, with a higher increment in the pure hydrological drought, therefore stretching the duration of the drought events.\\
+The Drought Cycle Analysis was concentrated in the three most intense drought events.
+The 1990–1994, 1997–2000, and 2010–2018 drought events are represented in Figure 7 showing the  drought phases for All Reservoirs and Large Reservoirs scenarios.
+Each month is associated with its color on the wheel, and on the horizontal bars are marked periods in which the influence of the DRN on drought evolution and intensity is particularly visible.
+In the first event, the AR scenario experiences an early transition towards the hydro-meteorological drought phase (May 1993) and the intensity remains higher until the end of the event.
+At the beginning of the second event (June 1997) the AR scenario was still in a hydrological drought condition, while the faster recharge in absence of the network (LR) allowed it to avoid a hydrological drought condition.
+The drought intensity in this first year of the event is considerably higher in the AR scenario, while afterwards they tend to become more similar.
+In the third event no changes of phase happen, just an increase in intensity in the AR scenario.
+The existence of the DRN then led to faster transitions towards hydrological drought phases and also increased their intensity.
+
+\subsection{Downstreamness}
+%Figure 8: Downstreamness of Stored Volume for the four modeled scenarios.
+In b.) AR and SR scenarios’ $D_{SV}$ are modified by multiplying the stored volume in the DRN by the mean ratio between volume and storage capacity (34% increase).
+
+\textbf{Downstrweamness of storage capacity ($\bm{D_{SC}}$)}
+
+The presence of the small reservoirs network in the AR scenario decreased the downstreamness of storage capacity by 7.76\% on average, compared to LR.
+The decrease varies from 8.75\% in 1980 to 7.1\% in 2018, due to constructions of new centralized reservoirs which have a high relative weight, decreasing the small reservoirs relative effect in the downstreamness.
+The most impactful large reservoirs in terms of increased storage capacity were Patu (constructed in 1988, +3.2\%),  Cipoada (1992, +3.7\%) and Fogareiro (1996, + 4.75\%).
+In terms of $D_{SC}$, 1992 was the most influential year, with 4 reservoirs built for a 4\% decrease in downstreamness with respect to the year before.
+The single most impactful reservoir in terms of $D_{SC}$ was Pirabibu (2000, -2.5\%) followed by Fogareiro (1996, -1.7\%).
+The existence of the small reservoirs network thus moves the potential water availability more upstream than what is permitted by the large reservoirs alone.
+The construction of centralized reservoirs always decreased the $D_{SC}$, which may suggest an infrastructural planning towards a more diffused storage capacity in the basin.
+
+\textbf{Downstrweamness of stored volume ($\bm{D_{SV}}$)}
+
+The scenarios’ $D_{SV}$ are plotted in Figure 8.
+The effect on the stored volume is instead not this clear.
+For the scenarios without large reservoirs $D_{SV}$’s behavior is similar to the storage capacity, confirming the network’s ability to store water more upstream: in SR the downstreamness of stored volume is lowered by the existence of small reservoirs (0.35\% on average), with a maximum decrease of 2\% in 1999 compared to N.
+The effect becomes less straightforward reintroducing the large reservoirs.
+Between 1980 and 2000 the presence of the DRN is associated with an average 3.85\% decrease in $D_{SV}$, peaking at 31\% in 1995.
+After 2000 the behavior is inverted: water is stored on average 4.6\% more downstream when the small reservoirs are present.
+Between 1995 and 2000 the volume stored in large reservoirs increased by 10\% with a 4.6\% decrease in $D_{SC}$, and this can be a factor for the inversion.
+The broad scale effect of the small reservoirs in space is thus limited and influenced by large reservoirs, which have a higher ability to move large quantities of water.
+The presence of small reservoirs marginally increases the variability of the stored volume distribution in the basin (Coefficient of Variation equal to 13.51\% in LR versus 13.66\% in AR).
+Without other reservoirs in place, the water would be stored in the centralized reservoirs only, which have less variability in their storage management than small reservoirs.
+Without large reservoirs this effect is enhanced: the Coefficient of Variation difference between SR and N scenarios is 0.42\%.
+The presence of the DRN can then increase stored volume variability across the basin, both before (2009) and during a drought event (2016), but the presence of a large reservoir network limits this effect.
+In all scenarios, $D_{SV}$ is higher than $D_{SC}$ 85\% of the time.
+As explained in Van Oel et al.
+(2011) this indicates that most of the time the water is stored more downstream than upstream.
+The modeled cumulative volume stored in the DRN at each time step is always one order of magnitude lower than the network’s total capacity.
+It is then possible that the model is underestimating the volume effectively retained in the DRN.
+To overcome this possibility and explore a condition in which the DRN is able to reach its storage capacity, new $D_{SV}$ for the AR and SR scenarios were obtained by multiplying the stored volume in the DRN by the mean ratio between volume and storage capacity (34\% increase).
+The result is shown in Figure 8b.
+The variability in the new series is increased, and it is more evident the effect of DRN existence: water is stored more upstream by an average of 9\% in SR modified and 7\% in AR modified, confirming how the existence of large reservoirs dampens the DRN effects.
+In AR, increasing the volume stored in the DRN confirmed that the overall trend of the water distribution in the basin is more dependent on the large reservoirs when these are more present, since the $D_{SV}$ still follows the LR series trend after 2000.
+At the same time the seasonal trend is more prominent in these scenarios, due to the DRN’ seasonal trend itself being more relevant.
+The fictional enhancement in the DRN’s stored volume confirmed the observations made on the previous series, both on the increased variability in water distribution and in the higher relative weight that large reservoirs have in determining the trend and where water is allocated.
+
+\section{Discussion}
+
+\subsection{Discussion of findings}
+Recent studies came to similar conclusions about the influence of reservoirs on droughts (Rabelo et al., 2021; Van Langen et al., 2021; Ribeiro Neto et al., 2022).
+Some results however remain open to discussion.
+The DSV result does not vary significantly without considering the DRN in the AR scenario calculation (RMSE of 0.181 between the two series).
+In the AR scenario the DRN contributes to 0.26\% of the total stored volume, while centralized reservoirs cover the remaining 99.74\%.
+However, the volume collected by the small reservoirs in the AR scenario is not able to match the volume increment collected by the centralized reservoirs while the DRN is missing (LR).
+The modeled cumulative volume effectively retained in the DRN is always one order of magnitude lower than its total storage capacity.
+This consistent reduction in the water yield could be explained by higher dispersion and transmission losses due to a more diffused network.
+The higher infiltration and evaporation rates in small reservoirs can also be an important factor of the difference, which in turn are enhanced by the DRN’s highly variable nature.
+However, this could also be explained by an underestimation operated by the model and can be linked to these uncertainties (Malveira et al., 2012) and also to the ones discussed in Section 5.1.
+In this research the DRN’s retained volume was used to assess the downstreamness of stored volume: to overcome this possible underestimation fictional scenarios with increased volume of the DRN were generated and presented.
+Future application of the methodology should also consider this issue or assess the uncertainty related to the volume.\\
+The downstreamness of stored volume ($D_{SV}$) results in AR and LR scenarios are not completely clear.
+To provide more details, downstreamness could be computed and analyzed also for each sub-catchment in the Banabuiú basin.
+This will result in higher resolution on the whole basin, making it possible to describe local and diverse conditions.
+The different reservoirs’ behavior throughout the basin in relation to the DRN can be analyzed to examine possible differences in the network’s influence between upstream and downstream reservoirs (van Langen et al., 2021).
+This could be also useful to explore a noted pattern: when a meteorological drought happens, the $D_{SV}$ tends towards lower values, thus moving the stored volume upstream.
+
+\subsection{Study limitations}
+In the model’s definition of small reservoirs, smaller reservoirs are assumed to be located upstream of larger ones, which has been based on experience in dryland areas in Brazil and qualitative reasoning form topographic maps (Mamede et al., 2018; Güntner et al., 2004).
+This assumption is an approximation of the real condition, which is a combination of cascade and parallel reservoirs.
+The interconnections between small reservoirs are then not fully considered, and this could lead to an underestimation of their effect on hydrological droughts.
+How much this simplified scheme influences the final results could be estimated by performing a comparison with a more detailed representation of large and small reservoirs as the one performed in Rabelo et al.
+(2021), where it was used to analyze the cumulative impact of small reservoirs on the horizontal hydrological connectivity.
+Hydrological modeling is defined as one of the best methods to estimate variables of interest as flow and volume in absence of direct measurements (Marahatta et al., 2021).
+The selection of a model, however, should be based on its adequacy to the task, as it has been done in this research (Addor and Melsen, 2019).
+WASA-SED hydrological model is feasible and ready to model a dense network of small reservoirs, as it already presents a module specifically for this task.
+Another promising and widely used large-scale model is MGB-IPH, made available from the Institute of Hydraulic Research of the Federal University of Rio Grande do Sul.
+Similarly to WASA-SED, MGB-IPH divides the hydrographic basin into small sub-basins, but its adaptability to the task of modeling a DRN hasn’t been proved yet (Collischonn et al., 2007; De Paiva et al., 2013).
+SWAT eco-hydrological model (Soil and Water Assessment Tool) is another candidate for the detailed representation and simulation of large and small reservoirs, in particular in catchments where water extraction and agriculture are relevant (Arnold et al., 2012; Rabelo et al., 2021).\\
+Water withdrawals time series from Arrojado Lisboa are not enough to fully explain the reservoir’s observed volume variations.
+Other drivers could be involved in periods where withdrawals don’t explain the volume decrease, which is not happening in the modeled simulations.
+Direct extractions from the reservoirs may be one of these drivers, for example extractions performed through water trucks or by mechanical pumps for households or commercial bottled water (de Lira Azevêdo et al., 2017).
+These sources of uncertainty in water management could be quantified or estimated, then added to the known withdrawals.\\
+Another source of uncertainty comes from the small reservoirs locations and size.
+The number of small reservoirs has been kept the same across the whole time series, by utilizing the survey made available by FUNCEME (FUNCEME et al., 2021).
+Small reservoirs without a counterpart in JRC’s Global Surface Water Explorer (procedure explained in 2.1) were removed from the dataset.
+It means that approximately 7,000 reservoirs were not modeled and their influence was not estimated.
+Even though these reservoirs would have fallen in the lowest class, it is still likely that their presence would have enhanced the DRN effects.
+Remote sensing techniques could be used to improve the detection and consideration of reservoirs also throughout the years (Ribeiro Neto et al., 2022; Pereira et al., 2019; Avisse et al., 2017; Ogilvie et al., 2016).
+The model itself introduced uncertainties, as the modeled volume time series can never perfectly reproduce the real world condition, even though the calibration and validation were satisfactory.
+The procedure to obtain the downstreamness of each small reservoir can introduce uncertainties since the downstreamness value is related to the accuracy of the DEM used as the starting point.
+In this study, the DEM resolution is 90 m at the equator (CGIAR STRM), so it permits an accurate representation of the downstreamness.
+
+\subsection{Further analyses and future studies: cooperation, policies and climate change}
+The analyses here conducted can be further applied involving more the Naturalized and Small Reservoirs scenarios.
+The influence of the hydraulic structures and their operations on drought evolution can then be calculated excluding other influences.
+For example, the hydrological drought driven only by climate can be obtained from the volume deviation in the N scenario.
+Then, the hydrological drought driven by small reservoirs can be obtained by subtracting N from SR, the one driven by large reservoirs from LR minus N, and the one driven by the combined effects of large and small reservoirs from AR minus N.
+In order to explore the evolution through space of the drought phases, the Drought Cycle Analysis could be performed by including the spatial dimension together with the already considered time dimension, in a similar way as Figure 5b.
+A visual representation of the basin could be provided, with drought phases and intensities information displayed in the different areas of the basin, for example in each sub-basin.\\
+Possibilities are open to further investigate the influence of DRN and to evaluate possible forms of mitigation of its effects.
+Cooperation between the reservoir operators could be a viable path to reduce the effects of the DRN on the centralized network of reservoirs, and could be investigated in future studies.
+Evidences in benefits from coordinated reservoir operations are highly documented, addressing optimization of economic, social and environmental issues (Castelletti et al., 2008), flood mitigation (Seibert et al., 2014), or multi-objective and complex international scenarios (Giuliani et al., 2021).
+Different possibilities arise when dealing with existing infrastructure: operable reservoirs included in the DRN could be used as buffers to collect water from extreme events and then distribute it in higher necessity periods, while the efficiency of some big centralized reservoirs could be questioned and rediscussed.
+Scenarios of cooperation could be already performed through the WASA-SED model.
+The operable reservoirs included in the DRN could be fully parameterized and considered as centralized reservoirs, a set of alternatives can then be evaluated defining and testing operational rules.
+The objectives of the scenario could be to minimize the hydrological drought phases length and to maximize the water distribution across the basin, in order to find a configuration which best fulfills these goals.
+Policies which improve meaningful public participation may represent a complementary DRN effects mitigation solution to the simulation of the reservoirs operations.
+Participatory management and plans involving local communities and other stakeholders can improve decision making at the river basin level, finding a balance between the need to decentralize water storage and the evidence that centralized reservoirs provide a more stable option in water storage (Lemos and de Oliveira, 2007; de Lira Azevêdo et al., 2017).
+A study on the policies and the existing realities in Ceará and in the Banabuiú basin could be useful to better understand how to address the existence and the impacts of the DRN on a more social level.
+On a last note, climate change is unequivocal and will influence most environmental aspects both in the present, near and distant future (IPCC, 2021), and studying which role the DRN can play in this changing context can be important.
+It has been observed that in the past its existence stretched the duration of hydrological drought periods in centralized reservoirs, and it is presumably that the same will happen in the future if anything changes.
+On which degree this will happen is uncertain, due to various sources of uncertainty (Hattermann et al., 2018; Randall et al., 2007).
+Studies have already been done on projected climate change scenarios in semiarid areas (Zhao et al., 2014; Marengo et al., 2016), but exploring the impacts of the small reservoirs network in these future contexts can be useful to address the drought preparedness of the region and possible mitigation solutions (Gutiérrez et al., 2014).
+
+\section{Conclusions}
+The study area presents a complex condition.
+As other semi-arid areas of the planet, small reservoirs are built without regulation nor monitoring, both as a preparedness measure to drought and to respond to the growing water demand (Krol et al., 2011; Avisse et al., 2017).
+They form a dense network, and its combined effects are mainly unexplored.
+This study wanted to analyze its effect on drought propagation, exploring both the time and space domains, providing novel information to answer the 22nd question from the 23 “unsolved problems in hydrology” (Blöschl et al., 2019): What are the synergies and tradeoffs between societal goals related to water management?
+To address the effect of the existence of a DRN on drought evolution, realization of the watershed including and excluding the small reservoirs have been simulated.
+WASA-SED was the model selected for this task, a semi-distributed hydrological model able to simulate wide semi-arid areas considering both state-controlled centralized reservoirs and networks of diffused reservoirs (Güntner, 2002; Güntner et al., 2004; Mueller et al., 2010).
+To explore the DRN effects in time the Drought Cycle Analysis was performed, which makes it possible to compare the drought phase and intensity between scenarios (Ribeiro Neto et al., 2022).
+To explore the effects in space, the Downstreamness Analysis was performed, assessing the changes in the distribution of the storage capacity and the stored volume throughout the basin (van Oel et al., 2018).
+Interesting aspects on the role of the DRN emerge from the results of the Drought Cycle Analysis and the Downstreamness analysis.
+In time, the presence of the network of small reservoirs accelerates the transition towards hydrological drought phases by 20\% on average and slows down the recharge period in centralized reservoirs by 25\%.
+This translates in a 7\% increase in hydro-meteorological drought periods and a 17\% increase in hydrological drought periods, for a combined 12\% increase in hydrological related droughts.
+These influences were proven stronger when big centralized reservoirs are missing, with a 26\% increase in hydrological related droughts.
+The presence of a large reservoir network acts then as an attenuator of the DRN effects in time.
+DRN may enhance droughts' impacts when the basin is already in a dry condition.
+When large reservoirs are already in a depletion condition, the effect of the DRN is enhanced: having a better knowledge of this phenomenon may help the implementation of short term drought preparedness measures when the reservoirs are below a threshold (e.g.
+75\% of the maximum capacity).
+In space, the DRN existence leads to an average increase of 8\% in upstream distribution of the storage capacity.
+When large reservoirs are missing, the DRN permits to store more volume upstream, reducing the $D_{SV}$.
+The low and highly variable actual stored volume retained in small reservoirs, however, results in a negligible direct influence on the downstreamness of stored volume when centralized reservoirs are present.
+This leads the water distribution in the basin to be more dependent on large reservoirs relative conditions.
+The methodology followed has been proved successful to permit an assessment of the DRN influence on the hydrological drought evolution in a basin in time.
+Interesting information about the DRN’s effect in the storage capacity and stored volume spatial variation, although the latter results become less interpretable when large reservoirs are present.
+There is however the possibility that the DRN’s retained volume is underestimated and although this doesn’t affect the main outcomes of this research it should be tested in future applications.
+The role of the DRN on the evolution of droughts is multifaceted: in time it increases the incidence and the intensity of hydrological drought phases; in space it increases the upstream storage capacity while it may lead downstream large reservoirs to store less water, leading them to potentially higher drought impacts.
+It is then useful to further explore the relationships between the effects in time and space, deepening the knowledge about the influences of the DRN and the causes behind the effects here identified through future studies and analyses.
+The results may help the implementation of drought preparedness and adaptation measures in the Banabuiú basin and in other similar conditions both in North-East Brazil and other semi-arid areas.
 
@@
 \section{Open Research}
+
 AGU requires an Availability Statement for the underlying data needed to understand, evaluate, and build upon the reported research at the time of peer review and publication.

### 2022-10-24 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
new version
started LateX work

@@
 
-\authors{P. Colombo\affil{1,3}, G. G. Ribeiro Neto\affil{2}, P. R. Van Oel\affil{3}, A. C. Costa\affil{4}}
-%, G. Mamede\affil{5}
+\authors{P. Colombo\affil{1,3}, G. G. Ribeiro Neto\affil{2}, P. R. Van Oel\affil{3}, A. C. Costa\affil{4}, G. Mamede\affil{4}}
 
@@
 \affiliation{4}{Institute of Engineering and Sustainable Development, Universidade da Integração Internacional da Lusofonia Afro-Brasileira (Unilab), Redenção, Brazil}
-%\affiliation{5}{Institute for Engineering and Sustainable Development, Univ. of International Afro-Brazilian Integration}
 
@@
 
-\correspondingauthor{Paolo Colombo}{paolo1.colombo@mail.polimi.it}
+\correspondingauthor{Germano G. Ribeiro Neto}{germano.gondimribeironeto@wur.nl}
 
@@
 \item We evaluated how a dense network of small and unmonitored reservoirs (DRN) impacts drought events in time and space
-\item Drought cycle analyses and the downstreamness concept were coupled with hydrological modeling-based DNR scenarios to assess the impacts in time and space, respectively
+\item Drought cycle analyses and the downstreamness concept were coupled with hydrological modeling-based DRN scenarios to assess the impacts in time and space, respectively
 \item The presence of small reservoirs accelerated the transition towards hydrological droughts by 20\% on average and slowed down drought recovery by 25\%, while shifting upstream water storage capacity distribution in space by 8\%
@@
 Together these reservoirs form a Dense Reservoir Network (DRN) and its presence generates numerous challenges for water management.
-Most of the reservoirs that constitute the network are unmonitored and unregistered, posing questions on their cumulative effects on centralized reservoirs and water distribution at watershed scale.
+Most of the reservoirs that constitute the network are unmonitored and unregistered, posing questions on their cumulative effects on strategic reservoirs and water distribution at watershed scale.
 Their influence on hydrological drought propagation is thus largely unexplored.
 The objective of this study is then to assess the DRN effects on droughts both in time and space.
-This study utilized a mesoscale semi-distributed hydrological model to reproduce the DRN in a large-scale tropical semiarid watershed (19,530 $km^2$), which presents both a network of large centralized reservoirs and a DRN.
+This study utilized a mesoscale semi-distributed hydrological model to reproduce the DRN in a large-scale tropical semiarid watershed (19,530 km2), which presents both a network of large strategic reservoirs and a DRN.
 To investigate the effects in time and space generated by the network’s presence, the differences between multiple network scenarios were analyzed.
-Results show that the presence of the DRN accelerates the transition from meteorological to hydrological drought phases by 20\% on average and slows down the recharge in centralized reservoirs by 25\%, leading to a 12\% increase of periods in hydrological drought conditions in a highly centralized basin and 26\% without centralized reservoirs.
+Results show that the presence of the DRN accelerates the transition from meteorological to hydrological drought phases by 20\% on average and slows down the recharge in strategic reservoirs by 25\%, leading to a 12\% increase of periods in hydrological drought conditions in a highly strategic basin and 26\% without strategic reservoirs.
 In space, the DRN shifts upstream the basin’s water storage capacity by 8\%, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward.
@@
 When drought hits, the most common effect is water shortages, which can lead to food shortages if agriculture is affected.
-Additional drought impacts include drying rivers and lakes, water use restrictions, dying forests, and wildfires.
+Additional drought impacts include drying rivers and lakes, water use restrictions, reduced electricity production, dying forests, and wildfires.
 Combined these can cause famine, diseases, and migration.
@@
 Thus, dealing with droughts also requires identifying how humans induce and modify exposure and vulnerability to drought.\\
-Articulating the role of drought preparedness in the context of watershed management areas with long term view can be an important practice to mitigate drought events (Gutiérrez et al., 2014).
+Articulating the role of drought preparedness in the context of watershed management areas with a long term view can be an important practice to mitigate drought events (Gutiérrez et al., 2014).
 Reservoirs are built in dryland regions both as a drought preparedness measure and as response to the growing water demand (Rabelo et al., 2021).
 However, reservoir construction without a holistic watershed management approach can in turn generate higher water demand, and at the same time reduces the incentive for adaptive actions on other levels.
-Therefore, reservoirs can intensify or even induce drought events, since storing water upstream worsened hydrological drought downstream (van Langen et al., 2021).
+Therefore, reservoirs can intensify or even induce drought events, since storing water upstream worsened hydrological drought downstream (Van Langen et al., 2021).
 This, in turn, can result in pressure to build more reservoirs, which may further aggravate the problem (Di Baldassarre et al., 2018).
@@
 This generates uncertainty on their number and capacity, increasing the difficulty of their analysis (Habets et al., 2018).
-Small reservoirs, when analyzed individually, are not expected to cause major impacts to a hydrological system, since their maximum storage capacity is some orders of magnitude lower than large centralized reservoirs.
+Small reservoirs, when analyzed individually, are not expected to cause major impacts to a hydrological system, since their maximum storage capacity is some orders of magnitude lower than strategic reservoirs (medium and large-sized reservoirs located on main rivers at the sub-basin’s outlet).
 However, the accumulated effect of a network of small reservoirs can lead to a 30\% increase in the duration of hydrological droughts (Ribeiro Neto et al., 2022).
@@
 Moreover, diagnosing droughts also needs the evaluation of the drought management measures in place (Walker et al., 2022).\\
-The aim of this research is to evaluate the spatio-temporal influence of a dense network of (small) reservoirs on drought evolution and its impacts on water availability at catchment scale.
-At the same time, assess the network modeling in a complex basin.
-We applied a methodology based on the combination of semi-distributed hydrological modeling with a framework for monitoring the evolution of drought events.
-This methodology was tested for the Banabuiú watershed in the state of Ceara in Brazil.\\
 The impact of reservoirs on drought development has been already researched.
@@
 However, direct consideration of the DRN effects on droughts have started to be considered, such as in Ribeiro Neto et al.
-(2022), where a novel analysis on this topic is proposed and tested in the Riacho do Sangue watershed in North-East Brazil.\\
-Integrating DRN's role in a broader water management perspective which does not only consider large and centralized reservoirs may help answer one of the “unsolved problems in hydrology”, the number 22: “What are the synergies and trade-offs between societal goals related to water management?” (Blöschl et al., 2019).
+(2022), where a novel analysis on this topic is proposed and tested in the Riacho do Sangue watershed in North-East Brazil.Integrating DRN's role in a broader water management perspective which does not only consider strategic centralized reservoirs may help answer one of the “unsolved problems in hydrology”, the number 22: “What are the synergies and trade-offs between societal goals related to water management?” (Blöschl et al., 2019).\\
+The aim of this research is to evaluate the spatio-temporal influence of a dense network of (small) reservoirs on drought evolution and its impacts on water availability at catchment scale.
+At the same time, assess the network modeling in a complex basin.
+We applied a methodology based on the combination of semi-distributed hydrological modeling with a framework for monitoring the evolution of drought events.
+This methodology was tested for the Banabuiú watershed in the state of Ceara in Brazil.
 
@@
 On the right, centralized reservoirs location and storage capacity, overlayed to DRN’s density in the Banabuiú basin.
-
-%Table 1:  List of centralized reservoirs, with storage capacity and upstream catchment. The table is ordered by decreasing storage capacity.
 The semi-arid region of Brazil (North-East Brazil) occupies about 11\% of the Brazilian territory (1,542,000 $km^2$) and contains 30\% of its population (Marengo et al., 2020).
@@
 2016, 2018).
-The combination of the predominance of soils and geology with low water storage capacity produces a dependency on the superficial storage of water (Marengo, Alves, et al., 2017; Marengo, Torres, \& Alves, 2017).
+The combination of the predominance of soils and geology with low water storage capacity produces a dependency on the superficial storage of water (Marengo, Alves, et al., 2017; Marengo, Torres, & Alves, 2017).
 Water supply then relies on the reservoirs that regularize discharges.
@@
 This system has a cumulative capacity of 707.36 billion $m^3$, according to the database from Reservoir Monitoring System of the Brazilian National Water Agency (Agência Nacional de Águas e Saneamento Básico) in 2016 (Nascimento and Ribeiro Neto, 2017).
-A representative example of this situation is Ceará, a state in semi-arid Brazil, where it is estimated the presence of 105, reservoirs with more than 20 meters in length in 148,886 $km^2$ (FUNCEME, 2021).
+A representative example of this situation is Ceará, a 148,886 km² wide state in semi-arid Brazil, where it is estimated the presence of 105,813 reservoirs with more than 20 meters in length (FUNCEME, 2021).
 Ceará presents areas with reservoir concentration higher than 7 reservoirs per $km^2$ (Ribeiro Neto et al., 2022), which greatly exceed other high concentration areas such as India (4.2 reservoirs/$km^2$) and Australia (6.1 reservoirs/$km^2$) (Rabelo et.
 al, 2021).\\
-The study area is a watershed located in the state of Ceará.
-The basin takes the name from its main river, Rio Banabuiú, and covers an area of approximately 19,000 km2.
-The river network, starting from the main tributary Rio Quixeramobim, delineates the division of the basin into sub-basins and determines the distribution of the big centralized reservoirs, placed along the network branches.
-The Banabuiú basin counts 19 monitored reservoirs with storage capacity above $1\cdot10^8 m^3$, with the biggest being Arrojado Lisboa at $1.6\cdot10^9 m^3$.
-These reservoirs, listed in Table 1, are centrally managed and account for $2.79\cdot10^9 m^3$, 93\% of the overall water storage capacity in the basin.
-At the same time, a cumulative $2.1\cdot10^8 m^3$ storage capacity is retained in approximately 10,000 small reservoirs, which constitute the DRN and are visualized together with centralized reservoirs present in the basin in Figure 1.
+The study area is the Banabuiu river watershed located in the state of Ceará which covers an area of approximately 19,000 $km^2$.
+The river network, starting from the main tributary Rio Quixeramobim, delineates the division of the basin into sub-basins and determines the distribution of the strategic reservoirs, placed along the network branches.
+The Banabuiú basin counts 19 monitored reservoirs with storage capacity above 1·$Hm^3$ ($10^6 m^3$) , with the biggest being Arrojado Lisboa at 1600 $Hm^3$.
+These reservoirs, shown in Figure 1, are continuously monitored and managed by the State water agency (Water Resources Company, COGERH) and account for 2790 $Hm^3$, 93\% of the overall water storage capacity in the basin.
+At the same time, a cumulative 210 $Hm^3$ storage capacity is retained in approximately 10,000 small reservoirs, which constitute the DRN and are visualized together with strategic reservoirs present in the basin in Figure 1.
 Despite their small proportion in relation to total capacity (7.1\%), small reservoirs have an important role in the water supply of small rural communities, whose needs are not met by the large hydrosystems, as the water stored in small reservoirs enables local distribution.
 In the region, most of the small reservoirs aim to meet the water necessities of subsistence farmers only in the short term (6-8 months in the dry season).
-However, their presence can reduce the potential yield of large, centralized reservoirs, which may determine a lower possibility to store and distribute water during droughts (Krol et al., 2011).
+The small reservoirs also serve as sediment detention basins, retaining a considerable amount of sediment generated within the catchment and extending the life-time of larger ones located downstream (MAMEDE et al.
+2018).
+However, their presence can reduce the potential yield of strategic reservoirs which may determine a lower possibility to store and distribute water during droughts (Krol et al., 2011).
 
 \subsection{DRN capacity estimation}
+%Table 1. Repartition of the reservoirs composing the Dense Reservoir Network in the Banabuiu basin.
 The capacity of the DRN-component reservoirs is needed to represent the network in the hydrological model.
@@
 Therefore, a capacity estimation has been obtained starting from the Joint Research Center’s (JRC) Global Surface Water Explorer, which provides a worldwide database of surface water imagery (Pekel et al., 2016).
-The maximum water extent raster, which maps the maximum extent of water bodies in an area, was connected with the locations of the DRN s(surveyed in FUNCEME et al.
+The maximum water extent raster, which maps the maximum extent of water bodies in an area, was connected with the locations of the DRN (surveyed in FUNCEME et al.
 2021), associating each reservoir location to the nearest water body through a nearest neighbor algorithm.
 In this way, 10,355 small reservoirs had their maximum area associated.
-Reservoirs without a corresponding water body in JRC’s representation (approximately 7,000) were left out of the final configuration, shown in Figure 1.
+Reservoirs without a corresponding water body in JRC’s representation (approximately 7,000) were left out of the final configuration, represented in Figure 1 and summarized in Table 1.
 The causes of them not being represented may lay in their small size, which is difficult to be detected and validated through JRC’s satellite images, or in inaccuracies in the survey operated by FUNCEME et al.
 (2021), where small topographic depressions could have been erroneously interpreted as reservoirs, such as natural depressions in lowlands and depressions close to roads.
-The capacity of each reservoir (V) was then obtained from the area (A) through Molle’s equation (Equation 1), where $\alpha$ and K parameters are equal to average values of 2.7 and 1,500 respectively, as used in literature in North-East Brazil (Mamede et al., 2018, 2012; Molle 1994).
-In this study, a reservoir is considered small when its capacity is lower or equal to 500,000 m3, since this was the highest storage capacity of the unmonitored reservoirs in the basin.
+The capacity of each reservoir (V) was then obtained from the area (A) through Molle’s equation (Equation 1), where α and K parameters are equal to average values of 2.7 and 1,500 respectively, as used in literature in North-East Brazil (Mamede et al., 2018, 2012; Molle 1994).
+In this study, a reservoir is considered small when its capacity is lower or equal to 500,000 $m^3$ (0.5 $Hm^3$), since this was the highest storage capacity of the unmonitored reservoirs in the basin.
 %\begin{linenomath*}
@@
 (2004), implementing for example equations to account for interception losses, evaporation and transpiration (modified Penman-Monteith approach (Shuttleworth and Wallace, 1985)) and for infiltration (Green-Ampt approach (Green and Ampt, 1911)) and other soil and vegetation related processes.
-The model can simulate both large centralized reservoirs and small diffuse networks of reservoirs (Güntner et al., 2004).
-The user manual, the link to the source code and other useful sources can be found at \url{https://github.com/TillF/WASA-SED}.
+The model can simulate both medium and large  centralized strategic reservoirs and small diffuse networks of reservoirs (Güntner et al., 2004).
+The user manual, the link to the source code and other useful sources can be found at \url{github.com/TillF/WASA-SED}.
 Detailed WASA-SED model parameterization for Banabuiú river basin was carried out by Costa et al.
@@
 The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size (Güntner et al., 2004).
-The centralized reservoirs listed in Table 1 are set as strategic and individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
+The strategic reservoirs listed in Table 1 are individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
 Their water balance is calculated explicitly and individually for each reservoir.
 Due to the uncontrolled and unmonitored nature of small reservoirs composing the DRN, not enough information is available concerning dam building, location, size and water use.
-They are grouped in 5 storage capacity classes and the water balance is computed for a hypothetical reservoir with mean characteristics, representative of each class and sub-basin.
+They are grouped into 5 storage capacity classes and the water balance is computed for a hypothetical reservoir with mean characteristics, representative of each class and sub-basin.
 The water storage volume is then given by the product of the water storage of the representative reservoir by the total number of reservoirs from that class within a sub-basin.
@@
 The calibration was carried out automatically following the sub-basins routing path of the model from upstream to downstream, testing a set of 35 values on each sub-basin (ranging from 0.2 to 7).
-For each run, five model performance indexes were computed (R2, NSE, KGE, PBIAS and NRMSE) comparing the modeled volume time series for the sub-basin’s centralized reservoir (or the direct downstream one in case the sub-basin did not present one itself) with the observed one.
+For each run, five model performance indexes were computed (R2, NSE, KGE, PBIAS and NRMSE) comparing the modeled volume time series for the sub-basin’s strategic reservoir (or the direct downstream one in case the sub-basin did not present one itself) with the observed one.
 The performance indexes were selected based on recent usage in hydrological modeling (Marahatta et al., 2021; Knoben et al., 2019; Uniyal et al., 2019).

### 2022-10-26 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
images, tables, biblio, appendix

@@
 \usepackage{bm}
+
+\usepackage{array}
 \linenumbers
@@
 \begin{document}
-
-%% ------------------------------------------------------------------------ %%
-%  Title
-%
-% (A title should be specific, informative, and brief. Use
-% abbreviations only if they are defined in the abstract. Titles that
-% start with general keywords then specific terms are optimized in
-% searches)
-%
-%% ------------------------------------------------------------------------ %%
-
-% Example: \title{This is a test title}
 
@@
 \section{Introduction}
-Droughts are defined as periods of exceptional lack of water that negatively impact human activities or environmental demands.
-(Van Loon et al., 2016).
+Droughts are defined as periods of exceptional lack of water that negatively impact human activities or environmental demands \cite{VanLoon2016}.
 When drought hits, the most common effect is water shortages, which can lead to food shortages if agriculture is affected.
@@
 Combined these can cause famine, diseases, and migration.
-Human activities can both aggravate and alleviate hydrological droughts, but the former case has been found more dominant (Van Loon et al., 2022).
-Identifying droughts’ drivers, both natural and human, is a major scientific challenge (Walker et al., 2022; Zaniolo et al., 2018).
+Human activities can both aggravate and alleviate hydrological droughts, but the former case has been found more dominant \cite{VanLoon2022}.
+Identifying droughts’ drivers, both natural and human, is a major scientific challenge \cite{Walker2022,Zaniolo2018}.
 Thus, dealing with droughts also requires identifying how humans induce and modify exposure and vulnerability to drought.\\
-Articulating the role of drought preparedness in the context of watershed management areas with a long term view can be an important practice to mitigate drought events (Gutiérrez et al., 2014).
-Reservoirs are built in dryland regions both as a drought preparedness measure and as response to the growing water demand (Rabelo et al., 2021).
+Articulating the role of drought preparedness in the context of watershed management areas with a long term view can be an important practice to mitigate drought events \cite{Gutierrez2014}.
+Reservoirs are built in dryland regions both as a drought preparedness measure and as response to the growing water demand \cite{Rabelo2021}.
 However, reservoir construction without a holistic watershed management approach can in turn generate higher water demand, and at the same time reduces the incentive for adaptive actions on other levels.
-Therefore, reservoirs can intensify or even induce drought events, since storing water upstream worsened hydrological drought downstream (Van Langen et al., 2021).
-This, in turn, can result in pressure to build more reservoirs, which may further aggravate the problem (Di Baldassarre et al., 2018).
+Therefore, reservoirs can intensify or even induce drought events, since storing water upstream worsened hydrological drought downstream \cite{HvanLangen2021}.
+This, in turn, can result in pressure to build more reservoirs, which may further aggravate the problem \cite{DiBaldassarre2018}.
 Both large publicly managed reservoirs and smaller privately owned reservoirs can play a role in this process.\\
-Many places across the world show forms of dense networks of small reservoirs: Australia (Fowler et al., 2015), France (Habets et al., 2014), Ghana (Annor et al., 2009), North-East Brazil (Mamede et al., 2012), South India (Mialhe, 2008), and Syria (Avisse et al., 2017), for example.
+Many places across the world show forms of dense networks of small reservoirs: Australia \cite{Fowler2016}, France \cite{Habets2014}, Ghana \cite{Annor2009}, North-East Brazil \cite{Mamede2012}, South India \cite{Mialhe2008}, and Syria \cite{Avisse2017}, for example.
 The influence of small reservoirs on water distribution and droughts is still not fully understood.
 They are commonly built without regulation nor monitoring in regions where there is a general lack of observational data.
-This generates uncertainty on their number and capacity, increasing the difficulty of their analysis (Habets et al., 2018).
+This generates uncertainty on their number and capacity, increasing the difficulty of their analysis \cite{Habets2018}.
 Small reservoirs, when analyzed individually, are not expected to cause major impacts to a hydrological system, since their maximum storage capacity is some orders of magnitude lower than strategic reservoirs (medium and large-sized reservoirs located on main rivers at the sub-basin’s outlet).
-However, the accumulated effect of a network of small reservoirs can lead to a 30\% increase in the duration of hydrological droughts (Ribeiro Neto et al., 2022).
+However, the accumulated effect of a network of small reservoirs can lead to a 30\% increase in the duration of hydrological droughts \cite{RibeiroNeto2022}.
 The investigation of the hydrological impact in time and space of a Dense Reservoir Network (DRN) is then highly relevant, both from a community perspective and from a drought and water management one.
-Moreover, diagnosing droughts also needs the evaluation of the drought management measures in place (Walker et al., 2022).\\
+Moreover, diagnosing droughts also needs the evaluation of the drought management measures in place \cite{Walker2022}.\\
 The impact of reservoirs on drought development has been already researched.
-However, most of these studies focused on large and medium-sized reservoirs (e.g.
-van Langen et al., 2021).
-Although some studies have analyzed the effect of small reservoirs on sediment/water dynamics (e.g.
-Mamede et al, 2018), the hydrological availability (e.g.
-Krol et al.
-2011), evaporation losses, and streamflow impact (e.g.
-Wisser et al., 2010, Malveira et al.2012), there is a scientific gap related to the cumulative effect of a DRN on drought in a complex hydrological system (Walker et al., 2022).
-However, direct consideration of the DRN effects on droughts have started to be considered, such as in Ribeiro Neto et al.
-(2022), where a novel analysis on this topic is proposed and tested in the Riacho do Sangue watershed in North-East Brazil.Integrating DRN's role in a broader water management perspective which does not only consider strategic centralized reservoirs may help answer one of the “unsolved problems in hydrology”, the number 22: “What are the synergies and trade-offs between societal goals related to water management?” (Blöschl et al., 2019).\\
+However, most of these studies focused on large and medium-sized reservoirs \cite <e.g.,>{HvanLangen2021}.
+Although some studies have analyzed the effect of small reservoirs on sediment/water dynamics  \cite <e.g.,>{Mamede2018}, the hydrological availability \cite <e.g.,>{Krol2011}, evaporation losses, and streamflow impact \cite <e.g.,>{Wisser2010, Malveira2012}, there is a scientific gap related to the cumulative effect of a DRN on drought in a complex hydrological system \cite{Walker2022}.
+However, direct consideration of the DRN effects on droughts have started to be considered, as in \citeA{RibeiroNeto2022}, where a novel analysis on this topic is proposed and tested in the Riacho do Sangue watershed in North-East Brazil.Integrating DRN's role in a broader water management perspective which does not only consider strategic centralized reservoirs may help answer one of the “unsolved problems in hydrology”, the number 22: “What are the synergies and trade-offs between societal goals related to water management?” \cite{Bloschl2019}.\\
 The aim of this research is to evaluate the spatio-temporal influence of a dense network of (small) reservoirs on drought evolution and its impacts on water availability at catchment scale.
@@
 We applied a methodology based on the combination of semi-distributed hydrological modeling with a framework for monitoring the evolution of drought events.
-This methodology was tested for the Banabuiú watershed in the state of Ceara in Brazil.
+This methodology was tested for the Banabuiú watershed in the state of Ceará in Brazil.
 
 \section{Materials and Methods}
-To assess the impacts on drought evolution and magnitude generated by the DRN presence, differences between case study watershed scenarios, including and excluding the DRN, have been analyzed (2.3).
-Modeling the Banabuiu basin has been selected as the way to represent these scenarios (2.2).
-The small reservoirs capacities have been estimated to be able to model the network (2.1).
+To assess the impacts on drought evolution and magnitude generated by the DRN presence, differences between case study watershed scenarios, including and excluding the DRN, have been analyzed (\ref{sec:analyses}).
+Modeling the Banabuiú basin has been selected as the way to represent these scenarios (\ref{sec:model}).
+The small reservoirs capacities have been estimated to be able to model the network (\ref{sec:drncap}).
+
 \subsection{Study area}
-%Figure 1: Study area framing.
+%Figure 1
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_1.png}
+ \caption{Study area framing.
 North-East Brazil, Ceará and Banabuiú catchment on the left.
-On the right, centralized reservoirs location and storage capacity, overlayed to DRN’s density in the Banabuiú basin.
-The semi-arid region of Brazil (North-East Brazil) occupies about 11\% of the Brazilian territory (1,542,000 $km^2$) and contains 30\% of its population (Marengo et al., 2020).
+On the right, centralized reservoirs location and storage capacity, overlayed to DRN’s density in the Banabuiú basin.}
+ \label{fig1}
+\end{figure}
+
+The semi-arid region of Brazil (North-East Brazil) occupies about 11\% of the Brazilian territory (1,006,654 $km^2$) and has a population of 26 million inhabitants \cite{Marengo2020}.
 It is a representative example of a region with a high concentration of reservoirs with great variation in size and storage capacity.
@@
 Sixteen out of the last 25 years registered rainfall below normal in the region.
-In 2010 the most severe drought ever recorded started, which ended in 2018 (Marengo et al.
-2016, 2018).
-The combination of the predominance of soils and geology with low water storage capacity produces a dependency on the superficial storage of water (Marengo, Alves, et al., 2017; Marengo, Torres, & Alves, 2017).
+In 2010 the most severe drought ever recorded started, which ended in 2018 \cite{MarengoOrsini2018,Marengo2017}.
+The combination of the predominance of soils and geology with low water storage capacity produces a dependency on the superficial storage of water \cite{Marengo2017,Rossato2017}.
 Water supply then relies on the reservoirs that regularize discharges.
@@
 A total of 17,083 reservoirs with surface area greater than 5 ha are located in the NEB.
-This system has a cumulative capacity of 707.36 billion $m^3$, according to the database from Reservoir Monitoring System of the Brazilian National Water Agency (Agência Nacional de Águas e Saneamento Básico) in 2016 (Nascimento and Ribeiro Neto, 2017).
-A representative example of this situation is Ceará, a 148,886 km² wide state in semi-arid Brazil, where it is estimated the presence of 105,813 reservoirs with more than 20 meters in length (FUNCEME, 2021).
-Ceará presents areas with reservoir concentration higher than 7 reservoirs per $km^2$ (Ribeiro Neto et al., 2022), which greatly exceed other high concentration areas such as India (4.2 reservoirs/$km^2$) and Australia (6.1 reservoirs/$km^2$) (Rabelo et.
-al, 2021).\\
-The study area is the Banabuiu river watershed located in the state of Ceará which covers an area of approximately 19,000 $km^2$.
+This system has a cumulative capacity of 707.36 billion $m^3$, according to the database from Reservoir Monitoring System of the Brazilian National Water Agency (Agência Nacional de Águas e Saneamento Básico) in 2016 \cite{Nascimento2017}.
+A representative example of this situation is Ceará, a 148,886 km² wide state in semi-arid Brazil, where it is estimated the presence of 105,813 reservoirs with more than 20 meters in length \cite{FUNCEME2021}.
+Ceará presents areas with reservoir concentration higher than 7 reservoirs per $km^2$ \cite{RibeiroNeto2022}, which greatly exceed other high concentration areas such as India (4.2 reservoirs/$km^2$) and Australia (6.1 reservoirs/$km^2$) \cite{Rabelo2021}.\\
+The study area is the Banabuiú river watershed located in the state of Ceará which covers an area of approximately 19,000 $km^2$.
 The river network, starting from the main tributary Rio Quixeramobim, delineates the division of the basin into sub-basins and determines the distribution of the strategic reservoirs, placed along the network branches.
 The Banabuiú basin counts 19 monitored reservoirs with storage capacity above 1·$Hm^3$ ($10^6 m^3$) , with the biggest being Arrojado Lisboa at 1600 $Hm^3$.
-These reservoirs, shown in Figure 1, are continuously monitored and managed by the State water agency (Water Resources Company, COGERH) and account for 2790 $Hm^3$, 93\% of the overall water storage capacity in the basin.
-At the same time, a cumulative 210 $Hm^3$ storage capacity is retained in approximately 10,000 small reservoirs, which constitute the DRN and are visualized together with strategic reservoirs present in the basin in Figure 1.
+These reservoirs, shown in Figure~\ref{fig1}, are continuously monitored and managed by the State water agency (Water Resources Company, COGERH) and account for 2790 $Hm^3$, 93\% of the overall water storage capacity in the basin.
+At the same time, a cumulative 210 $Hm^3$ storage capacity is retained in approximately 10,000 small reservoirs, which constitute the DRN and are visualized together with strategic reservoirs present in the basin in Figure~\ref{fig1}.
 Despite their small proportion in relation to total capacity (7.1\%), small reservoirs have an important role in the water supply of small rural communities, whose needs are not met by the large hydrosystems, as the water stored in small reservoirs enables local distribution.
 In the region, most of the small reservoirs aim to meet the water necessities of subsistence farmers only in the short term (6-8 months in the dry season).
-The small reservoirs also serve as sediment detention basins, retaining a considerable amount of sediment generated within the catchment and extending the life-time of larger ones located downstream (MAMEDE et al.
-2018).
-However, their presence can reduce the potential yield of strategic reservoirs which may determine a lower possibility to store and distribute water during droughts (Krol et al., 2011).
+The small reservoirs also serve as sediment detention basins, retaining a considerable amount of sediment generated within the catchment and extending the life-time of larger ones located downstream \cite{Mamede2018}.
+However, their presence can reduce the potential yield of strategic reservoirs which may determine a lower possibility to store and distribute water during droughts \cite{Krol2011}.
 
-\subsection{DRN capacity estimation}
-%Table 1. Repartition of the reservoirs composing the Dense Reservoir Network in the Banabuiu basin.
+\subsection{DRN capacity estimation}\label{sec:drncap}
+
+%Table 1
+\begin{table}
+ \caption{Repartition of the reservoirs composing the Dense Reservoir Network in the Banabuiú basin.}\label{tab1}
+ \centering
+ \begin{tabular*}{\textwidth}{m{1.5cm} m{2cm} m{2cm} m{2cm} m{2.3cm} m{2.3cm}}
+ \hline
+  Reservoir class & Storage volume - upper limit &  Number of reservoirs & Percentage of reservoirs & Class cumulative storage volume & Class cumulative storage volume\\
+  & [$m^3$] & & [\%] & [$Hm^3$] & [\%]\\
+ \hline
+1	& 5000	 & 6977	&	67.4	 &	7.2  &	3.4\\
+2	& 25000	 & 1787	&	17.3	 &	21	 & 10\\
+3	& 50000	 & 546	&	5.3	 &	20	 & 9.4\\
+4	& 100000	 & 447	&	4.3	 &	32	 & 14.8\\
+5	& 500621	 & 598	&	5.8	 &	130	 & 62.4\\
+ \hline
+Total &	-	& 10355 &	100	 &  210.2 &	100\\
+ \end{tabular*}
+\end{table}
+
 The capacity of the DRN-component reservoirs is needed to represent the network in the hydrological model.
 Neither capacity nor surface area were available.
-Therefore, a capacity estimation has been obtained starting from the Joint Research Center’s (JRC) Global Surface Water Explorer, which provides a worldwide database of surface water imagery (Pekel et al., 2016).
-The maximum water extent raster, which maps the maximum extent of water bodies in an area, was connected with the locations of the DRN (surveyed in FUNCEME et al.
-2021), associating each reservoir location to the nearest water body through a nearest neighbor algorithm.
+Therefore, a capacity estimation has been obtained starting from the Joint Research Center’s (JRC) Global Surface Water Explorer, which provides a worldwide database of surface water imagery \cite{Pekel2016}.
+The maximum water extent raster, which maps the maximum extent of water bodies in an area, was connected with the locations of the DRN (surveyed in \citeA{FUNCEME2021}), associating each reservoir location to the nearest water body through a nearest neighbor algorithm.
 In this way, 10,355 small reservoirs had their maximum area associated.
-Reservoirs without a corresponding water body in JRC’s representation (approximately 7,000) were left out of the final configuration, represented in Figure 1 and summarized in Table 1.
-The causes of them not being represented may lay in their small size, which is difficult to be detected and validated through JRC’s satellite images, or in inaccuracies in the survey operated by FUNCEME et al.
-(2021), where small topographic depressions could have been erroneously interpreted as reservoirs, such as natural depressions in lowlands and depressions close to roads.
-The capacity of each reservoir (V) was then obtained from the area (A) through Molle’s equation (Equation 1), where α and K parameters are equal to average values of 2.7 and 1,500 respectively, as used in literature in North-East Brazil (Mamede et al., 2018, 2012; Molle 1994).
+Reservoirs without a corresponding water body in JRC’s representation (approximately 7,000) were left out of the final configuration, represented in Figure~\ref{fig1} and summarized in Table~\ref{tab1}.
+The causes of them not being represented may lay in their small size, which is difficult to be detected and validated through JRC’s satellite images, or in inaccuracies in the survey operated by \citeA{FUNCEME2021}, where small topographic depressions could have been erroneously interpreted as reservoirs, such as natural depressions in lowlands and depressions close to roads.
+The capacity of each reservoir (V) was then obtained from the area (A) through Molle’s equation (Equation 1), where $\alpha$ and K parameters are equal to average values of 2.7 and 1,500 respectively, as used in literature in North-East Brazil \cite{Mamede2018,Mamede2012,Molle1994}.
 In this study, a reservoir is considered small when its capacity is lower or equal to 500,000 $m^3$ (0.5 $Hm^3$), since this was the highest storage capacity of the unmonitored reservoirs in the basin.
-%\begin{linenomath*}
-%\begin{equation}
-%	V = K \cdot (\frac{A}{ \alfa \cdot K})^\frac{ \alfa }{ \alfa - 1 }
-%\end{equation}
-%\end{linenomath*}
+\begin{linenomath*}
+	\begin{equation}
+	V = K \cdot (\frac{A}{\alpha\cdot K})^\frac{\alpha}{\alpha -1}
+	\end{equation}
+\end{linenomath*}
 
-\subsection{Modeling approach}
+\subsection{Modeling approach}\label{sec:model}
 \subsubsection{WASA-SED model}
-The model selected to model the Banabuiú river basin is WASA-SED (Water Availability in Semi-Arid environments-SEDiments), which has been developed within the joint Spanish-Brazilian-German research project SESAM (Sediment Export from Semi-Arid Catchments: Measurement and Modelling) and utilized to simulate North-East Brazil’s conditions (Güntner, 2002; Güntner et al., 2004; Mueller et al., 2010).
+The model selected to model the Banabuiú river basin is WASA-SED (Water Availability in Semi-Arid environments-SEDiments), which has been developed within the joint Spanish-Brazilian-German research project SESAM (Sediment Export from Semi-Arid Catchments: Measurement and Modelling) and utilized to simulate North-East Brazil’s conditions \cite{Guntner2002,Guntner2004,Mueller2010}.
 The model simulates the runoff and erosion processes at meso-scale, for domains ranging from several hundreds to thousands of square kilometers.
-It uses a hierarchical top-down disaggregation scheme, dividing each sub-basin of the model into landscape units (based on the Soil and Terrain Digital Database (SOTER) concept (Oldeman and van Engelen, 1993)), represented by multiple terrain components (defined by slope-gradient, length, soil and soil-vegetation components).
-The hydrological module is fully described in Güntner (2002) and Güntner et al.
-(2004), implementing for example equations to account for interception losses, evaporation and transpiration (modified Penman-Monteith approach (Shuttleworth and Wallace, 1985)) and for infiltration (Green-Ampt approach (Green and Ampt, 1911)) and other soil and vegetation related processes.
-The model can simulate both medium and large  centralized strategic reservoirs and small diffuse networks of reservoirs (Güntner et al., 2004).
+It uses a hierarchical top-down disaggregation scheme, dividing each sub-basin of the model into landscape units (based on the Soil and Terrain Digital Database (SOTER) concept \cite{Oldeman1993}), represented by multiple terrain components (defined by slope-gradient, length, soil and soil-vegetation components).
+The hydrological module is fully described in \citeA{Guntner2002} and \citeA{Guntner2004}, implementing for example equations to account for interception losses, evaporation and transpiration (modified Penman-Monteith approach \cite{Shuttleworth1985}) and for infiltration (Green-Ampt approach \cite{Green1911}) and other soil and vegetation related processes.
+The model can simulate both medium and large  centralized strategic reservoirs and small diffuse networks of reservoirs \cite{Guntner2004}.
 The user manual, the link to the source code and other useful sources can be found at \url{github.com/TillF/WASA-SED}.
-Detailed WASA-SED model parameterization for Banabuiú river basin was carried out by Costa et al.
-(2013), and adopted in this work.
+Detailed WASA-SED model parameterization for Banabuiú river basin was carried out by \citeA{Costa2013}, and adopted in this work.
 
 \subsubsection{Small reservoirs representation}
-The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size (Güntner et al., 2004).
-The strategic reservoirs listed in Table 1 are individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
+The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size \cite{Guntner2004}.
+The strategic reservoirs listed in Table~\ref{tab1} are individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
 Their water balance is calculated explicitly and individually for each reservoir.
@@
 The water storage volume is then given by the product of the water storage of the representative reservoir by the total number of reservoirs from that class within a sub-basin.
-The generated runoff of the sub-basin is distributed among the reservoir classes through a cascade routing scheme starting from the lowest class to the highest, using a weighting factor computed as a ratio between the runoff contributing area of that reservoir class and the sub-basin area (Mamede et al., 2018).
-A detailed description of the calculation of water fluxes through the classes of reservoirs can be found in Mamede (2008), while equations and other information about the hydrological and reservoir module can be found in Güntner (2002).
+The generated runoff of the sub-basin is distributed among the reservoir classes through a cascade routing scheme starting from the lowest class to the highest, using a weighting factor computed as a ratio between the runoff contributing area of that reservoir class and the sub-basin area \cite{Mamede2018}.
+A detailed description of the calculation of water fluxes through the classes of reservoirs can be found in \citeA{Mamede2008}, while equations and other information about the hydrological and reservoir module can be found in \citeA{Guntner2002}.
 
 \subsubsection{Calibration and validation}
-Calibration was focused on the “scaling factor” parameter, which modifies the soil saturated hydraulic conductivity, which is the most sensitive parameter  (Güntner et al., 2002; Güntner et al., 2021).
+Calibration was focused on the “scaling factor” parameter, which modifies the soil saturated hydraulic conductivity, which is the most sensitive parameter \cite{Guntner2002,WASA-SEDManual2021}.
 The calibration was carried out automatically following the sub-basins routing path of the model from upstream to downstream, testing a set of 35 values on each sub-basin (ranging from 0.2 to 7).
 For each run, five model performance indexes were computed (R2, NSE, KGE, PBIAS and NRMSE) comparing the modeled volume time series for the sub-basin’s strategic reservoir (or the direct downstream one in case the sub-basin did not present one itself) with the observed one.
-The performance indexes were selected based on recent usage in hydrological modeling (Marahatta et al., 2021; Knoben et al., 2019; Uniyal et al., 2019).
+The performance indexes were selected based on recent usage in hydrological modeling \cite{Marahatta2021,Knoben2019,Uniyal2019}.
 The parameter that would produce the best performance was selected.
@@
 
-\subsubsection{Scenarios generated and used in the analyses}
-%Figure 2: Visualization of the modeled scenarios design: Large Reservoirs (LR), centralized reservoirs only; All Reservoirs (AR), centralized reservoirs and DRN; Naturalized (N), Arrojado Lisboa only; and Small Reservoirs (SR), DRN and Arrojado Lisboa only.
-%Substitute all Figure 4 references to references to this figure (adding tag{fig:scenario} or something similar)
-Four different configurations were modeled, as visualized in Figure 4.
+\subsubsection{Scenarios generated and used in the analyses}\label{sec:scenarios}
+
+%Figure 2
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_2.png}
+ \caption{Visualization of the modeled scenarios design: Large Reservoirs (LR), centralized reservoirs only; All Reservoirs (AR), centralized reservoirs and DRN; Naturalized (N), Arrojado Lisboa only; and Small Reservoirs (SR), DRN and Arrojado Lisboa only.}
+ \label{fig2}
+\end{figure}
+
+Four different configurations were modeled, as visualized in Figure~\ref{fig2}.
 The All Reservoirs (AR) configuration represents the real condition, with the co-existence of the small and large reservoirs.
@@
 
-\subsection{Drought analyses}
+\subsection{Drought analyses}\label{sec:analyses}
 To effectively consider the effects that the existence of a DRN produces on drought evolution, two domains have been considered: time, to address impacts on frequency and duration of drought, and space, to include the effects on water distribution.
-This dual aspect has been analyzed through the Drought Cycle Analysis (2.4.1) (Ribeiro Neto et al., 2022) and the Downstreamness Analysis (2.4.2) (van Oel et al., 2018).
+This dual aspect has been analyzed through the Drought Cycle Analysis (\ref{sec:DCA}) \cite{RibeiroNeto2022} and the Downstreamness Analysis (\ref{sec:dwn}) \cite{VanOel2011}.
 The different scenarios created through the WASA-SED model will be compared with these methods in order to estimate the influence of the DRN on hydrological drought evolution and propagation.
 
-\subsubsection{Drought Cycle Analysis}
-%Figure 3: Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al. (2022). WSI: Water Scarcity Index, PI: Precipitation Index.
-%Sostituire Figure 2 nel testo
-The Drought Cycle Analysis (DCA) is a recent method proposed by Ribeiro Neto et al., 2022, based on a combination of precipitation and hydrological indexes.
+\subsubsection{Drought Cycle Analysis}\label{sec:DCA}
+
+%Figure 3
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_3.jpg}
+ \caption{Graphical representation of the Drought Cycle Analysis, from \citeA{RibeiroNeto2022}. WSI: Water Storage Index, PI: Precipitation Index.}
+ \label{fig3}
+\end{figure}
+
+The Drought Cycle Analysis (DCA) is a recent method proposed by \citeA{RibeiroNeto2022}, based on a combination of precipitation and hydrological indexes.
 It classifies drought events into four possible stages.
-The indexes values are positioned in quadrants in the coordinate system shown in Figure 3, with a hue and tone variation scheme to represent the intensity of drought event as well as its classification, respectively.\\
+The indexes values are positioned in quadrants in the coordinate system shown in Figure~\ref{fig3}, with a hue and tone variation scheme to represent the intensity of drought event as well as its classification, respectively.\\
 The first quadrant is the non-occurrence of drought: positive values of both Precipitation Index (PI, vertical axis) and Water Storage Index (WSI, horizontal axis).
@@
 Standardized indexes are used as they allow a better division in the quadrants proposed: negative values of the index mean a scarcity condition, while positive values mean the opposite.
-In order to compute the analysis, the Precipitation Index and the Water Scarcity Index can be chosen from the many available.
-The same procedure as Ribeiro Neto et al.
-(2022) has been followed.
+In order to compute the analysis, the Precipitation Index and the Water Storage Index can be chosen from the many available.
+The same procedure as \citeA{RibeiroNeto2022} has been followed.
 The Standardized Precipitation Index (SPI) over 12 months (SPI-12) has been utilized as PI (WMO, 2012).
@@
 The indexes are computed at monthly resolution, the results of the Drought Cycle Analysis will then have a monthly resolution themselves.
-Different studies and tools are available to select drought indicators (Zaniolo et al., 2018), more information on the selection operated here is found in Ribeiro Neto et al.
-(2022).
 This method considers a meteorological index for monitoring droughts (the vertical axis of the drought wheel) and information directly related to the impact that this can cause (the horizontal axis of the drought wheel).
 This allows us to identify drought events defined as disasters related to the exceptional lack of water that is prejudicial for human activities or environmental demands.
-Further details and discussion on this method can be found in Ribeiro Neto et al., 2022.
+Further details and discussion on this method can be found in \citeA{RibeiroNeto2022}.
 
-\subsubsection{Downstreamness analysis}
-The downstreamness concept aims to analyze the availability and distribution of water resources in a river basin, first introduced in van Oel (2009) and successively developed and used to analyze basin closure and to diagnose hydrological droughts (van Oel et al., 2011, 2018; van Langen et al., 2021).
-The downstreamness of a location ($D_{x}$), for example a reservoir’s dam outlet, is the ratio of its upstream catchment area ($A_{up}$) to the entire river basin area ($A_{tot}$) (Equation 2.a).
+\subsubsection{Downstreamness analysis}\label{sec:dwn}
+The downstreamness concept aims to analyze the availability and distribution of water resources in a river basin, first introduced in \citeA{VanOel2009} and successively developed and used to analyze basin closure and to diagnose hydrological droughts \cite{VanOel2011,VanOel2018,HvanLangen2021}.
+The downstreamness of a location ($D_{x}$), for example a reservoir’s dam outlet, is the ratio of its upstream catchment area ($A_{up}$) to the entire river basin area ($A_{tot}$) (Equation 2).
 Higher the index, the more downstream the location x will be.\\
-%Equation 2
-The downstreamness of a basin’s function (like water availability or water demand) is defined as the downstreamness-weighted integral of that function divided by its regular integral (van Oel et al., 2011).
+
+%Equation 2, 3, 4
+\begin{linenomath*}
+ \begin{equation}\label{Dx}
+ D_{x} = \frac{A_{up,x}}{A_{tot}} \cdot 100 [\%]
+ \end{equation}
+\end{linenomath*}
+\begin{linenomath*}
+ \begin{equation}\label{DSC}
+ D_{SC} = \frac{\sum_{x=1}^{n} SC_{x}D_{x}}{\sum_{x=1}^{n} SC_{x}}
+ \end{equation}
+\end{linenomath*}
+\begin{linenomath*}
+ \begin{equation}\label{DSV}
+ D_{SV} = \frac{\sum_{x=1}^{n} SV_{x}D_{x}}{\sum_{x=1}^{n} SV_{x}}
+ \end{equation}
+\end{linenomath*}
+
+The downstreamness of a basin’s function (like water availability or water demand) is defined as the downstreamness-weighted integral of that function divided by its regular integral \cite{VanOel2011}.
 Higher the index, more downstream the distribution of the variable will be.
-In this study, the functions considered are the basin’s storage capacity (Eq.
-2.b) and the basin’s stored volume (Eq 2.c).
+In this study, the functions considered are the basin’s storage capacity (Equation 3) and the basin’s stored volume (Equation 4).
 Each reservoir’ storage capacity ($SC_{x}$) and stored volume ($SV_{x}$) are utilized to find two monthly scaled indicators of the distribution of these variables in the basin ($D_{SC}$ and $D_{SV}$ respectively).
@@
 This approximation means that considerations about the effects of the evolution of the DRN in time can not be made, but at the same time it makes the analysis on the effects more sound because it reduces the growing uncertainty about the number and location of small reservoirs in the past, since a mapping of the small reservoirs across the years is not available.\\
-The information needed to compute $D_{SC}$ was available or made available for both centralized (from FUNCEME database: \url{http://www.funceme.br/hidro-ce-zend/}) and small reservoirs (from the operations explained in 2.2).
+The information needed to compute $D_{SC}$ was available or made available for both strategic (from FUNCEME database: \url{funceme.br/hidro-ce-zend/}) and small reservoirs (from the operations explained in \ref{sec:drncap}).
 $D_{SV}$ was computed using the modeled reservoirs volume time series.
-For the centralized reservoirs, the model output could be used untouched.
+For the strategic reservoirs, the model output could be used untouched.
 For the DRN, the WASA-SED model computes the small reservoirs volumes for the whole catchment after grouping them by reservoir size classes (one value for the whole catchment and each reservoir size class).
@@
 \subsection{Model calibration and validation results}
-%Table 2: Mean performance of WASA-SED model after calibration, validation and on the whole time series
+
+%Table 2
+\begin{table}
+ \caption{Mean performance of WASA-SED model after calibration, validation and on the whole time series}\label{tab2}
+ \centering
+ \begin{tabular}{c c c c}
+ \hline
+  Index  & Calibration period & Validation period & Whole period\\
+  & (1980 $-$ 2006) & (2007 $-$ 2018) & (1980 $-$ 2018)\\
+ \hline
+	$R^2$ & 0.598  & 0.600  & 0.519  \\
+	NSE   & 0.0497 & 0.360  & 0.271  \\
+	PBIAS & 7.853  & -3.881 & -1.523 \\
+	KGE   & 0.462  & 0.572  & 0.674  \\
+	NRMSE & 0.257  & 0.239  & 0.246  \\
+ \hline
+ \end{tabular}
+\end{table}
+
 From approximately 945 runs that were performed and evaluated an optimal configuration of parameters was selected.
-Table 2 shows the calibration, validation and whole time series performances averaged over the sub-basins.
+Table~\ref{tab2} shows the calibration, validation and whole time series performances averaged over the sub-basins.
 
@@
 \textbf{Meteorological Drought}
-%Figure 4: SPI-12 visualization.
+
+%Figure 4
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_4.png}
+ \caption{SPI-12 visualization.
 a.) 6-months moving average of the SPI-12 computed on the basin’s average precipitation and variability spectrum across the sub-basins.
-Spatial distribution of  SPI-12 in Banabuiu watershed sub-basins averaged for b.) 1992-1993 drought and c.) 2012-2018 drought.
-%Sostituire Figure 5 nel testo
+Spatial distribution of  SPI-12 in Banabuiú watershed sub-basins averaged for b.) 1992-1993 drought and c.) 2012-2018 drought.}
+ \label{fig4}
+\end{figure}
 
-The monthly SPI-12 computed for each sub-basin helped identify the periods of meteorological droughts (Figure 5).
+The monthly SPI-12 computed for each sub-basin helped identify the periods of meteorological droughts (Figure~\ref{fig4}).
 Results for the Banabuiú basin show the SPI-12 index consistently below 0 after 2012.
@@
 \textbf{Hydrological Drought}
-%Figure 5: Volume Deviation visualization for all modeled scenarios. Different relationships between storage conditions and the DNR effect are indicated.
-%Sostituire Figure 6 nel testo
 
-In Figure 6 the Volume Deviation (VD) of Arrojado Lisboa in the four scenarios is shown.
+%Figure 5
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_5.png}
+ \caption{Volume Deviation visualization for all modeled scenarios. Different relationships between storage conditions and the DRN effect are indicated.}
+ \label{fig5}
+\end{figure}
+
+In Figure~\ref{fig5} the Volume Deviation (VD) of Arrojado Lisboa in the four scenarios is shown.
 The shaded areas are periods of meteorological drought in the basin.
@@
 Removing the other large reservoirs (SR and N scenarios), the network’s effects are enhanced, with a higher difference between the two scenarios and an evident improved ability to reservoir recharge in the Naturalized scenario, as between 1996 and 2002.\\
-Depending on the storage condition in which the large reservoirs are at the beginning of the meteorological droughts, the DRN effects are found at different magnitudes (Figure 6).
+Depending on the storage condition in which the large reservoirs are at the beginning of the meteorological droughts, the DRN effects are found at different magnitudes (Figure~\ref{fig5}).
 When the large reservoir is full or near the maximum capacity (VD $\geq$ 0.75) the difference between AR and LR scenarios is negligible, while with VD lower than 0.75 the difference becomes more visible.
@@
 In other words, DRN may enhance hydrological droughts' impacts when the basin is in a dry condition.
-A greater impact from DRN in dry conditions was found also in Rabelo et al.
-(2021).
+A greater impact from DRN in dry conditions was found also in \citeA{Rabelo2021}.
 Having a better knowledge of this phenomenon may help the implementation of short term drought preparedness measures when the reservoirs are below a threshold (e.g.
@@
 \textbf{Drought phases}
-%Figure 6: Drought Cycle Analysis results for AR and LR, for three distinct drought events.
+
+%Figure 6
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_7.png}
+ \caption{Barplot of the drought phases percentages in the four scenarios. Percentage of months in the four drought phases in AR, LR, SR and N scenarios computed for Arrojado Lisboa.}
+ \label{fig6}
+\end{figure}
+
+%Figure 7
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_6.png}
+ \caption{Drought Cycle Analysis results for AR and LR, for three distinct drought events.
 The colors of the monthly-spaced horizontal bars align with the colors in the Drought Wheel.
 The black circle and star in between the horizontal bars indicate time periods that are indicated inside the Drought wheel.
-The distance between the circle and the star is the difference between scenarios, showing the impact of the small reservoirs in the DNR on volume deviation.
-%Sostituire Figure 7 nel testo
+The distance between the circle and the star is the difference between scenarios, showing the impact of the small reservoirs in the DRN on volume deviation.}
+ \label{fig7}
+\end{figure}
 
-%Figure 7: Barplot of the drought phases percentages in the four scenarios. Percentage of months in the four drought phases in AR, LR, SR and N scenarios computed for Arrojado Lisboa.
-%Sostituire Figure 8 nel testo
-
-The percentages of months in the 4 drought phases are shown in Figure 8.
+The percentages of months in the 4 drought phases are shown in Figure~\ref{fig6}.
 The scenarios follow the same pattern across the 4 phases.
@@
 The Drought Cycle Analysis was concentrated in the three most intense drought events.
-The 1990–1994, 1997–2000, and 2010–2018 drought events are represented in Figure 7 showing the  drought phases for All Reservoirs and Large Reservoirs scenarios.
+The 1992–1994, 1997–2002, and 2010–2018 drought events are represented in Figure~\ref{fig7} showing the  drought phases for All Reservoirs and Large Reservoirs scenarios.
 Each month is associated with its color on the wheel, and on the horizontal bars are marked periods in which the influence of the DRN on drought evolution and intensity is particularly visible.
@@
 \subsection{Downstreamness}
-%Figure 8: Downstreamness of Stored Volume for the four modeled scenarios.
-In b.) AR and SR scenarios’ $D_{SV}$ are modified by multiplying the stored volume in the DRN by the mean ratio between volume and storage capacity (34% increase).
+%Figure 8
+\begin{figure}
+ \noindent\includegraphics[width=\textwidth]{images/Figure_8.png}
+ \caption{Downstreamness of Stored Volume for the four modeled scenarios.
+In b.) AR and SR scenarios’ $D_{SV}$ are modified by multiplying the stored volume in the DRN by the mean ratio between volume and storage capacity (34\% increase).}
+ \label{fig8}
+\end{figure}
 
@@
 The presence of the small reservoirs network in the AR scenario decreased the downstreamness of storage capacity by 7.76\% on average, compared to LR.
-The decrease varies from 8.75\% in 1980 to 7.1\% in 2018, due to constructions of new centralized reservoirs which have a high relative weight, decreasing the small reservoirs relative effect in the downstreamness.
-The most impactful large reservoirs in terms of increased storage capacity were Patu (constructed in 1988, +3.2\%),  Cipoada (1992, +3.7\%) and Fogareiro (1996, + 4.75\%).
+The decrease varies from 8.75\% in 1980 to 7.1\% in 2018, due to constructions of new strategic reservoirs which have a high relative weight, decreasing the small reservoirs relative effect in the downstreamness.
+The most impactful large reservoirs in terms of increased storage capacity were Patu (constructed in 1988, capacity 71.8 $Hm^3$, +3.2\% increase),  Cipoada (1992, 86.1 $Hm^3$, +3.7\%) and Fogareiro (1996, 119 $Hm^3$, + 4.75\%).
 In terms of $D_{SC}$, 1992 was the most influential year, with 4 reservoirs built for a 4\% decrease in downstreamness with respect to the year before.
-The single most impactful reservoir in terms of $D_{SC}$ was Pirabibu (2000, -2.5\%) followed by Fogareiro (1996, -1.7\%).
+The single most impactful reservoir in terms of $D_{SC}$ was Pirabibu (2000, 74 $Hm^3$, -2.5\%) followed by Fogareiro (1996, 119 $Hm^3$, -1.7\%).
 The existence of the small reservoirs network thus moves the potential water availability more upstream than what is permitted by the large reservoirs alone.
-The construction of centralized reservoirs always decreased the $D_{SC}$, which may suggest an infrastructural planning towards a more diffused storage capacity in the basin.
+The construction of strategic reservoirs always decreased the $D_{SC}$, which may suggest an infrastructural planning towards a more diffused storage capacity in the basin.
 
@@
 
-The scenarios’ $D_{SV}$ are plotted in Figure 8.
+The scenarios’ $D_{SV}$ are plotted in Figure~\ref{fig8}.
 The effect on the stored volume is instead not this clear.
@@
 The presence of small reservoirs marginally increases the variability of the stored volume distribution in the basin (Coefficient of Variation equal to 13.51\% in LR versus 13.66\% in AR).
-Without other reservoirs in place, the water would be stored in the centralized reservoirs only, which have less variability in their storage management than small reservoirs.
+Without other reservoirs in place, the water would be stored in the strategic reservoirs only, which have less variability in their storage management than small reservoirs.
 Without large reservoirs this effect is enhanced: the Coefficient of Variation difference between SR and N scenarios is 0.42\%.
@@
 In all scenarios, $D_{SV}$ is higher than $D_{SC}$ 85\% of the time.
-As explained in Van Oel et al.
-(2011) this indicates that most of the time the water is stored more downstream than upstream.
+As explained in \citeA{VanOel2011} this indicates that most of the time the water is stored more downstream than upstream.\\
 The modeled cumulative volume stored in the DRN at each time step is always one order of magnitude lower than the network’s total capacity.
@@
 To overcome this possibility and explore a condition in which the DRN is able to reach its storage capacity, new $D_{SV}$ for the AR and SR scenarios were obtained by multiplying the stored volume in the DRN by the mean ratio between volume and storage capacity (34\% increase).
-The result is shown in Figure 8b.
+The result is shown in Figure~\ref{fig8}b.
 The variability in the new series is increased, and it is more evident the effect of DRN existence: water is stored more upstream by an average of 9\% in SR modified and 7\% in AR modified, confirming how the existence of large reservoirs dampens the DRN effects.
@@
 \subsection{Discussion of findings}
-Recent studies came to similar conclusions about the influence of reservoirs on droughts (Rabelo et al., 2021; Van Langen et al., 2021; Ribeiro Neto et al., 2022).
-Some results however remain open to discussion.
-The DSV result does not vary significantly without considering the DRN in the AR scenario calculation (RMSE of 0.181 between the two series).
-In the AR scenario the DRN contributes to 0.26\% of the total stored volume, while centralized reservoirs cover the remaining 99.74\%.
-However, the volume collected by the small reservoirs in the AR scenario is not able to match the volume increment collected by the centralized reservoirs while the DRN is missing (LR).
+Recent studies came to similar results about the influence of DRN on droughts in time \cite{Rabelo2021,HvanLangen2021,RibeiroNeto2022}.
+Some results about the influence in space however remain open to discussion: the $D_{SV}$ does not vary significantly without considering the DRN in the AR scenario calculation (RMSE of 0.181 between the two series).
+In the AR scenario the DRN contributes to 0.26\% of the total stored volume, while strategic reservoirs cover the remaining 99.74\%.
+However, the volume collected by the small reservoirs in the AR scenario is not able to match the volume increment collected by the strategic reservoirs while the DRN is missing (LR).
 The modeled cumulative volume effectively retained in the DRN is always one order of magnitude lower than its total storage capacity.
 This consistent reduction in the water yield could be explained by higher dispersion and transmission losses due to a more diffused network.
-The higher infiltration and evaporation rates in small reservoirs can also be an important factor of the difference, which in turn are enhanced by the DRN’s highly variable nature.
-However, this could also be explained by an underestimation operated by the model and can be linked to these uncertainties (Malveira et al., 2012) and also to the ones discussed in Section 5.1.
+The higher infiltration and evaporation rates in small reservoirs can also be an important factor of the difference, which in turn are enhanced by the DRN’s highly variable nature \cite{Malveira2012}.
+However, this could also be explained by an underestimation operated by the model and can be linked to these uncertainties as well as the ones described in Section~\ref{sec:studylim}.
 In this research the DRN’s retained volume was used to assess the downstreamness of stored volume: to overcome this possible underestimation fictional scenarios with increased volume of the DRN were generated and presented.
@@
 This will result in higher resolution on the whole basin, making it possible to describe local and diverse conditions.
-The different reservoirs’ behavior throughout the basin in relation to the DRN can be analyzed to examine possible differences in the network’s influence between upstream and downstream reservoirs (van Langen et al., 2021).
+The different reservoirs’ behavior throughout the basin in relation to the DRN can be analyzed to examine possible differences in the network’s influence between upstream and downstream reservoirs \cite{HvanLangen2021}.
 This could be also useful to explore a noted pattern: when a meteorological drought happens, the $D_{SV}$ tends towards lower values, thus moving the stored volume upstream.
 
-\subsection{Study limitations}
-In the model’s definition of small reservoirs, smaller reservoirs are assumed to be located upstream of larger ones, which has been based on experience in dryland areas in Brazil and qualitative reasoning form topographic maps (Mamede et al., 2018; Güntner et al., 2004).
+\subsection{Study limitations}\label{sec:studylim}
+In the model’s definition of small reservoirs, smaller reservoirs are assumed to be located upstream of larger ones, which has been based on experience in dryland areas in Brazil and qualitative reasoning form topographic maps \cite{Mamede2018,Guntner2004}.
 This assumption is an approximation of the real condition, which is a combination of cascade and parallel reservoirs.
-The interconnections between small reservoirs are then not fully considered, and this could lead to an underestimation of their effect on hydrological droughts.
-How much this simplified scheme influences the final results could be estimated by performing a comparison with a more detailed representation of large and small reservoirs as the one performed in Rabelo et al.
-(2021), where it was used to analyze the cumulative impact of small reservoirs on the horizontal hydrological connectivity.
-Hydrological modeling is defined as one of the best methods to estimate variables of interest as flow and volume in absence of direct measurements (Marahatta et al., 2021).
-The selection of a model, however, should be based on its adequacy to the task, as it has been done in this research (Addor and Melsen, 2019).
+The connections between small reservoirs are then not fully considered, and this could lead to an underestimation of their effect on hydrological droughts.
+How much this simplified scheme influences the final results could be estimated by performing a comparison with a more detailed representation of large and small reservoirs as the one performed in \citeA{Rabelo2021}, where it was used to analyze the cumulative impact of small reservoirs on the horizontal hydrological connectivity.
+Hydrological modeling is defined as one of the best methods to estimate variables of interest as flow and volume in absence of direct measurements \cite{Marahatta2021}.
+The selection of a model, however, should be based on its adequacy to the task, as it has been done in this research \cite{Addor2019}.
 WASA-SED hydrological model is feasible and ready to model a dense network of small reservoirs, as it already presents a module specifically for this task.
 Another promising and widely used large-scale model is MGB-IPH, made available from the Institute of Hydraulic Research of the Federal University of Rio Grande do Sul.
-Similarly to WASA-SED, MGB-IPH divides the hydrographic basin into small sub-basins, but its adaptability to the task of modeling a DRN hasn’t been proved yet (Collischonn et al., 2007; De Paiva et al., 2013).
-SWAT eco-hydrological model (Soil and Water Assessment Tool) is another candidate for the detailed representation and simulation of large and small reservoirs, in particular in catchments where water extraction and agriculture are relevant (Arnold et al., 2012; Rabelo et al., 2021).\\
+Similarly to WASA-SED, MGB-IPH divides the hydrographic basin into small sub-basins, but its adaptability to the task of modeling a DRN hasn’t been proved yet \cite{Collischonn2007,DePaiva2013}.
+SWAT eco-hydrological model (Soil and Water Assessment Tool) is another candidate for the detailed representation and simulation of large and small reservoirs, in particular in catchments where water extraction and agriculture are relevant (Arnold et al., 2012; \cite{Rabelo2021}).\\
 Water withdrawals time series from Arrojado Lisboa are not enough to fully explain the reservoir’s observed volume variations.
 Other drivers could be involved in periods where withdrawals don’t explain the volume decrease, which is not happening in the modeled simulations.
-Direct extractions from the reservoirs may be one of these drivers, for example extractions performed through water trucks or by mechanical pumps for households or commercial bottled water (de Lira Azevêdo et al., 2017).
+Direct extractions from the reservoirs may be one of these drivers, for example extractions performed through water trucks or by mechanical pumps for households or commercial bottled water \cite{DeLiraAzevedo2017}.
 These sources of uncertainty in water management could be quantified or estimated, then added to the known withdrawals.\\
 Another source of uncertainty comes from the small reservoirs locations and size.
-The number of small reservoirs has been kept the same across the whole time series, by utilizing the survey made available by FUNCEME (FUNCEME et al., 2021).
-Small reservoirs without a counterpart in JRC’s Global Surface Water Explorer (procedure explained in 2.1) were removed from the dataset.
+The number of small reservoirs has been kept the same across the whole time series, by utilizing the survey made available by FUNCEME \cite{FUNCEME2021}.
+Small reservoirs without a counterpart in JRC’s Global Surface Water Explorer (procedure explained in \ref{sec:drncap}) were removed from the dataset.
 It means that approximately 7,000 reservoirs were not modeled and their influence was not estimated.
-Even though these reservoirs would have fallen in the lowest class, it is still likely that their presence would have enhanced the DRN effects.
-Remote sensing techniques could be used to improve the detection and consideration of reservoirs also throughout the years (Ribeiro Neto et al., 2022; Pereira et al., 2019; Avisse et al., 2017; Ogilvie et al., 2016).
+Even though these reservoirs would probably have fallen in the lowest class, it is still likely that their presence would have enhanced the DRN effects.
+Remote sensing techniques could be used to improve the detection and consideration of reservoirs also throughout the years \cite{RibeiroNeto2022,Pereira2019,Avisse2017,Ogilvie2016}.
 The model itself introduced uncertainties, as the modeled volume time series can never perfectly reproduce the real world condition, even though the calibration and validation were satisfactory.
 The procedure to obtain the downstreamness of each small reservoir can introduce uncertainties since the downstreamness value is related to the accuracy of the DEM used as the starting point.
-In this study, the DEM resolution is 90 m at the equator (CGIAR STRM), so it permits an accurate representation of the downstreamness.
+In this study, the DEM resolution is 90 m at the equator \cite{CIAT2021}, so it permits an accurate representation of the downstreamness.
 
@@
 Then, the hydrological drought driven by small reservoirs can be obtained by subtracting N from SR, the one driven by large reservoirs from LR minus N, and the one driven by the combined effects of large and small reservoirs from AR minus N.
-In order to explore the evolution through space of the drought phases, the Drought Cycle Analysis could be performed by including the spatial dimension together with the already considered time dimension, in a similar way as Figure 5b.
+In order to explore the evolution through space of the drought phases, the Drought Cycle Analysis could be performed by including the spatial dimension together with the already considered time dimension, in a similar way as Figure~\ref{fig4}b.
 A visual representation of the basin could be provided, with drought phases and intensities information displayed in the different areas of the basin, for example in each sub-basin.\\
 Possibilities are open to further investigate the influence of DRN and to evaluate possible forms of mitigation of its effects.
-Cooperation between the reservoir operators could be a viable path to reduce the effects of the DRN on the centralized network of reservoirs, and could be investigated in future studies.
-Evidences in benefits from coordinated reservoir operations are highly documented, addressing optimization of economic, social and environmental issues (Castelletti et al., 2008), flood mitigation (Seibert et al., 2014), or multi-objective and complex international scenarios (Giuliani et al., 2021).
-Different possibilities arise when dealing with existing infrastructure: operable reservoirs included in the DRN could be used as buffers to collect water from extreme events and then distribute it in higher necessity periods, while the efficiency of some big centralized reservoirs could be questioned and rediscussed.
+Cooperation between the reservoir operators could be a viable path to reduce the effects of the DRN on the strategic network of reservoirs, and could be investigated in future studies.
+Evidences in benefits from coordinated reservoir operations are highly documented, addressing optimization of economic, social and environmental issues \cite{Castelletti2008}, flood mitigation \cite{Seibert2014}, or multi-objective and complex international scenarios \cite{Giuliani2021}.
+Different possibilities arise when dealing with existing infrastructure: operable reservoirs included in the DRN could be used as buffers to collect water from extreme events and then distribute it in higher necessity periods, while the efficiency of some big strategic reservoirs could be questioned and rediscussed.
 Scenarios of cooperation could be already performed through the WASA-SED model.
-The operable reservoirs included in the DRN could be fully parameterized and considered as centralized reservoirs, a set of alternatives can then be evaluated defining and testing operational rules.
+The operable reservoirs included in the DRN could be fully parameterized and considered as strategic reservoirs, a set of alternatives can then be evaluated defining and testing operational rules.
 The objectives of the scenario could be to minimize the hydrological drought phases length and to maximize the water distribution across the basin, in order to find a configuration which best fulfills these goals.
 Policies which improve meaningful public participation may represent a complementary DRN effects mitigation solution to the simulation of the reservoirs operations.
-Participatory management and plans involving local communities and other stakeholders can improve decision making at the river basin level, finding a balance between the need to decentralize water storage and the evidence that centralized reservoirs provide a more stable option in water storage (Lemos and de Oliveira, 2007; de Lira Azevêdo et al., 2017).
+Participatory management and plans involving local communities and other stakeholders can improve decision making at the river basin level, finding a balance between the need to decentralize water storage and the evidence that strategic reservoirs provide a more stable option in water storage \cite{Lemos2007,DeLiraAzevedo2017}.
 A study on the policies and the existing realities in Ceará and in the Banabuiú basin could be useful to better understand how to address the existence and the impacts of the DRN on a more social level.
-On a last note, climate change is unequivocal and will influence most environmental aspects both in the present, near and distant future (IPCC, 2021), and studying which role the DRN can play in this changing context can be important.
-It has been observed that in the past its existence stretched the duration of hydrological drought periods in centralized reservoirs, and it is presumably that the same will happen in the future if anything changes.
-On which degree this will happen is uncertain, due to various sources of uncertainty (Hattermann et al., 2018; Randall et al., 2007).
-Studies have already been done on projected climate change scenarios in semiarid areas (Zhao et al., 2014; Marengo et al., 2016), but exploring the impacts of the small reservoirs network in these future contexts can be useful to address the drought preparedness of the region and possible mitigation solutions (Gutiérrez et al., 2014).
+On a last note, climate change is unequivocal and will influence most environmental aspects both in the present, near and distant future \cite{IPCC2021}.
+Studying which role the DRN can play in this changing context can be important.
+It has been observed that in the past its existence stretched the duration of hydrological drought periods in strategic reservoirs, and it is presumably that the same will happen in the future if anything changes.
+On which degree this will happen is uncertain, due to various sources of uncertainty \cite{Hattermann2018,Randall2007}.
+Studies have already been done on projected climate change scenarios in semiarid areas \cite{Zhao2014,Marengo2020,Marengo2017}, but exploring the impacts of the small reservoirs network in these future contexts can be useful to address the drought preparedness of the region and possible mitigation solutions \cite{Gutierrez2014}.
 
 \section{Conclusions}
-The study area presents a complex condition.
-As other semi-arid areas of the planet, small reservoirs are built without regulation nor monitoring, both as a preparedness measure to drought and to respond to the growing water demand (Krol et al., 2011; Avisse et al., 2017).
+In many semi-arid areas small reservoirs are built without regulation nor monitoring, both as a preparedness measure to drought and to respond to the growing water demand \cite{Krol2011,Avisse2017}.
 They form a dense network, and its combined effects are mainly unexplored.
-This study wanted to analyze its effect on drought propagation, exploring both the time and space domains, providing novel information to answer the 22nd question from the 23 “unsolved problems in hydrology” (Blöschl et al., 2019): What are the synergies and tradeoffs between societal goals related to water management?
+This study shows its effect on drought propagation, exploring both the time and space domains, providing novel information to answer the 22nd question from the 23 “unsolved problems in hydrology” \cite{Bloschl2019}: What are the synergies and tradeoffs between societal goals related to water management?\\
 To address the effect of the existence of a DRN on drought evolution, realization of the watershed including and excluding the small reservoirs have been simulated.
-WASA-SED was the model selected for this task, a semi-distributed hydrological model able to simulate wide semi-arid areas considering both state-controlled centralized reservoirs and networks of diffused reservoirs (Güntner, 2002; Güntner et al., 2004; Mueller et al., 2010).
-To explore the DRN effects in time the Drought Cycle Analysis was performed, which makes it possible to compare the drought phase and intensity between scenarios (Ribeiro Neto et al., 2022).
-To explore the effects in space, the Downstreamness Analysis was performed, assessing the changes in the distribution of the storage capacity and the stored volume throughout the basin (van Oel et al., 2018).
+WASA-SED was the model selected for this task, a semi-distributed hydrological model able to simulate wide semi-arid areas considering both state-controlled strategic reservoirs and networks of diffused reservoirs \cite{Guntner2002,Guntner2004,Mueller2010}.
+To explore the DRN effects in time the Drought Cycle Analysis was performed, which makes it possible to compare the drought phase and intensity between scenarios \cite{RibeiroNeto2022}.
+To explore the effects in space, the Downstreamness Analysis was performed, assessing the changes in the distribution of the storage capacity and the stored volume throughout the basin \cite{VanOel2018}.
 Interesting aspects on the role of the DRN emerge from the results of the Drought Cycle Analysis and the Downstreamness analysis.
-In time, the presence of the network of small reservoirs accelerates the transition towards hydrological drought phases by 20\% on average and slows down the recharge period in centralized reservoirs by 25\%.
+In time, the presence of the network of small reservoirs accelerates the transition towards hydrological drought phases by 20\% on average and slows down the recharge period in strategic reservoirs by 25\%.
 This translates in a 7\% increase in hydro-meteorological drought periods and a 17\% increase in hydrological drought periods, for a combined 12\% increase in hydrological related droughts.
-These influences were proven stronger when big centralized reservoirs are missing, with a 26\% increase in hydrological related droughts.
+These influences were proven stronger when big strategic reservoirs are missing, with a 26\% increase in hydrological related droughts.
 The presence of a large reservoir network acts then as an attenuator of the DRN effects in time.
@@
 When large reservoirs are missing, the DRN permits to store more volume upstream, reducing the $D_{SV}$.
-The low and highly variable actual stored volume retained in small reservoirs, however, results in a negligible direct influence on the downstreamness of stored volume when centralized reservoirs are present.
+The low and highly variable actual stored volume retained in small reservoirs, however, results in a negligible direct influence on the downstreamness of stored volume when strategic reservoirs are present.
 This leads the water distribution in the basin to be more dependent on large reservoirs relative conditions.
@@
 Interesting information about the DRN’s effect in the storage capacity and stored volume spatial variation, although the latter results become less interpretable when large reservoirs are present.
-There is however the possibility that the DRN’s retained volume is underestimated and although this doesn’t affect the main outcomes of this research it should be tested in future applications.
+There is however the possibility that the DRN’s retained volume is underestimated and although this doesn’t affect the outcomes of this research the underestimation should be tested and eventually corrected in future applications.\\
 The role of the DRN on the evolution of droughts is multifaceted: in time it increases the incidence and the intensity of hydrological drought phases; in space it increases the upstream storage capacity while it may lead downstream large reservoirs to store less water, leading them to potentially higher drought impacts.
@@
 The results may help the implementation of drought preparedness and adaptation measures in the Banabuiú basin and in other similar conditions both in North-East Brazil and other semi-arid areas.
-
-%  Numbered lines in equations:
-%  To add line numbers to lines in equations,
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}
-
-%% Enter Figures and Tables near as possible to where they are first mentioned:
-%
-% DO NOT USE \psfrag or \subfigure commands.
-%
-% Figure captions go below the figure.
-% Table titles go above tables;  other caption information
-%  should be placed in last line of the table, using
-% \multicolumn2l{$^a$ This is a table note.}
-%
-%----------------
-% EXAMPLE FIGURES
-%
-% \begin{figure}
-% \includegraphics{example.png}
-% \caption{caption}
-% \end{figure}
-%
-% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
-% \begin{figure}
-% \noindent\includegraphics[width=\textwidth]{anothersample.png}
-%\caption{caption}
-%\label{pngfiguresample}
-%\end{figure}
-%
-%
-% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
-This is common when trying to add a PDF figure without pdflatex.
-% \begin{figure}
-% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.pdf}
-%\caption{caption}
-%\label{pdffiguresample}
-%\end{figure}
-%
-%
-% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
-%
-
-%
-% ---------------
-% EXAMPLE TABLE
-% Please do NOT include vertical lines in tables
-% if the paper is accepted, Wiley will replace vertical lines with white space
-% the CLS file modifies table padding and vertical lines may not display well
-%
- \begin{table}
- \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
- \centering
- \begin{tabular}{l c}
- \hline
-  Run  & Time (min)  \\
- \hline
-   $l1$  & 260   \\
-   $l2$  & 300   \\
-   $l3$  & 340   \\
-   $h1$  & 270   \\
-   $h2$  & 250   \\
-   $h3$  & 380   \\
-   $r1$  & 370   \\
-   $r2$  & 390   \\
- \hline
- \multicolumn{2}{l}{$^{a}$Footnote text here.}
- \end{tabular}
- \end{table}
-
-%% SIDEWAYS FIGURE and TABLE
-% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
-%
-% \begin{sidewaysfigure}
-% \includegraphics[width=20pc]{figsamp}
-% \caption{caption here}
-% \label{newfig}
-% \end{sidewaysfigure}
-%
-%  \begin{sidewaystable}
-%  \caption{Caption here}
-% \label{tab:signif_gap_clos}
-%  \begin{tabular}{ccc}
-% one&two&three\\
-% four&five&six
-%  \end{tabular}
-%  \end{sidewaystable}
-
-%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
-%\begin{linenomath*}
-%\begin{equation}
-%y|{f} \sim g(m, \sigma),
-%\end{equation}
-%\end{linenomath*}
 
@@
 
+\newpage
+\appendix
+\section{Additional table}
+
+%Table A
+\begin{table}
+ \caption{Appendix: List of centralized reservoirs, with storage capacity and upstream catchment.
+The table is ordered by decreasing storage capacity.
+Information retrieved from FUNCEME database \url{funceme.br/hidro-ce-zend/}.}\label{tabA}
+ \centering
+ \begin{tabular}{c c c c}
+ \hline
+  Name  & Year constructed & Storage capacity & Drainage area\\
+  & & [$Hm^3$] & [$km^2$]\\
+ \hline
+Arrojado Lisboa 	& 1966 &	 14,221	& 1600\\
+Pedras Brancas	& 1978	& 1,937 &	434\\
+Cedro			& 1906	& 206 &	126\\
+Fogareiro 		& 1996	 & 5,111 & 	119\\
+Cipoada			& 1992	& 351 &	86.1\\
+Pirabibu			& 2000	& 503	& 74\\
+Patu	 			& 1988	& 995	& 71.8\\
+Poço do Barro	& 1956	 & 374 & 52\\
+Serafim Dias 	& 1995 &	1,630 &	43\\
+Umari			& 2011	& 975	& 30\\
+Sao Jose II		& 1992	& 185	& 29.1\\
+Vieirão			& 1988	& 400 &	21\\
+Trapiá II 		& 1992 & 	129 &	18.2\\
+Curral Velho	 	& 2007 & 	79 & 	12.2\\
+Monsenhor Tabosa & 1998 & 77 &	12.1\\
+Quixeramobim 	& 1966 & 7,021 &	7.88\\
+Sao José I		& 1988 & 	188 & 	767\\
+Capitão Mor		& 1988	& 110 &	6\\
+Jatobá 			& 1997 &	40	& 1.07\\
+ \hline
+ \end{tabular}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Optional Glossary, Notation or Acronym section goes here:
-%
-%%%%%%%%%%%%%%
-% Glossary is only allowed in Reviews of Geophysics
-%  \begin{glossary}
-%  \term{Term}
-%   Term Definition here
-%  \term{Term}
-%   Term Definition here
-%  \term{Term}
-%   Term Definition here
-%  \end{glossary}
 
-%
 %%%%%%%%%%%%%%
 % Acronyms
-%   \begin{acronyms}
-%   \acro{Acronym}
-%   Definition here
-%   \acro{EMOS}
-%   Ensemble model output statistics
-%   \acro{ECMWF}
-%   Centre for Medium-Range Weather Forecasts
-%   \end{acronyms}
+   \begin{acronyms}
+   \acro{AR, LR, SR, N}
+   All Reservoirs, Large Reservoirs, Small Reservoirs and Naturalized scenarios generated with WASA-SED model. Explanation in Section~\ref{sec:scenarios}.
+   \acro{DEM}
+   Digital Elevation Model. 3D representation of elevation data to represent terrain or overlaying objects.
+   \acro{DRN}
+   Dense Reservoir Network. A great number of small reservoirs creating a network.
+   \acro{$\bm{D_{SC}}$, $\bm{D_{SV}}$}
+   Downstreamness of Storage Capacity and Stored Volume, respectively. Explanation in Section~\ref{sec:dwn}.
+   \end{acronyms}
 
-%
-%%%%%%%%%%%%%%
-% Notation
-%   \begin{notation}
-%   \notation{$a+b$} Notation Definition here
-%   \notation{$e=mc^2$}
-%   Equation in German-born physicist Albert Einstein's theory of special
-%  relativity that showed that the increased relativistic mass ($m$) of a
-%  body comes from the energy of motion of the body—that is, its kinetic
-%  energy ($E$)—divided by the speed of light squared ($c^2$).
-%   \end{notation}
+\section{Open research}
 
-\section{Open Research}
+\textbf{Data availability statement}\\
+The DEM used for the downstreamness analysis was downloaded through CGIAR’ SRTM database \cite{CIAT2021}.
+The location of the small unmonitored reservoirs identified by FUNCEME, the meteorological observations (precipitation, temperature, humidity and radiation) and the hydrological observations (strategic reservoirs volumes and releases) are available at \url{github.com/paolchol/DRN-analysis}.\\
 
-AGU requires an Availability Statement for the underlying data needed to understand, evaluate, and build upon the reported research at the time of peer review and publication.
+\textbf{Software availability statement}\\
+The WASA-SED source code is available at \url{github.com/TillF/WASA-SED}, the calibrated model used here is available at \url{github.com/paolchol/DRN-analysis} in the WASA-SED folder.
+The user guide is available at \url{tillf.github.io/WASA-SED/}.
+The R and Matlab code used to perform all the operations and figures is provided at \url{github.com/paolchol/DRN-analysis}.
 
-Authors should include an Availability Statement for the software that has a significant impact on the research.
+%AGU requires an Availability Statement for the underlying data needed to understand, evaluate, and build upon the reported research at the time of peer review and publication.
+
+%Authors should include an Availability Statement for the software that has a significant impact on the research.
 Details and templates are in the Availability Statement section of the Data and Software for Authors Guidance: \url{https://www.agu.org/Publish-with-AGU/Publish/Author-Resources/Data-and-Software-for-Authors#availability}
 
-It is important to cite individual datasets in this section and, and they must be included in your bibliography.
+%It is important to cite individual datasets in this section and, and they must be included in your bibliography.
 Please use the type field in your bibtex file to specify the type of data cited.
@@
 
-For physical samples, use the IGSN persistent identifier, see the International Geo Sample Numbers section:
-\url{https://www.agu.org/Publish-with-AGU/Publish/Author-Resources/Data-and-Software-for-Authors#IGSN}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \acknowledgments
-This section is optional. Include any Acknowledgments here.
-The acknowledgments should list:\\
-All funding sources related to this work from all authors\\
-Any real or perceived financial conflicts of interests for any author\\
-Other affiliations for any author \newline that may be perceived as having a conflict of interest with respect to the results of this paper.\\
+This work is part of the Joint SDG Research Initiative with project number W07.30318.016, which is (partly) financed by the Dutch Research Council (NWO) and the Interdisciplinary Research and Education Fund (INREF) of Wageningen University, the Netherlands.
 \clearpage
-It is also the appropriate place to thank colleagues and other contributors. AGU does not normally allow dedications.\\
-%\input{methods}
-Hello here is some text in Nick's file
-%\input{data}
 
@@
 
-%\bibliography{}
+\bibliography{bibliography}
 
@@
 \end{document}
-
-More Information and Advice:
-
-%% ------------------------------------------------------------------------ %%
-%
-%  SECTION HEADS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Capitalize the first letter of each word (except for
-% prepositions, conjunctions, and articles that are
-% three or fewer letters).
-
-% AGU follows standard outline style; therefore, there cannot be a section 1 without
-% a section 2, or a section 2.3.1 without a section 2.3.2.
-% Please make sure your section numbers are balanced.
-% ---------------
-% Level 1 head
-%
-% Use the \section{} command to identify level 1 heads;
-% type the appropriate head wording between the curly
-% brackets, as shown below.
-%
-%An example:
-%\section{Level 1 Head: Introduction}
-%
-% ---------------
-% Level 2 head
-%
-% Use the \subsection{} command to identify level 2 heads.
-%An example:
-%\subsection{Level 2 Head}
-%
-% ---------------
-% Level 3 head
-%
-% Use the \subsubsection{} command to identify level 3 heads
-%An example:
-%\subsubsection{Level 3 Head}
-%
-%---------------
-% Level 4 head
-%
-% Use the \subsubsubsection{} command to identify level 3 heads
-% An example:
-%\subsubsubsection{Level 4 Head} An example.
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  IN-TEXT LISTS
-%
-%% ------------------------------------------------------------------------ %%
-%
-% Do not use bulleted lists; enumerated lists are okay.
-% \begin{enumerate}
-% \item
-% \item
-% \item
-% \end{enumerate}
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATIONS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Single-line equations are centered.
-% Equation arrays will appear left-aligned.
-
-Math coded inside display math mode \[ ...\]
- will not be numbered, e.g.,:
- \[ x^2=y^2 + z^2\]
-
- Math coded inside \begin{equation} and \end{equation} will
- be automatically numbered, e.g.,:
- \begin{equation}
- x^2=y^2 + z^2
- \end{equation}
-
-% To create multiline equations, use the
-% \begin{eqnarray} and \end{eqnarray} environment
-% as demonstrated below.
-\begin{eqnarray}
-  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
-        && + (y - y_{0}) \sin \Theta  \nonumber \\
-  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
-        && + (y - y_{0}) \cos \Theta.
-\end{eqnarray}
-
-%If you don't want an equation number, use the star form:
-%\begin{eqnarray*}...\end{eqnarray*}
-
-% Break each line at a sign of operation
-% (+, -, etc.) if possible, with the sign of operation
-% on the new line.
-
-% Indent second and subsequent lines to align with
-% the first character following the equal sign on the
-% first line.
-
-% Use an \hspace{} command to insert horizontal space
-% into your equation if necessary. Place an appropriate
-% unit of measure between the curly braces, e.g.
-% \hspace{1in}; you may have to experiment to achieve
-% the correct amount of space.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATION NUMBERING: COUNTER
-%
-%% ------------------------------------------------------------------------ %%
-
-% You may change equation numbering by resetting
-% the equation counter or by explicitly numbering
-% an equation.
-
-% To explicitly number an equation, type \eqnum{}
-% (with the desired number between the brackets)
-% after the \begin{equation} or \begin{eqnarray}
-% command.  The \eqnum{} command will affect only
-% the equation it appears with; LaTeX will number
-% any equations appearing later in the manuscript
-% according to the equation counter.
-%
-
-% If you have a multiline equation that needs only
-% one equation number, use a \nonumber command in
-% front of the double backslashes (\\) as shown in
-% the multiline equation above.
-
-% If you are using line numbers, remember to surround
-% equations with \begin{linenomath*}...\end{linenomath*}
-
-%  To add line numbers to lines in equations:
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}

### 2022-10-26 R/main.R
update structure

@@ -1,4 +1,4 @@
-#Main to launch the core operations
+#Mock-up of a main to launch the core operations
 #
 #The launched operations are all stored in the "Core_code" folder.
 #Each code has the name of the operation it performs.

### 2022-10-26 R/Supporting_code/download_DEM.R
files from thesis folder

@@ -1,0 +1,8 @@
+#Script to download the DEM of the Banabuiu basin
+#from NASA database
+
+path <- "Data/1112536144-download.txt"
+links<-read.table(path)
+for(i in seq_len(nrow(links))){
+  browseURL(links[i,1])
+}

### 2022-10-28 LateX/Feb-3-22-latex-templates/paper_Colombo.tex
submission paper ended

@@
 \item We evaluated how a dense network of small and unmonitored reservoirs (DRN) impacts drought events in time and space
-\item Drought cycle analyses and the downstreamness concept were coupled with hydrological modeling-based DRN scenarios to assess the impacts in time and space, respectively
-\item The presence of small reservoirs accelerated the transition towards hydrological droughts by 20\% on average and slowed down drought recovery by 25\%, while shifting upstream water storage capacity distribution in space by 8\%
+\item Drought cycle and downstreamness analyses were coupled with hydrological modeling based DRN scenarios to assess impacts in time and space
+\item The DRN accelerated the transition towards hydrological droughts and slowed down drought recovery, while storage capacity was moved upstream
 \end{keypoints}
@@
 One of the most common strategies for reducing drought-related impacts is the construction of small reservoirs to store water.
-This practice can generate a false sense of water security and increase water demand, which in turn results in more reservoirs being constructed.
-When the presence of these reservoirs becomes diffused and in high numbers, it may enhance the persistence of droughts, making them longer and more intense.
+When these reservoirs are diffused and in high numbers, their presence may increase droughts intensity and length.
 Since these effects are still unclear, we modeled multiple scenarios representing a North-East Brazilian river basin with and without small reservoirs.
-Through two methods (the Drought Cycle Analysis and the Downstreamness analysis), these scenarios were analyzed to assess the reservoirs’ effects in time and space.
-We found that in the region drought events last on average 12\% longer due to the small reservoirs’ presence.
+These scenarios were analyzed through two methods to assess the reservoirs’ effects in time and space.
+We found that drought events last on average 12\% longer due to the small reservoirs’ presence in the region.
 This is linked to the accelerated transition from meteorological to hydrological drought (+20\%) and the slowdown of the large reservoirs’ recovery from a drought condition (-25\%).
-We found that the overall storage distribution is shifted upstream by 8\% on average, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward.
+The overall storage distribution is shifted upstream by 8\% on average, but when both large and small reservoirs are present the stored volume distribution behavior is not straightforward.
 The findings confirm the need to consider small reservoirs when addressing drought management policies.
@@
 The modeling approach to the reservoirs needs to classify them into strategic and small reservoirs, according to location and size \cite{Guntner2004}.
-The strategic reservoirs listed in Table~\ref{tab1} are individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
+The strategic reservoirs (listed in Supporting Information) are individually parameterized in WASA-SED, also providing their daily regulated discharge time series.
 Their water balance is calculated explicitly and individually for each reservoir.
@@
 
-\newpage
-\appendix
-\section{Additional table}
-
-%Table A
-\begin{table}
- \caption{Appendix: List of centralized reservoirs, with storage capacity and upstream catchment.
-The table is ordered by decreasing storage capacity.
-Information retrieved from FUNCEME database \url{funceme.br/hidro-ce-zend/}.}\label{tabA}
- \centering
- \begin{tabular}{c c c c}
- \hline
-  Name  & Year constructed & Storage capacity & Drainage area\\
-  & & [$Hm^3$] & [$km^2$]\\
- \hline
-Arrojado Lisboa 	& 1966 &	 14,221	& 1600\\
-Pedras Brancas	& 1978	& 1,937 &	434\\
-Cedro			& 1906	& 206 &	126\\
-Fogareiro 		& 1996	 & 5,111 & 	119\\
-Cipoada			& 1992	& 351 &	86.1\\
-Pirabibu			& 2000	& 503	& 74\\
-Patu	 			& 1988	& 995	& 71.8\\
-Poço do Barro	& 1956	 & 374 & 52\\
-Serafim Dias 	& 1995 &	1,630 &	43\\
-Umari			& 2011	& 975	& 30\\
-Sao Jose II		& 1992	& 185	& 29.1\\
-Vieirão			& 1988	& 400 &	21\\
-Trapiá II 		& 1992 & 	129 &	18.2\\
-Curral Velho	 	& 2007 & 	79 & 	12.2\\
-Monsenhor Tabosa & 1998 & 77 &	12.1\\
-Quixeramobim 	& 1966 & 7,021 &	7.88\\
-Sao José I		& 1988 & 	188 & 	767\\
-Capitão Mor		& 1988	& 110 &	6\\
-Jatobá 			& 1997 &	40	& 1.07\\
- \hline
- \end{tabular}
-\end{table}
+%\newpage
 

### 2023-08-26 R/Figures_code/paper_figures.Rmd
updates after reviews jhydr

@@
 ```{r, setwd, include = FALSE}
-knitr::opts_knit$set(root.dir = "C:/Directory_thesis_codes")
+knitr::opts_knit$set(root.dir = "C:/DRN-analysis")
 ```
@@
 ```{r, setup, include = FALSE}
-setwd("C:/Directory_thesis_codes")
+setwd("C:/DRN-analysis")
 source("./R/Libraries/Libraries.R")
@@
 North-East Brazil, Ceará and Banabuiú catchment on the left.
-On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure_1.png)
+On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/DRN-analysis/Figures and tables/paper/Figure_1.png)
 
@@
 (2022).
-WSI: Water Scarcity Index, PI: Precipitation Index.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure%202.jpg){width="682"}
+WSI: Water Scarcity Index, PI: Precipitation Index.](C:/DRN-analysis/Figures and tables/paper/Figure_2.jpg){width="682"}
 
@@
 ```{r figure 5a}
-setwd("C:/Directory_thesis_codes")
+setwd("C:/DRN-analysis")
 
@@
   geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
-  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 6) +
+  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 8) +
   geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
-  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 6) +
+  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 8) +
   geom_hline(yintercept = -1.5, color = 'orange', linetype = "dashed", size = 1.25, alpha = 0.8) +
-  geom_text(aes(as.Date("1985-01-01"), -1.5, label = "Severely dry", vjust = -0.5, hjust = 0), size = 6) +
+  geom_text(aes(as.Date("1985-01-01"), -1.5, label = "Severely dry", vjust = -0.5, hjust = 0), size = 8) +
   geom_hline(yintercept = -2, color = 'red', linetype = "dashed", size = 1.25, alpha = 0.8) +
-  geom_text(aes(as.Date("1985-01-01"), -2, label = "Extremely dry", vjust = -0.5, hjust = 0), size = 6) +
+  geom_text(aes(as.Date("1985-01-01"), -2, label = "Extremely dry", vjust = -0.5, hjust = 0), size = 8) +
   #Modify the axis
@@
   theme(
-        axis.text.x = element_text(size = 16),
-        axis.text.y = element_text(size = 20),
-        axis.title = element_text(size = 22),
-        legend.title = element_text(size = 20),
-        legend.text = element_text(size = 18),
+        axis.text.x = element_text(size = 22),
+        axis.text.y = element_text(size = 22),
+        axis.title.y = element_text(size = 24, face = "bold"),
+        axis.title.x = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(size = 22),
         legend.position = "bottom",
@@
 
-plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5.png")
+plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5_new.png")
 ```

### 2023-08-26 R/Libraries/Functions_MC.R

@@ -1,7 +1,7 @@
 #Functions for Model calibration
 
 #Other functions needed
-setwd("C:/Directory_thesis_codes")
+setwd("C:/DRN-analysis")
 source("./R/Libraries/Functions_TG.R")
 
 # Dataframe operations -----------------------------------------------------

### 2023-08-26 R/Libraries/Libraries_plot.R

@@ -4,4 +4,4 @@ library(ggplot2)
 require(scales)
 library(gridExtra)
 library(plotly)
-library(paletteer)
+# library(paletteer)

### 2023-10-20 R/Figures_code/update_fig5.R
updated figure 4

@@ -1,0 +1,210 @@
+setwd("C:/DRN-analysis")
+source("./R/Libraries/Libraries.R")
+source("./R/Libraries/Libraries_plot.R")
+source("./R/Libraries/Functions.R")
+source("./R/Libraries/Functions_MC.R")
+
+## New functions -----
+
+create_SPI_df <- function(dates, SPI_list, start, end, labels = NULL, relabel = FALSE){
+  idx <- dates %in% create_date_vector(start, end)
+  df <- as.data.frame(array(dim = c(sum(idx), length(SPI_list)+1)))
+  names(df) <- c("Date", names(SPI_list))
+  df$Date <- dates[idx]
+  for (res in colnames(df)[2:length(colnames(df))]){
+    for (i in seq_len(nrow(df))){
+      d <- as.Date(df[i,"Date"], "%d-%m-%Y")
+      df[i, res] <- SPI_list[[res]][["fitted"]][dates %in% d]
+    }
+  }
+  mean <- data.frame(df$Date, rowMeans(df[2:ncol(df)]))
+  names(mean) <- c("Date", "value")
+  if(relabel){
+    cols <- c("Date")
+    for (c in colnames(df)[2:ncol(df)]){
+      cols <- append(cols, labels[[c]])
+    }
+    names(df) <- cols
+    new_order <- sort(colnames(df))
+    df <- df[, new_order]
+  }
+  df <- reshape2::melt(df, id = "Date")
+  return(list(df, mean))
+}
+
+plot_box_sub <- function(df, breaks, limits){
+  p <- ggplot(data = df, aes(x = variable, y = value, group = variable)) +
+    geom_boxplot(fill = "#F24C4C", color = "#293462") +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 22),
+          axis.text.y = element_text(size = 22),
+          axis.title.y = element_text(size = 24, face = "bold"),
+          axis.title.x = element_blank(),
+          panel.background = element_rect(fill = "white", colour = "grey50")
+    ) +
+    #Add the drought indicator lines
+    geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
+    geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
+    geom_hline(yintercept = -1.5, color = 'orange', linetype = "dashed", size = 1.25, alpha = 0.8) +
[…]
